### 2023-12-06 paper.tex
Initial Overleaf Import

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}

\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Towards Reliable Machine Learning Deployments in the Cloud}
% \thanks{Identify applicable funding agency here. If none, delete this.}
\author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
cmeyers@cs.umu.se}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
fake@fake.se}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
tommmy@cs.umu.se}
\and
\IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
elmroth@cs.umu.se}
}

\maketitle

\begin{abstract}
Considering the growing prominence of production-level AI and the threat of adversarial attacks that can poison a machine learning model against a certain label, evade classification, or reveal sensitive data about the model and training data to an attacker, adversaries pose fundamental problems to machine learning systems. Prior research has noted the need to extend beyond the normal train-test split paradigm for evaluating models due of the ease with which one can generally find adversarial counterexamples. Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem. Furthermore, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex. So, instead of this train-test split methodology, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture. We evaluate several GPU types and use Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. In this way, we can evaluate our model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters. Using this technique, we demonstrate that newer, more-powerful hardware does increase model robustness, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
\cm{obviously, this needs to be written out formally, but this is a rough outline for now}
\subsection{Motivations}
\begin{itemize}
    \item \textbf{BIG} Data is the trend
    \item Costs are astronomical
    \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
    \item Other work relies on unreliable test/train split methodology
    \item Which means that cars, medical equipment is tested in the wild
\end{itemize}

\subsection{Research Questions}
Our goal is to answer three questions

\begin{itemize}
    \item What is relationship between latency, robustness, and deployment cost?
    \item What is the cheapest way to guarantee a certain response time and accuracy?
\end{itemize}

\subsection{Contributions}
\begin{itemize}
    \item Confirm previous work about the efficacy adversarial analysis for model selection
    \item Test the run-time behavior of several search algorithms
    \item Test several different cpu- and gpu- architectures
    \item Measure the monetary and power costs of model deployment with respect to the benign and adversarial survival times
    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of advesrarial robustness
\end{itemize}

\section{Background}
Machine learning pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges. In this paper, we present a comprehensive study on leveraging Kubernetes ~\cite{k8s} for managing a complex machine learning pipeline. We explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts.

Machine learning applications have witnessed tremendous growth in recent years, addressing a wide range of domains and providing significant advancements in various fields \cite{li_general_2016, croce_reliable_2020, athalye_obfuscated_2018}. As these applications become more sophisticated, the need to efficiently manage the underlying machine learning pipeline arises. The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference. Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.

To address these challenges, containerization and orchestration technologies have gained prominence in managing complex machine learning pipelines. Kubernetes, a widely adopted container orchestration platform, provides a scalable and flexible environment for deploying, scaling, and managing microservices-based applications. Its ability to handle heterogeneous hardware architectures and workload distribution across clusters makes it an ideal choice for managing the complex computational requirements of machine learning pipelines.

Furthermore, ensuring the robustness of machine learning (ML) models against adversarial attacks has become a critical concern \cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Adversarial attacks aim to exploit vulnerabilities in models by introducing subtle modifications to data submitted to various stages of the ML pipeline, leading to misclassification or otherwise erroneous outputs. Evaluating the robustness of machine learning models against adversarial attacks is crucial to assess their reliability and performance in real-world scenarios. By subjecting the machine learning pipeline to carefully crafted adversarial inputs, we can measure its resilience and identify potential vulnerabilities.

Additionally, understanding the relationship between computational cost, model loss, and prediction accuracy is vital for optimizing the pipeline's performance. Balancing computational resources, time constraints, and accuracy requirements is a fundamental consideration in deploying machine learning models in production environments. By analyzing the impact of computational cost on model loss and accuracy metrics, we can gain insights into the trade-offs involved and make informed decisions to optimize the pipeline's efficiency.

In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex machine learning pipeline across a variety of CPU and GPU architectures. We can investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts. Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying machine learning models under varying computational constraints and adversarial conditions.

For the sake of the reader, we provide a section for definitions and requisite background information below.

\subsection{Cloud Architectures}
A \textbf{microservice} is the smallest component of a `cloud-native' software stack. In the context of machine learning, that might be a tool for either training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. A microservice \textbf{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between microservices in a distributed system. It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services. A microservice mesh typically consists of a set of interconnected components or proxies deployed alongside the microservices within the system. These components facilitate various capabilities and functionalities essential for managing the communication between microservices. Kubernetes has become one of the largest open source projects on the code-sharing website Github \cite{k8s-size}, which provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures.

\subsection{Machine Learning Pipelines}
Machine Learning pipelines are often long-running and complex software tool-chains with many tunable hyperparameters. Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc, hydra, k8s}. In general, a dataset is split into \textbf{training} and \textbf{test} sets. The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated by users via application programming interface (API) calls. To verify the training process, the test set validated against the \textit{inference} configuration of a model which may run on different hardware than the \textbf{training} configuration to reduce cost, latency, or power consumption.

\subsection{Classifiers}

A classifier with model parameters, $\theta$, $K(x; \theta)$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization function without loss of generality.} an \textbf{objective} (or \textbf{loss}) \textbf{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the optimal loss value, $L^*$ is:
\[
L^*(y, K(x, \theta)) = \mathrm{argmin}_{\theta \in \Theta} y - K(x, \theta).
\]
From here, we can find the optimal configuration of the classifier by selecting the one that minimizes loss. In the case of neural-networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions. Instead of finding an analytical solution to this equation, we often rely on \textbf{stochastic gradient descent}, which iteratively shuffles the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss, $-\nabla L(y, K(x, \theta))$, after some number of \textbf{epochs} (iterative random shufflings of the data), $m$, such that:
\begin{equation}
\theta_{m+1} := \theta_{m} - \eta \nabla_x L(y, K(x, \theta_m))
\label{eq:sgd}
\end{equation}
where $\eta$ is a \textbf{learning rate} that is tuned to the particular model.

\subsection{Adversarial Attacks}

In the context of machine learning, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit machine learning models. Adversarial attacks are designed to deceive or mislead the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or produce undesired outputs. That is, a successful attack is one in which the model outputs on unperturbed data $\hat{y}$ are not the same as the model outputs on perturbed data, $x^*$. That is \textbf{adversarial success} or \textbf{accelerated failure} is one in which:
\begin{equation}
\hat{y} \neq y^* = K(x^*, \theta)
\label{eq:adv_success}
\end{equation}
The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the machine learning pipeline, including during training, inference, or deployment.

\begin{itemize}
    \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying or ignoring certain inputs. Attackers carefully craft perturbations or modify the input features to mislead the model while still appearing similar to the original input \cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
    \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset. The goal is to influence the model's behavior during training so that it learns to make incorrect predictions or exhibit unwanted behaviors when presented with specific inputs \cite{biggio_poisoning_2013, saha2020hidden}.
    \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details. By observing the model's predictions or confidence scores for carefully crafted inputs, attackers can extract information that should ideally be kept private \cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
    \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs. Attackers utilize the model's responses to iteratively reconstruct or approximate training examples that are similar to the ones used during training \cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
\end{itemize}
One attack designed to induce failures as quickly as possible~\cite{fgm,meyers_aft} works by iterating over a set of samples, $x_0$,

$$
x_{i+1} = x_{i} + \eta \mathrm{~sgn~}(\nabla_x L(y, K(x, \theta))).
$$
In essence, this is stochastic gradient \textit{ascent}, the opposite process from model training.

\subsection{Adversarial Analysis}

In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{}. Whether we discuss automotive safety~\cite{}, crytographic systems~\cite{}, or healthcare malpractice~\cite{}, a component, algorithm, or system is considered broken if the \textbf{failure rate} exceeds certain statistical thresholds. An order of magnitude more automotive accidents, security breaches, or deaths due to medical negligence would be unacceptable and, as such, these standards are non-negotiable. However, this would mean testing somewhere around $(10^6, 10^9)$ samples to justify every model change. This is just not computationally feasible. Instead, we can use adversarial failure analysis to improve the precision of our measurements while only using a small set of test-data.

\subsubsection{Accuracy}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted machine learning model to misclassify or produce incorrect outputs \cite{meyers}. It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textbf{robustness} against noise-induced failures. Throughout, we use the terminology \textbf{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy is defined as
\begin{equation}
 \mathrm{Accuracy} = 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}}
\label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data \cite{}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{biggio_evasion_2013,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
\ In addition, this method ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{}. Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples. Such that 
$$
y\neq\hat{y}\mathrm{~s.t.~}\| x^* - x \| \leq \varepsilon \leq \varepsilon_{max}
$$

where $\| \cdot \|$ represents some norm or pseudo-norm and $\varepsilon$ is some specified distance threshold bound by some distance, $\varepsilon_{max}$.

\subsubsection{Failure Rate}
 To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.} training time, inference time, attack generation time, etc.) and some covariates (\textit{e.g.} noise distance, model size, hardware resources) such that:
\[
h(t; \theta) :=  \frac{\textrm{False~Classifications}}{\textrm{Total~Time}}
\]
To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models~\cite{meyers_aft} that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
\[
S(t; x,y, \theta) := 1 - \int_{t=0}^{\infty} h(t;\theta) d \theta
\]

\subsection{AFR models}
\label{afr}
Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t; x,y, \theta)]$) across a wide variety of circumstances~\cite{aft_models,meyers_aft}. However, this requires a choice in modelling distribution for $S$. We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on AIC, BIC, and Concordance to choose the best-fit, following the best-practices of other research~\cite{aft_models,meyers_aft}.  This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial. However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces. In order to minimize the cost of evaluationm, we must be clever about how we search.

\subsection{Optimization}

Because of the relatively small run-time requirements of this approach (when compared to testing against massive in-distribution test sets), this method could, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples. Furthermore, by isolating changes and testing them as quickly as possible, it's much easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test. To further increase development velocity, we can use these models to quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}. However, hyper-parameters are often drawn from continuous and infinite spaces, so it's impossible to exhaustively evaluate the search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds, meaning that a proper search would keep this dual-objective in mind. Luckily, the field of multi-objective search is well researched and analyze the run-time requirements for several popular choices below, each of which will be useful for different types of search spaces.

\begin{itemize}
    \item TPE Sampler
    \item NGAS2/3
    \item Bayesian Optimization
\end{itemize}

\subsection{Pareto Set}
In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{}. A subset of examples that maximize one or more objective criteria is called the \textbf{pareto front}~\cite{zitzler2008quality}. It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}. Table~\ref{tab:pareto} shows the required number of queries to get estimates within the $\varepsilon$-sphere of the true Pareto front. As we can see, it is critical to minimize the dimensionality of our search. So instead of optimizing for latency, training time, cost, accuracy, and adversarial success rate independently, we introduce several metrics in the next section.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Please add the following required packages to your document preamble:
% 
\begin{table}[t!]
\begin{tabular}{cl|llll|}
\cline{3-6}
                                           &   & \multicolumn{4}{c|}{$\varepsilon$}            \\ \cline{3-6} 
                                           &   & .1     & .05          & .01    & .001      \\ \hline
\multicolumn{1}{|c|}{\multirow{3}{*}{$d$}} & 1 & 10     & 20           & 100    & 1000      \\
\multicolumn{1}{|c|}{}                     & 2 & 100    & 400          & $10^4$ & $10^6$    \\
\multicolumn{1}{|c|}{}                     & 4 & $10^4$ & $1.6 * 10^5$ & $10^9$ & $10^{12}$ \\ \hline
\end{tabular}
\caption{This table shows the number of queries required to $\varepsilon-$ approximate the Pareto front, $\mathcal{P}$, in $d$ dimensions.}
\label{tab:pareto}
\end{table}

\section{Metrics}

We withheld 100 examples from both the test and train sets as the initial values for adversarial examples, which gives us two significant figures for this measurement. In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack.

\subsection{Benign Success}
A \textit{success} can be thought of in both the adversarial and benign context, which are denoted with the subscripts $ben.,adv.$ throughout this work. Typically this is measured via the train/test methodology in which some subset of a benchmark dataset. However, this method has repeatedly shown itself to be an inadequate measure of real-world model performance, and is, at best, an optimistic best-case measure of the failure rate~\cite{croce_reliable_2020}. The benign success ratio is usually measured via the train/test split methodology mentioned in Section~\ref{train/test-split}.

\subsection{Adversarial Success}
A successful adversary, however, is one that is able to change the model's output from one class to another. For the benign case, we measure the test set accuracy as our success metric. However, we m

Furthermore, the computational difficulty of this task is often related to secondary optimization criteria~\cite{}, with a baseline of at least NP-Hard~\cite{madry2017towards}. Since many of the attacks have more success after a number of iterations\cite{fgm,deepfool,carlini_towards_2017,madry2017towards,hopskipjump}, it is appropriate to think about their success in terms of time.

\subsection{Training Time}
The training time, $T_t$, is the time it takes to evaluate $n$ samples for $m$ epochs such that the training time per sample per epoch $t_t$ is.
$$
T_t := t_t\cdot n\cdot m
$$

\subsection{Latency}
Latency is the time it takes to respond to a query. We assume that latency per sample is:
$$
T_i  := t_i \cdot n 
$$
which will be driven by the memory bandwidth (measured in bits/second) of a given cpu- or gpu-\cite{} and the size\cite{} and complexity\cite{} of a given neural network architecture.

\subsection{Attack Generation Time}
A successful attack is one that induces failure in a model. That is, the expected survival time, $\mathbb{E}[S(t;x,y,\theta)]$, can be thought of as the time it takes for an attacker to induce a change in the model output. We approximate this for each attack/defence configuration by taking the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$:

$$
T_a := t_i \cdot n \cdot i 
$$

\subsection{Cost}
Furthermore, we can think of cost of deployment at two scales. Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using GCP compute costs as a measure of total cost. However, at a certain scale, (\textit{e.g.} for deploying a self-driving car) it's more appropriate to talk about cost in terms of power. Finally, we define best-case and worst-case success metrics that give us an efficient way to minimize the latency, cost of deployment, and

\subsubsection{Hardware}
This value, measured in United States Dollars per hour, will indicate the operating cost of a given model. To calculate this, we used the price per hour from each of cloud service pricing page~\footnote{ Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} } ~\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing#accelerator-optimized}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$) and the inference time ($T_{i}$) such that the cost of training a model is
$$
    C_t = C_h \cdot T_t
    \label{eq:cost_training}
$$
the cost of model inference time is
$$
    C_i = C_h \cdot T_i,
    \label{eq:cost_inference}
$$
and the cost of an attack is:
$$
    C_a = C_h \cdot  T_a.
    \label{eq:cost_attack}
$$

\subsubsection{Power}
The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
$$
    P_t = P_h \cdot T_t,
    \label{eq:cost_training}
$$
the power consumption during model inference is:
$$
    P_i = P_h \cdot T_i
    \label{eq:cost_inference}
$$
and the power consumption during attack generation is:
$$
    P_a = P_h \cdot T_a
$$

\subsection{Survival Time}
Correspondingly, we can talk about the expected survival time under optimistic, $S_{ben.}$ as well as under adverse (accelerated failure rate distribution), $S_{adv.}$. If we assume that the distribution of failures is uniform with respect to latency, a
$$
S_{ben.} := S(t_i; x, y, \theta) \mathrm{~s.t.~} \varepsilon = 0
$$
and
$$
S_{adv.} :=  S(t_i; x, y, \theta) \mathrm{~s.t.~} 0 < \varepsilon \leq \varepsilon_{max}
$$
\subsection{Dollars per Second}

% $$
% \frac{\mathrm{Successful~Queries}}{\$} = \frac{\mathrm{Accuracy}\cdot n}{T_i} = 
% $$

\section{Methods}
\subsection{Cloud Platform and Hardware}
\textcolor{red}{To conduct the experiments and have access to different types of hard, we utilized Google Cloud Platform (GCP). Six virtual machines running Container Optimized Operating System provided by GCP constitute our testbed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster that comprises of six worker nodes. Three worker nodes were responsible for running the monitoring platform such as Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the 'e2-medium' instance type provided by Google Cloud Platform. In total, we used three different GPU based on their availability. For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4' node.}

\textcolor{red}{To assess the energy consumption of Deckard deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}. This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components. In essence, KEPLER uses extended Berkley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics. eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space. eBPF programs are invoked by the kernel when certain events, called hooks, occur. Examples of such hooks include system calls, network events. These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}.}
\begin{table}[]
\begin{tabular}{lllll}
                 & V100   & P100   & L4    &  \\
Cost (\$/hour)    & 2.55 & 1.60 & .81 &  \\
Power (Watts)           &        &        &       &  \\
Memory Bandwidth (GB/s) &        &        &       &

Costs were taken from \footnote{}
\label{tab:hardware}
\end{tabular}
\end{table}
\subsection{Software Pipeline}
\subsection{Datasets}
\subsection{Models}
\subsection{Attacks}
\subsection{Monetary Cost}
\subsection{Power}

\section{Results}
\subsection{Accuracy and Robustness}
\subsection{Training Time}
\subsection{Latency}
\subsection{Monetary Cost}
\subsection{Power}
\section{Considerations}
\begin{itemize}
 \item timing jitter, therefore process time and averages across n samples
 \item all models/datasets are small enough to fit entirely in GPU memory
 \item distributed/federated models are out of scope, but architectural choices regarding the configuration of workers (cpu cores) and gpus could be made for next steps.
 \item Only examined evasion attacks, though this would generalize to extraction, inversion, or poisoning attacks.
 \item 
\end{itemize}
\section{Conclusion}

\newpage
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\vspace{12pt}

\end{document}

### 2023-12-06 plots/cifar/aft_comparison.tex
removed symlinks

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -2992.60 & 0.91 & -2992.60 & 0.09 & 0.08 \\
cox & -- & 0.92 & -- & 0.03 & 0.08 \\
log_logistic & -3173.60 & 0.92 & -3173.60 & 0.09 & 0.08 \\
log_normal & -3072.67 & 0.92 & -3072.67 & 0.09 & 0.08 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-06 plots/cifar100/aft_comparison.tex
removed symlinks

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -3092.89 & 0.93 & -3092.89 & 0.13 & 0.09 \\
cox & -- & 0.97 & -- & 0.09 & 0.09 \\
log_logistic & -3817.38 & 0.96 & -3817.38 & 0.12 & 0.09 \\
log_normal & -3315.07 & 0.96 & -3315.07 & 0.12 & 0.09 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-06 plots/mnist/aft_comparison.tex
removed symlinks

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -2908.50 & 0.95 & -2908.50 & 0.06 & 0.06 \\
cox & -- & 0.96 & -- & 0.03 & 0.06 \\
log_logistic & -3089.51 & 0.96 & -3089.51 & 0.06 & 0.06 \\
log_normal & -3077.18 & 0.96 & -3077.18 & 0.06 & 0.06 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-11 plots/cifar/aft_comparison.tex
update data/plots

@@
 \midrule
-weibull & -2992.60 & 0.91 & -2992.60 & 0.09 & 0.08 \\
-cox & -- & 0.92 & -- & 0.03 & 0.08 \\
-log_logistic & -3173.60 & 0.92 & -3173.60 & 0.09 & 0.08 \\
-log_normal & -3072.67 & 0.92 & -3072.67 & 0.09 & 0.08 \\
+weibull & -472.03 & 0.83 & -472.03 & 0.25 & 0.22 \\
+cox & -- & 0.83 & -- & 0.20 & 0.25 \\
+log_logistic & -514.66 & 0.83 & -514.66 & 0.25 & 0.21 \\
+log_normal & -518.86 & 0.83 & -518.86 & 0.26 & 0.22 \\
 \bottomrule

### 2023-12-11 plots/cifar100/aft_comparison.tex
update data/plots

@@
 \midrule
-weibull & -3092.89 & 0.93 & -3092.89 & 0.13 & 0.09 \\
-cox & -- & 0.97 & -- & 0.09 & 0.09 \\
-log_logistic & -3817.38 & 0.96 & -3817.38 & 0.12 & 0.09 \\
-log_normal & -3315.07 & 0.96 & -3315.07 & 0.12 & 0.09 \\
+weibull & -329.38 & 0.83 & -329.38 & 0.33 & 0.18 \\
+cox & -- & 0.84 & -- & 0.24 & 0.16 \\
+log_logistic & -353.45 & 0.84 & -353.45 & 0.31 & 0.17 \\
+log_normal & -355.45 & 0.84 & -355.45 & 0.31 & 0.17 \\
 \bottomrule

### 2023-12-11 plots/mnist/aft_comparison.tex
update data/plots

@@
 \midrule
-weibull & -2908.50 & 0.95 & -2908.50 & 0.06 & 0.06 \\
-cox & -- & 0.96 & -- & 0.03 & 0.06 \\
-log_logistic & -3089.51 & 0.96 & -3089.51 & 0.06 & 0.06 \\
-log_normal & -3077.18 & 0.96 & -3077.18 & 0.06 & 0.06 \\
+weibull & -606.12 & 0.78 & -606.12 & 0.23 & 0.22 \\
+cox & -- & 0.78 & -- & 0.18 & 0.22 \\
+log_logistic & -606.18 & 0.78 & -606.18 & 0.22 & 0.22 \\
+log_normal & -616.30 & 0.78 & -616.30 & 0.23 & 0.22 \\
 \bottomrule

### 2023-12-11 paper.tex

@@
 \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
+\newcommand{\mr}[1]{\textit{{\color{red}#1}}}
 
@@
 In this way, we can evaluate our model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters.
-Using this technique, we demonstrate that newer, more-powerful hardware does increase model robustness, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
+Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+artificial intelligence, machine learning, adversarial AI, optimization, compliance
 \end{IEEEkeywords}
@@
 \section{Introduction}
-\cm{obviously, this needs to be written out formally, but this is a rough outline for now}
 \subsection{Motivations}
 \begin{itemize}
-    \item \textbf{BIG} Data is the trend
-    \item Costs are astronomical
+    % \item \textbf{BIG} Data is the trend
+    % \item Costs are astronomical
     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
@@
 
+Recently, artificial intelligence using neural networks has become a popular way to classify large amounts of data-- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
+However, neural networks need huge amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
+Furthermore, popular models like general purpose transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have hundreds of millions or billions of parameters, requiring equally large training datasets.
+Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
+Luckily, Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
+Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}.
+The newest version of this open-source LLM is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}.
+Given the immense cost of deploying modern neural networks, this raises serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be one in trillions~\cite{iso26262}.
+Collecting, labelling, and testing a new set of data for every software change-as required by law- would be prohibitively expensive.
+Therefore, a new evaluation methodology is required.
+As such, we propose an evaluation metholodgy, centered on the statistical field of survival analysis, which tests a model against `worst-case' input to verify the efficacy of one software or hardware decision over another.
+Then, we use this method to examine and minimize the deployment cost for a singular model architecture, measuring this in terms of both power and monetary cost.
+In short, our goal is to answer three questions.
+
 \subsection{Research Questions}
-Our goal is to answer three questions
-
+Our goal is to answer three questions.
 \begin{itemize}
@@
     \item What is the cheapest way to guarantee a certain response time and accuracy?
+    \item Does better hardware make better models?
 \end{itemize}
+
+However, before we can answer these questions, we need to model the asymptotic behavior of various architectural choices, develop a method for precisely measuring model performance without resorting to trillions of test samples, and find a metric (or metrics) that will set one model apart from the others with respect to both failure rate and deployment cost.
 
@@
 \begin{itemize}
-    \item Confirm previous work about the efficacy adversarial analysis for model selection
-    \item Test the run-time behavior of several search algorithms
-    \item Test several different cpu- and gpu- architectures
-    \item Measure the monetary and power costs of model deployment with respect to the benign and adversarial survival times
-    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of advesrarial robustness
+    \item We confirm previous work about the efficacy adversarial analysis for model selection
+    \item We measure the power and monetary cost of deploying a model across three different hardware architectures.
+    \item We combine survival analysis with adversarial analysis to build accelerated failure models to compare the effect of model parameter choices.
+    \item We use a Tree Parzen Estimator to minimize deployment cost while maximizing accuracy.
+    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of adversarial robustness.
 \end{itemize}
@@
 In the case of neural-networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions.
-Instead of finding an analytical solution to this equation, we often rely on \textbf{stochastic gradient descent}, which iteratively shuffles the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss, $-\nabla L(y, K(x, \theta))$, after some number of \textbf{epochs} (iterative random shufflings of the data), $m$, such that:
+Instead of finding an analytical solution to this equation, we often rely on \textbf{stochastic gradient descent}, which iteratively shuffles the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss, $-\nabla L(y, K(x, \theta))$, after some number of \textbf{epochs} (iterative random sampling of the data), $m$, such that:
 \begin{equation}
@@
 
+\subsection{Learning Rate Selection}
+\label{learning_rate}
+\cm{TODO}
+\begin{itemize}
+    \item Much work has gone into this~\cite{}.
+    \item A good learning rate will give us training times that are linear w.r.t sample size ~\cite{}
+    \item Will depend on the batch size and number of epochs (define epochs) ~\cite{}
+    \item The best batch size will depend on the memory bandwidth of the GPU~\cite{}
+    \item That bandwidth is not guaranteed in on-demand cloud environments~\cite{}
+    \item Hardware is charged by the hour, so minimizing training/inference times will reduce the costs of deployment.
+\end{itemize}
+
 \subsection{Adversarial Attacks}
-
+\label{attacks}
 In the context of machine learning, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit machine learning models.
 Adversarial attacks are designed to deceive or mislead the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or produce undesired outputs.
-That is, a successful attack is one in which the model outputs on unperturbed data $\hat{y}$ are not the same as the model outputs on perturbed data, $x^*$.
+That is, a successful attack is one in which the model outputs on unperturbed data $\hat{y}$ are not the same as the model outputs on perturbed data, $x'$.
 That is \textbf{adversarial success} or \textbf{accelerated failure} is one in which:
 \begin{equation}
-\hat{y} \neq y^* = K(x^*, \theta)
+\hat{y} \neq y^* = K(x', \theta)
 \label{eq:adv_success}
 \end{equation}
+Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textbf{adversarial accurracy}.
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
@@
 
+\cm{This itemize section could be cut and reduced to a couple sentences.}
 \begin{itemize}
@@
 \end{itemize}
-One attack designed to induce failures as quickly as possible~\cite{fgm,meyers_aft} works by iterating over a set of samples, $x_0$,
+One attack designed to induce failures as quickly as possible~\cite{fgm} works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that:
 
-$$
-x_{i+1} = x_{i} + \eta \mathrm{~sgn~}(\nabla_x L(y, K(x, \theta))).
-$$
-In essence, this is stochastic gradient \textit{ascent}, the opposite process from model training.
+\begin{equation}
+x' = x + \eta \mathrm{~sgn~}(\nabla_x L(y, K(x, \theta))).
+\label{eq:fgm}
+\end{equation}
+In essence, this is stochastic gradient \textit{ascent}, the opposite process from model training (stochastic gradient \textit{descent}).
 
@@
 Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{biggio_evasion_2013,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
-\ In addition, this method ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{}.
-Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples.
-Such that
+In addition, this method ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{}.
+Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples, such that
 $$
-y\neq\hat{y}\mathrm{~s.t.~}\| x^* - x \| \leq \varepsilon \leq \varepsilon_{max}
+y\neq\hat{y}\mathrm{~s.t.~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max}
 $$
@@
 \[
-h(t; \theta) :=  \frac{\textrm{False~Classifications}}{\textrm{Total~Time}}
+h(t; \theta) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t}
 \]
+where $\mathbb{P}$ is a probability and $\Delta t$ is a time interval.
 To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models~\cite{meyers_aft} that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
@@
 
-\subsection{Optimization}
-
-Because of the relatively small run-time requirements of this approach (when compared to testing against massive in-distribution test sets), this method could, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism.
-It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples.
-Furthermore, by isolating changes and testing them as quickly as possible, it's much easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test.
-To further increase development velocity, we can use these models to quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}.
-However, hyper-parameters are often drawn from continuous and infinite spaces, so it's impossible to exhaustively evaluate the search space.
-Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds, meaning that a proper search would keep this dual-objective in mind.
-Luckily, the field of multi-objective search is well researched and analyze the run-time requirements for several popular choices below, each of which will be useful for different types of search spaces.
-
-\begin{itemize}
-    \item TPE Sampler
-    \item NGAS2/3
-    \item Bayesian Optimization
-\end{itemize}
-
 \subsection{Pareto Set}
+\cm{This section could probably be cut without too much lost.}
 In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{}.
@@
 % 
-\begin{table}[t!]
+\begin{table}[h!]
 \begin{tabular}{cl|llll|}
@@
 
+\subsection{Optimization}
+
+Because of the relatively small run-time requirements of this approach (when compared to testing against massive in-distribution test sets), this method could, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism.
+It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples.
+Furthermore, by isolating changes and testing them as quickly as possible, it's much easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test.
+To further increase development velocity, we can use these models to quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}.
+However, hyper-parameters are often drawn from continuous and infinite spaces, so it's impossible to exhaustively evaluate the search space.
+Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds, meaning that a proper search would keep this dual-objective in mind.
+Luckily, the field of multi-objective search is well researched and analyze the run-time requirements for several popular choices below, each of which will be useful for different types of search spaces.
+We chose the Tree-structure Parzen Estimator (TPE) because of it's ability to work on mini-batches~\cite{}, in distributed settings~\cite{}, and while optimizing multiple objectives~\cite{} in a feasible number of trials ~\cite{}.
+
 \section{Metrics}
@@
 We withheld 100 examples from both the test and train sets as the initial values for adversarial examples, which gives us two significant figures for this measurement.
-In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack.
+In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack, as well as the benign and adversarial accuracies (see: Secs.~\ref{eq:acc} and ~\ref{eq:adv_success}).
 
-\subsection{Benign Success}
-A \textit{success} can be thought of in both the adversarial and benign context, which are denoted with the subscripts $ben.,adv.$ throughout this work.
+\subsection{Accuracy}
+We measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.
+
+% \subsection{Benign Success}
+% A \textit{success} can be thought of in both the adversarial and benign context, which are denoted with the subscripts $ben.,adv.$ throughout this work.
 Typically this is measured via the train/test methodology in which some subset of a benchmark dataset.
 However, this method has repeatedly shown itself to be an inadequate measure of real-world model performance, and is, at best, an optimistic best-case measure of the failure rate~\cite{croce_reliable_2020}.
-The benign success ratio is usually measured via the train/test split methodology mentioned in Section~\ref{train/test-split}.
+The benign success ratio is usually measured via the train/test split methodology mentioned in typical in the literature.
 
-\subsection{Adversarial Success}
-A successful adversary, however, is one that is able to change the model's output from one class to another. For the benign case, we measure the test set accuracy as our success metric. However, we m
+% \subsection{Adversarial Success}
+% A successful adversary, however, is one that is able to change the model's output from one class to another.
+For the benign case, we measure the test set accuracy as our success metric.
+However, we m
 
-Furthermore, the computational difficulty of this task is often related to secondary optimization criteria~\cite{}, with a baseline of at least NP-Hard~\cite{madry2017towards}.
+% Furthermore, the computational difficulty of this task is often related to secondary optimization criteria~\cite{}, with a baseline of at least NP-Hard~\cite{madry2017towards}.
 Since many of the attacks have more success after a number of iterations\cite{fgm,deepfool,carlini_towards_2017,madry2017towards,hopskipjump}, it is appropriate to think about their success in terms of time.
@@
     P_t = P_h \cdot T_t,
-    \label{eq:cost_training}
+    \label{eq:power_training}
 $$
@@
     P_i = P_h \cdot T_i
-    \label{eq:cost_inference}
+    \label{eq:power_inference}
 $$
@@
     P_a = P_h \cdot T_a
+    \label{eq:power_attack}
 $$
@@
 $$
-\subsection{Dollars per Second}
+\subsection{Relative Cost to an Attacker}
+In security analysis, it's routine to think in optimistic terms for both the attacker and defender.
+As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which adds noise of a specified magnitude to some samples in the direction that maximizes loss.
+If the cost to a model builder ($C_t$) is much larger than the attacker ($C_a$), then it's clear that a configuration.
 
@@
 \subsection{Cloud Platform and Hardware}
-\textcolor{red}{To conduct the experiments and have access to different types of hard, we utilized Google Cloud Platform (GCP).
+To conduct the experiments and have access to different types of hard, we utilized Google Cloud Platform (GCP).
 Six virtual machines running Container Optimized Operating System provided by GCP constitute our testbed.
@@
 In total, we used three different GPU based on their availability.
-For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4' node.}
-
-\textcolor{red}{To assess the energy consumption of Deckard deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}.
+For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4' node.
+To assess the energy consumption of the experiments deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}.
 This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components.
@@
 eBPF programs are invoked by the kernel when certain events, called hooks, occur.
-Examples of such hooks include system calls, network events.
-These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}.}
-\begin{table}[]
+Examples of such hooks include system calls or network events.
+These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}.
+A diagram of the cloud architecture can be found in Fig.~\ref{fig:architecture}.
+Finally, to meet our goal of developing a cost-effective model evaluation technique, we restricted all of our experiments to a single one-thousand United States dollar research grant from Google.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{plots/architecture.pdf}
+    \caption{Cloud Architecture Diagram}
+    \label{fig:architecture}
+\end{figure*}
+
+For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a pareto-optimal result~\cite{} for the TPE algorithm, within some expected error bounds (see: Tab.~\ref{tab:pareto}).
+We used three optimization criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
+We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples.
+Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy.
+Fig.~\ref{fig:experiments} illustrates this methodology.
+For each dataset, we tested this on ten random splits of the data.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
+    \caption{Experimental Pipeline Diagram}
+    \label{fig:experiments}
+\end{figure}
+
+\subsection{Datasets}
+For our experiments, we evaluated the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis ~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
+By modern standards (billions of parameters), these models are quite small (tens of thousands of samples), but our goal is not to rival the accuracy of industy leaders, but to develop a method that is practical for everyone else to use.
+Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets.
+Furthermore, to reduce the complexities of system overhead, distributed or federated training, and the effect of shared cloud environments, we restricted ourselves to datasets that are small enough to reside entirely within GPU memory with the model, since the disk read speed in cloud environments is incredibly variable.
+
+\subsection{Models}
+We restricted ourselves to a single model for our evaluations.
+Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware.
+As discussed in Sec.~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict.
+So, we sampled learning rates $\in [1e-6, 1]$, batch sizes $\in [1, 1e5]$, and epochs $\in [1,50]$ for MNIST and CIFAR10 on the P100 and V100.
+For Cifar100, we increased the range of the tested epochs to be $\in [1, 100]$.
+To evaluate the efficacy of different bit-depths on the L4 hardware, we used the Feature Squeezing defence~\cite{feature_squeezing} provided by IBM's adversarial robustness toolbox~\cite{art2018}.
+
+\subsection{Attacks}
+Since the goal in this paper is to evaluate how hardware and deployment cost affect adversarial robustness, we focused on evasion attacks since they induce failures by adding noise to the data.
+Prior research ~\cite{meyers} has shown that the Fast Gradient method (see: Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
+To evaluate the effect of noise on our samples, we varied $\varepsilon \in [0, 1]$.
+
+\subsection{GPU Configurations}
+We tested several hardware configurations, which have various hourly costs, peak power demands, and theoretical memory bandwidths.
+We tested three Nvidia cards-- the V100, the P100, and L4.
+The V100 was chosen as a baseline since it's allegedly the hardware behind large LLMs like GPT~\cite{}.
+The P100 architecture comes from the same line of server-grade training GPUs, but from an older generation.
+The L4, however, is advertised as a machine built for inference--not training, relying on a smaller number of bits per tensor core.
+Consequently, the number of operations per second is dependent on the bit depth of the data and the model weights, with the peak numbers outlined in Tab.~\ref{tab:hardware} referring to 8-bit inputs.
+\begin{table}[h]
 \begin{tabular}{lllll}
-                 & V100   & P100   & L4    &  \\
-Cost (\$/hour)    & 2.55 & 1.60 & .81 &  \\
-Power (Watts)           &        &        &       &  \\
-Memory Bandwidth (GB/s) &        &        &       &
-
-Costs were taken from \footnote{}
+\hline
+                        & V100   & P100   & L4    &  \\ \hline
+Cost (USD/hour)          & 2.55 & 1.60 & .81 &  \\
+Power (Watts)           & 250    & 250    & 72    &  \\
+Memory Bandwidth (GB/s) & 900    & 732    & 300   &  \\ \hline
 \label{tab:hardware}
 \end{tabular}
+\caption{Hardware specifications for tested GPUs. All specifications were retrieved from the Nvidia website at the following links: 
+\href{https://images.nvidia.com/content/technologies/volta/pdf/volta-v100-datasheet-update-us-1165301-r5.pdf}{V100 Datasheet},
+\href{https://images.nvidia.com/content/tesla/pdf/nvidia-tesla-p100-PCIe-datasheet.pdf}{P100 Datasheet}, and
+\href{https://nvdam.widen.net/s/rvq98gbwsw/l4-datasheet-2595652}{L4 Datasheet}.
+Prices were retrieved from Google Cloud Platform for the \texttt{europe-west4} region on 3 December 2023 at \href{https://cloud.google.com/pricing/list}{this link.}
+}
 \end{table}
-\subsection{Software Pipeline}
-\subsection{Datasets}
-\subsection{Models}
-\subsection{Attacks}
-\subsection{Monetary Cost}
-\subsection{Power}
 
 \section{Results}
+\cm{These are a brief overview of the results as I work on the plots and wait for the power data from Mohammad.
+Will add plots tonight, but you can see preliminary results in the plots folder.
+I'm still playing with how to squeeze all the data into a single page.
+I apologize for the delay.}
+
 \subsection{Accuracy and Robustness}
+Marginal gains in accuracy for faster hardware, but no significant change in survival time.
 \subsection{Training Time}
+Corresponds roughly to what we would expect from the peak GPU bandwidth numbers in Tab.~\ref{tab:hardware}.
 \subsection{Latency}
+Slower hardware is marginally slower. Results would be undetectable for a user with a reasonably small query.
 \subsection{Monetary Cost}
+Smaller hardware is significantly cheaper (roughly half the cost to train vs. the best hardware).
 \subsection{Power}
+Power tracks monetary cost closely, probably because that's the predominant cost for the datacenter itself~\cite{}.
+
 \section{Considerations}
-\begin{itemize}
- \item timing jitter, therefore process time and averages across n samples
- \item all models/datasets are small enough to fit entirely in GPU memory
- \item distributed/federated models are out of scope, but architectural choices regarding the configuration of workers (cpu cores) and gpus could be made for next steps.
- \item Only examined evasion attacks, though this would generalize to extraction, inversion, or poisoning attacks.
- \item 
-\end{itemize}
+ We have taken much care to conduct these measurements as carefully as possible.
+Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for neural networks \cite{}.
+Given the strong concordance results and uniformity across hardware shown in Table~\ref{}, this assumption appears to insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexaplained variance.
+Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning.
+In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
+Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth.
+However, we would like to note that the `inference-optimized' Nvidia 4 series GPUs are perfectly capable and affordable training machines.
+We restricted our search to only a single evasion attack (see: Eq.~\ref{eq:fgm}) in the interest of time (and therefore deployment cost), though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks, examples of which are outlined in Section~\ref{attacks}.
+ % As an additional note, we forgot to store the Prometheus database on the PVC and the data only existed in an ephemeral Docker container, and we recommend against this design flaw in future deployments.
+Instead the Prometheus database should be mounted to the PVC or linked to an external database via the provided web interface.
+ In general, we chose to use a PVC rather than externally linked databases to minimize the differences between a single-machine implementation and the cloud deployment and allow our results to be generally reproducible on a developer's local machine, though this comes with the downside of having to interact with critical experiment data manually.
+Proper permissions management on the attached volume store can prevent any critical errors during downstream analysis, though version control software like \texttt{dvc}~\cite{dvc} or the addition of some kind of searchable log store like \texttt{elasticsearch}\cite{} in combination with artifact storage\cite{} for the datasets, models, and attacks would be a welcome and obvious improvement.
 \section{Conclusion}

### 2023-12-12 plots/combined/aft_comparison.tex
new plots

\begin{table}
\caption{Comparison of AFR Models on the COMBINED dataset.}
\label{tab:Combined}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -4732.34 & 0.82 & -4732.34 & 0.00 & 0.00 \\
cox & -- & 0.82 & -- & 0.00 & 0.00 \\
log_logistic & -4770.78 & 0.81 & -4770.78 & 0.00 & 0.00 \\
log_normal & -4788.03 & 0.81 & -4788.03 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-12 paper.tex

@@
 \section{Results}
-\cm{These are a brief overview of the results as I work on the plots and wait for the power data from Mohammad.
-Will add plots tonight, but you can see preliminary results in the plots folder.
-I'm still playing with how to squeeze all the data into a single page.
-I apologize for the delay.}
+\cm{Here are most of the results.
+I'm still playing with how to 1.
+combine the hardware into a single model per dataset or 2.
+visualize 9 different combinations in a tiny space.
+I'd very much like to show the partial effects plots as I did before with the layers in the NEURIPS paper.}
 
@@
 Marginal gains in accuracy for faster hardware, but no significant change in survival time.
-\subsection{Training Time}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{plots/combined/acc.pdf}
+    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
+    \label{fig:acc}
+\end{figure*}
+
+\subsection{Time}
 Corresponds roughly to what we would expect from the peak GPU bandwidth numbers in Tab.~\ref{tab:hardware}.
-\subsection{Latency}
+
 Slower hardware is marginally slower. Results would be undetectable for a user with a reasonably small query.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{plots/combined/time.pdf}
+    \caption{Training, Prediction, and Attack times across datasets and hardware.}
+    \label{fig:time}
+\end{figure*}
+
 \subsection{Monetary Cost}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{plots/combined/cost.pdf}
+    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
+    \label{fig:time}
+\end{figure*}
 Smaller hardware is significantly cheaper (roughly half the cost to train vs. the best hardware).
+
 \subsection{Power}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{plots/combined/power.pdf}
+    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
+    \label{fig:time}
+\end{figure*}
 Power tracks monetary cost closely, probably because that's the predominant cost for the datacenter itself~\cite{}.
+
+\subsection{}
 
@@
 
-\newpage
+% \newpage
 \bibliographystyle{IEEEtran}

### 2023-12-13 plots/cifar/aft_comparison.tex
update plots

@@
 \midrule
-weibull & -472.03 & 0.83 & -472.03 & 0.25 & 0.22 \\
-cox & -- & 0.83 & -- & 0.20 & 0.25 \\
-log_logistic & -514.66 & 0.83 & -514.66 & 0.25 & 0.21 \\
-log_normal & -518.86 & 0.83 & -518.86 & 0.26 & 0.22 \\
+weibull & -550 & 0.856 & -550 & 0.266 & 0.219 \\
+cox & -- & 0.856 & -- & 0.202 & 0.254 \\
+log_logistic & -562 & 0.857 & -562 & 0.258 & 0.215 \\
+log_normal & -568 & 0.857 & -568 & 0.258 & 0.216 \\
 \bottomrule

### 2023-12-13 plots/cifar100/aft_comparison.tex
update plots

@@
 \midrule
-weibull & -329.38 & 0.83 & -329.38 & 0.33 & 0.18 \\
-cox & -- & 0.84 & -- & 0.24 & 0.16 \\
-log_logistic & -353.45 & 0.84 & -353.45 & 0.31 & 0.17 \\
-log_normal & -355.45 & 0.84 & -355.45 & 0.31 & 0.17 \\
+weibull & -361 & 0.845 & -361 & 0.331 & 0.179 \\
+cox & -- & 0.847 & -- & 0.238 & 0.162 \\
+log_logistic & -371 & 0.852 & -371 & 0.318 & 0.172 \\
+log_normal & -372 & 0.851 & -372 & 0.313 & 0.174 \\
 \bottomrule

### 2023-12-13 plots/combined/aft_comparison.tex
update plots

@@
 \midrule
-weibull & -4732.34 & 0.82 & -4732.34 & 0.00 & 0.00 \\
-cox & -- & 0.82 & -- & 0.00 & 0.00 \\
-log_logistic & -4770.78 & 0.81 & -4770.78 & 0.00 & 0.00 \\
-log_normal & -4788.03 & 0.81 & -4788.03 & 0.00 & 0.00 \\
+weibull & -6.36e+03 & 0.834 & -6.36e+03 & 0.00258 & 0.00195 \\
+cox & -- & 0.847 & -- & 0.00224 & 0.00199 \\
+log_logistic & -6.62e+03 & 0.862 & -6.62e+03 & 0.00274 & 0.00189 \\
+log_normal & -6.6e+03 & 0.862 & -6.6e+03 & 0.0027 & 0.00186 \\
 \bottomrule

### 2023-12-13 plots/mnist/aft_comparison.tex
update plots

@@
 \midrule
-weibull & -606.12 & 0.78 & -606.12 & 0.23 & 0.22 \\
-cox & -- & 0.78 & -- & 0.18 & 0.22 \\
-log_logistic & -606.18 & 0.78 & -606.18 & 0.22 & 0.22 \\
-log_normal & -616.30 & 0.78 & -616.30 & 0.23 & 0.22 \\
+weibull & -778 & 0.886 & -778 & 0.238 & 0.204 \\
+cox & -- & 0.888 & -- & 0.185 & 0.201 \\
+log_logistic & -759 & 0.884 & -759 & 0.226 & 0.204 \\
+log_normal & -752 & 0.881 & -752 & 0.225 & 0.202 \\
 \bottomrule

### 2023-12-13 paper.tex
Updates from Overleaf

@@
 \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
-\IEEEauthorblockA{\textit{dept. of Computing Science} \\
+\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
 \textit{Umeå University}\\
@@
 \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
-\IEEEauthorblockA{\textit{dept. of Computing Science} \\
+\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
 \textit{Umeå University}\\
@@
 \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
-\IEEEauthorblockA{\textit{dept. of Computing Science} \\
+\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
 \textit{Umeå University}\\
 Umeå, Sweden \\
-tommmy@cs.umu.se}
+tommy@cs.umu.se}
 \and
 \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
-\IEEEauthorblockA{\textit{dept. of Computing Science} \\
+\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
 \textit{Umeå University}\\
@@
 So, instead of this train-test split methodology, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture.
-We evaluate several GPU types and use Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously.
-In this way, we can evaluate our model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters.
+We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously.
+In this way, we can evaluate the model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters.
 Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
@@
 \subsection{Motivations}
-\begin{itemize}
-    % \item \textbf{BIG} Data is the trend
-    % \item Costs are astronomical
-    \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
-    \item Other work relies on unreliable test/train split methodology
-    \item Which means that cars, medical equipment is tested in the wild
-\end{itemize}
+% \begin{itemize}
+%     % \item \textbf{BIG} Data is the trend
+%     % \item Costs are astronomical
+%     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
+%     \item Other work relies on unreliable test/train split methodology
+%     \item Which means that cars, medical equipment is tested in the wild
+% \end{itemize}
 
-Recently, artificial intelligence using neural networks has become a popular way to classify large amounts of data-- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
-However, neural networks need huge amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
-Furthermore, popular models like general purpose transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have hundreds of millions or billions of parameters, requiring equally large training datasets.
+Recently, machine learning using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
+However, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
+Furthermore, popular models like Generative Pre-trained Transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions of parameters, requiring equally large training datasets.
 Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
-Luckily, Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
+Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
 Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}.
-The newest version of this open-source LLM is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}.
-Given the immense cost of deploying modern neural networks, this raises serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be one in trillions~\cite{iso26262}.
-Collecting, labelling, and testing a new set of data for every software change-as required by law- would be prohibitively expensive.
+The newest version of this open-source large language model (LLM) is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}.
+Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be between $[1e-12, 1e-15]$ depending on the number of lives at risk ~\cite{iso26262}.
+Collecting, labelling, and testing a new set of data for every software change-as required by law would be prohibitively expensive.
 Therefore, a new evaluation methodology is required.
-As such, we propose an evaluation metholodgy, centered on the statistical field of survival analysis, which tests a model against `worst-case' input to verify the efficacy of one software or hardware decision over another.
-Then, we use this method to examine and minimize the deployment cost for a singular model architecture, measuring this in terms of both power and monetary cost.
-In short, our goal is to answer three questions.
+As such, we propose an evaluation metholodgy, centered around survival analysis, which tests a model against `worst-case' input to verify the efficacy of one of modelling deployment decision over another.
+Then, we use this method to examine and minimize the deployment cost for a singule model architecture, measuring this in terms of both power and monetary cost.
+In short, our goal is to answer three questions,
 
 \subsection{Research Questions}
-Our goal is to answer three questions.
+Our goal is to answer the following three questions:
 \begin{itemize}
-    \item What is relationship between latency, robustness, and deployment cost?
+    \item What is the relationship between latency, robustness, and deployment cost?
     \item What is the cheapest way to guarantee a certain response time and accuracy?
-    \item Does better hardware make better models?
+    \item Does better hardware lead to better models?
 \end{itemize}
@@
 \begin{itemize}
-    \item We confirm previous work about the efficacy adversarial analysis for model selection
+    \item We confirm previous work about the efficacy of adversarial analysis for model selection.
     \item We measure the power and monetary cost of deploying a model across three different hardware architectures.
@@
 However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
-In this paper, we present a comprehensive study on leveraging Kubernetes ~\cite{k8s} for managing a complex machine learning pipeline.
+In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex machine learning pipeline.
 We explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts.
@@
 
-Furthermore, ensuring the robustness of machine learning (ML) models against adversarial attacks has become a critical concern \cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
+Furthermore, ensuring the robustness of machine learning  models against adversarial attacks has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
 Adversarial attacks aim to exploit vulnerabilities in models by introducing subtle modifications to data submitted to various stages of the ML pipeline, leading to misclassification or otherwise erroneous outputs.
-Evaluating the robustness of machine learning models against adversarial attacks is crucial to assess their reliability and performance in real-world scenarios.
-By subjecting the machine learning pipeline to carefully crafted adversarial inputs, we can measure its resilience and identify potential vulnerabilities.
+Evaluating the robustness of ML models against adversarial attacks is crucial to assess their reliability and performance in real-world scenarios.
+By subjecting the ML pipeline to carefully crafted adversarial inputs, we can measure its resilience and identify potential vulnerabilities.
 
@@
 
-In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex machine learning pipeline across a variety of CPU and GPU architectures.
+In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of CPU and GPU architectures.
 We can investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts.
@@
 where $\mathbb{P}$ is a probability and $\Delta t$ is a time interval.
-To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models~\cite{meyers_aft} that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
+To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
 \[
@@
 \label{afr}
-Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t; x,y, \theta)]$) across a wide variety of circumstances~\cite{aft_models,meyers_aft}.
+Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t; x,y, \theta)]$) across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
 However, this requires a choice in modelling distribution for $S$.
-We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on AIC, BIC, and Concordance to choose the best-fit, following the best-practices of other research~\cite{aft_models,meyers_aft}.
+We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance to choose the best-fit, following the best-practices of other research~\cite{aft_models}.
 This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial.
 However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces.
-In order to minimize the cost of evaluationm, we must be clever about how we search.
+In order to minimize the cost of evaluation, we must be clever about how we search.
 
@@
 
-\subsection{}
+\subsection{Survival Time}
+\input{plots/combined/aft_comparison}
 

### 2023-12-14 paper.tex

@@
 \usepackage{hyperref}
+\usepackage{booktabs}
+\usepackage{multirow}
 
@@
 % \begin{itemize}
-%     % \item \textbf{BIG} Data is the trend
+%     % \item \textit{BIG} Data is the trend
 %     % \item Costs are astronomical
@@
 
-Recently, machine learning using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
+Recently, machine learning (ML) using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
 However, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
 Furthermore, popular models like Generative Pre-trained Transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions of parameters, requiring equally large training datasets.
-Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
+Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
 Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
@@
 Therefore, a new evaluation methodology is required.
-As such, we propose an evaluation metholodgy, centered around survival analysis, which tests a model against `worst-case' input to verify the efficacy of one of modelling deployment decision over another.
-Then, we use this method to examine and minimize the deployment cost for a singule model architecture, measuring this in terms of both power and monetary cost.
-In short, our goal is to answer three questions,
+As such, we propose an evaluation metholodgy, centered around survival analysis, which tests a model against `worst-case' (e.g.
+adversarial) input to verify the efficacy of one of modelling deployment decision over another.
+Then, we use this method to examine and minimize the deployment cost for a single model architecture, measuring this in terms of both power and monetary cost.
+Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
 
-\subsection{Research Questions}
-Our goal is to answer the following three questions:
-\begin{itemize}
-    \item What is the relationship between latency, robustness, and deployment cost?
-    \item What is the cheapest way to guarantee a certain response time and accuracy?
-    \item Does better hardware lead to better models?
-\end{itemize}
+% \subsection{Research Questions}
+% Our goal is to answer the following three questions:
+% \begin{itemize}
+%     \item What is the relationship between latency, robustness, and deployment cost?
+%     \item What is the cheapest way to guarantee a certain response time and accuracy?
+%     \item Does better hardware lead to better models?
+% \end{itemize}
 
-However, before we can answer these questions, we need to model the asymptotic behavior of various architectural choices, develop a method for precisely measuring model performance without resorting to trillions of test samples, and find a metric (or metrics) that will set one model apart from the others with respect to both failure rate and deployment cost.
+% However, before we can answer these questions, we need to model the asymptotic behavior of various architectural choices, develop a method for precisely measuring model performance without resorting to trillions of test samples, and find a metric (or metrics) that will set one model apart from the others with respect to both failure rate and deployment cost.
 
 \subsection{Contributions}
+So, in order to tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective technique and source code that:
 \begin{itemize}
-    \item We confirm previous work about the efficacy of adversarial analysis for model selection.
-    \item We measure the power and monetary cost of deploying a model across three different hardware architectures.
-    \item We combine survival analysis with adversarial analysis to build accelerated failure models to compare the effect of model parameter choices.
-    \item We use a Tree Parzen Estimator to minimize deployment cost while maximizing accuracy.
-    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of adversarial robustness.
+    \item confirm previous work about the efficacy of adversarial analysis for model selection,
+    \item extend survival analysis to the realm of neural networks, 
+    \item demonstrate a scalable and effective method that allows us to tune a model and model the effect of the model parameters asymptotically,
+    \item and measure the power and monetary cost of deploying a model across three different hardware architectures to model the trade-offs between deployment hardware and robustness,
+to show that, despite a decrease in training time, that faster hardware or hardware with more memory does not aid models in the adversarial context.
+
 \end{itemize}
@@
 \section{Background}
-Machine learning pipelines play a crucial role in the development and deployment of robust and accurate models.
+ML pipelines play a crucial role in the development and deployment of robust and accurate models.
 However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
-In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex machine learning pipeline.
+In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex ML pipeline.
 We explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts.
 
-Machine learning applications have witnessed tremendous growth in recent years, addressing a wide range of domains and providing significant advancements in various fields \cite{li_general_2016, croce_reliable_2020, athalye_obfuscated_2018}.
-As these applications become more sophisticated, the need to efficiently manage the underlying machine learning pipeline arises.
+ML applications have witnessed tremendous growth in recent years, addressing a wide range of domains and providing significant advancements in various fields \cite{li_general_2016, croce_reliable_2020, athalye_obfuscated_2018}.
+As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises.
 The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference.
@@
 
-To address these challenges, containerization and orchestration technologies have gained prominence in managing complex machine learning pipelines.
+To address these challenges, containerization and orchestration technologies have gained prominence in managing complex ML pipelines.
 Kubernetes, a widely adopted container orchestration platform, provides a scalable and flexible environment for deploying, scaling, and managing microservices-based applications.
-Its ability to handle heterogeneous hardware architectures and workload distribution across clusters makes it an ideal choice for managing the complex computational requirements of machine learning pipelines.
+Its ability to handle heterogeneous hardware architectures and workload distribution across clusters makes it an ideal choice for managing the complex computational requirements of ML pipelines.
 
-Furthermore, ensuring the robustness of machine learning  models against adversarial attacks has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
-Adversarial attacks aim to exploit vulnerabilities in models by introducing subtle modifications to data submitted to various stages of the ML pipeline, leading to misclassification or otherwise erroneous outputs.
-Evaluating the robustness of ML models against adversarial attacks is crucial to assess their reliability and performance in real-world scenarios.
-By subjecting the ML pipeline to carefully crafted adversarial inputs, we can measure its resilience and identify potential vulnerabilities.
-
-Additionally, understanding the relationship between computational cost, model loss, and prediction accuracy is vital for optimizing the pipeline's performance.
-Balancing computational resources, time constraints, and accuracy requirements is a fundamental consideration in deploying machine learning models in production environments.
+% Additionally, understanding the relationship between computational cost, model loss, and prediction accuracy is vital for optimizing the pipeline's performance.
+Balancing computational resources, time constraints, and accuracy requirements is a fundamental consideration in deploying ML models in production environments.
 By analyzing the impact of computational cost on model loss and accuracy metrics, we can gain insights into the trade-offs involved and make informed decisions to optimize the pipeline's efficiency.
 
-In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of CPU and GPU architectures.
+In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of GPU architectures.
 We can investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts.
-Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying machine learning models under varying computational constraints and adversarial conditions.
+Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying ML models under varying computational constraints and adversarial conditions.
 
@@
 \subsection{Cloud Architectures}
-A \textbf{microservice} is the smallest component of a `cloud-native' software stack.
-In the context of machine learning, that might be a tool for either training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
-A microservice \textbf{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between microservices in a distributed system.
+A \textit{microservice} is the smallest component of a `cloud-native' software stack.
+In the context of ML, that might be a tool for either training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
+A microservice \textit{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between microservices in a distributed system.
 It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services.
@@
 
-\subsection{Machine Learning Pipelines}
-Machine Learning pipelines are often long-running and complex software tool-chains with many tunable hyperparameters.
-Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc, hydra, k8s}.
-In general, a dataset is split into \textbf{training} and \textbf{test} sets.
-The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated by users via application programming interface (API) calls.
-To verify the training process, the test set validated against the \textit{inference} configuration of a model which may run on different hardware than the \textbf{training} configuration to reduce cost, latency, or power consumption.
+\subsection{ML Pipelines}
+ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters.
+Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}.
+In general, a dataset is split into \textit{training} and \textit{test} sets.
+The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
+To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
 
@@
 
-A classifier with model parameters, $\theta$, $K(x; \theta)$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization function without loss of generality.} an \textbf{objective} (or \textbf{loss}) \textbf{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the optimal loss value, $L^*$ is:
+A classifier, $K(x; \theta)$, with model parameters, $\theta$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization without loss of generality.} an \textit{objective} (or \textit{loss}) \textit{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the optimal loss value, $L^*$ is:
 \[
@@
 \]
-From here, we can find the optimal configuration of the classifier by selecting the one that minimizes loss.
-In the case of neural-networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions.
-Instead of finding an analytical solution to this equation, we often rely on \textbf{stochastic gradient descent}, which iteratively shuffles the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss, $-\nabla L(y, K(x, \theta))$, after some number of \textbf{epochs} (iterative random sampling of the data), $m$, such that:
+ In the case of neural networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions and the loss function is non-convex.
+Instead of finding an analytical solution to this equation, we often rely on numerical optimisation, and one choice is \textit{stochastic gradient descent}, which samples the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss.
+This is in the direction of the negative gradient of the loss, $-\nabla L(y, K(x, \theta))$.
+This procedure is repeated for some number of \textit{epochs} (iteration through the entire training set), $m$, and every iteration thus performs the step,
 \begin{equation}
-\theta_{m+1} := \theta_{m} - \eta \nabla_x L(y, K(x, \theta_m))
+    \theta_{m+1} = \theta_{m} - \eta \nabla_x L\big(y, K(x, \theta_m)\big),
 \label{eq:sgd}
 \end{equation}
-where $\eta$ is a \textbf{learning rate} that is tuned to the particular model.
+where $\eta$ is a \textit{learning rate} that is tuned to the particular model.
 
@@
 \label{learning_rate}
-\cm{TODO}
-\begin{itemize}
-    \item Much work has gone into this~\cite{}.
-    \item A good learning rate will give us training times that are linear w.r.t sample size ~\cite{}
-    \item Will depend on the batch size and number of epochs (define epochs) ~\cite{}
-    \item The best batch size will depend on the memory bandwidth of the GPU~\cite{}
-    \item That bandwidth is not guaranteed in on-demand cloud environments~\cite{}
-    \item Hardware is charged by the hour, so minimizing training/inference times will reduce the costs of deployment.
-\end{itemize}
+Choosing the correct learning rate is critical for model performance---greatly effecting both the accuracy and the run-time requirements.
+A small learning rate will have a smaller error bound~cite{}, but will converge slower, all other things being equal.
+Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data.
+Graphics cards with larger amounts of RAM will be able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch.
+In theory, a `good' learning rate can converge quickly ~\cite{smith2019super} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, and bit depth of the data.
+However, since cloud infrastructure is virutalized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}.
+Furthermore, since hardware is billed by the hour, optimizing the training and inference times allows us to minimize the cost of deployment.
 
@@
 \label{attacks}
-In the context of machine learning, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit machine learning models.
-Adversarial attacks are designed to deceive or mislead the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or produce undesired outputs.
-That is, a successful attack is one in which the model outputs on unperturbed data $\hat{y}$ are not the same as the model outputs on perturbed data, $x'$.
-That is \textbf{adversarial success} or \textbf{accelerated failure} is one in which:
+In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models.
+Adversarial attacks are designed to deceive or change the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or otherwise produce undesired outputs.
+That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $y'$.
+That is \textit{adversarial success} or \textit{accelerated failure} is one in which
 \begin{equation}
-\hat{y} \neq y^* = K(x', \theta)
+    \hat{y} \neq y' = K(x + \varepsilon; \theta).
 \label{eq:adv_success}
 \end{equation}
-Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textbf{adversarial accurracy}.
+Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accurracy}.
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
-These attacks can occur during various stages of the machine learning pipeline, including during training, inference, or deployment.
+These attacks can occur during various stages of the ML pipeline, including during training, inference, or deployment, examples of which are outlined below.
 
-\cm{This itemize section could be cut and reduced to a couple sentences.}
 \begin{itemize}
-    \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying or ignoring certain inputs.
-Attackers carefully craft perturbations or modify the input features to mislead the model while still appearing similar to the original input \cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
-    \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset.
-The goal is to influence the model's behavior during training so that it learns to make incorrect predictions or exhibit unwanted behaviors when presented with specific inputs \cite{biggio_poisoning_2013, saha2020hidden}.
-    \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details.
-By observing the model's predictions or confidence scores for carefully crafted inputs, attackers can extract information that should ideally be kept private \cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
-    \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs.
-Attackers utilize the model's responses to iteratively reconstruct or approximate training examples that are similar to the ones used during training \cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
+    \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying certain inputs or otherwise change the behavior of a modelt~\cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
+    % Attackers carefully craft perturbations or modify the input features to mislead the model while still appearing similar to the original input~\cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
+    \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset to influence the model's behaviour at run-time~\cite{biggio_poisoning_2013, saha2020hidden}.
+    % The goal is to influence the model's behavior during training so that it learns to make incorrect predictions or exhibit unwanted behaviors when presented with specific inputs \cite{biggio_poisoning_2013, saha2020hidden}.
+    \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
+    % By observing the model's predictions or confidence scores for carefully crafted inputs, attackers can extract information that should ideally be kept private \cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
+    \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
+    % Attackers utilize the model's responses to iteratively reconstruct or approximate training examples that are similar to the ones used during training \cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
 \end{itemize}
-One attack designed to induce failures as quickly as possible~\cite{fgm} works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that:
-
+One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}.
+It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that,
 \begin{equation}
-x' = x + \eta \mathrm{~sgn~}(\nabla_x L(y, K(x, \theta))).
+x' = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
 \label{eq:fgm}
 \end{equation}
-In essence, this is stochastic gradient \textit{ascent}, the opposite process from model training (stochastic gradient \textit{descent}).
+In essence, this is process seeks to maximize loss in contrast to model training which seeks to minimize it.
 
@@
 
-In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{}.
-Whether we discuss automotive safety~\cite{}, crytographic systems~\cite{}, or healthcare malpractice~\cite{}, a component, algorithm, or system is considered broken if the \textbf{failure rate} exceeds certain statistical thresholds.
-An order of magnitude more automotive accidents, security breaches, or deaths due to medical negligence would be unacceptable and, as such, these standards are non-negotiable.
-However, this would mean testing somewhere around $(10^6, 10^9)$ samples to justify every model change.
+In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}.
+Whether we discuss automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}.
+An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable.
+However, this would mean testing a million samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems.
 This is just not computationally feasible.
@@
 \subsubsection{Accuracy}
-The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted machine learning model to misclassify or produce incorrect outputs \cite{meyers}.
+The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}.
 It measures the vulnerability or susceptibility of the model to noise-induced failures.
-A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textbf{robustness} against noise-induced failures.
-Throughout, we use the terminology \textbf{benign accuracy} to refer to the performance on the test set using unperturbed data.
+A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures.
+Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data.
 The benign accuracy is defined as
@@
 \end{equation}
-which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data \cite{}.
+which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}.
 However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}.
 Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{biggio_evasion_2013,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
-In addition, this method ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{}.
+In addition,  ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}.
 Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples, such that
 $$
-y\neq\hat{y}\mathrm{~s.t.~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max}
+    y\neq\hat{y}\text{~~while~~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max},
 $$ 
-
-where $\| \cdot \|$ represents some norm or pseudo-norm and $\varepsilon$ is some specified distance threshold bound by some distance, $\varepsilon_{max}$.
+where $\| \cdot \|$ represents some norm or pseudo-norm and $\varepsilon$ is some specified  perturbation distance threshold bound by a maximum distance, $\varepsilon_{max}$.
 
 \subsubsection{Failure Rate}
- To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.} training time, inference time, attack generation time, etc.) and some covariates (\textit{e.g.} noise distance, model size, hardware resources) such that:
+ To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates (\textit{e.g.}, noise distance, model size, hardware resources) such that,
 \[
-h(t; \theta) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t}
+    h_{ \theta}(t) :=  \frac{P(\textrm{False~Classification})}{\Delta t} t
 \]
-where $\mathbb{P}$ is a probability and $\Delta t$ is a time interval.
-To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
+where $P(\textrm{False~Classification})$ is the probability of a false classification and $\Delta t$ is a time interval.
+To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textit{survival time}, $S(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
 \[
-S(t; x,y, \theta) := 1 - \int_{t=0}^{\infty} h(t;\theta) d \theta
+    S_{\theta}(t) := 1 - \int_{t=0}^{\infty} h_{\theta}(t) \,d\theta.
 \]
@@
 \label{afr}
-Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t; x,y, \theta)]$) across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
+Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t)]$) across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
 However, this requires a choice in modelling distribution for $S$.
-We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance to choose the best-fit, following the best-practices of other research~\cite{aft_models}.
+We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance to choose the best-fit, following the best-practices of this method~\cite{aft_models,kleinbaum1996survival}.
 This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial.
@@
 
-\subsection{Pareto Set}
-\cm{This section could probably be cut without too much lost.}
-In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{}.
-A subset of examples that maximize one or more objective criteria is called the \textbf{pareto front}~\cite{zitzler2008quality}.
+% \subsection{Pareto Set}
+
+% In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{kamal2017study,leurent2020sha}.
+A subset of examples that maximize one or more objective criteria is called the \textit{pareto front}~\cite{zitzler2008quality}.
 It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}.
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-% Please add the following required packages to your document preamble:
-% 
-\begin{table}[h!]
-\begin{tabular}{cl|llll|}
-\cline{3-6}
-                                           &   & \multicolumn{4}{c|}{$\varepsilon$}            \\ \cline{3-6} 
-                                           &   & .1     & .05          & .01    & .001      \\ \hline
-\multicolumn{1}{|c|}{\multirow{3}{*}{$d$}} & 1 & 10     & 20           & 100    & 1000      \\
-\multicolumn{1}{|c|}{}                     & 2 & 100    & 400          & $10^4$ & $10^6$    \\
-\multicolumn{1}{|c|}{}                     & 4 & $10^4$ & $1.6 * 10^5$ & $10^9$ & $10^{12}$ \\ \hline
-\end{tabular}
-\caption{This table shows the number of queries required to $\varepsilon-$ approximate the Pareto front, $\mathcal{P}$, in $d$ dimensions.}
-\label{tab:pareto}
-\end{table}
+% % Please add the following required packages to your document preamble:
+% % \usepackage{multirow}
+% % Please add the following required packages to your document preamble:
+% % 
+% \begin{table}[h!]
+% \begin{tabular}{cl|llll|}
+% \cline{3-6}
+%                                            &   & \multicolumn{4}{c|}{$\varepsilon$}            \\ \cline{3-6} 
+%                                            &   & .1     & .05          & .01    & .001      \\ \hline
+% \multicolumn{1}{|c|}{\multirow{3}{*}{$d$}} & 1 & 10     & 20           & 100    & 1000      \\
+% \multicolumn{1}{|c|}{}                     & 2 & 100    & 400          & $10^4$ & $10^6$    \\
+% \multicolumn{1}{|c|}{}                     & 4 & $10^4$ & $1.6 * 10^5$ & $10^9$ & $10^{12}$ \\ \hline
+% \end{tabular}
+% \caption{This table shows the number of queries required to $\varepsilon-$ approximate the Pareto front, $\mathcal{P}$, in $d$ dimensions.}
+% \label{tab:pareto}
+% \end{table}
 
@@
 Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds, meaning that a proper search would keep this dual-objective in mind.
-Luckily, the field of multi-objective search is well researched and analyze the run-time requirements for several popular choices below, each of which will be useful for different types of search spaces.
-We chose the Tree-structure Parzen Estimator (TPE) because of it's ability to work on mini-batches~\cite{}, in distributed settings~\cite{}, and while optimizing multiple objectives~\cite{} in a feasible number of trials ~\cite{}.
+Luckily, the field of multi-objective search is well researched.
+We chose the Tree-structure Parzen Estimator (TPE) because of it's ability to work on mini-batches, in distributed settings, and while optimizing multiple objectives in a feasible number of trials ~\cite{ozaki2020multiobjective}, though research in this field is very much ongoing~\cite{ozaki2022multiobjective}.
 
@@
 
-We withheld 100 examples from both the test and train sets as the initial values for adversarial examples, which gives us two significant figures for this measurement.
  In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack, as well as the benign and adversarial accuracies (see: Secs.~\ref{eq:acc} and ~\ref{eq:adv_success}).
+Eighty percent of the data for each dataset was used for training and the remaining twenty percent was used for evaluation.
+We withheld 100 examples from the test set as the initial values for adversarial examples, which gives us two significant figures for this measurement, while benign accuracy was measured with 10s of thousands of samples, giving us 4 significant figures for that metric.
+For all reported times, we assumed that the time was distributed uniformly across the samples to minimize jitter and account for GPU-based parallelization.
 
@@
 \subsection{Training Time}
-The training time, $T_t$, is the time it takes to evaluate $n$ samples for $m$ epochs such that the training time per sample per epoch $t_t$ is.
+The training time, $T_t$, is the time it takes to evaluate $n$ samples such that the training time per sample per epoch $t_t$ is.
 $$
-T_t := t_t\cdot n\cdot m
+T_t := t_t\cdot n
 $$
@@
 $$
-which will be driven by the memory bandwidth (measured in bits/second) of a given cpu- or gpu-\cite{} and the size\cite{} and complexity\cite{} of a given neural network architecture.
+which will be driven by the memory bandwidth (measured in bits/second) of a given cpu- or gpu- and the size\cite{vgg} and complexity\cite{resnet} of a given neural network architecture.
 
@@
 $$
+In the interest of attack speed, we restricted this to a single iteration.
 
@@
 This value, measured in United States Dollars per hour, will indicate the operating cost of a given model.
-To calculate this, we used the price per hour from each of cloud service pricing page~\footnote{ Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} } ~\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing#accelerator-optimized}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$) and the inference time ($T_{i}$) such that the cost of training a model is
+To calculate this, we used the price per hour from each of cloud service pricing page~\footnote{ Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} } ~\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimized}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$) and the inference time ($T_{i}$) such that the cost of training a model is
 $$
@@
 \subsection{Cloud Platform and Hardware}
-To conduct the experiments and have access to different types of hard, we utilized Google Cloud Platform (GCP).
+To conduct the experiments and have access to different types of hardware, we utilized Google Cloud Platform (GCP).
 Six virtual machines running Container Optimized Operating System provided by GCP constitute our testbed.
-Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster that comprises of six worker nodes.
+Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster consisting of six worker nodes.
 Three worker nodes were responsible for running the monitoring platform such as Prometheus 2.47.2 and Grafana 10.2.0.
 These nodes were of the 'e2-medium' instance type provided by Google Cloud Platform.
-In total, we used three different GPU based on their availability.
-For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4' node.
+In total, we used three GPU models.
+For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4'.
 To assess the energy consumption of the experiments deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}.
@@
 eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space.
-eBPF programs are invoked by the kernel when certain events, called hooks, occur.
-Examples of such hooks include system calls or network events.
+eBPF programs are invoked by the kernel when certain events occur.
+Examples of such events include system calls or network activity.
 These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}.
@@
 
-For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a pareto-optimal result~\cite{} for the TPE algorithm, within some expected error bounds (see: Tab.~\ref{tab:pareto}).
+For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}.
 We used three optimization criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
@@
 To evaluate the efficacy of different bit-depths on the L4 hardware, we used the Feature Squeezing defence~\cite{feature_squeezing} provided by IBM's adversarial robustness toolbox~\cite{art2018}.
+Model parameters were chosen using the \texttt{optuna} optimization framework, configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.
 
@@
 Prior research ~\cite{meyers} has shown that the Fast Gradient method (see: Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
-To evaluate the effect of noise on our samples, we varied $\varepsilon \in [0, 1]$.
+To evaluate the effect of adversarial noise on our samples, we varied $\varepsilon \in [0, 1]$, using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
 
@@
 We tested three Nvidia cards-- the V100, the P100, and L4.
-The V100 was chosen as a baseline since it's allegedly the hardware behind large LLMs like GPT~\cite{}.
+The V100 was chosen as a baseline, since it's routinely cited in the literature~\cite{svedin2021benchmarking,xu2018deep}.
 The P100 architecture comes from the same line of server-grade training GPUs, but from an older generation.
@@
 
+\subsection{Survival Analysis}
+In addition to the optimization criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the distribution, $S(t)$.
+We attempted adding dummy variables for hardware (\textit{e.g.}~peak power and peak bandwidth) as well as the datasets (\textit{e.g~}resolution, bit depth, and number of color channels), but each of these were strongly colinear with training time and hindered modelling of the distribution.
+As such, they were not included.
+To find the distribution of the measured data and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}.
+We also compare the chosen distributions (see: Section ~\ref{afr}).
+These results can be found in the next section.
+
 \section{Results}
-\cm{Here are most of the results.
-I'm still playing with how to 1.
-combine the hardware into a single model per dataset or 2.
-visualize 9 different combinations in a tiny space.
-I'd very much like to show the partial effects plots as I did before with the layers in the NEURIPS paper.}
+Below, we examine the effect of hardware and dataset on the distribution of the benign/adversarial accuracy (Fig.~\ref{fig:acc}), training/inference/attack time (Fig.~\ref{fig:time}), and both monetary (Fig.~\ref{fig:cost}) and power (Fig.~\ref{fig:power}) costs for training/inference/attacks.
+We also compare all three survival time distributions outlined in Sec.~\ref{afr} using the criteria outlined in the same section.
+Using the best-fit distribution (again, see:~\ref{afr}), we plotted the effect of several covariates on the survival time of the model (Fig.~\ref{partial_effect}).Fig.~\ref{fig:acc} reveals little to no improvement in accuracy or adversarial accuracy, regardless of hardware though we see that the Cifar10 has worse benign performance and Cifar100 has significantly adversarial performance.
+Fig.~\ref{fig:time} reveals the training time proportional to the GPU bandwidth numbers in Tab.~\ref{tab:hardware}.
+Slower hardware is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
+This should be no surprise since the less-capable hardware is meant to be used exclusively for inference.
+Additionally, we see that the attack time is colinear with both the training and prediction times across hardware and datasets.
+The power consumption (Fig.~\ref{fig:power})  tracks monetary cost  (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it's unsurprising that cloud billing is colinear with this metric.
+Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).
 
-\subsection{Accuracy and Robustness}
-Marginal gains in accuracy for faster hardware, but no significant change in survival time.
 \begin{figure*}
     \centering
-    \includegraphics[width=\textwidth]{plots/combined/acc.pdf}
+    \includegraphics[width=.5\textwidth]{plots/combined/acc.pdf}
     \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
@@
 \end{figure*}
-
-\subsection{Time}
-Corresponds roughly to what we would expect from the peak GPU bandwidth numbers in Tab.~\ref{tab:hardware}.
-
-Slower hardware is marginally slower. Results would be undetectable for a user with a reasonably small query.
-
 \begin{figure*}
@@
 
-\subsection{Monetary Cost}
-
 \begin{figure*}
@@
     \includegraphics[width=\textwidth]{plots/combined/cost.pdf}
-    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
-    \label{fig:time}
+    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
+    \label{fig:cost}
 \end{figure*}
-Smaller hardware is significantly cheaper (roughly half the cost to train vs. the best hardware).
 
-\subsection{Power}
 \begin{figure*}
@@
     \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
-    \label{fig:time}
+    \label{fig:power}
 \end{figure*}
-Power tracks monetary cost closely, probably because that's the predominant cost for the datacenter itself~\cite{}.
 
-\subsection{Survival Time}
+\cm{TODO}
 \input{plots/combined/aft_comparison}
+\begin{figure*}
+    \centering
+    \includegraphics[width=.45\textwidth]{plots/combined/log_logistic_epochs_partial_effect.pdf}
+    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
+    \label{fig:cost}
+\end{figure*}
 
@@
  We have taken much care to conduct these measurements as carefully as possible.
-Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for neural networks \cite{}.
-Given the strong concordance results and uniformity across hardware shown in Table~\ref{}, this assumption appears to insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexaplained variance.
+Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for neural networks \cite{ma2022state}.
+Given the strong ( $>.5$) concordance results and uniformity across ditributions in Table~\ref{tab:Combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexaplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning.
@@
 Instead the Prometheus database should be mounted to the PVC or linked to an external database via the provided web interface.
- In general, we chose to use a PVC rather than externally linked databases to minimize the differences between a single-machine implementation and the cloud deployment and allow our results to be generally reproducible on a developer's local machine, though this comes with the downside of having to interact with critical experiment data manually.
-Proper permissions management on the attached volume store can prevent any critical errors during downstream analysis, though version control software like \texttt{dvc}~\cite{dvc} or the addition of some kind of searchable log store like \texttt{elasticsearch}\cite{} in combination with artifact storage\cite{} for the datasets, models, and attacks would be a welcome and obvious improvement.
+ % In general, we chose to use a PVC rather than externally linked databases to minimize the differences between a single-machine implementation and the cloud deployment and allow our results to be generally reproducible on a developer's local machine, though this comes with the downside of having to interact with critical experiment data manually.
+Proper permissions management on the attached volume store can prevent any critical errors during downstream analysis, though the addition of some kind of searchable log store like \texttt{elasticsearch}\cite{gormley2015elasticsearch} in combination with artifact storage\cite{daher2018cloud} for the datasets, models, and attacks would be a welcome and obvious improvement.
+
 \section{Conclusion}
-
+\cm{TODO}
 % \newpage

### 2023-12-14 plots/combined/aft_comparison.tex

--- 2023-12-12 plots/combined/aft_comparison.tex
@@
-\begin{table}
-\caption{Comparison of AFR Models on the COMBINED dataset.}
-\label{tab:Combined}
+\begin{table*}
+\centering
+\caption{Comparison of AFR Models for the combined hardware and datasets.}
 \begin{tabular}{llrlrr}
@@
 \midrule
-weibull & -4732.34 & 0.82 & -4732.34 & 0.00 & 0.00 \\
-cox & -- & 0.82 & -- & 0.00 & 0.00 \\
-log_logistic & -4770.78 & 0.81 & -4770.78 & 0.00 & 0.00 \\
-log_normal & -4788.03 & 0.81 & -4788.03 & 0.00 & 0.00 \\
+Weibull & -6.36e+03 & 0.834 & -6.36e+03 & 0.00258 & 0.00195 \\
+% Cox & -- & 0.847 & -- & 0.00224 & 0.00199 \\
+Log-Logistic & -6.62e+03 & 0.862 & -6.62e+03 & 0.00274 & 0.00189 \\
+Log-Normal & -6.6e+03 & 0.862 & -6.6e+03 & 0.0027 & 0.00186 \\
 \bottomrule
 \end{tabular}
-\end{table}
+\label{tab:Combined}
+\end{table*}

### 2024-03-28 plots/cifar/aft_comparison.tex
update plots

@@
 \label{tab:cifar}
-\begin{tabular}{llrlrr}
+\begin{tabular}{llrrlrr}
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
+ & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
 \midrule
-weibull & -550 & 0.856 & -550 & 0.266 & 0.219 \\
-cox & -- & 0.856 & -- & 0.202 & 0.254 \\
-log_logistic & -562 & 0.857 & -562 & 0.258 & 0.215 \\
-log_normal & -568 & 0.857 & -568 & 0.258 & 0.216 \\
+weibull & -1292.89 & 0.79 & 0.80 & -1292.89 & 0.20 & 0.67 \\
+cox & -- & 0.80 & 0.80 & -- & 0.12 & 0.11 \\
+log_logistic & -1474.32 & 0.79 & 0.79 & -1474.32 & 0.17 & 0.20 \\
+log_normal & -1459.29 & 0.79 & 0.79 & -1459.29 & 0.18 & 0.21 \\
 \bottomrule

### 2024-03-28 plots/cifar100/aft_comparison.tex
update plots

@@
 \label{tab:cifar100}
-\begin{tabular}{llrlrr}
+\begin{tabular}{llrrlrr}
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
+ & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
 \midrule
-weibull & -361 & 0.845 & -361 & 0.331 & 0.179 \\
-cox & -- & 0.847 & -- & 0.238 & 0.162 \\
-log_logistic & -371 & 0.852 & -371 & 0.318 & 0.172 \\
-log_normal & -372 & 0.851 & -372 & 0.313 & 0.174 \\
+weibull & -1159.72 & 0.79 & 0.76 & -1159.72 & 0.21 & 0.21 \\
+cox & -- & 0.79 & 0.76 & -- & 0.13 & 0.13 \\
+log_logistic & -1313.15 & 0.78 & 0.77 & -1313.15 & 0.20 & 0.20 \\
+log_normal & -1299.38 & 0.79 & 0.77 & -1299.38 & 0.20 & 0.20 \\
 \bottomrule

### 2024-03-28 plots/mnist/aft_comparison.tex
update plots

@@
 \label{tab:mnist}
-\begin{tabular}{llrlrr}
+\begin{tabular}{llrrlrr}
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
+ & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
 \midrule
-weibull & -778 & 0.886 & -778 & 0.238 & 0.204 \\
-cox & -- & 0.888 & -- & 0.185 & 0.201 \\
-log_logistic & -759 & 0.884 & -759 & 0.226 & 0.204 \\
-log_normal & -752 & 0.881 & -752 & 0.225 & 0.202 \\
+weibull & -1631.26 & 0.90 & 0.89 & -1631.26 & 0.15 & 0.69 \\
+cox & -- & 0.90 & 0.89 & -- & 0.11 & 0.11 \\
+log_logistic & -1842.71 & 0.90 & 0.90 & -1842.71 & 0.14 & 0.19 \\
+log_normal & -1799.93 & 0.90 & 0.90 & -1799.93 & 0.14 & 0.29 \\
 \bottomrule

### 2024-03-28 plots/combined/aft_comparison.tex
update plots

--- 2023-12-12 plots/combined/aft_comparison.tex
@@
 \label{tab:Combined}
-\begin{tabular}{llrlrr}
+\begin{tabular}{lrrrrrr}
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
+ & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
 \midrule
-weibull & -4732.34 & 0.82 & -4732.34 & 0.00 & 0.00 \\
-cox & -- & 0.82 & -- & 0.00 & 0.00 \\
-log_logistic & -4770.78 & 0.81 & -4770.78 & 0.00 & 0.00 \\
-log_normal & -4788.03 & 0.81 & -4788.03 & 0.00 & 0.00 \\
+weibull & -5810.78 & 0.84 & 0.84 & -5810.78 & 2.08 & 0.65 \\
+log_logistic & -6204.80 & 0.85 & 0.84 & -6204.80 & 0.23 & 0.17 \\
+log_normal & -6076.91 & 0.84 & 0.84 & -6076.91 & 0.17 & 0.15 \\
 \bottomrule

### 2024-03-28 main.tex
merge

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%% 
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%

% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{algpseudocode}

\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}

% \newcommand{\cm}[1]{#1}
\newcommand{\mr}[1]{\textit{{\color{red}#1}}}
\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
cmeyers@cs.umu.se}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
\IEEEauthorblockA{\textit{Elastisys} \\
% \textit{Umeå University}\\
% Lund, Sweden \\
mohammad.saleh@elastisys.com}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
tommy@cs.umu.se}
\and
\IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
elmroth@cs.umu.se}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
\cm{Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model a run-time, evaluating the robustness of models to these evasion attacks is of critical importance.}
Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect. We address the problem of neural network validation and verification --- more specifically, we address the problem of continuous integration and deployment for safety-critical models in a cloud-native environment. For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, \cm{so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data. However, in practice, this means that each model configuration needs to be evaluated against real-world deployment samples which can be prohibitively expensive or time-consuming to collect --- especially when other parts of the software or hardware stack are developed in parallel.} To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world. We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. This provides a way to evaluate the model and optimize it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy. Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

\begin{IEEEkeywords}
artificial intelligence, machine learning, adversarial AI, optimisation, compliance
\end{IEEEkeywords}

\section{Introduction}
\subsection{Motivation}
% \begin{itemize}
%     % \item \textit{BIG} Data is the trend
%     % \item Costs are astronomical
%     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
%     \item Other work relies on unreliable test/train split methodology
%     \item Which means that cars, medical equipment is tested in the wild
% \end{itemize}

Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. 
\cm{Statistical learning theory \cite{} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters. To overcome this, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has  yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. We also know that  reaching safety-critical standards using test-set accuracy would require an infeasibly large test set \cite{meyers}. Therefore, we propose using AFR models to simulate edge-cases and verify models using a small number of samples.}

\cm{Modern neural networks are massive--they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}}.
One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. One version of this open-source large language model (LLM) was able to outperform the commercially available GPT-3.5 model~\cite{liu2023goat} with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU), suggesting that consumer-level hardware can be used to effectively train large models in a reasonable time. Furthermore, popular models like Generative Pre-trained Transformer (GPT)~\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions or billions of parameters, requiring infeasibly large training datasets to verify a model\cite{vcdimension}. Media reports place the cost of training a GPT3 somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. \cm{While the benefits of a more portable model are plentiful, there is not yet a method for formalizing the relationship between cost and model performance. We present training and validation methodology with a focus on compute- and time-efficiency.}

Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for \cm{assessing model generalization}~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk~\cite{iso26262}. Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern \cm{since inducing a failure at run-time has consistently shown to be trivial}~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Collecting, labelling, and testing a new set of data for every software change --- as required by law --- would be prohibitively expensive. Therefore, a new evaluation methodology is required.

% As such, the methodology proposed in this paper, centered around survival analysis, tests a model against ``worst-case" (\textit{e.g.}, adversarial) inputs to verify the efficacy of one modelling deployment decision over another. 
We propose to use survival analysis as a methodological framework to model the failure conditions of a machine learning model. Instead of having a test set large enough to cover all of the failure cases, we generate adversarial samples crafted specifically to make the model fail and then use survival analysis to predict these failures in general.

\cm{The methodology outlined in Section~\ref{afr} allows the model-builder to minimize the training cost, optimize for adversarial robustness, and estimate the partial effects of covariates on model performance during routine training procedures. We then demonstrate the efficacy of this methodology in Section~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Section~\ref{experiments}.}

\subsection{Contributions}
To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective \cm{methodology and software framework for the training (see: Sec.~\ref{afr}) and evaluation (see: Sec.~\ref{cost}) of machine learning models} that:
\begin{itemize}
    \item optimizes for benign and adversarial accuracy simultaneously,
    \item extends survival analysis to the realm of neural networks, 
    \item demonstrates a scalable and effective method that trains a model while simultaneously estimating the asymptotic effect of various hyperparameters, and
    \item measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
    \item and demonstrates that, despite a decrease in training time, that faster hardware, \cm{hardware with more bit-depth}, and/or more power-hungry hardware do not lead to more adversarially robust models.

\end{itemize}

\cm{Section~\ref{background} defines terms used throughout the paper. Section~\ref{afr} outlines the training and evaluation methodology presented in this paper.  Section ~\ref{cost} outlines the resulting cost analysis framework, arising from the methodology in the previous section. Section~\ref{experiments} outlines the software components and specific experiments that were conducted, while Section~\ref{results} contains the results and discussions of those experiments. Section~\ref{considerations} and Section~\ref{conclusion} reveal the caveats and the conclusions respectively.}

\section{Background}
\label{background}

In this paper, we present a comprehensive methodology for evaluating model robustness during training time and model the asymptotic effect of the various parameters in the search space. For the sake of the reader, we provide a section for definitions and requisite background information below.

% Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying ML models under varying computational and adversarial constraints. 
\subsection{Cloud Architectures}

ML pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises. The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference. Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.

A \textit{service} is the smallest component of a ``cloud-native" software stack. In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. A service \textit{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between services in a distributed system. It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services.

A service \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the services within the system. These components facilitate various capabilities and functionalities essential for managing the communication between services. Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures. \cm{For ML applications, these services are often divided into ``training" and ``inference" configurations that often distinct hardware and software configurations~\cite{wang2019benchmarking}. In this work, we leveraged Kubernetes to manage a multi-stage ML pipeline.}

\subsection{ML Pipelines}
ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters. Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}. In general, a dataset is split into \textit{training} and \textit{test} sets. The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users. To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.

\subsection{Classifiers}

We consider classifiers, $K(x; \theta)$ with model parameters, $\theta$. The true labels are denoted by $y$, and the model predictions by $\hat{y} = K(x; \theta)$ and $x$ is a batch of samples with size $N$. The loss function is denoted by $L(y, \hat{y})$.

Because of the complexity of modern machine learning models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset of the training samples.
% selects the next $N$ samples from the training set before adjusting the model parameters, $\theta$, in the direction that decreases the loss.
% This is in the direction of the negative gradient of the loss, $-\nabla L(y, K(x, \theta))$.
This procedure is repeated for some number of \textit{epochs} (iterations through the entire training set). Every iteration takes a step,
\begin{equation}
    \theta^{(i+1)} = \theta^{(i)} - \eta \nabla_{\theta^{(i)}} L(y, K(x, \theta^{(i)}))
    \label{eq:sgd}
\end{equation}
where the gradient is approximated using a subset of samples and $\eta$ is a \textit{learning rate} (or step size) that is tuned to the particular model.

\subsection{Learning Rate Selection}
\label{learning_rate}

Choosing the correct learning rate is critical for model performance --- greatly effecting both the accuracy and the run-time requirements. A small learning rate will will more closely follow the true gradient of a class boundary~\cite{cao2019generalization}, but will converge slower, all other things being equal. Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data, \textit{etc}~\cite{granziol2022learning}. Graphics cards with larger amounts of RAM are able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch. A ``good" learning rate will allow a model converge quickly~\cite{smith2019super,granziol2022learning} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, scale, and bit depth of the data. However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}. Furthermore, since hardware is typically billed by the hour on public clouds, so optimizing the training and inference times allows a model-builder to minimize the cost of deployment.

\subsection{Adversarial Attacks}
\label{attacks}
In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models. Adversarial attacks are designed to deceive or change the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or otherwise produce undesired outputs. That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $\hat{y_a}$. That is \textit{adversarial success} or \textit{accelerated failure} is one in which
\begin{equation}
    \hat{y} \neq \hat{y_a} = K(x + \varepsilon; \theta).
\label{eq:adv_success}
\end{equation}
Additionally, one can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accuracy}. The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the ML pipeline, including during training \cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment ~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.

% \cm{I cut itemized list more discussion about learning rate tuning?}
% \begin{itemize}
%     \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying certain inputs or otherwise change the behavior of a modelt~\cite{ carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
%     \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset to influence the model's behaviour at run-time~\cite{biggio_poisoning_2013, saha2020hidden}. 
%     \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
%     \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}. 
% \end{itemize}

One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}. It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x_a$, such that,
\begin{equation}
x_a = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
\label{eq:fgm}
\end{equation}
In essence, this is process seeks to increase the loss  in contrast to model training which seeks to minimize it.

\subsection{Adversarial Analysis}

In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}. Whether in the context of automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}. An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable. However, this would mean testing a million samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems. This is just not computationally feasible. Instead, researchers can use adversarial failure analysis~\cite{carlini_towards_2017,biggio_evasion_2013,meyers} to improve the precision of our measurements while only using a small set of test-data.

\section{Survival Analysis for Robustness Verification during Training}
\label{afr}

We propose a methodology for model training and verification using accelerated failure rate (AFR) models, drawn from the field of \textit{survival analysis}. \cm{Additionally, since one of our goals is a cost-effective model evaluation technique, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.}
AFR models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. \cm{In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components. This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.}
\cm{The section below outlines our methodology for modelling the effect of model hyper-parameters during routine training procedures. In this section, we precisely outline the methodology for using survival analysis during the training of machine learning algorithms. We provide a formal algorithm in Fig.~\ref{fig:alg} and a visual diagram in ~\ref{fig:experiments}.}

\cm{In the subsections below, we define accuracy (Sec.~\ref{acc}) and failure rate (Sec.~\ref{failure_rate})  in the context of survival analysis to provide a pedagogical definition of survival time (Sec.~\ref{survival_time}). We then discuss the importance of the ``acceleration assumption" (Sec.~\ref{accelerated}), the optimization algorithm (Sec.~\ref{optimisation}), and the advantages of this approach (Sec.~\ref{advantages}).}

\begin{figure}
    \caption{Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x $ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x)$, and a number of trials, $n$, where the subscripts $t,i$ refer to the respective value for either the train and test sets.
    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Optimise $\theta$} according to some method (e.g Eq.~\ref{eq:sgd}).
    \State Record Training Time, $ T_t[i] $
    \State \textbf{Model Inference:} Compute $ \hat{y_i} = K(x_i, \theta) $
    \State Record Inference Time $ T_i[i] $
    \State \textbf{Benign Accuracy:} Calculate $\lambda_{ben}[i]$ using Eq.~\ref{eq:acc}
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}
    \State Record attack generation time, $T_a[i]$
    \State \textbf{Model Inference:} Compute $ y' = K(x_a, \theta) $
    \State \textbf{Adversarial Accuracy:} Calculate $\lambda_{adv}[i]$ with Eq.~\ref{eq:acc}
    \State \textbf{Append} accuracies and times to their respective arrays.
    \EndWhile
    \State \textbf{Fit Accelerated Model, $S_{adv}$} using $\lambda_{adv}$ and $T_a$
    \State \textbf{Fit Benign Model, $S_{ben}$} using $\lambda_{ben}$ and $T_i$
    \Ensure$ S_{adv} \approx  \phi S_{ben}(\phi t)$
    \Return $S_{adv}$
\end{algorithmic}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
    \caption{Experimental Pipeline Diagram}
    \label{fig:experiments}
\end{figure}

\subsection{Accuracy}
\label{acc}
 It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures. Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy, $\lambda_{ben}$, is defined as
\begin{equation}
    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
    \label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. In addition, it ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. \cm{We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test set $\lambda_{adv}$ to denote the accuracy on the adversarial examples.}

\subsection{Failure Rate}
\label{failure_rate}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}. To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, \cm{such that the failure rate is}
\[
    h_{ \theta}(t) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t} t,
\]
where $\mathbb{P}(\textrm{False~Classification})$ is the probability of a false classification, $\Delta t$ is a time interval, and $t$ is a point in time. \cm{Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$. By reparameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure rate model.}

\subsection{AFR Models}
\label{survival_time}
\cm{Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance.}

The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
$$
S_{\theta}(t)= \mathbb{P}(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
$$
\cm{where $\mathbb{P}(T>t)$ is the probability that a model has not failed by time $t$. Then, the expected survival time is}
\[
	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty} t \cdot S_\theta(t) \,dt.
\]

However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$. The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival}.  \cm{For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval. This should be measured in both the benign and adversarial contexts as a way to measure the cost of a particular model in both contexts.}

To choose a best-fit from the possible AFR functions, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}. \cm{For AIC and BIC, that means choosing the smallest value. Concordance, however, is a number between $-1$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival}. By evaluating $\mathbb{E}_{S_\theta}[T]$ for both adversarial and benign data, we can test the model under extreme perturbations and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}}

\subsection{Benign and Adversarial Survival Time}
\label{accelerated}
Using accelerated failure rate models, we can find the expected survival time under optimistic circumstances, $S_{ben}$ as well as under adverse ones (accelerated failure rate), $S_{adv}$. The survival time for benign samples is
$$
    S_{ben} := S(t_i; x, y, \theta) \mathrm{~~where~~} \varepsilon = 0
$$
and the survival time for the adversarial samples is
$$
    S_{adv} :=  S(t_i; x, y, \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
$$
\cm{This can also be thought of in terms of the accelerated failure rate assumption~\cite{kleinbaum1996survival}:
\begin{equation}
S_{adv} \approx  \phi S_{ben}(\phi t)
\label{assumption}
\end{equation}
where $\phi$ is some acceleration factor describing the joint effect of the covariates. This assumption means we can evaluate the benign accuracy using a small number of adversarial samples ~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.} 
\cm{However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space intelligently.}

\subsection{Optimisation}
\label{optimisation}
\cm{Machine learning models are typically trained across a wide variety of hyper-parameters to determine the ``best" model by minimizing an optimisation program (minimizing a loss function associated with the machine learning problem) by measuring the loss across many configurations of a model.} However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of such parameters,
making it infeasible to exhaustively evaluate the search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}--with several researchers noting an inverse relationship between model accuracy and model robustness ~\cite{carlini_towards_2017,meyers}. Therefore, a proper search would keep this dual-objective in mind.
\cm{To optimize for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because of its ability to work in distributed settings,  while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}}.

\subsection{Advantages of this Methodology}
\label{advantages}
\cm{Because of the small number of samples needed for building AFR models (when compared to testing against massive in-distribution test sets), AFR models could}, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}. Furthermore, by isolating changes and testing them as quickly as possible, it is  easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test. To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}. This risk analysis is outlined in the subsection below.

\section{Cost Analysis}
\label{cost}
\cm{In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by ISO26262~\cite{iso26262} which allows us to quantify the marginal risk. To quantify this marginal risk, one must measure} the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack. The final subsection outlines why these metrics are important and their usage in this methodology.

\subsection{Accuracy}
\cm{In order to estimate the number of failures in a given time period}, we measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss. \cm{Under the AFR framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period.}

\subsection{Training Time}
The training time, $T_t$, is the time it takes to evaluate $n$ samples such that the training time per sample $t_t$ is
$$
    T_t := t_t * n  * m.
$$
where $m$ is the number of epochs and $*$ is normal scalar multiplication.

\subsection{Latency}
Latency is the time it takes to respond to a query. We assume that latency per sample is
$$
    T_i := t_i *n,
$$
which will be driven by the memory bandwidth (measured in bits/second) of a given CPU or GPU and the size\cite{vgg} and complexity\cite{resnet} of a given neural network architecture.

\subsection{Attack Generation Time}
A successful attack is one that induces failure in a model. That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output. We approximate this for each attack/defence configuration by the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
\begin{equation}
    \label{attack_time}
    T_a := t_i *n *i.
\end{equation}
We restricted this to a single iteration \cm{such that $i =1$} as described in FGM~\cite{fgm}.

\subsection{Cost}
Furthermore, we approach the cost of deployment at two scales. Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost. However, at a certain scale, (\textit{e.g.} for deploying a self-driving car) it is  more appropriate to talk about cost in terms of power. Finally, we define best-case and worst-case success metrics that provide an efficient way to minimize the latency, cost of deployment, and 
maximize the generalized performance of a model. We define the training cost ($C_t$) as
$$
    C_t = C_h *T_t,
    \label{eq:cost_training}
$$
the cost of model inference time as,
$$
    C_i = C_h *T_i,
    \label{eq:cost_inference}
$$
and the cost of an attack as,
$$
    C_a = C_h * T_a.
    \label{eq:cost_attack}
$$
where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time.

\subsubsection{Power}
The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
$$
    P_t = P_h *T_t,
    \label{eq:power_training}
$$
the power consumption during model inference is
$$
    P_i = P_h *T_i,
    \label{eq:power_inference}
$$
and the power consumption during attack generation is
$$
    P_a = P_h *T_a.
    \label{eq:power_attack}
$$
where $P_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time.

\subsection{Comparative Risk}
\cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice. The \textit{marginal risk} is the change in survival time divided by change in attack compared to some control model such that:
\[
    \textrm{Comparative~Risk} := \frac{\% \Delta S(t)}{\% \Delta C_a},
\]
where $\% \Delta$ reflects the percent change from the control model.}

\cm{Another advantage is that we can quickly discard ineffective model choices with this method.} In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. \cm{In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken"). For our purposes, by assuming the best-case scenario for both attacker and defender, we can model the Pareto front --- the best-case asymptotic behavior --- of either party~\cite{zitzler2008quality}.}
As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.

\section{Experiments}
\label{experiments}

This section outlines specific implementation details for the evaluation of the methodology outlined in Section~\ref{afr}.

\subsection{Cloud Platform and Hardware}
To conduct the experiments and have access to different types of hardware, we utilized GCP. Six virtual machines running Container Optimized Operating System provided by GCP constituted our testbed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster consisting of six worker nodes. Three worker nodes were responsible for running the monitoring platforms such as Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the ``e2-medium" instance type provided by GCP. In total, we used three GPU models. For P100 and V100 GPUs, we used ``n1-standard-2'' type for the nodes and for L4 GPUs we used ``g2-standard-4''.

To assess the energy consumption of the experiments deployed on a Google Kubernetes Engine, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}. This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components. In essence, KEPLER uses extended Berkley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics. eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space. eBPF programs are invoked by the kernel when certain events occur. Examples of such events include system calls or network activity. These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}. A diagram of the cloud architecture can be found in Fig.~\ref{fig:architecture}. Finally, to meet our goal of developing a cost-effective model evaluation technique, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google. Approximately 10\% of this was used for development and 90\% was used for the evaluations.

\begin{figure*}
    \centering
    \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
    \caption{Cloud Architecture Diagram}
    \label{fig:architecture}
\end{figure*}

\subsection{AFR Models}

For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}. We used three optimisation criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Fig.~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data. For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack. Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time. The inference time and training time were used to conduct the cost analysis outlined in the next section (Sec.~\ref{cost})

\subsection{Datasets}
The AFR models were evaluated using the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets. Furthermore, to reduce the complexities of system overhead, distributed or federated training, and the effect of shared cloud environments, we restricted ourselves to datasets that were small enough to reside entirely within GPU memory with the model, since the disk read speed in cloud environments is incredibly variable.

\subsection{Models}
We restricted ourselves to a single model for our evaluations. Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware. As discussed in Sec.~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict. So, we sampled learning rates $\in [10^{-6}, 1]$, batch sizes $\in [1, 10^5]$, and epochs $\in [1, 50]$ for MNIST and CIFAR10 on the P100 and V100. For CIFAR100, we increased the range of the tested epochs to be $\in [1, 100]$. To evaluate the efficacy of different bit-depths on the L4 hardware, we used the Feature Squeezing defence~\cite{feature_squeezing} provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{Pytorch} compatible arrays. Model parameters were chosen using the \texttt{Optuna} optimisation framework, the configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.

\subsection{Attacks}
Since one goal of this paper was to evaluate how hardware and deployment cost affect adversarial robustness during run-time, we focused on evasion attacks since they induce failures by adding noise to the data at run-time. Prior research~\cite{meyers} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time. To evaluate the effect of adversarial noise on our samples, we varied $\varepsilon \in [0, 1]$, using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.

\subsection{GPU Configurations}
We tested several hardware configurations, which have various hourly costs, peak power demands, and theoretical memory bandwidths. The V100 was chosen as a baseline, since it is  routinely used in the literature ~\cite{svedin2021benchmarking,xu2018deep}. The P100 architecture comes from the same line of server-grade GPUs, but from an older generation. The L4, however, is advertised as a machine built for inference --- not training --- relying on a smaller number of bits per tensor core. Consequently, the number of operations per second is dependent on the bit depth of the data and the model weights, with the peak numbers outlined in Tab.~\ref{tab:hardware} referring to 8-bit inputs.

\begin{table}[h]
    \centering
    \begin{tabular}{lllll}
    \toprule
                            & V100   & P100   & L4    &  \\
    \midrule
    Cost (USD/hour)         & 2.55   & 1.60   & 0.81   &  \\
    Power (Watts)           & 250    & 250    & 72    &  \\
    Memory Bandwidth (GB/s) & 900    & 732    & 300   &  \\
    \bottomrule
    \end{tabular}
    \caption{Hardware specifications for tested GPUs. All specifications were retrieved from the Nvidia website at the following links: 
    \href{https://images.nvidia.com/content/technologies/volta/pdf/volta-v100-datasheet-update-us-1165301-r5.pdf}{V100 Datasheet},
    \href{https://images.nvidia.com/content/tesla/pdf/nvidia-tesla-p100-PCIe-datasheet.pdf}{P100 Datasheet}, and
    \href{https://nvdam.widen.net/s/rvq98gbwsw/l4-datasheet-2595652}{L4 Datasheet}. Prices were retrieved from Google Cloud Platform for the \texttt{europe-west4} region on 3 December 2023 at \href{https://cloud.google.com/pricing/list}{this link.}
    }
    \label{tab:hardware}
\end{table}

\subsection{Survival Analysis}
In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the funciton, $S(t)$. We attempted adding dummy variables for hardware (\textit{e.g.}, peak power and peak bandwidth) as well as the datasets (\textit{e.g.}, resolution, bit depth, and number of color channels), but each of these were strongly co-linear with training time and hindered modelling. As such, they were not included. To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}. We also compared the chosen modelling functions (see Section~\ref{afr}).  These results can be found in Section~\ref{results}.

\subsubsection{Hardware}
The rental cost of the hardware, measured in United States Dollars per hour, will indicate the operating cost of a given model. To calculate this, we used the price per hour from each of cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.}}\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimized}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).

\section{Results and Discussion}
\label{results}

Below, we demonstrate the effect of hardware and dataset on the benign/adversarial accuracy (Fig.~\ref{fig:acc}), training/inference/attack time (Fig.~\ref{fig:time}), and both monetary (Fig.~\ref{fig:cost}) and power (Fig.~\ref{fig:power}) costs for training/inference/attacks. We also compared all three survival times outlined in Sec.~\ref{afr} using the criteria outlined in the same section. Using the best-fit function (again, see Sec.~\ref{afr}), we examined the effect of the covariates on the survival time of the model (Figs.~\ref{fig:partial_effect_train_time}-\ref{fig:partial_effect_attack_eps}).

\cm{I will cut this accuracy subsection. In exchange, I will conduct a log-rank test}
\subsection{Accuracy}
Fig.~\ref{fig:acc} shows the advernsarial and benign accuracies for all datasets and hardware. It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware though CIFAR10 has worse benign performance and CIFAR100 has substantially worse adversarial performance. For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (e.g. the accuracy we would expect on random noise), demonstrating the efficacy of the attack outlined in Sec.~\ref{optimisation}.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,trim={30pt 0 10pt 0},clip]{plots/combined/acc.pdf}
    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
    \label{fig:acc}
\end{figure}

\subsection{Time}
Fig.~\ref{fig:time} reveals the training time. Slower hardware (see Memory Bandwidth in Tab.~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference. This should be no surprise since the less-capable hardware is meant to be used exclusively for inference. Additionally, the attack time increases with both the training and prediction times across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/time.pdf}
    \caption{Training, Prediction, and Attack times across datasets and hardware.}
    \label{fig:time}
\end{figure}

\subsection{Power}
The power consumption, illustrated in Fig.~\ref{fig:power}, tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric. Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/power.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:power}
\end{figure}

\subsection{Cost}
The monetary cost for each dataset and each piece of hardware is shown in Fig.~\ref{fig:cost}. \cm{For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample. In the best case scenario, they are comparable. However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always. This reveals an essential advantage for the attacker on the reference model and hardware architecture --- attacks consistently succeed with 100s of samples while model training requires orders of magnitude more.}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/cost.pdf}
    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
    \label{fig:cost}
\end{figure}

\subsection{AFR Models}
\cm{TODO: add 1. fitted parameters and 2. their statistical significance here. Discuss what that means. Move table here. Discuss why we chose Log-Logistic. Discuss accelerated failure assumption again.}

Table~\ref{tab:Combined} shows that the aft models using log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render the plots due to its marginally improved AIC.

\input{plots/combined/aft_comparison}

\cm{Figure TODO shows the p-values for each of the covariates}

Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time. However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that and increase the attack distance by an order of magnitude reduces the survival time marginally. Additionally, we see that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.

\begin{figure}
  \centering
  % include first image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
  \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_train_time}
\end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}  
  \caption{The partial effect of the attack distance on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_attack_eps}
\end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_accuracy_partial_effect.pdf} 
  \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_accuracy}
\end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_adv_failure_rate_partial_effect.pdf} 
  \caption{TODO: replace this with epochs and batch size}
  \label{fig:partial_effect_adv_failure_rate}
\end{figure}

\subsection{Comparative Risk}
\cm{TODO}
Call back to the comparative risk and the fast rejection mechanism.

\section{Considerations}
\label{considerations}
We have taken much care to conduct these measurements as carefully as possible. Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for maximum likelihood learning~\cite{ma2022state}. Given the strong ($>0.5$) concordance results and uniformity across AFR functions in Table~\ref{tab:Combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance. Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning. \cm{While this obscures the effect of GPU parallelization, the result doesn't change since all metrics are measured on a particular piece of hardware for both the attacker and defender. Furthermore, we see the attack batch size and the training batch size to be the same for every trial. If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.} In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above. Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth. However, we would like to note that the ``inference-optimized" Nvidia 4-series GPUs are perfectly capable and affordable training machines. We restricted our search to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time (and therefore deployment cost), though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks.

\section{Conclusions}
\label{conclusion}
In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and to evaluate them in the presence of adversarial noise, allowing us the model performance as a function of tested model parameters. Using this technique, we showed that despite reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time. Furthermore, we demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields substantially similar results when compared to more expensive and power hungry hardware. However, the marginal run-time is substantial, even if it's cost-effective.

% no keywords
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\clearpage
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\end{document}

### 2024-03-28 old (ccgrid).tex
merge

%  Moved to main.tex for cloud conference
% \documentclass[conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
% \usepackage{cite}
% \usepackage{amsmath,amssymb,amsfonts}
% \usepackage{algorithmic}
% \usepackage{graphicx}
% \usepackage{textcomp}
% \usepackage{xcolor}
% \usepackage{multirow}
% \usepackage{hyperref}
% \usepackage{booktabs}
% \usepackage{subcaption}

% % \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}

% \newcommand{\cm}[1]{#1}
% \newcommand{\mr}[1]{\textit{{\color{red}#1}}}

% % \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
% %     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
% % \begin{document}

% \title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}
% % \thanks{Identify applicable funding agency here. If none, delete this.}
% % \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% % \textit{Umeå University}\\
% % Umeå, Sweden \\
% % cmeyers@cs.umu.se}
% % \and
% % \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% % \textit{Umeå University}\\
% % Umeå, Sweden \\
% % fake@fake.se}
% % \and
% % \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% % \textit{Umeå University}\\
% % Umeå, Sweden \\
% % tommy@cs.umu.se}
% % \and
% % \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% % \textit{Umeå University}\\
% % Umeå, Sweden \\
% % elmroth@cs.umu.se}
% % }

% \maketitle

% \begin{abstract}
% Considering the growing prominence of production-level AI and the threat of adversarial attacks that can poison a machine learning model against a certain label, evade classification, or reveal sensitive data about the model and training data to an attacker, adversaries pose fundamental problems to machine learning systems. 
% Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect. We address the problem of neural network validation and verification. More specifically, we address the problem of continuous integration and deployment for safety-critical models.
% For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, meaning that each software change would need to be evaluated against new real-world deployment samples which can be prohibitively expensive or time-consuming to collect. To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture. We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. This provides a way to evaluate the model and optimize it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy. Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
% \end{abstract}

% \begin{IEEEkeywords}
% artificial intelligence, machine learning, adversarial AI, optimization, compliance
% \end{IEEEkeywords}

% \section{Introduction}
% \subsection{Motivations}
% % \begin{itemize}
% %     % \item \textit{BIG} Data is the trend
% %     % \item Costs are astronomical
% %     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
% %     \item Other work relies on unreliable test/train split methodology
% %     \item Which means that cars, medical equipment is tested in the wild
% % \end{itemize}

% Recently, machine learning (ML) using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. However, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. Furthermore, popular models like Generative Pre-trained Transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions of parameters, requiring equally large training datasets. Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. The newest version of this open-source large language model (LLM) is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}. Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be between $[1e-12, 1e-15]$ depending on the number of lives at risk ~\cite{iso26262}. Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Collecting, labelling, and testing a new set of data for every software change-as required by law-would be prohibitively expensive. Therefore, a new evaluation methodology is required. As such, the proposed methodology, centered around survival analysis, tests a model against "worst-case" (e.g. adversarial) input to verify the efficacy of one modelling deployment decision over another. \cm{This methodology allows to minimize the training cost, optimize for adversarial robustness, and estimate the partial effects of covariates on model performance during routine training procedures.}

% \subsection{Contributions}
% So, in order to tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective technique and source code that:
% \begin{itemize}
%     \item optimizes for benign and adversarial accuracy simultaneously,
%     \item extends survival analysis to the realm of neural networks, 
%     \item demonstrates a scalable and effective method that allows us to tune a model while simultaneously estimating the asymptotic effect of various hyperparameters,
%     \item and measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
%     \item We show that, despite a decrease in training time, that faster hardware, more precise hardware, and/or more power-hungry hardware do not lead to more adversarial robust models.

% \end{itemize}

% \section{Background}
% ML pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges. In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex ML pipeline.
%  As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises. The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference. Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.

% To address these challenges, containerization and orchestration technologies have gained prominence in managing complex ML pipelines. Kubernetes, a widely adopted container orchestration platform, provides a scalable and flexible environment for deploying, scaling, and managing microservice-based applications. Its ability to handle heterogeneous hardware architectures and workload distribution across clusters makes it an ideal choice for managing the complex computational requirements of ML pipelines.

% % Using this microservice architecture, it's possible explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts across heterogeneous hardware to minimize the deployment cost in the cloud.
% % Additionally, understanding the relationship between computational cost, model loss, and prediction accuracy is vital for optimizing the pipeline's performance. Balancing computational resources, time constraints, and accuracy requirements is a fundamental consideration in deploying ML models in production environments. By analyzing the impact of computational cost on model loss and accuracy metrics, we can gain insights into the trade-offs involved and make informed decisions to optimize the pipeline's efficiency.

% In this paper, we present a comprehensive study that leverages Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of GPU architectures. We then investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts. Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying ML models under varying computational constraints and adversarial conditions.

% For the sake of the reader, we provide a section for definitions and requisite background information below.

% \subsection{Cloud Architectures}
% A \textit{microservice} is the smallest component of a `cloud-native' software stack. In the context of ML, that might be a tool for either training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. A microservice \textit{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between microservices in a distributed system. It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services.

% A microservice \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the microservices within the system. These components facilitate various capabilities and functionalities essential for managing the communication between microservices. Kubernetes has become one of the largest open source projects on the code-sharing website Github \cite{k8s-size}, which provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures.

% \subsection{ML Pipelines}
% ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters. Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}. In general, a dataset is split into \textit{training} and \textit{test} sets. The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users. To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.

% \subsection{Classifiers}

% A classifier, $K(x; \theta)$, with model parameters, $\theta$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization without loss of generality.} an \textit{objective} (or \textit{loss}) \textit{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the loss value, $L$ for some optimal set of parameters, $\theta^*$ is:
% \[
% L(y, K(x, \theta^*)) = \mathrm{argmin}_{\theta \in \Theta} (y - K(x, \theta)).
% \]
%  In the case of neural networks, however, finding the optimal set of hyper-parameters is non-trivial as the number of tunable parameters is often measured in the millions and the loss function is non-convex. Instead of finding an analytical solution to this equation, we often rely on numerical optimisation, and one choice is \textit{stochastic gradient descent}, which samples the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss. This is in the direction of the negative gradient of the loss, $-\nabla L(y, K(x, \theta))$. This procedure is repeated for some number of \textit{epochs} (iteration through the entire training set), $i$, and every iteration thus performs the step,
% \[
% \theta^{(i+1)} = \theta^{(i)} - \eta \nabla_{\theta} L(y, K(x, \theta^{(i)}))
% \]
% where $\eta$ is a \textit{learning rate} that is tuned to the particular model and fixed batch size.

% \subsection{Learning Rate Selection}
% \label{learning_rate}
% Choosing the correct learning rate is critical for model performance---greatly effecting both the accuracy and the run-time requirements. A small learning rate will have a smaller error bound ~\cite{}, but will converge slower, all other things being equal. Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data ~\cite{}. Graphics cards with larger amounts of RAM will be able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch. In theory, a `good' learning rate can converge quickly ~\cite{smith2019super} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, and bit depth of the data. However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so we must evaluate this \textit{in situ}. Furthermore, since hardware is billed by the hour, optimizing the training and inference times allows us to minimize the cost of deployment.

% \subsection{Adversarial Attacks}
% \label{attacks}
% In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models. Adversarial attacks are designed to deceive or change the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or otherwise produce undesired outputs. That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $y'$. That is \textit{adversarial success} or \textit{accelerated failure} is one in which
% \begin{equation}
%     \hat{y} \neq y' = K(x + \varepsilon; \theta).
% \label{eq:adv_success}
% \end{equation}
% Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accurracy}. The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the ML pipeline, including during training \cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment ~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.

% % \cm{I cut itemized list more discussion about learning rate tuning?}
% % \begin{itemize}
% %     \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying certain inputs or otherwise change the behavior of a modelt~\cite{ carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
% %     \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset to influence the model's behaviour at run-time~\cite{biggio_poisoning_2013, saha2020hidden}. 
% %     \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
% %     \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}. 
% % \end{itemize}

% One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}. It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that,
% \begin{equation}
% x' = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
% \label{eq:fgm}
% \end{equation}
% In essence, this is process seeks to maximize loss in contrast to model training which seeks to minimize it.

% \subsection{Adversarial Analysis}

% In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}. Whether we discuss automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}. An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable. However, this would mean testing a million samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems. This is just not computationally feasible. Instead, we can use adversarial failure analysis to improve the precision of our measurements while only using a small set of test-data.

% \cm{Moved Accuracy/ Failure Rate to this section}
% \section{AFR models for Robustness Verification during Training}
% \label{afr}
% Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.

% \subsection{Accuracy}
% The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}. It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures. Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy is defined as
% \begin{equation}
%  \mathrm{Accuracy} = 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}}
% \label{eq:acc}
% \end{equation}
% which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. In addition,  ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}.

% % \cm{Didn't discuss adversarial success again.}
% % Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples, such that 
% % $$
% %     y\neq\hat{y}\text{~~while~~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max},
% % $$ 
% % where $\| \cdot \|$ represents some norm or pseudo-norm and $\varepsilon$ is some specified  perturbation distance threshold bound by a maximum distance, $\varepsilon_{max}$.

% \subsection{Failure Rate}
%  To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates (\textit{e.g.}, noise distance, model size, hardware resources, $\theta$) such that,
% \[
%     h_{ \theta}(t) :=  \frac{P(\textrm{False~Classification})}{\Delta t} t
% \]
% where $P(\textrm{False~Classification})$ is the probability of a false classification and $\Delta t$ is a time interval. \cm{Note that this is equivalent to 1 - accuracy when $\Delta t = t$.} To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textit{survival time}, $S(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
% $$
% S_{\theta}(t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
% $$
% We can use the survival function to compute the expected survival time or average time-to-failure:
% \[
% 	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty} t \cdot S_\theta(t) \,dt.
% \]

% \subsection{Survival Time}
% \label{survival_time}
% \cm{Accelerated failure time models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance. For each trial, we measured the prediction time for both benign and adersarial samples to define our time interval and used benign/adversarial accuracy as an estimate of the number of failures in that time interval.} However, modelling $S_{\theta}(t)$ requires a choice in modelling distribution for $S$. Log-Logistic, Log-Normal, and Weibull distributions are widely used options. To choose a best-fit model, we compared Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}.  This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial. However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces. In order to minimize the cost of evaluation, we must be clever about how we search.

% % \subsection{Pareto Set}

% % In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{kamal2017study,leurent2020sha}. A subset of examples that maximize one or more objective criteria is called the \textit{pareto front}~\cite{zitzler2008quality}. It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}. Table~\ref{tab:pareto} shows the required number of queries to get estimates within the $\varepsilon$-sphere of the true Pareto front. As we can see, it is critical to minimize the dimensionality of our search. So instead of optimizing for latency, training time, cost, accuracy, and adversarial success rate independently, we introduce several metrics in the next section.

% % % Please add the following required packages to your document preamble:
% % % \usepackage{multirow}
% % % Please add the following required packages to your document preamble:
% % % 
% % \begin{table}[h!]
% % \begin{tabular}{cl|llll|}
% % \cline{3-6}
% %                                            &   & \multicolumn{4}{c|}{$\varepsilon$}            \\ \cline{3-6} 
% %                                            &   & .1     & .05          & .01    & .001      \\ \hline
% % \multicolumn{1}{|c|}{\multirow{3}{*}{$d$}} & 1 & 10     & 20           & 100    & 1000      \\
% % \multicolumn{1}{|c|}{}                     & 2 & 100    & 400          & $10^4$ & $10^6$    \\
% % \multicolumn{1}{|c|}{}                     & 4 & $10^4$ & $1.6 * 10^5$ & $10^9$ & $10^{12}$ \\ \hline
% % \end{tabular}
% % \caption{This table shows the number of queries required to $\varepsilon-$ approximate the Pareto front, $\mathcal{P}$, in $d$ dimensions.}
% % \label{tab:pareto}
% % \end{table}

% \subsection{Optimization}
%  \cm{Machine learning models are typically trained across a wide variety of hyper-parameters and determining the "best" model by solving some optimization problem (typically maximizing accuracy or minimizing loss) through posterior evaluations across the entire search space.} However, these hyper-parameters are often drawn from continuous and infinite spaces, so it's impossible to exhaustively evaluate the search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}, meaning that a proper search would keep this dual-objective in mind. Luckily, the field of multi-objective search is well researched. We chose the Tree-structure Parzen Estimator (TPE) because of it's ability to work on mini-batches, in distributed settings, and while optimizing multiple objectives in a feasible number of trials ~\cite{ozaki2020multiobjective}, though research in this field is very much ongoing~\cite{ozaki2022multiobjective}. The ideal algorithm will vary with the distribution of the parameters, the population size of the search space, and the presence or absence of categorical variables.

% \subsection{Metrics}

%  In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack, as well as the benign and adversarial accuracies (see: Secs.~\ref{eq:acc} and ~\ref{eq:adv_success}). 80\% percent of the data for each dataset was used for training and the remaining twenty percent was used for evaluation. We withheld 100 examples from the test set as the initial values for adversarial examples, which gives us two significant figures for this measurement, while benign accuracy was measured with 10s of thousands of samples, giving us 4 significant figures for that metric. For all reported times, we assumed that the time was distributed uniformly across the samples to minimize jitter and account for GPU-based parallelization.

% \subsubsection{Accuracy}
% We measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.

% % \subsection{Benign Success}
% % A \textit{success} can be thought of in both the adversarial and benign context, which are denoted with the subscripts $ben.,adv.$ throughout this work. Typically this is measured via the train/test methodology in which some subset of a benchmark dataset. However, this method has repeatedly shown itself to be an inadequate measure of real-world model performance, and is, at best, an optimistic best-case measure of the failure rate~\cite{croce_reliable_2020}. The benign success ratio is usually measured via the train/test split methodology mentioned in typical in the literature.

% % \subsection{Adversarial Success}
% % A successful adversary, however, is one that is able to change the model's output from one class to another. For the benign case, we measure the test set accuracy as our success metric. However, we m

% % Furthermore, the computational difficulty of this task is often related to secondary optimization criteria~\cite{}, with a baseline of at least NP-Hard~\cite{madry2017towards}. Since many of the attacks have more success after a number of iterations\cite{fgm,deepfool,carlini_towards_2017,madry2017towards,hopskipjump}, it is appropriate to think about their success in terms of time.

% \subsubsection{Training Time}
% The training time, $T_t$, is the time it takes to evaluate $n$ samples such that the training time per sample per epoch $t_t$ is.
% $$
% T_t := t_t\cdot n
% $$

% \subsubsection{Latency}
% Latency is the time it takes to respond to a query. We assume that latency per sample is:
% $$
% T_i  := t_i \cdot n
% $$
% which will be driven by the memory bandwidth (measured in bits/second) of a given cpu- or gpu- and the size\cite{vgg} and complexity\cite{resnet} of a given neural network architecture.

% \subsubsection{Attack Generation Time}
% A successful attack is one that induces failure in a model. That is, the expected survival time, $\mathbb{E}[S(t;x,y,\theta)]$, can be thought of as the time it takes for an attacker to induce a change in the model output. We approximate this for each attack/defence configuration by taking the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$:

% \begin{equation}
% T_a := t_i \cdot n \cdot i
% \label{attack_time}
% \end{equation}

% In the interest of attack speed, we restricted this to a single iteration.

% \subsubsection{Cost}
% Furthermore, we can think of cost of deployment at two scales. Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using GCP compute costs as a measure of total cost. However, at a certain scale, (\textit{e.g.} for deploying a self-driving car) it's more appropriate to talk about cost in terms of power. Finally, we define best-case and worst-case success metrics that give us an efficient way to minimize the latency, cost of deployment, and 
% maximize the generalized performance of a model. We define the training cost ($C_t$) as:
% $$
%     C_t = C_h \cdot T_t,
%     \label{eq:cost_training}
% $$
% the cost of model inference time as:
% $$
%     C_i = C_h \cdot T_i,
%     \label{eq:cost_inference}
% $$
% and the cost of an attack as:
% $$
%     C_a = C_h \cdot  T_a.
%     \label{eq:cost_attack}
% $$

% \subsubsection{Power}
% The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
% $$
%     P_t = P_h \cdot T_t,
%     \label{eq:power_training}
% $$
% the power consumption during model inference is:
% $$
%     P_i = P_h \cdot T_i
%     \label{eq:power_inference}
% $$
% and the power consumption during attack generation is:
% $$
%     P_a = P_h \cdot T_a
%     \label{eq:power_attack}
% $$

% \subsection{Advantages of this Methodology}
% \cm{moved}

% Because of the relatively small run-time requirements of this approach (when compared to testing against massive in-distribution test sets), this method could, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples. Furthermore, by isolating changes and testing them as quickly as possible, it's much easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test. To further increase development velocity, we can use these models to quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}. This risk analysis is outlined in the subsection below.

% \subsubsection{Relative Cost to an Attacker}
% In security analysis, it's routine to think in optimistic terms for both the attacker and defender. \cm{In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptogrpahic system~\cite{kamal2017study,leurent2020sha} (e.g. whether or not a given cryptographic method should be considered "broken").}
% As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which is both effective and fast. If the cost to a model builder is much larger than the cost to an attacker ($C_t >> C_a$), then it's clear that model is "broken" in this cryptographic sense and can be discarded as ineffective.

% \section{Implementation Details}

% This section outlines specific implementation details for the evaluation of the methodology proposed in Section~\ref{afr}.

% \subsection{Cloud Platform and Hardware}
% To conduct the experiments and have access to different types of hardware, we utilized Google Cloud Platform (GCP). Six virtual machines running Container Optimized Operating System provided by GCP constitute our testbed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster consisting of six worker nodes. Three worker nodes were responsible for running the monitoring platform such as Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the 'e2-medium' instance type provided by Google Cloud Platform. In total, we used three GPU models. For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4'.
% To assess the energy consumption of the experiments deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}. This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components. In essence, KEPLER uses extended Berkley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics. eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space. eBPF programs are invoked by the kernel when certain events occur. Examples of such events include system calls or network activity. These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}. A diagram of the cloud architecture can be found in Fig.~\ref{fig:architecture}. Finally, to meet our goal of developing a cost-effective model evaluation technique, we restricted all of our experiments to a single one-thousand United States dollar research grant from Google.

% \begin{figure*}
%     \centering
%     \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
%     \caption{Cloud Architecture Diagram}
%     \label{fig:architecture}
% \end{figure*}

% For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}. We used three optimization criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Fig.~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data.

% \begin{figure}
%     \centering
%     \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
%     \caption{Experimental Pipeline Diagram}
%     \label{fig:experiments}
% \end{figure}

% \subsection{Datasets}
% For our experiments, we evaluated the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis ~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results. By modern standards (billions of parameters), these models are quite small (tens of thousands of samples), but our goal is not to rival the accuracy of industy leaders, but to develop a method that is practical for everyone else to use.
% Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets. Furthermore, to reduce the complexities of system overhead, distributed or federated training, and the effect of shared cloud environments, we restricted ourselves to datasets that are small enough to reside entirely within GPU memory with the model, since the disk read speed in cloud environments is incredibly variable.

% \subsection{Models}
% We restricted ourselves to a single model for our evaluations. Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware. As discussed in Sec.~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict. So, we sampled learning rates $\in [1e-6, 1]$, batch sizes $\in [1, 1e5]$, and epochs $\in [1,50]$ for MNIST and CIFAR10 on the P100 and V100. For Cifar100, we increased the range of the tested epochs to be $\in [1, 100]$. To evaluate the efficacy of different bit-depths on the L4 hardware, we used the Feature Squeezing defence~\cite{feature_squeezing} provided by IBM's adversarial robustness toolbox~\cite{art2018}. Model parameters were chosen using the \texttt{optuna} optimization framework, configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.

% \subsection{Attacks}
% Since the goal in this paper is to evaluate how hardware and deployment cost affect adversarial robustness, we focused on evasion attacks since they induce failures by adding noise to the data. Prior research ~\cite{meyers} has shown that the Fast Gradient method (see: Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time. To evaluate the effect of adversarial noise on our samples, we varied $\varepsilon \in [0, 1]$, using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.

% \subsection{GPU Configurations}
% We tested several hardware configurations, which have various hourly costs, peak power demands, and theoretical memory bandwidths. We tested three Nvidia cards-- the V100, the P100, and L4. The V100 was chosen as a baseline, since it's routinely cited in the literature~\cite{svedin2021benchmarking,xu2018deep}. The P100 architecture comes from the same line of server-grade training GPUs, but from an older generation. The L4, however, is advertised as a machine built for inference--not training, relying on a smaller number of bits per tensor core. Consequently, the number of operations per second is dependent on the bit depth of the data and the model weights, with the peak numbers outlined in Tab.~\ref{tab:hardware} referring to 8-bit inputs.
% \begin{table}[h]
% \begin{tabular}{lllll}
% \hline
%                         & V100   & P100   & L4    &  \\ \hline
% Cost (USD/hour)         & 2.55   & 1.60   & .81   &  \\
% Power (Watts)           & 250    & 250    & 72    &  \\
% Memory Bandwidth (GB/s) & 900    & 732    & 300   &  \\ \hline
% \end{tabular}

% \caption{Hardware specifications for tested GPUs. All specifications were retrieved from the Nvidia website at the following links: 
% \href{https://images.nvidia.com/content/technologies/volta/pdf/volta-v100-datasheet-update-us-1165301-r5.pdf}{V100 Datasheet},
% \href{https://images.nvidia.com/content/tesla/pdf/nvidia-tesla-p100-PCIe-datasheet.pdf}{P100 Datasheet}, and
% \href{https://nvdam.widen.net/s/rvq98gbwsw/l4-datasheet-2595652}{L4 Datasheet}. Prices were retrieved from Google Cloud Platform for the \texttt{europe-west4} region on 3 December 2023 at \href{https://cloud.google.com/pricing/list}{this link.}
% }
% \label{tab:hardware}
% \end{table}

% \subsection{Survival Analysis}
% In addition to the optimization criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the distribution, $S(t)$. We attempted adding dummy variables for hardware (\textit{e.g.}~peak power and peak bandwidth) as well as the datasets (\textit{e.g~}resolution, bit depth, and number of color channels), but each of these were strongly co-linear with training time and hindered modelling of the distribution. As such, they were not included. To find the distribution of the measured data and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}. We also compare the chosen distributions (see: Section~\ref{afr}).  These results can be found Section~\ref{results}.

% \subsubsection{Hardware}
% This value, measured in United States Dollars per hour, will indicate the operating cost of a given model. To calculate this, we used the price per hour from each of cloud service pricing page~\footnote{ Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} } ~\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimized}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$) and the inference time ($T_{i}$).

% \subsection{Survival Time}

% Correspondingly, we can talk about the expected survival time under optimistic, $S_{ben.}$ as well as under adverse (accelerated failure rate distribution), $S_{adv.}$. If we assume that the distribution of failures is uniform with respect to latency \footnote{\cm{While this is not necessarily the case, neural networks generally assume independent and identically distributed data~\cite{ma2022state}, but we admit that tracking the per-sample failure rate would be a good way to detect under-sampled regions or otherwise likely-to-fail samples. Furthermore, since the modelling distributions include shape and scale parameters for each covariate as well as the model as a whole, whether or not we divide by the number of samples is irrelevant since these shape and scale parameters will absorb this value anyway. We include this normalization so that we can compare the benign and adversarial prediction times which are calculated across 10 thousand and 100 samples respectively. That is, we merely scaled the y-axis on Figs~\ref{fig:time}~and~\ref{fig:cost} without changing the behaviour of $S(t)$ for the sake of comparison.}}
% $$
% S_{ben.} := S(t_i; x, y, \theta) \mathrm{~s.t.~} \varepsilon = 0
% $$
% and
% $$
% S_{adv.} :=  S(t_i; x, y, \theta) \mathrm{~s.t.~} 0 < \varepsilon \leq \varepsilon_{max}
% $$

% \section{Results}
% \label{results}
% Below, we examine the effect of hardware and dataset on the distribution of the benign/adversarial accuracy (Fig.~\ref{fig:acc}), training/inference/attack time (Fig.~\ref{fig:time}), and both monetary (Fig.~\ref{fig:cost}) and power (Fig.~\ref{fig:power}) costs for training/inference/attacks. We also compare all three survival time distributions outlined in Sec.~\ref{afr} using the criteria outlined in the same section. Using the best-fit distribution (again, see:~\ref{afr}), we plotted the effect of several covariates on the survival time of the model (Fig.~\ref{fig:partial_effect_train_time}).

% \subsection{Accuracy}
% Fig.~\ref{fig:acc} reveals little to no improvement in accuracy or adversarial accuracy, regardless of hardware though we see that the Cifar10 has worse benign performance and Cifar100 has significantly adversarial performance. 
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=.5\textwidth]{plots/combined/acc.pdf}
%     \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
%     \label{fig:acc}
% \end{figure}

% \subsection{Time}
% Fig.~\ref{fig:time} reveals the training time proportional to the GPU bandwidth numbers in Tab.~\ref{tab:hardware}. Slower hardware is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference. This should be no surprise since the less-capable hardware is meant to be used exclusively for inference. Additionally, we see that the attack time is colinear with both the training and prediction times across hardware and datasets-- an expected result since this will be driven by the number of samples and the inference time (see: Eq.~\ref{attack_time}). 
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=.56\textwidth]{plots/combined/time.pdf}
%     \caption{Training, Prediction, and Attack times across datasets and hardware.}
%     \label{fig:time}
% \end{figure}

% \subsection{Power}
% The power consumption (Fig.~\ref{fig:power})  tracks monetary cost  (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it's unsurprising that cloud billing is colinear with this metric. Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).

% \subsection{Cost}
% \cm{TODO}

% \begin{figure}
%     \centering
%     \includegraphics[width=.5\textwidth]{plots/combined/power.pdf}
%     \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
%     \label{fig:power}
% \end{figure}

% \subsection{Partial Effects of Covariates}
% Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time. However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that increase the attack distance by an order of magnitude reduces the survival time marginally. Furthermore, Table~\ref{tab:Combined} shows that the log-logistic and log-normal distributions have similar predictive power, but we used the log-logistic model to render the plots due to its marginally improved AIC.

% \begin{figure}
%     \centering
%     \includegraphics[width=.5\textwidth]{plots/combined/cost.pdf}
%     \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
%     \label{fig:cost}
% \end{figure}

% \input{plots/combined/aft_comparison}
% %

% \begin{figure}[ht]
%   \centering
%   % include first image
%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
%   \caption{This depicts the partial effect of the training time on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
%   \label{fig:partial_effect_train_time}
% \end{figure}

% \begin{figure}
%   \centering
%   % include second image
%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_accuracy_partial_effect.pdf} 
%   \caption{This depicts the partial effect of the accuracy on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
%   \label{fig:partial_effect_accuracy}
% \end{figure}

% \begin{figure}
%   \centering
%   % include second image
%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_adv_failure_rate_partial_effect.pdf} 
%   \caption{This depicts the partial effect of the adversarial failure rate on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
%   \label{fig:partial_effect_adv_failure_rate}
% \end{figure}

% \begin{figure}
%   \centering
%   % include second image
%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}  
%   \caption{This depicts the partial effct of the attack distance on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
%   \label{fig:partial_effect_attack_eps}
% \end{figure}

% \section{Considerations}
%  We have taken much care to conduct these measurements as carefully as possible. Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for neural networks \cite{ma2022state}. Given the strong ( $>.5$) concordance results and uniformity across distributions in Table~\ref{tab:Combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance. Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning. \cm{While this obscures the effect of GPU parallelization, the result doesn't change since all metrics are measured on a particular piece of hardware for both the attacker and defender. If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.} In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above. Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth. However, we would like to note that the `inference-optimized' Nvidia 4-series GPUs are perfectly capable and affordable training machines. We restricted our search to only a single evasion attack (see: Eq.~\ref{eq:fgm}) in the interest of time (and therefore deployment cost), though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks. . 
%  % As an additional note, we forgot to store the Prometheus database on the PVC and the data only existed in an ephemeral Docker container, and we recommend against this design flaw in future deployments. Instead the Prometheus database should be mounted to the PVC or linked to an external database via the provided web interface. 
%  % In general, we chose to use a PVC rather than externally linked databases to minimize the differences between a single-machine implementation and the cloud deployment and allow our results to be generally reproducible on a developer's local machine, though this comes with the downside of having to interact with critical experiment data manually. Proper permissions management on the attached volume store can prevent any critical errors during downstream analysis, though the addition of some kind of searchable log store like \texttt{elasticsearch}\cite{gormley2015elasticsearch} in combination with artifact storage\cite{daher2018cloud} for the datasets, models, and attacks would be a welcome and obvious improvement.

% \section{Conclusion}
% In this work, we introduced survival analysis to machine learning, developed a method for quickly and efficiently test model parameter choices and to evaluate them in the presence of adversarial noise, allowing us the model the Pareto front as a function of tested model parameters. Using this technique, we showed that despite reduced run-times with newer and/or larger hardware, that adversarial robustness is not significantly effected and that the specific choice of attack parameters is far more important than model training time. Furthermore, we demonstrate the un-advertised training capability of the Nvidia L4 GPU which can get substantially similar results when compared to more expensive and power hungry hardware. However, the marginal run-time is significant, even if it's cost-effective.

% \bibliographystyle{IEEEtran}
% \bibliography{bibliography}
% \end{document}

### 2024-03-28 main.tex
update image references

@@
 
-\begin{figure}
-  \centering
-  % include first image
-  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
-  \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
+% \begin{figure}
+%   \centering
+%   % include first image
+%   \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
+%   \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
 The dotted line represents the baseline survival function $S_{ben}$.}
-  \label{fig:partial_effect_train_time}
-\end{figure}
+%   \label{fig:partial_effect_train_time}
+% \end{figure}
 
@@
   % include second image
-  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_accuracy_partial_effect.pdf} 
+  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_epochs_partial_effect.pdf} 
   \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
 The dotted line represents the baseline survival function $S_{ben}$.}
-  \label{fig:partial_effect_accuracy}
+  \label{fig:partial_effect_epochs}
 \end{figure}
@@
   % include second image
-  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_adv_failure_rate_partial_effect.pdf} 
+  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_batch_size_partial_effect.pdf} 
   \caption{TODO: replace this with epochs and batch size}
-  \label{fig:partial_effect_adv_failure_rate}
+  \label{fig:partial_effect_batch_size}
 \end{figure}

### 2024-03-28 plots/cifar/aft_comparison.tex
update image references

@@
 \midrule
-weibull & -1292.89 & 0.79 & 0.80 & -1292.89 & 0.20 & 0.67 \\
-cox & -- & 0.80 & 0.80 & -- & 0.12 & 0.11 \\
-log_logistic & -1474.32 & 0.79 & 0.79 & -1474.32 & 0.17 & 0.20 \\
-log_normal & -1459.29 & 0.79 & 0.79 & -1459.29 & 0.18 & 0.21 \\
+Weibull & -1292.89 & 0.79 & 0.80 & -1292.89 & 0.20 & 0.67 \\
+Cox & -- & 0.80 & 0.80 & -- & 0.12 & 0.11 \\
+Log Logistic & -1474.32 & 0.79 & 0.79 & -1474.32 & 0.17 & 0.20 \\
+Log Normal & -1459.29 & 0.79 & 0.79 & -1459.29 & 0.18 & 0.21 \\
 \bottomrule

### 2024-03-28 plots/cifar100/aft_comparison.tex
update image references

@@
 \midrule
-weibull & -1159.72 & 0.79 & 0.76 & -1159.72 & 0.21 & 0.21 \\
-cox & -- & 0.79 & 0.76 & -- & 0.13 & 0.13 \\
-log_logistic & -1313.15 & 0.78 & 0.77 & -1313.15 & 0.20 & 0.20 \\
-log_normal & -1299.38 & 0.79 & 0.77 & -1299.38 & 0.20 & 0.20 \\
+Weibull & -1159.72 & 0.79 & 0.76 & -1159.72 & 0.21 & 0.21 \\
+Cox & -- & 0.79 & 0.76 & -- & 0.13 & 0.13 \\
+Log Logistic & -1313.15 & 0.78 & 0.77 & -1313.15 & 0.20 & 0.20 \\
+Log Normal & -1299.38 & 0.79 & 0.77 & -1299.38 & 0.20 & 0.20 \\
 \bottomrule

### 2024-03-28 plots/mnist/aft_comparison.tex
update image references

@@
 \midrule
-weibull & -1631.26 & 0.90 & 0.89 & -1631.26 & 0.15 & 0.69 \\
-cox & -- & 0.90 & 0.89 & -- & 0.11 & 0.11 \\
-log_logistic & -1842.71 & 0.90 & 0.90 & -1842.71 & 0.14 & 0.19 \\
-log_normal & -1799.93 & 0.90 & 0.90 & -1799.93 & 0.14 & 0.29 \\
+Weibull & -1631.26 & 0.90 & 0.89 & -1631.26 & 0.15 & 0.69 \\
+Cox & -- & 0.90 & 0.89 & -- & 0.11 & 0.11 \\
+Log Logistic & -1842.71 & 0.90 & 0.90 & -1842.71 & 0.14 & 0.19 \\
+Log Normal & -1799.93 & 0.90 & 0.90 & -1799.93 & 0.14 & 0.29 \\
 \bottomrule

### 2024-03-29 plots/cifar100/aft_comparison.tex
update plots

--- 2023-12-13 plots/cifar100/aft_comparison.tex
@@
-\begin{table}
+\begin{table*}
 \caption{Comparison of AFR Models on the CIFAR100 dataset.}
@@
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
+ & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
 \midrule
-weibull & -361 & 0.845 & -361 & 0.331 & 0.179 \\
-cox & -- & 0.847 & -- & 0.238 & 0.162 \\
-log_logistic & -371 & 0.852 & -371 & 0.318 & 0.172 \\
-log_normal & -372 & 0.851 & -372 & 0.313 & 0.174 \\
+Weibull & -1159.72 & 0.79 & -1159.72 & 0.21 & 0.13 \\
+Cox & -- & 0.79 & -- & 0.13 & 0.07 \\
+Log Logistic & -1313.15 & 0.78 & -1313.15 & 0.20 & 0.12 \\
+Log Normal & -1299.38 & 0.79 & -1299.38 & 0.20 & 0.12 \\
 \bottomrule
 \end{tabular}
-\end{table}
+\end{table*}

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

--- 2023-12-13 plots/mnist/aft_comparison.tex
@@
-\begin{table}
+\begin{table*}
 \caption{Comparison of AFR Models on the MNIST dataset.}
@@
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
+ & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
 \midrule
-weibull & -778 & 0.886 & -778 & 0.238 & 0.204 \\
-cox & -- & 0.888 & -- & 0.185 & 0.201 \\
-log_logistic & -759 & 0.884 & -759 & 0.226 & 0.204 \\
-log_normal & -752 & 0.881 & -752 & 0.225 & 0.202 \\
+Weibull & -1631.26 & 0.90 & -1631.26 & 0.15 & 0.09 \\
+Cox & -- & 0.90 & -- & 0.11 & 0.05 \\
+Log Logistic & -1842.71 & 0.90 & -1842.71 & 0.14 & 0.08 \\
+Log Normal & -1799.93 & 0.90 & -1799.93 & 0.14 & 0.08 \\
 \bottomrule
 \end{tabular}
-\end{table}
+\end{table*}

### 2024-03-29 main.tex
Updates from Overleaf

@@
 \[
-	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty} t \cdot S_\theta(t) \,dt.
+	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty}  S_\theta(t) \,dt.
 \]
@@
 \cm{For AIC and BIC, that means choosing the smallest value.
-Concordance, however, is a number between $-1$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival}.
+Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and .5 reflects random chance.
 By evaluating $\mathbb{E}_{S_\theta}[T]$ for both adversarial and benign data, we can test the model under extreme perturbations and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}}
@@
 Therefore, a proper search would keep this dual-objective in mind.
-\cm{To optimize for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because of its ability to work in distributed settings,  while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}}.
+\cm{To optimize for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}}.
 
@@
 Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time.
-However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that and increase the attack distance by an order of magnitude reduces the survival time marginally.
-Additionally, we see that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.
+However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that and increasing the attack distance ($\varepsilon$) by an order of magnitude only marginally reduces the survival time.
+Additionally, that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.
 

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

--- 2023-12-13 plots/cifar/aft_comparison.tex
@@
-\begin{table}
+\begin{table*}
 \caption{Comparison of AFR Models on the CIFAR dataset.}
@@
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
+ & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
 \midrule
-weibull & -550 & 0.856 & -550 & 0.266 & 0.219 \\
-cox & -- & 0.856 & -- & 0.202 & 0.254 \\
-log_logistic & -562 & 0.857 & -562 & 0.258 & 0.215 \\
-log_normal & -568 & 0.857 & -568 & 0.258 & 0.216 \\
+Weibull & 527.37 & 0.72 & 527.37 & 1.83 & 0.97 \\
+Cox & -- & 0.73 & -- & 0.85 & 0.32 \\
+Log Logistic & 544.73 & 0.74 & 544.73 & 1.66 & 1.05 \\
+Log Normal & 532.28 & 0.74 & 532.28 & 1.61 & 1.05 \\
 \bottomrule
 \end{tabular}
-\end{table}
+\end{table*}

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1631.26 & 0.90 & -1631.26 & 0.15 & 0.09 \\
-Cox & -- & 0.90 & -- & 0.11 & 0.05 \\
-Log Logistic & -1842.71 & 0.90 & -1842.71 & 0.14 & 0.08 \\
-Log Normal & -1799.93 & 0.90 & -1799.93 & 0.14 & 0.08 \\
+Weibull & 133.22 & 0.80 & 133.22 & 2.10 & 0.81 \\
+Cox & -- & 0.80 & -- & 0.63 & 0.28 \\
+Log Logistic & 93.77 & 0.77 & 93.77 & 1.22 & 0.82 \\
+Log Normal & 104.95 & 0.76 & 104.95 & 1.21 & 0.84 \\
 \bottomrule

### 2024-03-29 plots/cifar100/aft_comparison.tex

@@
 \midrule
-Weibull & -1159.72 & 0.79 & -1159.72 & 0.21 & 0.13 \\
-Cox & -- & 0.79 & -- & 0.13 & 0.07 \\
-Log Logistic & -1313.15 & 0.78 & -1313.15 & 0.20 & 0.12 \\
-Log Normal & -1299.38 & 0.79 & -1299.38 & 0.20 & 0.12 \\
+Weibull & 124.83 & 0.66 & 124.83 & 0.98 & 0.92 \\
+Cox & -- & 0.67 & -- & 0.34 & 0.29 \\
+Log Logistic & 80.29 & 0.68 & 80.29 & 0.98 & 0.95 \\
+Log Normal & 76.14 & 0.67 & 76.14 & 0.98 & 0.95 \\
 \bottomrule

### 2024-03-29 main.tex
Updates from Overleaf

--- 2024-03-28 main.tex
@@
 
-\cm{I will cut this accuracy subsection. In exchange, I will conduct a log-rank test}
 \subsection{Accuracy}
-Fig.~\ref{fig:acc} shows the advernsarial and benign accuracies for all datasets and hardware.
+Fig.~\ref{fig:acc} shows the adversarial (right) and benign (left) accuracies for all datasets and hardware.
 It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware though CIFAR10 has worse benign performance and CIFAR100 has substantially worse adversarial performance.
@@
 \subsection{Time}
-Fig.~\ref{fig:time} reveals the training time.
+Fig.~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models.
 Slower hardware (see Memory Bandwidth in Tab.~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
 This should be no surprise since the less-capable hardware is meant to be used exclusively for inference.
-Additionally, the attack time increases with both the training and prediction times across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).
+Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/time.pdf}
+    \includegraphics[width=0.5\textwidth,clip]{plots/combined/time.pdf}
     \caption{Training, Prediction, and Attack times across datasets and hardware.}
@@
     \centering
-    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/power.pdf}
+    \includegraphics[width=0.5\textwidth,clip]{plots/combined/power.pdf}
     \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
@@
     \centering
-    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/cost.pdf}
+    \includegraphics[width=0.5\textwidth,clip]{plots/combined/cost.pdf}
     \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}

### 2024-03-29 main.tex

@@
 
-\begin{figure}[h!]
+\begin{figure*}[h]
     \centering
-    \includegraphics[width=0.5\textwidth,clip]{plots/combined/time.pdf}
+    \includegraphics[width=.7\textwidth,clip]{plots/combined/time.pdf}
     \caption{Training, Prediction, and Attack times across datasets and hardware.}
     \label{fig:time}
-\end{figure}
+\end{figure*}
 
 \subsection{Power}
-The power consumption, illustrated in Fig.~\ref{fig:power}, tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric.
+The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Fig.~\ref{fig:power}. It is clearly obvious that training is several orders of m
+
+It tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric.
 Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).
 
-\begin{figure}[h!]
+\begin{figure*}[h]
     \centering
-    \includegraphics[width=0.5\textwidth,clip]{plots/combined/power.pdf}
+    \includegraphics[width=0.7\textwidth,clip]{plots/combined/power.pdf}
     \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
     \label{fig:power}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-    \includegraphics[width=0.5\textwidth,clip]{plots/combined/cost.pdf}
     \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
     \label{fig:cost}
-\end{figure}
+\end{figure*}
 

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & 527.37 & 0.72 & 527.37 & 1.83 & 0.97 \\
-Cox & -- & 0.73 & -- & 0.85 & 0.32 \\
-Log Logistic & 544.73 & 0.74 & 544.73 & 1.66 & 1.05 \\
-Log Normal & 532.28 & 0.74 & 532.28 & 1.61 & 1.05 \\
+Weibull & -1292.89 & 0.79 & -1292.89 & 0.20 & 0.11 \\
+Cox & -- & 0.80 & -- & 0.12 & 0.06 \\
+Log Logistic & -1474.32 & 0.79 & -1474.32 & 0.17 & 0.10 \\
+Log Normal & -1459.29 & 0.79 & -1459.29 & 0.18 & 0.11 \\
 \bottomrule

### 2024-03-29 main.tex

@@
 
-\begin{figure}
-    \caption{Survival Analysis for ML}
+\begin{figure}[h!]
+    \caption{\textbf{Algorithm: }Survival Analysis for ML}
     \label{fig:alg}
@@
     \centering
-    \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
+    \includegraphics[width=.35\textwidth]{plots/experiment.pdf}
     \caption{Experimental Pipeline Diagram}
@@
 
-\subsection{Comparative Risk}
+\subsection{Marginal Risk}
 \cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice.
@@
 \[
-    \textrm{Comparative~Risk} := \frac{\% \Delta S(t)}{\% \Delta C_a},
+    \textrm{Comparative~Risk} := \frac{ \Delta S(t)}{\Delta C_a},
 \]
-where $\% \Delta$ reflects the percent change from the control model.}
+where $\Delta$ reflects the change from the control model.}
 
@@
 For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack.
-Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time.
-The inference time and training time were used to conduct the cost analysis outlined in the next section (Sec.~\ref{cost})
+Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
+The inference time and training time were used to conduct the cost analysis outlined in the next section (Sec.~\ref{cost}).
 
@@
 \subsection{Survival Analysis}
-In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the funciton, $S(t)$.
-We attempted adding dummy variables for hardware (\textit{e.g.}, peak power and peak bandwidth) as well as the datasets (\textit{e.g.}, resolution, bit depth, and number of color channels), but each of these were strongly co-linear with training time and hindered modelling.
-As such, they were not included.
+In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the function, $S(t)$.
 To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}.
@@
 
+\begin{figure*}[h]
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
+        \caption{Training, Prediction, and Attack times}
+        \label{fig:time}
+    \end{subfigure}
+    \begin{subfigure}[b]{.8\textwidth}
+        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
+        \caption{Training, Prediction, and Attack Power Consumption}
+        \label{fig:power}
+    \end{subfigure}
+    \begin{subfigure}[b]{.8\textwidth}
+        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
+        \caption{Training, Prediction, and Attack Monetary Cost}
+        \label{fig:cost}
+    \end{subfigure}
+    \caption{Combined Figures}
+\end{figure*}
+
 \subsection{Time}
@@
 
-\begin{figure*}[h]
-    \centering
-    \includegraphics[width=.7\textwidth,clip]{plots/combined/time.pdf}
-    \caption{Training, Prediction, and Attack times across datasets and hardware.}
-    \label{fig:time}
-\end{figure*}
-
 \subsection{Power}
@@
 Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).
-
-\begin{figure*}[h]
-    \centering
-    \includegraphics[width=0.7\textwidth,clip]{plots/combined/power.pdf}
-    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
-    \label{fig:power}
-\end{figure*}
 
@@
 
-\begin{figure*}
-    \centering
-    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
-    \label{fig:cost}
-\end{figure*}
+\subsection{AFR Models}
 
-\subsection{AFR Models}
-\cm{TODO: add 1.
-fitted parameters and 2.
-their statistical significance here.
-Discuss what that means.
-Move table here.
-Discuss why we chose Log-Logistic.
-Discuss accelerated failure assumption again.}
-
-Table~\ref{tab:Combined} shows that the aft models using log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render the plots due to its marginally improved AIC.
-
+Table~\ref{tab:Combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
+It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render partial effect due to its marginally improved AIC.
 \input{plots/combined/aft_comparison}
 
-\cm{Figure TODO shows the p-values for each of the covariates}
-
 Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time.
-However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that and increasing the attack distance ($\varepsilon$) by an order of magnitude only marginally reduces the survival time.
+However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, increasing the attack distance ($\varepsilon$) by an order of magnitude only marginally reduces the survival time (y-axis).
 Additionally, that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.
@@
 %   % include first image
-%   \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
+%   \includegraphics[width=0.8\linewidth,clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
 %   \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
@@
 
-\begin{figure}
+\begin{figure}[h!]
     \centering
-  % include second image
-  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}  
-  \caption{The partial effect of the attack distance on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
-The dotted line represents the baseline survival function $S_{ben}$.}
-  \label{fig:partial_effect_attack_eps}
+    \begin{subfigure}[b]{\linewidth}
+        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
+        \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_aft.pdf}
+        \caption{Coefficients of the Covariates}
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_batch_size_partial_effect.pdf}
+        \caption{Batch Size Partial Effect}
+    \end{subfigure}
+    \caption{This shows the partial effects plots for}
 \end{figure}
 
-\begin{figure}
-  \centering
-  % include second image
-  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_epochs_partial_effect.pdf} 
-  \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
+%   \caption{The partial effect of the attack distance on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
 The dotted line represents the baseline survival function $S_{ben}$.}
-  \label{fig:partial_effect_epochs}
-\end{figure}
+%   \label{fig:partial_effect_attack_eps}
+% \end{figure}
 
-\begin{figure}
-  \centering
-  % include second image
-  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_batch_size_partial_effect.pdf} 
-  \caption{TODO: replace this with epochs and batch size}
-  \label{fig:partial_effect_batch_size}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   % include second image
+%   \begin{subfigure}
+
+%   \end{subfigure}
+%   \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
+The dotted line represents the baseline survival function $S_{ben}$.}
+%   \label{fig:partial_effect_epochs}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   % include second image
+
+%   \caption{TODO: replace this with epochs and batch size}
+%   \label{fig:partial_effect_batch_size}
+% \end{figure}
 

### 2024-03-29 main.tex

@@
 
-Below, we demonstrate the effect of hardware and dataset on the benign/adversarial accuracy (Fig.~\ref{fig:acc}), training/inference/attack time (Fig.~\ref{fig:time}), and both monetary (Fig.~\ref{fig:cost}) and power (Fig.~\ref{fig:power}) costs for training/inference/attacks.
-We also compared all three survival times outlined in Sec.~\ref{afr} using the criteria outlined in the same section.
-Using the best-fit function (again, see Sec.~\ref{afr}), we examined the effect of the covariates on the survival time of the model (Figs.~\ref{fig:partial_effect_train_time}-\ref{fig:partial_effect_attack_eps}).
+In this section, we display and discuss the results for all of the experiments across all datasets and hardware. First, we discuss the measured data in Secs.~\ref{res:acc}-\ref{res:cost}.
 
 \subsection{Accuracy}
+\label{res:acc}
 Fig.~\ref{fig:acc} shows the adversarial (right) and benign (left) accuracies for all datasets and hardware.
@@
     \end{subfigure}
-    \caption{Combined Figures}
+    \caption{The run-times, power consumption, and monetary cost of training, prediction, and attack generation across all hardwware and datasets.}
 \end{figure*}
@@
 Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).
+We can also see that training takes slightly more than than attack generation, when we normalize by the number of samples.
 
 \subsection{Power}
-The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Fig.~\ref{fig:power}. It is clearly obvious that training is several orders of m
-
+The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Fig.~\ref{fig:power}.
 It tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric.
@@
 \subsection{Cost}
+\label{res:cost}
 The monetary cost for each dataset and each piece of hardware is shown in Fig.~\ref{fig:cost}.
@@
 \subsection{AFR Models}
-
+\label{res:afr}
 Table~\ref{tab:Combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
@@
 
-Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time.
-However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, increasing the attack distance ($\varepsilon$) by an order of magnitude only marginally reduces the survival time (y-axis).
-Additionally, that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.
-
-% \begin{figure}
-%   \centering
-%   % include first image
-%   \includegraphics[width=0.8\linewidth,clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
-%   \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
-The dotted line represents the baseline survival function $S_{ben}$.}
-%   \label{fig:partial_effect_train_time}
-% \end{figure}
-
 \begin{figure}[h!]
@@
     \begin{subfigure}[b]{\linewidth}
-        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
-        \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
+        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \caption{Batch Size Partial Effect}
     \end{subfigure}
@@
     \begin{subfigure}[b]{\linewidth}
-        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_batch_size_partial_effect.pdf}
-        \caption{Batch Size Partial Effect}
+        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
+        \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
     \end{subfigure}
@@
 \end{figure}
-
-%   \caption{The partial effect of the attack distance on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
-The dotted line represents the baseline survival function $S_{ben}$.}
-%   \label{fig:partial_effect_attack_eps}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   % include second image
-%   \begin{subfigure}
-
-%   \end{subfigure}
-%   \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}.
-The dotted line represents the baseline survival function $S_{ben}$.}
-%   \label{fig:partial_effect_epochs}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   % include second image
-
-%   \caption{TODO: replace this with epochs and batch size}
-%   \label{fig:partial_effect_batch_size}
-% \end{figure}
 

### 2024-03-29 main.tex

@@
 \label{res:afr}
-Table~\ref{tab:Combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
+Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
 It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render partial effect due to its marginally improved AIC.
@@
     \begin{subfigure}[b]{\linewidth}
-        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
-        \caption{Batch Size Partial Effect}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \caption{Plot depicting the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis).}
     \end{subfigure}
     \begin{subfigure}[b]{\linewidth}
-        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_aft.pdf}
-        \caption{Coefficients of the Covariates}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_aft.pdf}
+        \caption{Coefficients of the Covariates for the Log Logistic AFR model}
     \end{subfigure}
     \begin{subfigure}[b]{\linewidth}
-        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
         \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
@@
 \end{figure}
-
-\subsection{Comparative Risk}
-\cm{TODO}
-Call back to the comparative risk and the fast rejection mechanism.
 

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

--- 2024-03-29 plots/cifar/aft_comparison.tex
@@
 \begin{table*}
+\centering
 \caption{Comparison of AFR Models on the CIFAR dataset.}
 \label{tab:cifar}
-\begin{tabular}{llrlrr}
+\begin{tabular}{lllrrrr}
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
 \midrule
-Weibull & 527.37 & 0.72 & 527.37 & 1.83 & 0.97 \\
-Cox & -- & 0.73 & -- & 0.85 & 0.32 \\
-Log Logistic & 544.73 & 0.74 & 544.73 & 1.66 & 1.05 \\
-Log Normal & 532.28 & 0.74 & 532.28 & 1.61 & 1.05 \\
+Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.00 & 0.00 \\
+Cox & -- & -- & 0.80 & 0.80 & 0.00 & 0.00 \\
+Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.01 & 0.00 \\
+Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.01 & 0.00 \\
 \bottomrule

### 2024-03-29 plots/cifar100/aft_comparison.tex
update plots

@@
 \begin{table*}
+\centering
 \caption{Comparison of AFR Models on the CIFAR100 dataset.}
 \label{tab:cifar100}
-\begin{tabular}{llrlrr}
+\begin{tabular}{lllrrrr}
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
 \midrule
-Weibull & 124.83 & 0.66 & 124.83 & 0.98 & 0.92 \\
-Cox & -- & 0.67 & -- & 0.34 & 0.29 \\
-Log Logistic & 80.29 & 0.68 & 80.29 & 0.98 & 0.95 \\
-Log Normal & 76.14 & 0.67 & 76.14 & 0.98 & 0.95 \\
+Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.00 & 0.00 \\
+Cox & -- & -- & 0.79 & 0.76 & 0.00 & 0.00 \\
+Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.01 & 0.00 \\
+Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.01 & 0.00 \\
 \bottomrule

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

@@
 \begin{table*}
+\centering
 \caption{Comparison of AFR Models on the MNIST dataset.}
 \label{tab:mnist}
-\begin{tabular}{llrlrr}
+\begin{tabular}{lllrrrr}
 \toprule
- & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
 \midrule
-Weibull & 133.22 & 0.80 & 133.22 & 2.10 & 0.81 \\
-Cox & -- & 0.80 & -- & 0.63 & 0.28 \\
-Log Logistic & 93.77 & 0.77 & 93.77 & 1.22 & 0.82 \\
-Log Normal & 104.95 & 0.76 & 104.95 & 1.21 & 0.84 \\
+Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.00 & 0.00 \\
+Cox & -- & -- & 0.90 & 0.89 & 0.00 & 0.00 \\
+Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.00 & 0.00 \\
+Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.00 & 0.00 \\
 \bottomrule

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.00 & 0.00 \\
-Cox & -- & -- & 0.80 & 0.80 & 0.00 & 0.00 \\
-Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.01 & 0.00 \\
-Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.01 & 0.00 \\
+Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.02 & 0.02 \\
+Cox & -- & -- & 0.80 & 0.80 & 0.14 & 0.16 \\
+Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.07 & 0.07 \\
+Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.11 & 0.11 \\
 \bottomrule

### 2024-03-29 plots/cifar100/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.00 & 0.00 \\
-Cox & -- & -- & 0.79 & 0.76 & 0.00 & 0.00 \\
-Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.01 & 0.00 \\
-Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.01 & 0.00 \\
+Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.01 & 0.01 \\
+Cox & -- & -- & 0.79 & 0.76 & 0.16 & 0.16 \\
+Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.08 & 0.08 \\
+Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.11 & 0.12 \\
 \bottomrule

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.00 & 0.00 \\
-Cox & -- & -- & 0.90 & 0.89 & 0.00 & 0.00 \\
-Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.00 & 0.00 \\
-Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.00 & 0.00 \\
+Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.01 & 0.01 \\
+Cox & -- & -- & 0.90 & 0.89 & 0.01 & 0.01 \\
+Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.08 & 0.06 \\
+Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.13 & 0.13 \\
 \bottomrule

### 2024-03-29 main.tex

@@
 Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
-We address the problem of neural network validation and verification --- more specifically, we address the problem of continuous integration and deployment for safety-critical models in a cloud-native environment.
+\cm{In this paper, we use survival analysis to present a time-efficient and formal method for predicting model performance in the presence of adversarial noise.}
 For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, \cm{so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data.
@@
 Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
-\cm{Statistical learning theory \cite{} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
+\cm{Statistical learning theory \cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
 To overcome this, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has  yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
@@
 
-\cm{Modern neural networks are massive--they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}}.
+\cm{Modern neural networks are massive--- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}}.
 One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
@@
 Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern \cm{since inducing a failure at run-time has consistently shown to be trivial}~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
-Collecting, labelling, and testing a new set of data for every software change --- as required by law --- would be prohibitively expensive.
+Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive.
 Therefore, a new evaluation methodology is required.
@@
 
-\cm{The methodology outlined in Section~\ref{afr} allows the model-builder to minimize the training cost, optimize for adversarial robustness, and estimate the partial effects of covariates on model performance during routine training procedures.
-We then demonstrate the efficacy of this methodology in Section~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Section~\ref{experiments}.}
+\cm{In this paper, we use accelerated methods to predict model performance as a function of various model parameters.
+The methodology outlined in Sec.~\ref{afr} allows the model-builder to minimize the training cost, optimize for adversarial robustness, estimate the partial effects of covariates on model performance during routine training procedures, and perform a cost analysis (Sec.~\ref{cost}).
+We then demonstrate the efficacy of this methodology in Sec.~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Sec.~\ref{experiments}.}
 
@@
 \begin{itemize}
-    \item optimizes for benign and adversarial accuracy simultaneously,
-    \item extends survival analysis to the realm of neural networks, 
-    \item demonstrates a scalable and effective method that trains a model while simultaneously estimating the asymptotic effect of various hyperparameters, and
-    \item measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
-    \item and demonstrates that, despite a decrease in training time, that faster hardware, \cm{hardware with more bit-depth}, and/or more power-hungry hardware do not lead to more adversarially robust models.
-
+    \item Optimizes for benign and adversarial accuracy simultaneously,
+    \item Extends survival analysis to the realm of neural networks, 
+    \item Demonstrates a scalable and effective method that trains a model while simultaneously estimating the asymptotic effect of various hyperparameters, and
+    \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.   
 \end{itemize}
 
-\cm{Section~\ref{background} defines terms used throughout the paper.
-Section~\ref{afr} outlines the training and evaluation methodology presented in this paper.
+\cm{Sec.~\ref{background} defines terms used throughout the paper.
+Sec.~\ref{afr} outlines the training and evaluation methodology presented in this paper.
 Section ~\ref{cost} outlines the resulting cost analysis framework, arising from the methodology in the previous section.
-Section~\ref{experiments} outlines the software components and specific experiments that were conducted, while Section~\ref{results} contains the results and discussions of those experiments.
-Section~\ref{considerations} and Section~\ref{conclusion} reveal the caveats and the conclusions respectively.}
+Sec.~\ref{experiments} outlines the software components and specific experiments that were conducted, while Sec.~\ref{results} contains the results and discussions of those experiments.
+Sec.~\ref{considerations} and Sec.~\ref{conclusion} reveal the caveats and the conclusions respectively.}
 
@@
 \end{equation}
-Additionally, one can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accuracy}.
+Additionally, one can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accuracy} which is Eq.~\ref{eq:acc} calculated on the perturbed samples.
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
@@
     \EndWhile
-    \State \textbf{Fit Accelerated Model, $S_{adv}$} using $\lambda_{adv}$ and $T_a$
+    \State \textbf{Fit Accelerated Failure Rate Model, $S_{adv}$} using $\lambda_{adv}$ and $T_a$
     \State \textbf{Fit Benign Model, $S_{ben}$} using $\lambda_{ben}$ and $T_i$
@@
 $$
-    T_t := t_t * n  * m.
+    T_t := t_t \cdot n  \cdot m.
 $$
@@
 $$
-    T_i := t_i *n,
+    T_i := t_i \cdot n,
 $$
@@
     \label{attack_time}
-    T_a := t_i *n *i.
+    T_a := t_i \cdot n \cdot i.
 \end{equation}
@@
 $$
-    C_t = C_h *T_t,
+    C_t = C_h \cdot T_t,
     \label{eq:cost_training}
@@
 $$
-    C_i = C_h *T_i,
+    C_i = C_h \cdot T_i,
     \label{eq:cost_inference}
@@
 $$
-    C_a = C_h * T_a.
+    C_a = C_h \cdot T_a.
     \label{eq:cost_attack}
@@
 $$
-    P_t = P_h *T_t,
+    P_t = P_h \cdot T_t,
     \label{eq:power_training}
@@
 $$
-    P_i = P_h *T_i,
+    P_i = P_h \cdot T_i,
     \label{eq:power_inference}
@@
 $$
-    P_a = P_h *T_a.
+    P_a = P_h \cdot T_a.
     \label{eq:power_attack}
@@
 
-\subsection{Marginal Risk}
-\cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice.
+\subsection{Why Cost Matters}
+% \cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice.
 The \textit{marginal risk} is the change in survival time divided by change in attack compared to some control model such that:
-\[
-    \textrm{Comparative~Risk} := \frac{ \Delta S(t)}{\Delta C_a},
-\]
-where $\Delta$ reflects the change from the control model.}
+% \[
+%     \textrm{Marginal~Risk} := \frac{ \Delta S(t)}{\Delta C_a},
+% \]
+% where $\Delta$ reflects the change from the control model.}
 
-\cm{Another advantage is that we can quickly discard ineffective model choices with this method.} In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
+ In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
 \cm{In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
@@
 
-This section outlines specific implementation details for the evaluation of the methodology outlined in Section~\ref{afr}.
+This section outlines specific implementation details for the evaluation of the methodology outlined in Sec.~\ref{afr}.
 
@@
 \subsection{Attacks}
-Since one goal of this paper was to evaluate how hardware and deployment cost affect adversarial robustness during run-time, we focused on evasion attacks since they induce failures by adding noise to the data at run-time.
+Since we are examining the effect of model parameters at run-run, we focused on evasion attacks since they induce failures by adding noise to the data at the inference stage.
 Prior research~\cite{meyers} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
@@
 To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}.
-We also compared the chosen modelling functions (see Section~\ref{afr}).
-These results can be found in Section~\ref{results}.
+We also compared the chosen modelling functions (see Sec.~\ref{afr}).
+These results can be found in Sec.~\ref{results}.
 
@@
 Fig.~\ref{fig:acc} shows the adversarial (right) and benign (left) accuracies for all datasets and hardware.
-It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware though CIFAR10 has worse benign performance and CIFAR100 has substantially worse adversarial performance.
+It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware.
+Benign accuracy decreases with resolution (CIFAR10 vs MNIST) or with the number of classes (CIFAR10 vs CIFAR100).
 For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (e.g.
@@
 \label{res:afr}
+\cm{
 Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
-It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render partial effect due to its marginally improved AIC.
+It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but below we examine the log-logistic model due to its improved AIC.
+Fig.~\ref{fig:qq} compares the AFR-predicted failures with the empirical failures.
+We can see that the model is largely effective, though becomes less effective as the number of failures increases.
+It is, however, very precise when measuring a small number of failures, which is far more important for safety-critical design.
+}
 \input{plots/combined/aft_comparison}
+\cm{
+Fig.~\ref{fig:aft} shows the log-scale coefficients for the AFR model.
+It shows that epochs, batch size, and training time have no effect on the survival time.
+Additionally, it reveals this for the random state variable, which is expected.
+However, we can clearly see that inference time (e.g.
+how long it takes to query the model) is as strong an indicator as the attack noise distance, revealing that model speed is at least as important as the attack itself.
+Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance).
+}
+\cm{
+Using the $S(t)$ described in Sec.~\ref{afr}, we can model the partial effect of various hardware devices, which is depicted in Fig.~\ref{fig:partial}.
+It clearly shows that hardware choice has no bearing on robustness, despite the disparity in cost outlined in Table~\ref{tab:hardware}.
+}
 
@@
         \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
-        \caption{Plot depicting the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis).}
+        \caption{Plot depicting the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
+        \label{fig:qq}
     \end{subfigure}
@@
         \caption{Coefficients of the Covariates for the Log Logistic AFR model}
+        \label{fig:aft}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
-        \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_device_num_partial_effect.pdf}
+        \caption{Partial Effect  of $\varepsilon$ on $S(t)$ }
+        \label{fig:partial}
     \end{subfigure}
@@
 Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for maximum likelihood learning~\cite{ma2022state}.
-Given the strong ($>0.5$) concordance results and uniformity across AFR functions in Table~\ref{tab:Combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+Given the strong ($>0.5$) concordance results and uniformity across AFR functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning.
@@
 \label{conclusion}
-In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and to evaluate them in the presence of adversarial noise, allowing us the model performance as a function of tested model parameters.
+In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing us the model performance as a function of tested model parameters.
 Using this technique, we showed that despite reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.02 & 0.02 \\
-Cox & -- & -- & 0.80 & 0.80 & 0.14 & 0.16 \\
-Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.07 & 0.07 \\
-Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.11 & 0.11 \\
+Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.02 & 0.00 \\
+Cox & -- & -- & 0.80 & 0.80 & 0.01 & 0.00 \\
+Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.01 & 0.00 \\
+Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.01 & 0.00 \\
 \bottomrule

### 2024-03-29 plots/cifar100/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.01 & 0.01 \\
-Cox & -- & -- & 0.79 & 0.76 & 0.16 & 0.16 \\
-Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.08 & 0.08 \\
-Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.11 & 0.12 \\
+Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.00 & 0.00 \\
+Cox & -- & -- & 0.79 & 0.76 & 0.02 & 0.00 \\
+Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.01 & 0.00 \\
+Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.00 & 0.00 \\
 \bottomrule

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.01 & 0.01 \\
-Cox & -- & -- & 0.90 & 0.89 & 0.01 & 0.01 \\
-Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.08 & 0.06 \\
-Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.13 & 0.13 \\
+Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.02 & 0.00 \\
+Cox & -- & -- & 0.90 & 0.89 & 0.03 & 0.00 \\
+Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.02 & 0.00 \\
+Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.01 & 0.00 \\
 \bottomrule

### 2024-03-30 plots/cifar/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.02 & 0.00 \\
-Cox & -- & -- & 0.80 & 0.80 & 0.01 & 0.00 \\
-Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.01 & 0.00 \\
-Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.01 & 0.00 \\
+Weibull & -1.23e+03 & -1.23e+03 & 0.79 & 0.8 & 0.02 & 0 \\
+Cox & -- & -- & 0.8 & 0.8 & 0.01 & 0 \\
+Log Logistic & -1.34e+03 & -1.34e+03 & 0.79 & 0.79 & 0.01 & 0 \\
+Log Normal & -1.39e+03 & -1.39e+03 & 0.79 & 0.79 & 0.01 & 0 \\
 \bottomrule

### 2024-03-30 plots/cifar100/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.00 & 0.00 \\
-Cox & -- & -- & 0.79 & 0.76 & 0.02 & 0.00 \\
-Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.01 & 0.00 \\
-Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.00 & 0.00 \\
+Weibull & -1.11e+03 & -1.11e+03 & 0.78 & 0.76 & 0 & 0 \\
+Cox & -- & -- & 0.79 & 0.76 & 0.02 & 0 \\
+Log Logistic & -1.2e+03 & -1.2e+03 & 0.78 & 0.77 & 0.01 & 0 \\
+Log Normal & -1.24e+03 & -1.24e+03 & 0.79 & 0.77 & 0 & 0 \\
 \bottomrule

### 2024-03-30 plots/mnist/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.02 & 0.00 \\
-Cox & -- & -- & 0.90 & 0.89 & 0.03 & 0.00 \\
-Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.02 & 0.00 \\
-Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.01 & 0.00 \\
+Weibull & -1.56e+03 & -1.56e+03 & 0.9 & 0.9 & 0.02 & 0 \\
+Cox & -- & -- & 0.9 & 0.89 & 0.03 & 0 \\
+Log Logistic & -1.67e+03 & -1.67e+03 & 0.9 & 0.9 & 0.02 & 0 \\
+Log Normal & -1.71e+03 & -1.71e+03 & 0.9 & 0.9 & 0.01 & 0 \\
 \bottomrule

### 2024-03-30 main.tex

@@
 
-This section outlines specific implementation details for the evaluation of the methodology outlined in Sec.~\ref{afr}.
+This section outlines specific implementation details for the evaluation of the survival analysis methodology outlined in Sec.~\ref{afr} and the cost analysis methodology outlined in Sec~\ref{cost}.
 
@@
 Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
-The inference time and training time were used to conduct the cost analysis outlined in the next section (Sec.~\ref{cost}).
 
@@
     \end{subfigure}
-    \caption{The run-times, power consumption, and monetary cost of training, prediction, and attack generation across all hardwware and datasets.}
+    \caption{The all cost metrics for all hardware and datasets.}
 \end{figure*}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
-        \caption{Plot depicting the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
+        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_qq.pdf}
+        \caption{The red line depicts the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
         \label{fig:qq}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_aft.pdf}
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_aft.pdf}
         \caption{Coefficients of the Covariates for the Log Logistic AFR model}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_device_num_partial_effect.pdf}
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_device_num_partial_effect.pdf}
         \caption{Partial Effect  of $\varepsilon$ on $S(t)$ }

### 2024-03-30 main.tex
Updates from Overleaf

@@
 Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
-\cm{In this paper, we use survival analysis to present a time-efficient and formal method for predicting model performance in the presence of adversarial noise.}
+\cm{In this paper, we use survival analysis to present a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.}
 For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, \cm{so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data.
@@
 The loss function is denoted by $L(y, \hat{y})$.
-
 Because of the complexity of modern machine learning models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset of the training samples.
@@
 \end{equation}
-where the gradient is approximated using a subset of samples and $\eta$ is a \textit{learning rate} (or step size) that is tuned to the particular model.
+where the gradient is approximated using $b$ batches per epoch and $\eta$ is a \textit{learning rate} (or step size) that is tuned to the particular model.
 
@@
 \begin{algorithmic}
-    \Require Samples $x $ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x)$, and a number of trials, $n$, where the subscripts $t,i$ refer to the respective value for either the train and test sets.
+    \Require Samples $x$ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and a number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, e.g.
+$N_t$ is size of the training set.
     \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
@@
     \While{ $i < n$}
-    \State \textbf{Optimise $\theta$} according to some method (e.g Eq.~\ref{eq:sgd}).
-    \State Record Training Time, $ T_t[i] $
-    \State \textbf{Model Inference:} Compute $ \hat{y_i} = K(x_i, \theta) $
-    \State Record Inference Time $ T_i[i] $
-    \State \textbf{Benign Accuracy:} Calculate $\lambda_{ben}[i]$ using Eq.~\ref{eq:acc}
-    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}
-    \State Record attack generation time, $T_a[i]$
-    \State \textbf{Model Inference:} Compute $ y' = K(x_a, \theta) $
-    \State \textbf{Adversarial Accuracy:} Calculate $\lambda_{adv}[i]$ with Eq.~\ref{eq:acc}
-    \State \textbf{Append} accuracies and times to their respective arrays.
+    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
+    \State \textbf{Optimise $\theta$:} over $x_t$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
+    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
+    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
+    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
+    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
+    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
+    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
+    \State \textbf{Infer:}  $ y' = K(x_a, \theta) $.
+    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc})
     \EndWhile
-    \State \textbf{Fit Accelerated Failure Rate Model, $S_{adv}$} using $\lambda_{adv}$ and $T_a$
-    \State \textbf{Fit Benign Model, $S_{ben}$} using $\lambda_{ben}$ and $T_i$
-    \Ensure$ S_{adv} \approx  \phi S_{ben}(\phi t)$
-    \Return $S_{adv}$
+    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates, $N_a$ is the attack size array.
+    \State \textbf{Return:} $S_{\theta}$
 \end{algorithmic}
@@
 
-To choose a best-fit from the possible AFR functions, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}.
+To choose a best-fit from the possible AFR functions, one should prepare the collected metrics, parameters, scores and/or meta data.
+
+Then, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}.
 \cm{For AIC and BIC, that means choosing the smallest value.
 Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and .5 reflects random chance.
-By evaluating $\mathbb{E}_{S_\theta}[T]$ for both adversarial and benign data, we can test the model under extreme perturbations and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}}
+By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}.
+In addition, one should measure the integrated calibration index (ICI) the error at the median (E50)~\cite{ici}.
+These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively ~\cite{ici}.
+Then, one should plot all the expected and observed values for all three functions according to the method described by Austin et al.~\cite{ici}.}
 
@@
 $$
-where $m$ is the number of epochs and $*$ is normal scalar multiplication.
+where $m$ is the number of epochs.
 
@@
     \label{attack_time}
-    T_a := t_i \cdot n \cdot i.
+    T_a := t_a \cdot n \cdot i.
 \end{equation}
@@
 % \[
-%     \textrm{Marginal~Risk} := \frac{ \Delta S(t)}{\Delta C_a},
+%     \textrm{Marginal~Risk} := \frac{ \Delta S_{\theta}(t)}{\Delta C_a},
 % \]
@@
 \subsection{Survival Analysis}
-In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the function, $S(t)$.
+In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the function, $S_{\theta}(t)$.
 To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}.
@@
 
-In this section, we display and discuss the results for all of the experiments across all datasets and hardware. First, we discuss the measured data in Secs.~\ref{res:acc}-\ref{res:cost}.
+In this section, we display and discuss the results for all of the experiments across all datasets and hardware.
+First, we discuss the measured data in Secs.~\ref{res:acc}-\ref{res:cost} before discussing the fitted AFR model in Sec.~\ref{res:afr}.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth,trim={30pt 0 10pt 0},clip]{plots/combined/acc.pdf}
+    \includegraphics[width=0.5\textwidth,clip]{plots/combined/acc.pdf}
     \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
@@
     \end{subfigure}
-    \caption{The all cost metrics for all hardware and datasets.}
+    \caption{The all cost metrics for all hardware and datasets. For these plots, the y-axes have been scaled by the the number of samples for the sake of comparison.}
 \end{figure*}
 
-\subsection{Time}
+\subsection{Time, Power, Cost}
+\label{res:cost}
 Fig.~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models.
@@
 
-\subsection{Power}
 The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Fig.~\ref{fig:power}.
@@
 
-\subsection{Cost}
-\label{res:cost}
 The monetary cost for each dataset and each piece of hardware is shown in Fig.~\ref{fig:cost}.
 \cm{For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
-In the best case scenario, they are comparable.
-However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
-This reveals an essential advantage for the attacker on the reference model and hardware architecture --- attacks consistently succeed with 100s of samples while model training requires orders of magnitude more.}
+In the best case scenario, they are comparable, but attacks consistently succeed with 100s of samples while model training requires orders of magnitude more.}
+%  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
 
@@
 \label{res:afr}
-\cm{
-Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
-It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but below we examine the log-logistic model due to its improved AIC.
-Fig.~\ref{fig:qq} compares the AFR-predicted failures with the empirical failures.
-We can see that the model is largely effective, though becomes less effective as the number of failures increases.
-It is, however, very precise when measuring a small number of failures, which is far more important for safety-critical design.
-}
+\cm{Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
+For building the AFR model, we used 75\% of the available data and withheld 25\% for verification.
+The concordance is both strong (>.5) and similar for all three AFR models and both the train and test sets.
+We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFR models.
+Fig.~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFR models.
+For further analysis, we chose the Weibull AFR due to its superior fir in  Fig.~\ref{fig:qq}.}
 \input{plots/combined/aft_comparison}
-\cm{
-Fig.~\ref{fig:aft} shows the log-scale coefficients for the AFR model.
+
+\cm{Fig.~\ref{fig:aft} shows the log-scale coefficients for the AFR model.
 It shows that epochs, batch size, and training time have no effect on the survival time.
 Additionally, it reveals this for the random state variable, which is expected.
-However, we can clearly see that inference time (e.g.
-how long it takes to query the model) is as strong an indicator as the attack noise distance, revealing that model speed is at least as important as the attack itself.
-Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance).
-}
+However, we can clearly see that inference time  is as strong an indicator as the attack noise distance, revealing that model speed is at least as important as the attack itself.
+Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance)\cite{carlini_towards_2017}.}
 \cm{
-Using the $S(t)$ described in Sec.~\ref{afr}, we can model the partial effect of various hardware devices, which is depicted in Fig.~\ref{fig:partial}.
+Using the $S_{\theta}(t)$ described in Sec.~\ref{afr}, we can model the partial effect of various hardware devices, which is depicted in Fig.~\ref{fig:partial}.
 It clearly shows that hardware choice has no bearing on robustness, despite the disparity in cost outlined in Table~\ref{tab:hardware}.
 }
-
+\begin{figure*}[h!]
+    \centering
+    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \caption{ }
+    \end{subfigure}
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{The red line depicts the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
+    \label{fig:qq}
+\end{figure*}
 \begin{figure}[h!]
     \centering
+    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
     \begin{subfigure}[b]{\linewidth}
         \centering
-        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_qq.pdf}
-        \caption{The red line depicts the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
-        \label{fig:qq}
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_aft.pdf}
-        \caption{Coefficients of the Covariates for the Log Logistic AFR model}
+        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft.pdf}
+        \caption{Coefficients of the Covariates for the Log Logistic AFR model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
         \label{fig:aft}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_device_num_partial_effect.pdf}
-        \caption{Partial Effect  of $\varepsilon$ on $S(t)$ }
+        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_device_num_partial_effect.pdf}
+        \caption{Partial Effect  of device on $S_{\theta}(t)$ }
         \label{fig:partial}
     \end{subfigure}
-    \caption{This shows the partial effects plots for}
+    \caption{Weibull AFR Model.}
 \end{figure}
@@
 We have taken much care to conduct these measurements as carefully as possible.
-Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for maximum likelihood learning~\cite{ma2022state}.
-Given the strong ($>0.5$) concordance results and uniformity across AFR functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial.
+Given the strong results and uniformity across AFR functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning.
-\cm{While this obscures the effect of GPU parallelization, the result doesn't change since all metrics are measured on a particular piece of hardware for both the attacker and defender.
-Furthermore, we see the attack batch size and the training batch size to be the same for every trial.
-If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.} In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
+\cm{Furthermore, we set the attack batch size and the training batch size to be the same for every trial for each dataset and piece of hardware.
+If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.} 
 Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth. 
-However, we would like to note that the ``inference-optimized" Nvidia 4-series GPUs are perfectly capable and affordable training machines.
-We restricted our search to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time (and therefore deployment cost), though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks.
+In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
+We restricted our search to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.
 

### 2024-05-20 plots/combined/aft_comparison.tex
update image references
update plots
Updates from Overleaf
clean bibliography

@@
-\begin{table}
-\caption{Comparison of AFR Models on the COMBINED dataset.}
-\label{tab:Combined}
+\begin{table*}
+\centering
+\caption{Comparison of AFR Models on the Combined dataset. The metrics are defined in Sec.~\ref{afr}}
+\label{tab:combined}
 \begin{tabular}{lrrrrrr}
 \toprule
- & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
 \midrule
-weibull & -5810.78 & 0.84 & 0.84 & -5810.78 & 2.08 & 0.65 \\
-log_logistic & -6204.80 & 0.85 & 0.84 & -6204.80 & 0.23 & 0.17 \\
-log_normal & -6076.91 & 0.84 & 0.84 & -6076.91 & 0.17 & 0.15 \\
+Weibull & -5.57e+03 & -5.57e+03 & 0.84 & 0.84 & 0 & 0 \\
+Log Logistic & -5.71e+03 & -5.71e+03 & 0.85 & 0.84 & 0.01 & 0 \\
+Log Normal & -5.85e+03 & -5.85e+03 & 0.84 & 0.84 & 0.01 & 0 \\
 \bottomrule
 \end{tabular}
-\end{table}
+\end{table*}

### 2024-05-20 plots/cifar/aft_comparison.tex
update plots

@@
 \label{tab:cifar}
-\begin{tabular}{lllrrrr}
+\begin{tabular}{lllrrrrrr}
 \toprule
- & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
 \midrule
-Weibull & -1.23e+03 & -1.23e+03 & 0.79 & 0.8 & 0.02 & 0 \\
-Cox & -- & -- & 0.8 & 0.8 & 0.01 & 0 \\
-Log Logistic & -1.34e+03 & -1.34e+03 & 0.79 & 0.79 & 0.01 & 0 \\
-Log Normal & -1.39e+03 & -1.39e+03 & 0.79 & 0.79 & 0.01 & 0 \\
+Weibull & -4.87e+03 & -4.87e+03 & 0.8 & 0.79 & 0.01 & 0 & 0 & 0 \\
+Cox & -- & -- & 0.8 & 0.79 & 0.03 & 0.02 & 0 & 0 \\
+Log Logistic & -5.07e+03 & -5.07e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -5.27e+03 & -5.27e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-05-20 plots/cifar100/aft_comparison.tex
update plots

@@
 \label{tab:cifar100}
-\begin{tabular}{lllrrrr}
+\begin{tabular}{lllrrrrrr}
 \toprule
- & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
 \midrule
-Weibull & -1.11e+03 & -1.11e+03 & 0.78 & 0.76 & 0 & 0 \\
-Cox & -- & -- & 0.79 & 0.76 & 0.02 & 0 \\
-Log Logistic & -1.2e+03 & -1.2e+03 & 0.78 & 0.77 & 0.01 & 0 \\
-Log Normal & -1.24e+03 & -1.24e+03 & 0.79 & 0.77 & 0 & 0 \\
+Weibull & -4.19e+03 & -4.19e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
+Cox & -- & -- & 0.77 & 0.76 & 0.01 & 0.01 & 0 & 0 \\
+Log Logistic & -4.49e+03 & -4.49e+03 & 0.77 & 0.75 & 0.02 & 0.01 & 0 & 0 \\
+Log Normal & -4.65e+03 & -4.65e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
 \bottomrule

### 2024-05-20 plots/combined/aft_comparison.tex
update plots

@@
 \centering
-\caption{Comparison of AFR Models on the Combined dataset. The metrics are defined in Sec.~\ref{afr}}
+\caption{Comparison of AFR Models on the combined dataset.}
 \label{tab:combined}
-\begin{tabular}{lrrrrrr}
+\begin{tabular}{lrrrrrrrr}
 \toprule
- & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
 \midrule
-Weibull & -5.57e+03 & -5.57e+03 & 0.84 & 0.84 & 0 & 0 \\
-Log Logistic & -5.71e+03 & -5.71e+03 & 0.85 & 0.84 & 0.01 & 0 \\
-Log Normal & -5.85e+03 & -5.85e+03 & 0.84 & 0.84 & 0.01 & 0 \\
+Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
+Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
 \bottomrule

### 2024-05-20 plots/mnist/aft_comparison.tex
update plots

@@
 \label{tab:mnist}
-\begin{tabular}{lllrrrr}
+\begin{tabular}{lllrrrrrr}
 \toprule
- & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
+ & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
 \midrule
-Weibull & -1.56e+03 & -1.56e+03 & 0.9 & 0.9 & 0.02 & 0 \\
-Cox & -- & -- & 0.9 & 0.89 & 0.03 & 0 \\
-Log Logistic & -1.67e+03 & -1.67e+03 & 0.9 & 0.9 & 0.02 & 0 \\
-Log Normal & -1.71e+03 & -1.71e+03 & 0.9 & 0.9 & 0.01 & 0 \\
+Weibull & -5.83e+03 & -5.83e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Log Logistic & -6.1e+03 & -6.1e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
+Log Normal & -6.25e+03 & -6.25e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
 \bottomrule

### 2024-05-20 main.tex
Updates from Overleaf

@@
 
-\documentclass[conference]{IEEEtran}
+\documentclass[journal]{IEEEtran}
 % Some Computer Society conferences also require the compsoc mode option,
@@
 % correct bad hyphenation here
-
-\usepackage{cite}
+\usepackage[maxcitenames=3,natbib=true,giveninits=true]{biblatex}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 
-\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
+% \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
 
-% \newcommand{\cm}[1]{#1}
+\newcommand{\cm}[1]{#1}
 \newcommand{\mr}[1]{\textit{{\color{red}#1}}}
@@
 % affiliations
-\author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
-\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-\textit{Umeå University}\\
-Umeå, Sweden \\
-cmeyers@cs.umu.se}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
-\IEEEauthorblockA{\textit{Elastisys} \\
+% \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
+% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
 % \textit{Umeå University}\\
-% Lund, Sweden \\
-mohammad.saleh@elastisys.com}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
-\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-\textit{Umeå University}\\
-Umeå, Sweden \\
-tommy@cs.umu.se}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
-\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-\textit{Umeå University}\\
-Umeå, Sweden \\
-elmroth@cs.umu.se}
-}
+% Umeå, Sweden \\
+% cmeyers@cs.umu.se}
+% \and
+% \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
+% \IEEEauthorblockA{\textit{Elastisys} \\
+% % \textit{Umeå University}\\
+% % Lund, Sweden \\
+% mohammad.saleh@elastisys.com}
+% \and
+% \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
+% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
+% \textit{Umeå University}\\
+% Umeå, Sweden \\
+% tommy@cs.umu.se}
+% \and
+% \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
+% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
+% \textit{Umeå University}\\
+% Umeå, Sweden \\
+% elmroth@cs.umu.se}
+% }
 
@@
 \begin{abstract}
-\cm{Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model a run-time, evaluating the robustness of models to these evasion attacks is of critical importance.}
+Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model a run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
 Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
-\cm{In this paper, we use survival analysis to present a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.}
-For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, \cm{so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data.
-However, in practice, this means that each model configuration needs to be evaluated against real-world deployment samples which can be prohibitively expensive or time-consuming to collect --- especially when other parts of the software or hardware stack are developed in parallel.} To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world.
+In this paper, we use survival analysis to present a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.
+For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data.
+However, in practice, this means that each model configuration needs to be evaluated against real-world deployment samples which can be prohibitively expensive or time-consuming to collect --- especially when other parts of the software or hardware stack are developed in parallel.
+To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world.
 We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously.
-This provides a way to evaluate the model and optimize it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy.
+This provides a way to evaluate the model and optimise it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy.
 Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
@@
 Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
-\cm{Statistical learning theory \cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
+Statistical learning theory \cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
 To overcome this, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has  yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
 We also know that  reaching safety-critical standards using test-set accuracy would require an infeasibly large test set \cite{meyers}.
-Therefore, we propose using AFR models to simulate edge-cases and verify models using a small number of samples.}
+Therefore, we propose using accelerated failure time models to simulate edge-cases and verify models using a small number of samples.
 
-\cm{Modern neural networks are massive--- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}}.
+Modern neural networks are massive--- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}.
 One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
@@
 Media reports place the cost of training a GPT3 somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
-\cm{While the benefits of a more portable model are plentiful, there is not yet a method for formalizing the relationship between cost and model performance.
-We present training and validation methodology with a focus on compute- and time-efficiency.}
+While the benefits of a more portable model are plentiful, there is not yet a method for formalizing the relationship between cost and model performance.
 
-Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for \cm{assessing model generalization}~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk~\cite{iso26262}.
-Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern \cm{since inducing a failure at run-time has consistently shown to be trivial}~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
+Furthermore, even if we ignore the immense cost of training modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for assessing model generalization~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk.
+Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern since inducing a failure at run-time has consistently shown to be trivial~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
 Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive.
@@
 
-\cm{In this paper, we use accelerated methods to predict model performance as a function of various model parameters.
-The methodology outlined in Sec.~\ref{afr} allows the model-builder to minimize the training cost, optimize for adversarial robustness, estimate the partial effects of covariates on model performance during routine training procedures, and perform a cost analysis (Sec.~\ref{cost}).
-We then demonstrate the efficacy of this methodology in Sec.~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Sec.~\ref{experiments}.}
+In this paper, we use accelerated methods to predict model performance as a function of various model parameters.
+The methodology outlined in Sec.~\ref{afr} allows the model-builder to minimize the training cost, optimise for adversarial robustness, estimate the partial effects of covariates on model performance during routine training procedures.
+Then, one can perform a cost analysis (Sec.~\ref{cost}).
+We then demonstrate the efficacy of this methodology in Sec.~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Sec.~\ref{experiments}.
 
 \subsection{Contributions}
-To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective \cm{methodology and software framework for the training (see: Sec.~\ref{afr}) and evaluation (see: Sec.~\ref{cost}) of machine learning models} that:
+To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see: Figs.~\ref{fig:alg}\&~\ref{fig:experiments}) and software framework (see: Fig.~\ref{fig:architecture}) for the training (see: Sec.~\ref{afr}) and evaluation (see: Sec.~\ref{cost}) of machine learning models that:
 \begin{itemize}
-    \item Optimizes for benign and adversarial accuracy simultaneously,
+    \item optimises for benign and adversarial accuracy simultaneously,
     \item Extends survival analysis to the realm of neural networks, 
@@
 
-\cm{Sec.~\ref{background} defines terms used throughout the paper.
+Sec.~\ref{background} defines terms used throughout the paper.
 Sec.~\ref{afr} outlines the training and evaluation methodology presented in this paper.
@@
 Sec.~\ref{experiments} outlines the software components and specific experiments that were conducted, while Sec.~\ref{results} contains the results and discussions of those experiments.
-Sec.~\ref{considerations} and Sec.~\ref{conclusion} reveal the caveats and the conclusions respectively.}
+Sec.~\ref{considerations} and Sec.~\ref{conclusion} reveal the caveats and the conclusions respectively.
 
@@
 As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises.
-The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference.
-Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.
+The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, attack generation, and inference.
+Efficiently orchestrating  and evaluating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.
 
+One popular solution is using a network of interconnected services \cite{panchal2024reusable,hasselbring2017microservice,zhong2022machine,singh2023load}.
 A \textit{service} is the smallest component of a ``cloud-native" software stack.
 In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
-A service \textit{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between services in a distributed system.
-It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services.
-
 A service \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the services within the system.
 These components facilitate various capabilities and functionalities essential for managing the communication between services.
-Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures.
-\cm{For ML applications, these services are often divided into ``training" and ``inference" configurations that often distinct hardware and software configurations~\cite{wang2019benchmarking}.
-In this work, we leveraged Kubernetes to manage a multi-stage ML pipeline.}
+Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures using a service mesh.
+For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}.
+In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see: Fig.~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see: Fig.~\ref{fig:architecture}) across a variety of different hardware architectures (see: Tab.~\ref{tab:hardware}).
 
@@
 
-Choosing the correct learning rate is critical for model performance --- greatly effecting both the accuracy and the run-time requirements.
+Choosing the correct learning rate is critical for model performance --- greatly effecting both the accuracy and the training cost.
 A small learning rate will will more closely follow the true gradient of a class boundary~\cite{cao2019generalization}, but will converge slower, all other things being equal.
@@
 However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}.
-Furthermore, since hardware is typically billed by the hour on public clouds, so optimizing the training and inference times allows a model-builder to minimize the cost of deployment.
+Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.
 
@@
 We propose a methodology for model training and verification using accelerated failure rate (AFR) models, drawn from the field of \textit{survival analysis}.
-\cm{Additionally, since one of our goals is a cost-effective model evaluation technique, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.}
+Additionally, since one goal is cost-efficiency, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
 AFR models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
-\cm{In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components.
-This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.}
-\cm{The section below outlines our methodology for modelling the effect of model hyper-parameters during routine training procedures.
+In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components.
+This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
+The section below outlines our methodology for modelling the effect of model hyper-parameters during routine training procedures.
 In this section, we precisely outline the methodology for using survival analysis during the training of machine learning algorithms.
-We provide a formal algorithm in Fig.~\ref{fig:alg} and a visual diagram in ~\ref{fig:experiments}.}
-
-\cm{In the subsections below, we define accuracy (Sec.~\ref{acc}) and failure rate (Sec.~\ref{failure_rate})  in the context of survival analysis to provide a pedagogical definition of survival time (Sec.~\ref{survival_time}).
-We then discuss the importance of the ``acceleration assumption" (Sec.~\ref{accelerated}), the optimization algorithm (Sec.~\ref{optimisation}), and the advantages of this approach (Sec.~\ref{advantages}).}
+First, we provide a formal algorithm in Fig.~\ref{fig:alg} and a visual diagram in ~\ref{fig:experiments}.
+Then, in  the subsections below, we define accuracy (Sec.~\ref{acc}) and failure rate (Sec.~\ref{failure_rate})  in the context of survival analysis to provide a pedagogical definition of survival time (Sec.~\ref{survival_time}).
+We then discuss the importance of the ``acceleration assumption" (Sec.~\ref{accelerated}), the optimisation algorithm (Sec.~\ref{optimisation}), and the advantages of this approach (Sec.~\ref{advantages}).
 
@@
     \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
-    \State \textbf{Optimise $\theta$:} over $x_t$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
+    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
     \State \textbf{Record:} $T_t[i] \gets$ Training Time.
@@
     \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
-    \State \textbf{Infer:}  $ y' = K(x_a, \theta) $.
-    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc})
+    \State \textbf{Infer:}  $ \hat{y}_a = K(x_a, \theta) $.
+    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
     \EndWhile
-    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates, $N_a$ is the attack size array.
+    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
     \State \textbf{Return:} $S_{\theta}$
@@
 \label{acc}
- It measures the vulnerability or susceptibility of the model to noise-induced failures.
+  Accuracy measures the vulnerability or susceptibility of the model to noise-induced failures.
 A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures.
 Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data.
-The benign accuracy, $\lambda_{ben}$, is defined as
+The accuracy, $\lambda$, is defined as
 \begin{equation}
@@
 Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
-\cm{We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test set $\lambda_{adv}$ to denote the accuracy on the adversarial examples.}
+We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test set $\lambda_{adv}$ to denote the accuracy on the adversarial examples.
 
@@
 The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}.
-To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, \cm{such that the failure rate is}
+To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, such that the failure rate is
 \[
@@
 where $\mathbb{P}(\textrm{False~Classification})$ is the probability of a false classification, $\Delta t$ is a time interval, and $t$ is a point in time.
-\cm{Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$.
-By reparameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure rate model.}
+Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$.
+By re-parameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure rate model.
 
@@
 \label{survival_time}
-\cm{Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$.
+Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$.
 For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely.
 For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease.
-For machine learning, this means inducing failures during training to measure generalization performance.}
+For machine learning, this means inducing failures during training to measure generalization performance.
 
@@
 $$
-\cm{where $\mathbb{P}(T>t)$ is the probability that a model has not failed by time $t$. Then, the expected survival time is}
+where $\mathbb{P}(T>t)$ is the probability that a model has not failed by time $t$. Then, the expected survival time is
 \[
@@
 The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival}.
-\cm{For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval.
-This should be measured in both the benign and adversarial contexts as a way to measure the cost of a particular model in both contexts.}
+For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval.
+This should be measured in both the benign and adversarial contexts.
+The full algorithm can be seen in Fig.~\ref{fig:alg}.
 
-To choose a best-fit from the possible AFR functions, one should prepare the collected metrics, parameters, scores and/or meta data.
-
+To choose a best-fit from the possible AFR functions, one should prepare the collected metrics and scores.
 Then, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}.
-\cm{For AIC and BIC, that means choosing the smallest value.
+For AIC and BIC, that means choosing the smallest value.
 Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and .5 reflects random chance.
 By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}.
-In addition, one should measure the integrated calibration index (ICI) the error at the median (E50)~\cite{ici}.
+In addition, one should measure the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}.
 These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively ~\cite{ici}.
-Then, one should plot all the expected and observed values for all three functions according to the method described by Austin et al.~\cite{ici}.}
+Then, one should plot all the expected and observed values for all three functions according to the method described by Austin et al.~\cite{ici} (see: Fig.~\ref{fig:qq}) to visually inspect each model for goodness-of-fit.
 
@@
 $$
-\cm{This can also be thought of in terms of the accelerated failure rate assumption~\cite{kleinbaum1996survival}:
+This can also be thought of in terms of the accelerated failure rate assumption~\cite{kleinbaum1996survival}:
 \begin{equation}
@@
 where $\phi$ is some acceleration factor describing the joint effect of the covariates.
-This assumption means we can evaluate the benign accuracy using a small number of adversarial samples ~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.}
-\cm{However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space intelligently.}
+This assumption means we can evaluate the benign accuracy using a small number of adversarial samples ~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
+However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space intelligently.
 
@@
 \label{optimisation}
-\cm{Machine learning models are typically trained across a wide variety of hyper-parameters to determine the ``best" model by minimizing an optimisation program (minimizing a loss function associated with the machine learning problem) by measuring the loss across many configurations of a model.} However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of such parameters,
+Machine learning models are typically trained across a wide variety of hyper-parameters to determine the ``best" model by minimizing an optimisation program (minimizing a loss function associated with the machine learning problem) by measuring the loss across many configurations of a model.
+However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of such parameters,
 making it infeasible to exhaustively evaluate the search space.
-Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}--with several researchers noting an inverse relationship between model accuracy and model robustness ~\cite{carlini_towards_2017,meyers}.
+Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}--with several researchers noting an inverse relationship between model accuracy and model robustness ~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}.
 Therefore, a proper search would keep this dual-objective in mind.
-\cm{To optimize for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}}.
+To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}.
 
@@
 \label{advantages}
-\cm{Because of the small number of samples needed for building AFR models (when compared to testing against massive in-distribution test sets), AFR models could}, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}.
+Because of the small number of samples needed for building AFR models (when compared to testing against massive in-distribution test sets), AFR models could, for example, act as a unit test in machine learning applications.
+This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}.
 It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}.
 Furthermore, by isolating changes and testing them as quickly as possible, it is  easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test.
-To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}.
+To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictaFted by the ISO 26262 standard \cite{iso26262}.
 This risk analysis is outlined in the subsection below.
@@
 \label{cost}
-\cm{In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by ISO26262~\cite{iso26262} which allows us to quantify the marginal risk.
-To quantify this marginal risk, one must measure} the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack.
+In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by ISO26262~\cite{iso26262} which allows us to quantify the marginal risk.
+To quantify this marginal risk, one must measure the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack.
 The final subsection outlines why these metrics are important and their usage in this methodology.
@@
 \subsection{Accuracy}
-\cm{In order to estimate the number of failures in a given time period}, we measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.
-\cm{Under the AFR framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period.}
+In order to estimate the number of failures in a given time period, we measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.
+Under the AFR framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period as outlined in Fig.~\ref{fig:alg}.
 
@@
 \end{equation}
-We restricted this to a single iteration \cm{such that $i =1$} as described in FGM~\cite{fgm}.
+We restricted this to a single iteration such that $i =1$ as described in FGM~\cite{fgm}.
 
@@
  In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
-\cm{In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
-For our purposes, by assuming the best-case scenario for both attacker and defender, we can model the Pareto front --- the best-case asymptotic behavior --- of either party~\cite{zitzler2008quality}.}
+In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
+For our purposes, by assuming the best-case scenario for both attacker and defender, we can model the Pareto front --- the best-case asymptotic behavior --- of either party~\cite{zitzler2008quality}.
 As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
@@
 To conduct the experiments and have access to different types of hardware, we utilized GCP.
-Six virtual machines running Container Optimized Operating System provided by GCP constituted our testbed.
+Six virtual machines running Container optimised Operating System provided by GCP constituted our testbed.
 Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster consisting of six worker nodes.
@@
 Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
+Additionally, we fit the function as described in Fig.~\ref{fig:alg}.
 
@@
 The rental cost of the hardware, measured in United States Dollars per hour, will indicate the operating cost of a given model.
-To calculate this, we used the price per hour from each of cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.}}\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimized}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
+To calculate this, we used the price per hour from each of cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.}}\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
 
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
-        \caption{Training, Prediction, and Attack times}
+        \caption{Training (left), Prediction (center), and Attack (right) Times}
         \label{fig:time}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
-        \caption{Training, Prediction, and Attack Power Consumption}
+        \caption{Training (left), Prediction (center), and Attack (right) Power Consumption}
         \label{fig:power}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
-        \caption{Training, Prediction, and Attack Monetary Cost}
+        \caption{Training (left), Prediction (center), and Attack (right) Monetary Cost}
         \label{fig:cost}
@@
 The monetary cost for each dataset and each piece of hardware is shown in Fig.~\ref{fig:cost}.
-\cm{For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
-In the best case scenario, they are comparable, but attacks consistently succeed with 100s of samples while model training requires orders of magnitude more.}
+For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
+In the best case scenario, they are comparable, but attacks consistently succeed with 100s of samples while model training requires orders of magnitude more.
 %  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
@@
 \label{res:afr}
-\cm{Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
+Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
 For building the AFR model, we used 75\% of the available data and withheld 25\% for verification.
@@
 Fig.~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFR models.
-For further analysis, we chose the Weibull AFR due to its superior fir in  Fig.~\ref{fig:qq}.}
+For further analysis, we chose the Weibull AFR due to its superior fir in  Fig.~\ref{fig:qq}.
 \input{plots/combined/aft_comparison}
 
-\cm{Fig.~\ref{fig:aft} shows the log-scale coefficients for the AFR model.
+Fig.~\ref{fig:aft} shows the log-scale coefficients for the AFR model.
 It shows that epochs, batch size, and training time have no effect on the survival time.
@@
 However, we can clearly see that inference time  is as strong an indicator as the attack noise distance, revealing that model speed is at least as important as the attack itself.
-Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance)\cite{carlini_towards_2017}.}
-\cm{
+Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance)\cite{carlini_towards_2017}.
+
 Using the $S_{\theta}(t)$ described in Sec.~\ref{afr}, we can model the partial effect of various hardware devices, which is depicted in Fig.~\ref{fig:partial}.
 It clearly shows that hardware choice has no bearing on robustness, despite the disparity in cost outlined in Table~\ref{tab:hardware}.
-}
+
 \begin{figure*}[h!]
@@
         \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft.pdf}
-        \caption{Coefficients of the Covariates for the Log Logistic AFR model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
+        \caption{Coefficients of the Covariates for the Weibull AFR model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
         \label{fig:aft}
@@
 Given the strong results and uniformity across AFR functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
-Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning.
-\cm{Furthermore, we set the attack batch size and the training batch size to be the same for every trial for each dataset and piece of hardware.
-If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.} 
+Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around data storage, file systems, and various access mechanisms.
+Furthermore, we set the attack batch size and the training batch size to be the same for every trial for each dataset and piece of hardware.
+If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.
 Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth. 
@@
 In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing us the model performance as a function of tested model parameters.
+We then formalize a technique to model the survival time as a function of various model parameters.
 Using this technique, we showed that despite reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.
 Furthermore, we demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields substantially similar results when compared to more expensive and power hungry hardware.
-However, the marginal run-time is substantial, even if it's cost-effective.
 

### 2024-08-15 main.tex
TLs Edits

@@
-%% bare_conf.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%% 
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[journal]{IEEEtran}
-% Some Computer Society conferences also require the compsoc mode option,
-% but others use the standard conference format.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\usepackage[maxcitenames=3,natbib=true,giveninits=true]{biblatex}
+\documentclass[conference]{IEEEtran}
+\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{subcaption}
+\usepackage{algorithm}
 \usepackage{algpseudocode}
 
-% \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
-
-\newcommand{\cm}[1]{#1}
-\newcommand{\mr}[1]{\textit{{\color{red}#1}}}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\minimise}{\textrm{minimise}}
+\DeclareMathOperator*{\maximise}{\textrm{maximise}}
+\newcommand{\Ie}{\textit{I.e.}\xspace}
+\newcommand{\ie}{\textit{i.e.}\xspace}
+\newcommand{\Eg}{\textit{E.g.}\xspace}
+\newcommand{\eg}{\textit{e.g.}\xspace}
+\newcommand{\probP}{\text{I\kern-0.15em P}}
+\newcommand{\tl}[1]{\textit{[{\color{red}#1}]}}
+\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
+\newcommand{\erik}[1]{\textit{[{\color{brown}Erik: #1}]}}
+\newcommand{\mr}[1]{\textit{[{\color{brown}Mohammed: #1}]}}
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
 \title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}
 
+\author{}
 % author names and affiliations
@@
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
 \maketitle
@@
 \begin{abstract}
-Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model a run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
-Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
-In this paper, we use survival analysis to present a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.
-For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data.
+Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model at run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
+Additionally, testing model changes likely means deploying the models to \textit{e.g.}, a car, a medical imaging device, or a drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
+In this work, we used survival analysis as a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.
+For neural networks in particular, the relationships between the learning rate, batch size, training time, convergence time, and deployment cost are highly complex, so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data.
 However, in practice, this means that each model configuration needs to be evaluated against real-world deployment samples which can be prohibitively expensive or time-consuming to collect --- especially when other parts of the software or hardware stack are developed in parallel.
-To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world.
+To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world.
 We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously.
@@
 Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
-Statistical learning theory \cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
-To overcome this, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has  yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
-We also know that  reaching safety-critical standards using test-set accuracy would require an infeasibly large test set \cite{meyers}.
+Statistical learning theory~\cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
+To overcome this, neural networks need large amounts of data~\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
+It is also clear that reaching safety-critical standards using test-set accuracy would require an infeasibly large test set~\cite{meyers}.
 Therefore, we propose using accelerated failure time models to simulate edge-cases and verify models using a small number of samples.
 
-Modern neural networks are massive--- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}.
-One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
+\cm{
+Modern neural networks are massive --- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}.
+For image systems, VGG19~\cite{vgg} is now considered small with \textit{only} 138 million parameters.
+ResNet152 has a similar number of parameters at 116 million~\cite{resnet}.
+However, modern advancements in transformer architectures have lead to an explosion in model size with the recent Mamba model boasting a massive 8 \textit{billion} tunable parameters~\cite{mamba}.
+At these scales, we have no statistical guarantees about the performance of these models and test-set validation would require many, many billions of samples for each and every model change.
+}
+% One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
 Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}.
@@
 Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern since inducing a failure at run-time has consistently shown to be trivial~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
-Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive.
+Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive for these large models.
 Therefore, a new evaluation methodology is required.
@@
 
-In this paper, we use accelerated methods to predict model performance as a function of various model parameters.
-The methodology outlined in Sec.~\ref{afr} allows the model-builder to minimize the training cost, optimise for adversarial robustness, estimate the partial effects of covariates on model performance during routine training procedures.
-Then, one can perform a cost analysis (Sec.~\ref{cost}).
-We then demonstrate the efficacy of this methodology in Sec.~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Sec.~\ref{experiments}.
+In this work, we used accelerated failure-time methods to predict model performance as a function of various model parameters.
+The methodology outlined in Section~\ref{aft} allows the model-builder to minimize the training cost, optimise for adversarial robustness, estimate the effects of covariates on model performance during routine training procedures.
+Then, one can perform a cost analysis (Section~\ref{cost}).
+We then demonstrate the efficacy of this methodology in Section~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Section~\ref{experiments}.
 
 \subsection{Contributions}
-To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see: Figs.~\ref{fig:alg}\&~\ref{fig:experiments}) and software framework (see: Fig.~\ref{fig:architecture}) for the training (see: Sec.~\ref{afr}) and evaluation (see: Sec.~\ref{cost}) of machine learning models that:
+To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see Algorithm~\ref{fig:alg} and Figure~\ref{fig:experiments}) and software framework (see Figure~\ref{fig:architecture}) for the training (see Section~\ref{aft}) and evaluation (see Section~\ref{cost}) of machine learning models that:
 \begin{itemize}
-    \item optimises for benign and adversarial accuracy simultaneously,
-    \item Extends survival analysis to the realm of neural networks, 
-    \item Demonstrates a scalable and effective method that trains a model while simultaneously estimating the asymptotic effect of various hyperparameters, and
+    \item Optimises for benign and adversarial accuracy simultaneously,
+    % \item Extends survival analysis to the realm of neural networks, 
+    \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyperparameters, and
     \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
+    \item \cm{Demonstrates that, even when we control for the slower clock speed of "inference only hardware" compared to hardware marketed for training, that models trained using the "inference only" devices are more robust for image classification tasks than models built on hardware designed for training.}
 \end{itemize}
 
-Sec.~\ref{background} defines terms used throughout the paper.
-Sec.~\ref{afr} outlines the training and evaluation methodology presented in this paper.
-Section ~\ref{cost} outlines the resulting cost analysis framework, arising from the methodology in the previous section.
-Sec.~\ref{experiments} outlines the software components and specific experiments that were conducted, while Sec.~\ref{results} contains the results and discussions of those experiments.
-Sec.~\ref{considerations} and Sec.~\ref{conclusion} reveal the caveats and the conclusions respectively.
+Section~\ref{background} defines the terminology used throughout the paper.
+Section~\ref{aft} outlines the training and evaluation methodology presented in this paper.
+Section ~\ref{cost} discusses the resulting cost analysis framework, arising from the methodology in the previous section.
+Section~\ref{experiments} outlines the software components and specific experiments that were conducted, while Section~\ref{results} contains the results and discussions of those experiments.
+Section~\ref{considerations} and Section~\ref{conclusion} reveal the caveats and the conclusions respectively.
 
@@
 
-In this paper, we present a comprehensive methodology for evaluating model robustness during training time and model the asymptotic effect of the various parameters in the search space.
+In this paper, we evaluate a comprehensive methodology for evaluating model robustness during training time and model the asymptotic effect of the various parameters in the hyper-parameter search space.
 For the sake of the reader, we provide a section for definitions and requisite background information below.
@@
 However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
-As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises.
-The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, attack generation, and inference.
-Efficiently orchestrating  and evaluating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.
-
-One popular solution is using a network of interconnected services \cite{panchal2024reusable,hasselbring2017microservice,zhong2022machine,singh2023load}.
-A \textit{service} is the smallest component of a ``cloud-native" software stack.
+One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native" software stack.
 In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
@@
 For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}.
-In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see: Fig.~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see: Fig.~\ref{fig:architecture}) across a variety of different hardware architectures (see: Tab.~\ref{tab:hardware}).
+In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see Figure~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see Figure~\ref{fig:architecture}) across a variety of different hardware architectures (see Table~\ref{tab:hardware}).
 
@@
 To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
+Likewise, Nvidia offers hardware that is marketed as either for training (\textit{e.g.}, v100 and p100) or only for inference (\textit{e.g.}, l4).
 
@@
 
-We consider classifiers, $K(x; \theta)$ with model parameters, $\theta$.
-The true labels are denoted by $y$, and the model predictions by $\hat{y} = K(x; \theta)$ and $x$ is a batch of samples with size $N$.
-The loss function is denoted by $L(y, \hat{y})$.
-Because of the complexity of modern machine learning models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset of the training samples.
+We consider ML classifiers, $K(x; \theta)$ with model parameters, $\theta$.
+The true labels are denoted by $y$, and the model predictions by $\hat{y} = K(x; \theta)$ where $x$ is a mini-batch of size $N$ of data samples.
+The loss function, the measure of discrepancy between the true label and the predicted label, is denoted by $L(y, \hat{y})$.
+Because of the complexity of modern machine learning models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset (a mini-batch) of the training samples instead of all training samples.
 % selects the next $N$ samples from the training set before adjusting the model parameters, $\theta$, in the direction that decreases the loss.
@@
 \end{equation}
-where the gradient is approximated using $b$ batches per epoch and $\eta$ is a \textit{learning rate} (or step size) that is tuned to the particular model.
+where the gradient is approximated using $b$ samples per mini-batch and $\eta$ is the \textit{learning rate} (or step size) that is tuned to the particular model and data.
 
@@
 
-Choosing the correct learning rate is critical for model performance --- greatly effecting both the accuracy and the training cost.
-A small learning rate will will more closely follow the true gradient of a class boundary~\cite{cao2019generalization}, but will converge slower, all other things being equal.
-Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data, \textit{etc}~\cite{granziol2022learning}.
-Graphics cards with larger amounts of RAM are able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch.
-A ``good" learning rate will allow a model converge quickly~\cite{smith2019super,granziol2022learning} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, scale, and bit depth of the data.
+Choosing a good learning rate is critical for model performance --- greatly effecting both the accuracy and the training cost.
+A small learning rate will more accurately approximate the class boundaries~\cite{cao2019generalization}, but will converge slower, all other things being equal.
+Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the mini-batch size, number of epochs, dimensionality of the input data, \textit{etc.}~\cite{granziol2022learning}.
+GPUs with larger amounts of VRAM are able to hold more data in memory at a time, increasing the effective mini-batch size, and reducing the number of model-tuning steps per epoch.
+A ``good" learning rate will allow a model to converge quickly~\cite{smith2019super,granziol2022learning} and the ideal mini-batch size will be determined by the memory bandwidth of the GPU and the size of the model and the size and dimensionality of the data.
 However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}.
@@
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
-These attacks can occur during various stages of the ML pipeline, including during training \cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment ~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
+These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
 
@@
 \end{equation}
-In essence, this is process seeks to increase the loss  in contrast to model training which seeks to minimize it.
+In essence, this is process seeks to increase the loss by changing the input data, in contrast to model training which seeks to minimize the loss by changing the model parameters.
 
@@
 An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable.
-However, this would mean testing a million samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems.
+However, this would mean testing many millions of samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems.
 This is just not computationally feasible.
-Instead, researchers can use adversarial failure analysis~\cite{carlini_towards_2017,biggio_evasion_2013,meyers} to improve the precision of our measurements while only using a small set of test-data.
+Instead, researchers can use adversarial failure analysis~\cite{carlini_towards_2017,biggio_evasion_2013,meyers} to improve the precision of our estimates while only using a small set of test-data.
 
 \section{Survival Analysis for Robustness Verification during Training}
-\label{afr}
+\label{aft}
 
-We propose a methodology for model training and verification using accelerated failure rate (AFR) models, drawn from the field of \textit{survival analysis}.
+We propose a methodology for model training and verification using accelerated failure-time (AFT) models, drawn from the field of \textit{survival analysis}.
 Additionally, since one goal is cost-efficiency, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
-AFR models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
+AFT models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
 In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components.
 This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
-The section below outlines our methodology for modelling the effect of model hyper-parameters during routine training procedures.
-In this section, we precisely outline the methodology for using survival analysis during the training of machine learning algorithms.
-First, we provide a formal algorithm in Fig.~\ref{fig:alg} and a visual diagram in ~\ref{fig:experiments}.
-Then, in  the subsections below, we define accuracy (Sec.~\ref{acc}) and failure rate (Sec.~\ref{failure_rate})  in the context of survival analysis to provide a pedagogical definition of survival time (Sec.~\ref{survival_time}).
-We then discuss the importance of the ``acceleration assumption" (Sec.~\ref{accelerated}), the optimisation algorithm (Sec.~\ref{optimisation}), and the advantages of this approach (Sec.~\ref{advantages}).
+The next section outlines the methodology for modelling the effect of model hyper-parameters during routine training procedures.
+We precisely outline the methodology for using survival analysis during the training of machine learning methods.
+% First, we present the proposed procedure in Algorithm~\ref{fig:alg} and a visual diagram of it in Figure~\ref{fig:experiments}.
+Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}).
+We then discuss the importance of the ``acceleration assumption" (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).
 
-\begin{figure}[h!]
-    \caption{\textbf{Algorithm: }Survival Analysis for ML}
+\begin{algorithm}[h!]
+    \caption{Survival Analysis for ML}
     \label{fig:alg}
 \begin{algorithmic}
-    \Require Samples $x$ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and a number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, e.g.
-$N_t$ is size of the training set.
-    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
+    \Require Samples $x$ of size $N$, model parameters $\theta$, loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and the number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, \textit{e.g.}, $N_t$ is size of the training set.
+    \State Initialize classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
     \State $i = 0$
@@
     \EndWhile
-    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
+    \State \textbf{Fit AFT Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
     \State \textbf{Return:} $S_{\theta}$
 \end{algorithmic}
-\end{figure}
+\end{algorithm}
 
@@
 \label{acc}
+
 Accuracy measures the vulnerability or susceptibility of the model to noise-induced failures.
@@
 \end{equation}
-which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}.
+which is generally assumed to indicate the rate of failures in real-world data sampled from the same distribution as the test data~\cite{tan2021critical}.
 However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}.
-In addition, it ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}.
+In addition, it ignores the run-time cost of a given architectural decision, caring only about accuracy on benchmark data~\cite{desislavov2021compute,bailly2022effects}.
 Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
-We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test set $\lambda_{adv}$ to denote the accuracy on the adversarial examples.
+We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test data set $\lambda_{adv}$ to denote the accuracy on adversarial samples.
 
@@
 \label{failure_rate}
-The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}.
+
+The failure rate refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs~\cite{meyers}.
 To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, such that the failure rate is
 \[
-    h_{ \theta}(t) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t} t,
+    h_{\theta}(t) :=  \frac{p(\textrm{False~Classification} \mid \theta)}{\Delta t} t,
 \]
-where $\mathbb{P}(\textrm{False~Classification})$ is the probability of a false classification, $\Delta t$ is a time interval, and $t$ is a point in time.
+where $p(\textrm{False~Classification} \mid \theta)$ is the probability of a false classification given a particular set of hyper-parameters, $\theta$, $\Delta t$ is a time interval, and $t$ is a point in time.
 Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$.
-By re-parameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure rate model.
+By re-parameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure time model.
 
-\subsection{AFR Models}
+\subsection{AFT Models}
 \label{survival_time}
-Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$.
+
+Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time.
 For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely.
@@
 $$
-S_{\theta}(t)= \mathbb{P}(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
+    S_{\theta}(t) = p(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
 $$
-where $\mathbb{P}(T>t)$ is the probability that a model has not failed by time $t$. Then, the expected survival time is
+where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
 \[
-	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty}  S_\theta(t) \,dt.
+	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt,
 \]
-
+where $t^*$ is the latest time observed in the survival data.
 However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$.
@@
 This should be measured in both the benign and adversarial contexts.
-The full algorithm can be seen in Fig.~\ref{fig:alg}.
+The full algorithm can be seen in Algorithm~\ref{fig:alg}.
 
-To choose a best-fit from the possible AFR functions, one should prepare the collected metrics and scores.
-Then, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}.
+\subsubsection{Choosing the best AFT Model}
+
+To choose a best-fit from the possible AFT functions, one should prepare the collected metrics and scores and then compare them using \textit{e.g.}, Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), or Concordance, as per the best-practices for this methodology~\cite{aft_models,kleinbaum1996survival}.
 For AIC and BIC, that means choosing the smallest value.
-Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and .5 reflects random chance.
+Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and 0.5 reflects random chance.
 By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}.
-In addition, one should measure the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}.
-These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively ~\cite{ici}.
-Then, one should plot all the expected and observed values for all three functions according to the method described by Austin et al.~\cite{ici} (see: Fig.~\ref{fig:qq}) to visually inspect each model for goodness-of-fit.
+Other measures include the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}.
+These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}.
+Then, one should plot all the expected and observed values for all three functions according to the method described by Austin \textit{et al.}~\cite{ici} (see Figure~\ref{fig:qq}) to visually inspect each model for goodness-of-fit.
+\cm{Additionally, we split the data into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and measured the concordance, ICI, and E50 for each set.}
+
+\subsubsection{\cm{The Advantages of AFT models}}
+\cm{
+}
 
@@
 \label{accelerated}
-Using accelerated failure rate models, we can find the expected survival time under optimistic circumstances, $S_{ben}$ as well as under adverse ones (accelerated failure rate), $S_{adv}$.
-The survival time for benign samples is
-$$
-    S_{ben} := S(t_i; x, y, \theta) \mathrm{~~where~~} \varepsilon = 0
-$$
-and the survival time for the adversarial samples is
+
+Using accelerated failure time models under adverse ones (accelerated failure time), $S_{adv}$. The survival time for is
 $$
@@
 $$
-This can also be thought of in terms of the accelerated failure rate assumption~\cite{kleinbaum1996survival}:
-\begin{equation}
-S_{adv} \approx  \phi S_{ben}(\phi t)
-\label{assumption}
+This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
+\begin{equation} \label{assumption}
+    S_{adv} \approx  \phi S_{ben}(\phi t),
 \end{equation}
-where $\phi$ is some acceleration factor describing the joint effect of the covariates.
-This assumption means we can evaluate the benign accuracy using a small number of adversarial samples ~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
-However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space intelligently.
+where $\phi$ is some acceleration factor described by the joint effect of the covariates.
+This assumption means we can evaluate the benign accuracy using a small number of adversarial samples~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
+However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.
 
@@
 \label{optimisation}
-Machine learning models are typically trained across a wide variety of hyper-parameters to determine the ``best" model by minimizing an optimisation program (minimizing a loss function associated with the machine learning problem) by measuring the loss across many configurations of a model.
-However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of such parameters,
-making it infeasible to exhaustively evaluate the search space.
-Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}--with several researchers noting an inverse relationship between model accuracy and model robustness ~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}.
+
+ML models are typically trained across a wide variety of hyper-parameters where each model is determined by minimizing an optimisation program (minimizing a loss function) associated with the machine learning problem.
+However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
+making it infeasible to exhaustively evaluate the entire hyper-parameter search space.
+Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017} --- with several researchers noting an inverse relationship between model accuracy and model robustness~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}.
 Therefore, a proper search would keep this dual-objective in mind.
@@
 \label{advantages}
-Because of the small number of samples needed for building AFR models (when compared to testing against massive in-distribution test sets), AFR models could, for example, act as a unit test in machine learning applications.
+
+Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in machine learning applications.
 This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}.
 It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}.
-Furthermore, by isolating changes and testing them as quickly as possible, it is  easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test.
-To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictaFted by the ISO 26262 standard \cite{iso26262}.
+Furthermore, by isolating changes and testing them as quickly as possible, it is  easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars, drones, or industrial equipment) to effectively test.
+To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard~\cite{iso26262}.
 This risk analysis is outlined in the subsection below.
@@
 \label{cost}
+
 In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by ISO26262~\cite{iso26262} which allows us to quantify the marginal risk.
@@
 \subsection{Accuracy}
+
 In order to estimate the number of failures in a given time period, we measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.
-Under the AFR framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period as outlined in Fig.~\ref{fig:alg}.
+Under the AFT framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period as outlined in Algorithm~\ref{fig:alg}.
 
 \subsection{Training Time}
-The training time, $T_t$, is the time it takes to evaluate $n$ samples such that the training time per sample $t_t$ is
+
+The training time, $T_t$, is the time it takes to evaluate $n$ samples when $t_t$ is the training time per sample. It is defined as
 $$
-    T_t := t_t \cdot n  \cdot m.
+    T_t := t_t \cdot n  \cdot m,
 $$
@@
 \subsection{Latency}
+
 Latency is the time it takes to respond to a query. We assume that latency per sample is
@@
 $$
-which will be driven by the memory bandwidth (measured in bits/second) of a given CPU or GPU and the size\cite{vgg} and complexity\cite{resnet} of a given neural network architecture.
+which will be driven by the memory bandwidth (measured in bits/second) of a given CPU or GPU and the size~\cite{vgg} and complexity~\cite{resnet} of a given neural network architecture.
 
 \subsection{Attack Generation Time}
+
 A successful attack is one that induces failure in a model.
@@
 \subsection{Cost}
+
 Furthermore, we approach the cost of deployment at two scales.
-Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost.
-However, at a certain scale, (\textit{e.g.} for deploying a self-driving car) it is  more appropriate to talk about cost in terms of power.
+Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using \textit{e.g.}, the Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost.
+However, at a certain scale, (\textit{e.g.}, to deploy a self-driving car) it is  more appropriate to talk about cost in terms of power.
 Finally, we define best-case and worst-case success metrics that provide an efficient way to minimize the latency, cost of deployment, and
-maximize the generalized performance of a model. We define the training cost ($C_t$) as
+maximize the generalized performance of a model. We define the training cost as
 $$
@@
 $$
-where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time.
+where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.
 
 \subsubsection{Power}
-The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
+
+The power consumption for a particular piece of hardware, $P_h$, measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
 $$
@@
 $$
-    P_a = P_h \cdot T_a.
+    P_a = P_h \cdot T_a,
     \label{eq:power_attack}
 $$
-where $P_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time.
+where $P_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.
 
 \subsection{Why Cost Matters}
-% \cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice.
-The \textit{marginal risk} is the change in survival time divided by change in attack compared to some control model such that:
-% \[
-%     \textrm{Marginal~Risk} := \frac{ \Delta S_{\theta}(t)}{\Delta C_a},
-% \]
-% where $\Delta$ reflects the change from the control model.}
 
@@
 For our purposes, by assuming the best-case scenario for both attacker and defender, we can model the Pareto front --- the best-case asymptotic behavior --- of either party~\cite{zitzler2008quality}.
-As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
+As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
 If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
@@
 
-This section outlines specific implementation details for the evaluation of the survival analysis methodology outlined in Sec.~\ref{afr} and the cost analysis methodology outlined in Sec~\ref{cost}.
+This section outlines specific implementation details for the evaluation of the survival analysis methodology outlined in Section~\ref{aft} and the cost analysis methodology outlined in Sec~\ref{cost}.
 
@@
 To conduct the experiments and have access to different types of hardware, we utilized GCP.
-Six virtual machines running Container optimised Operating System provided by GCP constituted our testbed.
-Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster consisting of six worker nodes.
+Six virtual machines running container optimised operating system provided by GCP constituted the test-bed.
+Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0, a cluster consisting of six worker nodes was created.
 Three worker nodes were responsible for running the monitoring platforms such as Prometheus 2.47.2 and Grafana 10.2.0.
 These nodes were of the ``e2-medium" instance type provided by GCP.
-In total, we used three GPU models.
-For P100 and V100 GPUs, we used ``n1-standard-2'' type for the nodes and for L4 GPUs we used ``g2-standard-4''.
+In total, three GPU models were used--the Nvidia P100, V100, and L4.
+For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.
 
-To assess the energy consumption of the experiments deployed on a Google Kubernetes Engine, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}.
-This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components.
-In essence, KEPLER uses extended Berkley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics.
-eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space.
-eBPF programs are invoked by the kernel when certain events occur.
+To assess the energy consumption of the experiments deployed on a Google Kubernetes Engine, the Kubernetes Efficient Power Level Exporter (KEPLER) was employed as measurement tool~\cite{amaral2023kepler}.
+This approach enables gathering energy consumption data on granular levels as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components.
+In essence, KEPLER uses extended Berkeley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics.
+The eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space.
+The eBPF programs are invoked by the kernel when certain events occur.
 Examples of such events include system calls or network activity.
 These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}.
-A diagram of the cloud architecture can be found in Fig.~\ref{fig:architecture}.
-Finally, to meet our goal of developing a cost-effective model evaluation technique, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
+A diagram of the cloud architecture can be found in Figure~\ref{fig:architecture}.
+Finally, for a cost-effective model evaluation technique, all of the experiments were restricted to a single one-thousand United States dollar budget (a research grant from Google).
 Approximately 10\% of this was used for development and 90\% was used for the evaluations.
@@
 
-\subsection{AFR Models}
+\subsection{AFT Models}
 
-For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}.
-We used three optimisation criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
+For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds~\cite{legriel2010approximating}.
+We used three optimisation criteria: benign accuracy, training time, and adversarial accuracy, seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
 We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples.
 Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy.
-Fig.~\ref{fig:experiments} illustrates this methodology.
+Figure~\ref{fig:experiments} illustrates this methodology.
 For each dataset, we tested this on ten random splits of the data.
 For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack.
-Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
-Additionally, we fit the function as described in Fig.~\ref{fig:alg}.
+Using these values, we fit an AFT model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
+Additionally, we fit the function as described in Algorithm~\ref{fig:alg}.
 
 \subsection{Datasets}
-The AFR models were evaluated using the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
+
+The AFT models were evaluated using the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
 Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets.
@@
 \subsection{Models}
-We restricted ourselves to a single model for our evaluations.
+
+The evaluations were restricted to a single model.
 Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware.
-As discussed in Sec.~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict.
+As discussed in Section~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict.
 So, we sampled learning rates $\in [10^{-6}, 1]$, batch sizes $\in [1, 10^5]$, and epochs $\in [1, 50]$ for MNIST and CIFAR10 on the P100 and V100.
-For CIFAR100, we increased the range of the tested epochs to be $\in [1, 100]$.
-To evaluate the efficacy of different bit-depths on the L4 hardware, we used the Feature Squeezing defence~\cite{feature_squeezing} provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{Pytorch} compatible arrays.
+For CIFAR100, the range of the tested epochs was increased to be $\in [1, 100]$.
+The Feature Squeezing defence~\cite{feature_squeezing} was used to evaluate the efficacy of different bit-depths on the L4 hardware, as provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{Pytorch} compatible arrays.
 Model parameters were chosen using the \texttt{Optuna} optimisation framework, the configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.
@@
 \subsection{Attacks}
+
 Since we are examining the effect of model parameters at run-run, we focused on evasion attacks since they induce failures by adding noise to the data at the inference stage.
 Prior research~\cite{meyers} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
-To evaluate the effect of adversarial noise on our samples, we varied $\varepsilon \in [0, 1]$, using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
+To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in [0, 1]$.
+This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
 
 \subsection{GPU Configurations}
-We tested several hardware configurations, which have various hourly costs, peak power demands, and theoretical memory bandwidths.
-The V100 was chosen as a baseline, since it is  routinely used in the literature ~\cite{svedin2021benchmarking,xu2018deep}.
+
+Several hardware configurations were tested, that had various hourly costs, peak power demands, and theoretical memory bandwidths.
+The V100 was chosen as a baseline, since it is routinely used in the literature~\cite{svedin2021benchmarking,xu2018deep}.
 The P100 architecture comes from the same line of server-grade GPUs, but from an older generation.
 The L4, however, is advertised as a machine built for inference --- not training --- relying on a smaller number of bits per tensor core.
-Consequently, the number of operations per second is dependent on the bit depth of the data and the model weights, with the peak numbers outlined in Tab.~\ref{tab:hardware} referring to 8-bit inputs.
+Consequently, the number of operations per second depends on the bit depth of the data and model weights, with peak numbers outlined in Table~\ref{tab:hardware} for 8-bit inputs.
 
@@
     \end{tabular}
-    \caption{Hardware specifications for tested GPUs. All specifications were retrieved from the Nvidia website at the following links: 
+    \caption{Hardware specifications for the tested GPUs. The specifications were retrieved from Nvidia's website at the following links: 
     \href{https://images.nvidia.com/content/technologies/volta/pdf/volta-v100-datasheet-update-us-1165301-r5.pdf}{V100 Datasheet},
@@
     \href{https://nvdam.widen.net/s/rvq98gbwsw/l4-datasheet-2595652}{L4 Datasheet}.
-Prices were retrieved from Google Cloud Platform for the \texttt{europe-west4} region on 3 December 2023 at \href{https://cloud.google.com/pricing/list}{this link.}
+Prices were retrieved from Google Cloud Platform for the \texttt{europe-west4} region on 3 December 2023 at \href{https://cloud.google.com/pricing/list}{this link}.
     }
@@
 \subsection{Survival Analysis}
-In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the function, $S_{\theta}(t)$.
-To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}.
-We also compared the chosen modelling functions (see Sec.~\ref{afr}).
-These results can be found in Sec.~\ref{results}.
+
+In addition to the optimisation criteria of benign/adversarial accuracy and training time, prediction times, attack times, power consumption, batch size, and number of epochs were also collected to be used as covariates of the function, $S_{\theta}(t)$.
+To fit the AFT model and to plot the effect of the covariates, the \texttt{lifelines} Python package was used~\cite{lifelines}.
+The chosen modelling functions (see Section~\ref{aft}) were also compared.
+The results can be found in Section~\ref{results}.
 
 \subsubsection{Hardware}
-The rental cost of the hardware, measured in United States Dollars per hour, will indicate the operating cost of a given model.
-To calculate this, we used the price per hour from each of cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.}}\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
+
+The rental cost of the hardware, measured in United States Dollars per hour, indicates the operating cost of a given model.
+To calculate this, the price per hour from each cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.}}\footnote{Google Cloud prices for L4 obtained \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} were used and the cost of training ($C_{t}$) and the ($C_{i}$) calculated from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
 
@@
 
-In this section, we display and discuss the results for all of the experiments across all datasets and hardware.
-First, we discuss the measured data in Secs.~\ref{res:acc}-\ref{res:cost} before discussing the fitted AFR model in Sec.~\ref{res:afr}.
+This section presents and discusses the results for all of the experiments across all datasets and hardware.
+First, the measured data in Secs.~\ref{res:acc}-\ref{res:cost} are discussed, and then the fitted AFT model in Section~\ref{res:aft}.
 
@@
 \label{res:acc}
-Fig.~\ref{fig:acc} shows the adversarial (right) and benign (left) accuracies for all datasets and hardware.
+
+Figure~\ref{fig:acc} shows the benign (left) and adversarial (right) accuracies for all datasets and hardware.
 It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware.
-Benign accuracy decreases with resolution (CIFAR10 vs MNIST) or with the number of classes (CIFAR10 vs CIFAR100).
-For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (e.g.
-the accuracy we would expect on random noise), demonstrating the efficacy of the attack outlined in Sec.~\ref{optimisation}.
+The benign accuracy decreases with resolution (CIFAR10 vs MNIST) or with the number of classes (CIFAR10 vs CIFAR100).
+For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (\textit{i.e.}, the accuracy we would expect with random data), demonstrating the efficacy of the attack outlined in Section~\ref{optimisation}.
 
@@
     \includegraphics[width=0.5\textwidth,clip]{plots/combined/acc.pdf}
-    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
+    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware.}
     \label{fig:acc}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
-        \caption{Training (left), Prediction (center), and Attack (right) Times}
+        \caption{Training (left), Prediction (center), and Attack (right) Times.}
         \label{fig:time}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
-        \caption{Training (left), Prediction (center), and Attack (right) Power Consumption}
+        \caption{Training (left), Prediction (center), and Attack (right) Power Consumption.}
         \label{fig:power}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
-        \caption{Training (left), Prediction (center), and Attack (right) Monetary Cost}
+        \caption{Training (left), Prediction (center), and Attack (right) Monetary Cost.}
         \label{fig:cost}
@@
 \label{res:cost}
-Fig.~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models.
-Slower hardware (see Memory Bandwidth in Tab.~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
+
+Figure~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models.
+Slower hardware (see Memory Bandwidth in Table~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
 This should be no surprise since the less-capable hardware is meant to be used exclusively for inference.
@@
 
-The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Fig.~\ref{fig:power}.
-It tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric.
-Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).
+The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Figure~\ref{fig:power}.
+It tracks monetary cost (Figure~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is correlated with this metric.
+Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Figure~\ref{fig:power}).
 
-The monetary cost for each dataset and each piece of hardware is shown in Fig.~\ref{fig:cost}.
+The monetary cost for each dataset and each piece of hardware is shown in Figure~\ref{fig:cost}.
 For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
@@
 
-\subsection{AFR Models}
-\label{res:afr}
-Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
-For building the AFR model, we used 75\% of the available data and withheld 25\% for verification.
-The concordance is both strong (>.5) and similar for all three AFR models and both the train and test sets.
-We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFR models.
-Fig.~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFR models.
-For further analysis, we chose the Weibull AFR due to its superior fir in  Fig.~\ref{fig:qq}.
-\input{plots/combined/aft_comparison}
+\input{plots/combined/aft_comparison}  % Table II
 
-Fig.~\ref{fig:aft} shows the log-scale coefficients for the AFR model.
+\subsection{AFT Models}
+\label{res:aft}
+
+Table~\ref{tab:combined} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
+A total 75\% of the available data were used to build the AFT models and 25\% were withheld for verification.
+The concordance is both strong ($>0.5$) and similar for all three AFT models and both the train and test sets.
+We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFT models.
+Figure~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFT models.
+For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}.
+
+Figure~\ref{fig:aft} shows the log-scale coefficients for the AFT model.
 It shows that epochs, batch size, and training time have no effect on the survival time.
@@
 However, we can clearly see that inference time  is as strong an indicator as the attack noise distance, revealing that model speed is at least as important as the attack itself.
-Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance)\cite{carlini_towards_2017}.
+Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance)~\cite{carlini_towards_2017}.
 
-Using the $S_{\theta}(t)$ described in Sec.~\ref{afr}, we can model the partial effect of various hardware devices, which is depicted in Fig.~\ref{fig:partial}.
+Using the $S_{\theta}(t)$ described in Section~\ref{aft}, we can model the effect of various hardware devices, which is depicted in Figure~\ref{fig:dummies}.
 It clearly shows that hardware choice has no bearing on robustness, despite the disparity in cost outlined in Table~\ref{tab:hardware}.
@@
     \end{subfigure}
-    \caption{The red line depicts the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
+    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
+The dotted line indicates a perfect model.}}
     \label{fig:qq}
@@
         \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft.pdf}
-        \caption{Coefficients of the Covariates for the Weibull AFR model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
+        \caption{Coefficients of the Covariates for the Weibull AFT model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
         \label{fig:aft}
@@
         \centering
-        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_device_num_partial_effect.pdf}
-        \caption{Partial Effect  of device on $S_{\theta}(t)$ }
-        \label{fig:partial}
+        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft_dummies.pdf}
+        \caption{Partial Effect of device and dataset on $S_{\theta}(t)$.}
+        \label{fig:dummies}
     \end{subfigure}
-    \caption{Weibull AFR Model.}
+    \caption{Weibull AFT Model.}
 \end{figure}
@@
 \label{considerations}
+
 We have taken much care to conduct these measurements as carefully as possible.
 Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial.
-Given the strong results and uniformity across AFR functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+Given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around data storage, file systems, and various access mechanisms.
-Furthermore, we set the attack batch size and the training batch size to be the same for every trial for each dataset and piece of hardware.
+Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware.
 If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.
 Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth. 
-In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
-We restricted our search to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.
+In general, distributed/federated models were out of scope for this work, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
+The search was restricted to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.
 
@@
 \label{conclusion}
-In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing us the model performance as a function of tested model parameters.
+
+In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing the model performance as a function of tested model parameters.
 We then formalize a technique to model the survival time as a function of various model parameters.
@@
 \bibliography{bibliography}
+
 \end{document}

### 2024-08-15 old (ccgrid).tex
TLs Edits

@@
-%  Moved to main.tex for cloud conference
-% \documentclass[conference]{IEEEtran}
-% \IEEEoverridecommandlockouts
-% % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-% \usepackage{cite}
-% \usepackage{amsmath,amssymb,amsfonts}
-% \usepackage{algorithmic}
-% \usepackage{graphicx}
-% \usepackage{textcomp}
-% \usepackage{xcolor}
-% \usepackage{multirow}
-% \usepackage{hyperref}
-% \usepackage{booktabs}
-% \usepackage{subcaption}
+%% bare_conf.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%% 
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% conference paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
 
-% % \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
 
-% \newcommand{\cm}[1]{#1}
-% \newcommand{\mr}[1]{\textit{{\color{red}#1}}}
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
 
-% % \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-% %     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-% % \begin{document}
+\documentclass[conference]{IEEEtran}
+% Some Computer Society conferences also require the compsoc mode option,
+% but others use the standard conference format.
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[conference]{../sty/IEEEtran}
 
-% \title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}
-% % \thanks{Identify applicable funding agency here. If none, delete this.}
-% % \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
-% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+%\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{multirow}
+\usepackage{hyperref}
+\usepackage{booktabs}
+\usepackage{subcaption}
+\usepackage{algpseudocode}
+
+% \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
+
+\newcommand{\cm}[1]{#1}
+\newcommand{\mr}[1]{\textit{{\color{red}#1}}}
+\begin{document}
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+\title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}
+
+% author names and affiliations
+% use a multiple column layout for up to three different
+% affiliations
+% \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
+% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
+% \textit{Umeå University}\\
+% Umeå, Sweden \\
+% cmeyers@cs.umu.se}
+% \and
+% \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
+% \IEEEauthorblockA{\textit{Elastisys} \\
 % % \textit{Umeå University}\\
-% % Umeå, Sweden \\
-% % cmeyers@cs.umu.se}
-% % \and
-% % \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
-% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-% % \textit{Umeå University}\\
-% % Umeå, Sweden \\
-% % fake@fake.se}
-% % \and
-% % \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
-% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-% % \textit{Umeå University}\\
-% % Umeå, Sweden \\
-% % tommy@cs.umu.se}
-% % \and
-% % \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
-% % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-% % \textit{Umeå University}\\
-% % Umeå, Sweden \\
-% % elmroth@cs.umu.se}
-% % }
+% % Lund, Sweden \\
+% mohammad.saleh@elastisys.com}
+% \and
+% \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
+% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
+% \textit{Umeå University}\\
+% Umeå, Sweden \\
+% tommy@cs.umu.se}
+% \and
+% \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
+% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
+% \textit{Umeå University}\\
+% Umeå, Sweden \\
+% elmroth@cs.umu.se}
+% }
 
-% \maketitle
+% conference papers do not typically use \thanks and this command
+% is locked out in conference mode. If really needed, such as for
+% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
+% after \documentclass
 
-% \begin{abstract}
-% Considering the growing prominence of production-level AI and the threat of adversarial attacks that can poison a machine learning model against a certain label, evade classification, or reveal sensitive data about the model and training data to an attacker, adversaries pose fundamental problems to machine learning systems.
-% Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
-We address the problem of neural network validation and verification.
-More specifically, we address the problem of continuous integration and deployment for safety-critical models.
-% For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, meaning that each software change would need to be evaluated against new real-world deployment samples which can be prohibitively expensive or time-consuming to collect.
-To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture.
+% for over three affiliations, or if they all won't fit within the width
+% of the page, use this alternative format:
+% 
+%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
+%Homer Simpson\IEEEauthorrefmark{2},
+%James Kirk\IEEEauthorrefmark{3}, 
+%Montgomery Scott\IEEEauthorrefmark{3} and
+%Eldon Tyrell\IEEEauthorrefmark{4}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
+%Georgia Institute of Technology,
+%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212, Fax: (888) 555--1212}
+%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
+\maketitle
+
+\begin{abstract}
+Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model a run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
+Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
+In this paper, we use survival analysis to present a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.
+For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data.
+However, in practice, this means that each model configuration needs to be evaluated against real-world deployment samples which can be prohibitively expensive or time-consuming to collect --- especially when other parts of the software or hardware stack are developed in parallel.
+To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world.
 We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously.
-This provides a way to evaluate the model and optimize it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy.
+This provides a way to evaluate the model and optimise it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy.
 Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
-% \end{abstract}
+\end{abstract}
 
-% \begin{IEEEkeywords}
-% artificial intelligence, machine learning, adversarial AI, optimization, compliance
-% \end{IEEEkeywords}
+\begin{IEEEkeywords}
+artificial intelligence, machine learning, adversarial AI, optimisation, compliance
+\end{IEEEkeywords}
 
-% \section{Introduction}
-% \subsection{Motivations}
-% % \begin{itemize}
-% %     % \item \textit{BIG} Data is the trend
-% %     % \item Costs are astronomical
-% %     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
-% %     \item Other work relies on unreliable test/train split methodology
-% %     \item Which means that cars, medical equipment is tested in the wild
-% % \end{itemize}
-
-% Recently, machine learning (ML) using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
-However, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
-Furthermore, popular models like Generative Pre-trained Transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions of parameters, requiring equally large training datasets.
-Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
-Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
-Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}.
-The newest version of this open-source large language model (LLM) is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}.
-Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be between $[1e-12, 1e-15]$ depending on the number of lives at risk ~\cite{iso26262}.
-Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
-Collecting, labelling, and testing a new set of data for every software change-as required by law-would be prohibitively expensive.
-Therefore, a new evaluation methodology is required.
-As such, the proposed methodology, centered around survival analysis, tests a model against "worst-case" (e.g.
-adversarial) input to verify the efficacy of one modelling deployment decision over another.
-\cm{This methodology allows to minimize the training cost, optimize for adversarial robustness, and estimate the partial effects of covariates on model performance during routine training procedures.}
-
-% \subsection{Contributions}
-% So, in order to tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective technique and source code that:
+\section{Introduction}
+\subsection{Motivation}
 % \begin{itemize}
-%     \item optimizes for benign and adversarial accuracy simultaneously,
-%     \item extends survival analysis to the realm of neural networks, 
-%     \item demonstrates a scalable and effective method that allows us to tune a model while simultaneously estimating the asymptotic effect of various hyperparameters,
-%     \item and measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
-%     \item We show that, despite a decrease in training time, that faster hardware, more precise hardware, and/or more power-hungry hardware do not lead to more adversarial robust models.
-
+%     % \item \textit{BIG} Data is the trend
+%     % \item Costs are astronomical
+%     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
+%     \item Other work relies on unreliable test/train split methodology
+%     \item Which means that cars, medical equipment is tested in the wild
 % \end{itemize}
 
-% \section{Background}
-% ML pipelines play a crucial role in the development and deployment of robust and accurate models.
+Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
+Statistical learning theory \cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
+To overcome this, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has  yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
+We also know that  reaching safety-critical standards using test-set accuracy would require an infeasibly large test set \cite{meyers}.
+Therefore, we propose using accelerated failure time models to simulate edge-cases and verify models using a small number of samples.
+
+Modern neural networks are massive--- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}.
+One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
+Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}.
+One version of this open-source large language model (LLM) was able to outperform the commercially available GPT-3.5 model~\cite{liu2023goat} with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU), suggesting that consumer-level hardware can be used to effectively train large models in a reasonable time.
+Furthermore, popular models like Generative Pre-trained Transformer (GPT)~\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions or billions of parameters, requiring infeasibly large training datasets to verify a model\cite{vcdimension}.
+Media reports place the cost of training a GPT3 somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
+While the benefits of a more portable model are plentiful, there is not yet a method for formalizing the relationship between cost and model performance.
+
+Furthermore, even if we ignore the immense cost of training modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for assessing model generalization~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk.
+Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern since inducing a failure at run-time has consistently shown to be trivial~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
+Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive.
+Therefore, a new evaluation methodology is required.
+
+% As such, the methodology proposed in this paper, centered around survival analysis, tests a model against ``worst-case" (\textit{e.g.}, adversarial) inputs to verify the efficacy of one modelling deployment decision over another.
+We propose to use survival analysis as a methodological framework to model the failure conditions of a machine learning model.
+Instead of having a test set large enough to cover all of the failure cases, we generate adversarial samples crafted specifically to make the model fail and then use survival analysis to predict these failures in general.
+
+In this paper, we use accelerated methods to predict model performance as a function of various model parameters.
+The methodology outlined in Sec.~\ref{afr} allows the model-builder to minimize the training cost, optimise for adversarial robustness, estimate the partial effects of covariates on model performance during routine training procedures.
+Then, one can perform a cost analysis (Sec.~\ref{cost}).
+We then demonstrate the efficacy of this methodology in Sec.~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Sec.~\ref{experiments}.
+
+\subsection{Contributions}
+To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see: Figs.~\ref{fig:alg}\&~\ref{fig:experiments}) and software framework (see: Fig.~\ref{fig:architecture}) for the training (see: Sec.~\ref{afr}) and evaluation (see: Sec.~\ref{cost}) of machine learning models that:
+\begin{itemize}
+    \item optimises for benign and adversarial accuracy simultaneously,
+    \item Extends survival analysis to the realm of neural networks, 
+    \item Demonstrates a scalable and effective method that trains a model while simultaneously estimating the asymptotic effect of various hyperparameters, and
+    \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.   
+\end{itemize}
+
+Sec.~\ref{background} defines terms used throughout the paper.
+Sec.~\ref{afr} outlines the training and evaluation methodology presented in this paper.
+Section ~\ref{cost} outlines the resulting cost analysis framework, arising from the methodology in the previous section.
+Sec.~\ref{experiments} outlines the software components and specific experiments that were conducted, while Sec.~\ref{results} contains the results and discussions of those experiments.
+Sec.~\ref{considerations} and Sec.~\ref{conclusion} reveal the caveats and the conclusions respectively.
+
+\section{Background}
+\label{background}
+
+In this paper, we present a comprehensive methodology for evaluating model robustness during training time and model the asymptotic effect of the various parameters in the search space.
+For the sake of the reader, we provide a section for definitions and requisite background information below.
+
+% Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying ML models under varying computational and adversarial constraints. 
+\subsection{Cloud Architectures}
+
+ML pipelines play a crucial role in the development and deployment of robust and accurate models.
 However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
-In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex ML pipeline.
-%  As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises.
-The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference.
-Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.
+As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises.
+The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, attack generation, and inference.
+Efficiently orchestrating  and evaluating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.
 
-% To address these challenges, containerization and orchestration technologies have gained prominence in managing complex ML pipelines.
-Kubernetes, a widely adopted container orchestration platform, provides a scalable and flexible environment for deploying, scaling, and managing microservice-based applications.
-Its ability to handle heterogeneous hardware architectures and workload distribution across clusters makes it an ideal choice for managing the complex computational requirements of ML pipelines.
+One popular solution is using a network of interconnected services \cite{panchal2024reusable,hasselbring2017microservice,zhong2022machine,singh2023load}.
+A \textit{service} is the smallest component of a ``cloud-native" software stack.
+In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
+A service \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the services within the system.
+These components facilitate various capabilities and functionalities essential for managing the communication between services.
+Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures using a service mesh.
+For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}.
+In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see: Fig.~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see: Fig.~\ref{fig:architecture}) across a variety of different hardware architectures (see: Tab.~\ref{tab:hardware}).
 
-% % Using this microservice architecture, it's possible explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts across heterogeneous hardware to minimize the deployment cost in the cloud.
-% % Additionally, understanding the relationship between computational cost, model loss, and prediction accuracy is vital for optimizing the pipeline's performance.
-Balancing computational resources, time constraints, and accuracy requirements is a fundamental consideration in deploying ML models in production environments.
-By analyzing the impact of computational cost on model loss and accuracy metrics, we can gain insights into the trade-offs involved and make informed decisions to optimize the pipeline's efficiency.
-
-% In this paper, we present a comprehensive study that leverages Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of GPU architectures.
-We then investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts.
-Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying ML models under varying computational constraints and adversarial conditions.
-
-% For the sake of the reader, we provide a section for definitions and requisite background information below.
-
-% \subsection{Cloud Architectures}
-% A \textit{microservice} is the smallest component of a `cloud-native' software stack.
-In the context of ML, that might be a tool for either training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
-A microservice \textit{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between microservices in a distributed system.
-It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services.
-
-% A microservice \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the microservices within the system.
-These components facilitate various capabilities and functionalities essential for managing the communication between microservices.
-Kubernetes has become one of the largest open source projects on the code-sharing website Github \cite{k8s-size}, which provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures.
-
-% \subsection{ML Pipelines}
-% ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters.
+\subsection{ML Pipelines}
+ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters.
 Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}.
@@
 
-% \subsection{Classifiers}
+\subsection{Classifiers}
 
-% A classifier, $K(x; \theta)$, with model parameters, $\theta$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization without loss of generality.} an \textit{objective} (or \textit{loss}) \textit{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the loss value, $L$ for some optimal set of parameters, $\theta^*$ is:
-% \[
-% L(y, K(x, \theta^*)) = \mathrm{argmin}_{\theta \in \Theta} (y - K(x, \theta)).
-% \]
-%  In the case of neural networks, however, finding the optimal set of hyper-parameters is non-trivial as the number of tunable parameters is often measured in the millions and the loss function is non-convex.
-Instead of finding an analytical solution to this equation, we often rely on numerical optimisation, and one choice is \textit{stochastic gradient descent}, which samples the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss.
-This is in the direction of the negative gradient of the loss, $-\nabla L(y, K(x, \theta))$.
-This procedure is repeated for some number of \textit{epochs} (iteration through the entire training set), $i$, and every iteration thus performs the step,
-% \[
-% \theta^{(i+1)} = \theta^{(i)} - \eta \nabla_{\theta} L(y, K(x, \theta^{(i)}))
-% \]
-% where $\eta$ is a \textit{learning rate} that is tuned to the particular model and fixed batch size.
+We consider classifiers, $K(x; \theta)$ with model parameters, $\theta$.
+The true labels are denoted by $y$, and the model predictions by $\hat{y} = K(x; \theta)$ and $x$ is a batch of samples with size $N$.
+The loss function is denoted by $L(y, \hat{y})$.
+Because of the complexity of modern machine learning models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset of the training samples.
+% selects the next $N$ samples from the training set before adjusting the model parameters, $\theta$, in the direction that decreases the loss.
+% This is in the direction of the negative gradient of the loss, $-\nabla L(y, K(x, \theta))$.
+This procedure is repeated for some number of \textit{epochs} (iterations through the entire training set). Every iteration takes a step,
+\begin{equation}
+    \theta^{(i+1)} = \theta^{(i)} - \eta \nabla_{\theta^{(i)}} L(y, K(x, \theta^{(i)}))
+    \label{eq:sgd}
+\end{equation}
+where the gradient is approximated using $b$ batches per epoch and $\eta$ is a \textit{learning rate} (or step size) that is tuned to the particular model.
 
-% \subsection{Learning Rate Selection}
-% \label{learning_rate}
-% Choosing the correct learning rate is critical for model performance---greatly effecting both the accuracy and the run-time requirements.
-A small learning rate will have a smaller error bound ~\cite{}, but will converge slower, all other things being equal.
-Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data ~\cite{}.
-Graphics cards with larger amounts of RAM will be able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch.
-In theory, a `good' learning rate can converge quickly ~\cite{smith2019super} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, and bit depth of the data.
-However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so we must evaluate this \textit{in situ}.
-Furthermore, since hardware is billed by the hour, optimizing the training and inference times allows us to minimize the cost of deployment.
+\subsection{Learning Rate Selection}
+\label{learning_rate}
 
-% \subsection{Adversarial Attacks}
-% \label{attacks}
-% In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models.
+Choosing the correct learning rate is critical for model performance --- greatly effecting both the accuracy and the training cost.
+A small learning rate will will more closely follow the true gradient of a class boundary~\cite{cao2019generalization}, but will converge slower, all other things being equal.
+Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data, \textit{etc}~\cite{granziol2022learning}.
+Graphics cards with larger amounts of RAM are able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch.
+A ``good" learning rate will allow a model converge quickly~\cite{smith2019super,granziol2022learning} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, scale, and bit depth of the data.
+However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}.
+Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.
+
+\subsection{Adversarial Attacks}
+\label{attacks}
+In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models.
 Adversarial attacks are designed to deceive or change the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or otherwise produce undesired outputs.
-That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $y'$.
+That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $\hat{y_a}$.
 That is \textit{adversarial success} or \textit{accelerated failure} is one in which
-% \begin{equation}
-%     \hat{y} \neq y' = K(x + \varepsilon; \theta).
-% \label{eq:adv_success}
-% \end{equation}
-% Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accurracy}.
+\begin{equation}
+    \hat{y} \neq \hat{y_a} = K(x + \varepsilon; \theta).
+\label{eq:adv_success}
+\end{equation}
+Additionally, one can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accuracy} which is Eq.~\ref{eq:acc} calculated on the perturbed samples.
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
@@
 
-% % \cm{I cut itemized list more discussion about learning rate tuning?}
-% % \begin{itemize}
-% %     \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying certain inputs or otherwise change the behavior of a modelt~\cite{ carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
-% %     \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset to influence the model's behaviour at run-time~\cite{biggio_poisoning_2013, saha2020hidden}.
-% %     \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
-% %     \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
-% % \end{itemize}
+% \cm{I cut itemized list more discussion about learning rate tuning?}
+% \begin{itemize}
+%     \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying certain inputs or otherwise change the behavior of a modelt~\cite{ carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
+%     \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset to influence the model's behaviour at run-time~\cite{biggio_poisoning_2013, saha2020hidden}.
+%     \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
+%     \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
+% \end{itemize}
 
-% One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}.
-It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that,
-% \begin{equation}
-% x' = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
-% \label{eq:fgm}
-% \end{equation}
-% In essence, this is process seeks to maximize loss in contrast to model training which seeks to minimize it.
+One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}.
+It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x_a$, such that,
+\begin{equation}
+x_a = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
+\label{eq:fgm}
+\end{equation}
+In essence, this is process seeks to increase the loss  in contrast to model training which seeks to minimize it.
 
-% \subsection{Adversarial Analysis}
+\subsection{Adversarial Analysis}
 
-% In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}.
-Whether we discuss automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}.
+In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}.
+Whether in the context of automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}.
 An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable.
@@
 This is just not computationally feasible.
-Instead, we can use adversarial failure analysis to improve the precision of our measurements while only using a small set of test-data.
+Instead, researchers can use adversarial failure analysis~\cite{carlini_towards_2017,biggio_evasion_2013,meyers} to improve the precision of our measurements while only using a small set of test-data.
 
-% \cm{Moved Accuracy/ Failure Rate to this section}
-% \section{AFR models for Robustness Verification during Training}
-% \label{afr}
-% Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
+\section{Survival Analysis for Robustness Verification during Training}
+\label{afr}
 
-% \subsection{Accuracy}
-% The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}.
-It measures the vulnerability or susceptibility of the model to noise-induced failures.
+We propose a methodology for model training and verification using accelerated failure rate (AFR) models, drawn from the field of \textit{survival analysis}.
+Additionally, since one goal is cost-efficiency, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
+AFR models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
+In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components.
+This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
+The section below outlines our methodology for modelling the effect of model hyper-parameters during routine training procedures.
+In this section, we precisely outline the methodology for using survival analysis during the training of machine learning algorithms.
+First, we provide a formal algorithm in Fig.~\ref{fig:alg} and a visual diagram in ~\ref{fig:experiments}.
+Then, in  the subsections below, we define accuracy (Sec.~\ref{acc}) and failure rate (Sec.~\ref{failure_rate})  in the context of survival analysis to provide a pedagogical definition of survival time (Sec.~\ref{survival_time}).
+We then discuss the importance of the ``acceleration assumption" (Sec.~\ref{accelerated}), the optimisation algorithm (Sec.~\ref{optimisation}), and the advantages of this approach (Sec.~\ref{advantages}).
+
+\begin{figure}[h!]
+    \caption{\textbf{Algorithm: }Survival Analysis for ML}
+    \label{fig:alg}
+\begin{algorithmic}
+    \Require Samples $x$ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and a number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, e.g.
+$N_t$ is size of the training set.
+    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
+    \State $i = 0$
+    \While{ $i < n$}
+    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
+    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
+    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
+    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
+    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
+    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
+    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
+    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
+    \State \textbf{Infer:}  $ \hat{y}_a = K(x_a, \theta) $.
+    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
+    \EndWhile
+    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
+    \State \textbf{Return:} $S_{\theta}$
+\end{algorithmic}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.35\textwidth]{plots/experiment.pdf}
+    \caption{Experimental Pipeline Diagram}
+    \label{fig:experiments}
+\end{figure}
+
+\subsection{Accuracy}
+\label{acc}
+  Accuracy measures the vulnerability or susceptibility of the model to noise-induced failures.
 A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures.
 Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data.
-The benign accuracy is defined as
-% \begin{equation}
-%  \mathrm{Accuracy} = 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}}
-% \label{eq:acc}
-% \end{equation}
-% which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}.
+The accuracy, $\lambda$, is defined as
+\begin{equation}
+    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
+    \label{eq:acc}
+\end{equation}
+which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}.
 However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}.
-Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
-In addition,  ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}.
+In addition, it ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}.
+Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
+We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test set $\lambda_{adv}$ to denote the accuracy on the adversarial examples.
 
-% % \cm{Didn't discuss adversarial success again.}
-% % Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples, such that 
-% % $$
-% %     y\neq\hat{y}\text{~~while~~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max},
-% % $$ 
-% % where $\| \cdot \|$ represents some norm or pseudo-norm and $\varepsilon$ is some specified  perturbation distance threshold bound by a maximum distance, $\varepsilon_{max}$.
+\subsection{Failure Rate}
+\label{failure_rate}
+The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}.
+To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, such that the failure rate is
+\[
+    h_{ \theta}(t) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t} t,
+\]
+where $\mathbb{P}(\textrm{False~Classification})$ is the probability of a false classification, $\Delta t$ is a time interval, and $t$ is a point in time.
+Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$.
+By re-parameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure rate model.
 
-% \subsection{Failure Rate}
-%  To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates (\textit{e.g.}, noise distance, model size, hardware resources, $\theta$) such that,
-% \[
-%     h_{ \theta}(t) :=  \frac{P(\textrm{False~Classification})}{\Delta t} t
-% \]
-% where $P(\textrm{False~Classification})$ is the probability of a false classification and $\Delta t$ is a time interval.
-\cm{Note that this is equivalent to 1 - accuracy when $\Delta t = t$.} To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textit{survival time}, $S(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
-% $$
-% S_{\theta}(t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
-% $$
-% We can use the survival function to compute the expected survival time or average time-to-failure:
-% \[
-% 	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty} t \cdot S_\theta(t) \,dt.
-% \]
-
-% \subsection{Survival Time}
-% \label{survival_time}
-% \cm{Accelerated failure time models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$.
+\subsection{AFR Models}
+\label{survival_time}
+Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$.
 For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely.
@@
 For machine learning, this means inducing failures during training to measure generalization performance.
-For each trial, we measured the prediction time for both benign and adersarial samples to define our time interval and used benign/adversarial accuracy as an estimate of the number of failures in that time interval.} However, modelling $S_{\theta}(t)$ requires a choice in modelling distribution for $S$.
-Log-Logistic, Log-Normal, and Weibull distributions are widely used options.
-To choose a best-fit model, we compared Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}.
-This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial.
-However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces.
-In order to minimize the cost of evaluation, we must be clever about how we search.
 
-% % \subsection{Pareto Set}
+The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
+$$
+S_{\theta}(t)= \mathbb{P}(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
+$$
+where $\mathbb{P}(T>t)$ is the probability that a model has not failed by time $t$. Then, the expected survival time is
+\[
+	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty}  S_\theta(t) \,dt.
+\]
 
-% % In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{kamal2017study,leurent2020sha}.
-A subset of examples that maximize one or more objective criteria is called the \textit{pareto front}~\cite{zitzler2008quality}.
-It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}.
-Table~\ref{tab:pareto} shows the required number of queries to get estimates within the $\varepsilon$-sphere of the true Pareto front.
-As we can see, it is critical to minimize the dimensionality of our search.
-So instead of optimizing for latency, training time, cost, accuracy, and adversarial success rate independently, we introduce several metrics in the next section.
+However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$.
+The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival}.
+For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval.
+This should be measured in both the benign and adversarial contexts.
+The full algorithm can be seen in Fig.~\ref{fig:alg}.
 
-% % % Please add the following required packages to your document preamble:
-% % % \usepackage{multirow}
-% % % Please add the following required packages to your document preamble:
-% % % 
-% % \begin{table}[h!]
-% % \begin{tabular}{cl|llll|}
-% % \cline{3-6}
-% %                                            &   & \multicolumn{4}{c|}{$\varepsilon$}            \\ \cline{3-6} 
-% %                                            &   & .1     & .05          & .01    & .001      \\ \hline
-% % \multicolumn{1}{|c|}{\multirow{3}{*}{$d$}} & 1 & 10     & 20           & 100    & 1000      \\
-% % \multicolumn{1}{|c|}{}                     & 2 & 100    & 400          & $10^4$ & $10^6$    \\
-% % \multicolumn{1}{|c|}{}                     & 4 & $10^4$ & $1.6 * 10^5$ & $10^9$ & $10^{12}$ \\ \hline
-% % \end{tabular}
-% % \caption{This table shows the number of queries required to $\varepsilon-$ approximate the Pareto front, $\mathcal{P}$, in $d$ dimensions.}
-% % \label{tab:pareto}
-% % \end{table}
+To choose a best-fit from the possible AFR functions, one should prepare the collected metrics and scores.
+Then, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}.
+For AIC and BIC, that means choosing the smallest value.
+Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and .5 reflects random chance.
+By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}.
+In addition, one should measure the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}.
+These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively ~\cite{ici}.
+Then, one should plot all the expected and observed values for all three functions according to the method described by Austin et al.~\cite{ici} (see: Fig.~\ref{fig:qq}) to visually inspect each model for goodness-of-fit.
 
-% \subsection{Optimization}
-%  \cm{Machine learning models are typically trained across a wide variety of hyper-parameters and determining the "best" model by solving some optimization problem (typically maximizing accuracy or minimizing loss) through posterior evaluations across the entire search space.} However, these hyper-parameters are often drawn from continuous and infinite spaces, so it's impossible to exhaustively evaluate the search space.
-Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}, meaning that a proper search would keep this dual-objective in mind.
-Luckily, the field of multi-objective search is well researched.
-We chose the Tree-structure Parzen Estimator (TPE) because of it's ability to work on mini-batches, in distributed settings, and while optimizing multiple objectives in a feasible number of trials ~\cite{ozaki2020multiobjective}, though research in this field is very much ongoing~\cite{ozaki2022multiobjective}.
-The ideal algorithm will vary with the distribution of the parameters, the population size of the search space, and the presence or absence of categorical variables.
+\subsection{Benign and Adversarial Survival Time}
+\label{accelerated}
+Using accelerated failure rate models, we can find the expected survival time under optimistic circumstances, $S_{ben}$ as well as under adverse ones (accelerated failure rate), $S_{adv}$.
+The survival time for benign samples is
+$$
+    S_{ben} := S(t_i; x, y, \theta) \mathrm{~~where~~} \varepsilon = 0
+$$
+and the survival time for the adversarial samples is
+$$
+    S_{adv} :=  S(t_i; x, y, \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
+$$
+This can also be thought of in terms of the accelerated failure rate assumption~\cite{kleinbaum1996survival}:
+\begin{equation}
+S_{adv} \approx  \phi S_{ben}(\phi t)
+\label{assumption}
+\end{equation}
+where $\phi$ is some acceleration factor describing the joint effect of the covariates.
+This assumption means we can evaluate the benign accuracy using a small number of adversarial samples ~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
+However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space intelligently.
 
-% \subsection{Metrics}
+\subsection{Optimisation}
+\label{optimisation}
+Machine learning models are typically trained across a wide variety of hyper-parameters to determine the ``best" model by minimizing an optimisation program (minimizing a loss function associated with the machine learning problem) by measuring the loss across many configurations of a model.
+However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of such parameters,
+making it infeasible to exhaustively evaluate the search space.
+Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}--with several researchers noting an inverse relationship between model accuracy and model robustness ~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}.
+Therefore, a proper search would keep this dual-objective in mind.
+To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}.
 
-%  In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack, as well as the benign and adversarial accuracies (see: Secs.~\ref{eq:acc} and ~\ref{eq:adv_success}).
-80\% percent of the data for each dataset was used for training and the remaining twenty percent was used for evaluation.
-We withheld 100 examples from the test set as the initial values for adversarial examples, which gives us two significant figures for this measurement, while benign accuracy was measured with 10s of thousands of samples, giving us 4 significant figures for that metric.
-For all reported times, we assumed that the time was distributed uniformly across the samples to minimize jitter and account for GPU-based parallelization.
-
-% \subsubsection{Accuracy}
-% We measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.
-
-% % \subsection{Benign Success}
-% % A \textit{success} can be thought of in both the adversarial and benign context, which are denoted with the subscripts $ben.,adv.$ throughout this work.
-Typically this is measured via the train/test methodology in which some subset of a benchmark dataset.
-However, this method has repeatedly shown itself to be an inadequate measure of real-world model performance, and is, at best, an optimistic best-case measure of the failure rate~\cite{croce_reliable_2020}.
-The benign success ratio is usually measured via the train/test split methodology mentioned in typical in the literature.
-
-% % \subsection{Adversarial Success}
-% % A successful adversary, however, is one that is able to change the model's output from one class to another.
-For the benign case, we measure the test set accuracy as our success metric.
-However, we m
-
-% % Furthermore, the computational difficulty of this task is often related to secondary optimization criteria~\cite{}, with a baseline of at least NP-Hard~\cite{madry2017towards}.
-Since many of the attacks have more success after a number of iterations\cite{fgm,deepfool,carlini_towards_2017,madry2017towards,hopskipjump}, it is appropriate to think about their success in terms of time.
-
-% \subsubsection{Training Time}
-% The training time, $T_t$, is the time it takes to evaluate $n$ samples such that the training time per sample per epoch $t_t$ is.
-% $$
-% T_t := t_t\cdot n
-% $$
-
-% \subsubsection{Latency}
-% Latency is the time it takes to respond to a query. We assume that latency per sample is:
-% $$
-% T_i  := t_i \cdot n
-% $$
-% which will be driven by the memory bandwidth (measured in bits/second) of a given cpu- or gpu- and the size\cite{vgg} and complexity\cite{resnet} of a given neural network architecture.
-
-% \subsubsection{Attack Generation Time}
-% A successful attack is one that induces failure in a model.
-That is, the expected survival time, $\mathbb{E}[S(t;x,y,\theta)]$, can be thought of as the time it takes for an attacker to induce a change in the model output.
-We approximate this for each attack/defence configuration by taking the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$:
-
-% \begin{equation}
-% T_a := t_i \cdot n \cdot i
-% \label{attack_time}
-% \end{equation}
-
-% In the interest of attack speed, we restricted this to a single iteration.
-
-% \subsubsection{Cost}
-% Furthermore, we can think of cost of deployment at two scales.
-Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using GCP compute costs as a measure of total cost.
-However, at a certain scale, (\textit{e.g.} for deploying a self-driving car) it's more appropriate to talk about cost in terms of power.
-Finally, we define best-case and worst-case success metrics that give us an efficient way to minimize the latency, cost of deployment, and
-% maximize the generalized performance of a model. We define the training cost ($C_t$) as:
-% $$
-%     C_t = C_h \cdot T_t,
-%     \label{eq:cost_training}
-% $$
-% the cost of model inference time as:
-% $$
-%     C_i = C_h \cdot T_i,
-%     \label{eq:cost_inference}
-% $$
-% and the cost of an attack as:
-% $$
-%     C_a = C_h \cdot  T_a.
-%     \label{eq:cost_attack}
-% $$
-
-% \subsubsection{Power}
-% The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
-% $$
-%     P_t = P_h \cdot T_t,
-%     \label{eq:power_training}
-% $$
-% the power consumption during model inference is:
-% $$
-%     P_i = P_h \cdot T_i
-%     \label{eq:power_inference}
-% $$
-% and the power consumption during attack generation is:
-% $$
-%     P_a = P_h \cdot T_a
-%     \label{eq:power_attack}
-% $$
-
-% \subsection{Advantages of this Methodology}
-% \cm{moved}
-
-% Because of the relatively small run-time requirements of this approach (when compared to testing against massive in-distribution test sets), this method could, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism.
-It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples.
-Furthermore, by isolating changes and testing them as quickly as possible, it's much easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test.
-To further increase development velocity, we can use these models to quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}.
+\subsection{Advantages of this Methodology}
+\label{advantages}
+Because of the small number of samples needed for building AFR models (when compared to testing against massive in-distribution test sets), AFR models could, for example, act as a unit test in machine learning applications.
+This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}.
+It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}.
+Furthermore, by isolating changes and testing them as quickly as possible, it is  easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test.
+To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictaFted by the ISO 26262 standard \cite{iso26262}.
 This risk analysis is outlined in the subsection below.
 
-% \subsubsection{Relative Cost to an Attacker}
-% In security analysis, it's routine to think in optimistic terms for both the attacker and defender.
-\cm{In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptogrpahic system~\cite{kamal2017study,leurent2020sha} (e.g.
-whether or not a given cryptographic method should be considered "broken").}
-% As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which is both effective and fast.
-If the cost to a model builder is much larger than the cost to an attacker ($C_t >> C_a$), then it's clear that model is "broken" in this cryptographic sense and can be discarded as ineffective.
+\section{Cost Analysis}
+\label{cost}
+In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by ISO26262~\cite{iso26262} which allows us to quantify the marginal risk.
+To quantify this marginal risk, one must measure the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack.
+The final subsection outlines why these metrics are important and their usage in this methodology.
 
-% \section{Implementation Details}
+\subsection{Accuracy}
+In order to estimate the number of failures in a given time period, we measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.
+Under the AFR framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period as outlined in Fig.~\ref{fig:alg}.
 
-% This section outlines specific implementation details for the evaluation of the methodology proposed in Section~\ref{afr}.
+\subsection{Training Time}
+The training time, $T_t$, is the time it takes to evaluate $n$ samples such that the training time per sample $t_t$ is
+$$
+    T_t := t_t \cdot n  \cdot m.
+$$
+where $m$ is the number of epochs.
 
-% \subsection{Cloud Platform and Hardware}
-% To conduct the experiments and have access to different types of hardware, we utilized Google Cloud Platform (GCP).
-Six virtual machines running Container Optimized Operating System provided by GCP constitute our testbed.
+\subsection{Latency}
+Latency is the time it takes to respond to a query. We assume that latency per sample is
+$$
+    T_i := t_i \cdot n,
+$$
+which will be driven by the memory bandwidth (measured in bits/second) of a given CPU or GPU and the size\cite{vgg} and complexity\cite{resnet} of a given neural network architecture.
+
+\subsection{Attack Generation Time}
+A successful attack is one that induces failure in a model.
+That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output.
+We approximate this for each attack/defence configuration by the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
+\begin{equation}
+    \label{attack_time}
+    T_a := t_a \cdot n \cdot i.
+\end{equation}
+We restricted this to a single iteration such that $i =1$ as described in FGM~\cite{fgm}.
+
+\subsection{Cost}
+Furthermore, we approach the cost of deployment at two scales.
+Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost.
+However, at a certain scale, (\textit{e.g.} for deploying a self-driving car) it is  more appropriate to talk about cost in terms of power.
+Finally, we define best-case and worst-case success metrics that provide an efficient way to minimize the latency, cost of deployment, and
+maximize the generalized performance of a model. We define the training cost ($C_t$) as
+$$
+    C_t = C_h \cdot T_t,
+    \label{eq:cost_training}
+$$
+the cost of model inference time as,
+$$
+    C_i = C_h \cdot T_i,
+    \label{eq:cost_inference}
+$$
+and the cost of an attack as,
+$$
+    C_a = C_h \cdot T_a.
+    \label{eq:cost_attack}
+$$
+where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time.
+
+\subsubsection{Power}
+The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
+$$
+    P_t = P_h \cdot T_t,
+    \label{eq:power_training}
+$$
+the power consumption during model inference is
+$$
+    P_i = P_h \cdot T_i,
+    \label{eq:power_inference}
+$$
+and the power consumption during attack generation is
+$$
+    P_a = P_h \cdot T_a.
+    \label{eq:power_attack}
+$$
+where $P_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time.
+
+\subsection{Why Cost Matters}
+% \cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice.
+The \textit{marginal risk} is the change in survival time divided by change in attack compared to some control model such that:
+% \[
+%     \textrm{Marginal~Risk} := \frac{ \Delta S_{\theta}(t)}{\Delta C_a},
+% \]
+% where $\Delta$ reflects the change from the control model.}
+
+ In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
+In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
+For our purposes, by assuming the best-case scenario for both attacker and defender, we can model the Pareto front --- the best-case asymptotic behavior --- of either party~\cite{zitzler2008quality}.
+As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
+If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
+
+\section{Experiments}
+\label{experiments}
+
+This section outlines specific implementation details for the evaluation of the survival analysis methodology outlined in Sec.~\ref{afr} and the cost analysis methodology outlined in Sec~\ref{cost}.
+
+\subsection{Cloud Platform and Hardware}
+To conduct the experiments and have access to different types of hardware, we utilized GCP.
+Six virtual machines running Container optimised Operating System provided by GCP constituted our testbed.
 Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster consisting of six worker nodes.
-Three worker nodes were responsible for running the monitoring platform such as Prometheus 2.47.2 and Grafana 10.2.0.
-These nodes were of the 'e2-medium' instance type provided by Google Cloud Platform.
+Three worker nodes were responsible for running the monitoring platforms such as Prometheus 2.47.2 and Grafana 10.2.0.
+These nodes were of the ``e2-medium" instance type provided by GCP.
 In total, we used three GPU models.
-For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4'.
-% To assess the energy consumption of the experiments deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}.
+For P100 and V100 GPUs, we used ``n1-standard-2'' type for the nodes and for L4 GPUs we used ``g2-standard-4''.
+
+To assess the energy consumption of the experiments deployed on a Google Kubernetes Engine, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}.
 This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components.
@@
 A diagram of the cloud architecture can be found in Fig.~\ref{fig:architecture}.
-Finally, to meet our goal of developing a cost-effective model evaluation technique, we restricted all of our experiments to a single one-thousand United States dollar research grant from Google.
+Finally, to meet our goal of developing a cost-effective model evaluation technique, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
+Approximately 10\% of this was used for development and 90\% was used for the evaluations.
 
-% \begin{figure*}
-%     \centering
-%     \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
-%     \caption{Cloud Architecture Diagram}
-%     \label{fig:architecture}
-% \end{figure*}
+\begin{figure*}
+    \centering
+    \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
+    \caption{Cloud Architecture Diagram}
+    \label{fig:architecture}
+\end{figure*}
 
-% For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}.
-We used three optimization criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
+\subsection{AFR Models}
+
+For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}.
+We used three optimisation criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
 We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples.
@@
 For each dataset, we tested this on ten random splits of the data.
+For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack.
+Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
+Additionally, we fit the function as described in Fig.~\ref{fig:alg}.
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
-%     \caption{Experimental Pipeline Diagram}
-%     \label{fig:experiments}
-% \end{figure}
+\subsection{Datasets}
+The AFR models were evaluated using the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
+Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets.
+Furthermore, to reduce the complexities of system overhead, distributed or federated training, and the effect of shared cloud environments, we restricted ourselves to datasets that were small enough to reside entirely within GPU memory with the model, since the disk read speed in cloud environments is incredibly variable.
 
-% \subsection{Datasets}
-% For our experiments, we evaluated the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis ~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
-By modern standards (billions of parameters), these models are quite small (tens of thousands of samples), but our goal is not to rival the accuracy of industy leaders, but to develop a method that is practical for everyone else to use.
-% Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets.
-Furthermore, to reduce the complexities of system overhead, distributed or federated training, and the effect of shared cloud environments, we restricted ourselves to datasets that are small enough to reside entirely within GPU memory with the model, since the disk read speed in cloud environments is incredibly variable.
-
-% \subsection{Models}
-% We restricted ourselves to a single model for our evaluations.
+\subsection{Models}
+We restricted ourselves to a single model for our evaluations.
 Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware.
 As discussed in Sec.~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict.
-So, we sampled learning rates $\in [1e-6, 1]$, batch sizes $\in [1, 1e5]$, and epochs $\in [1,50]$ for MNIST and CIFAR10 on the P100 and V100.
-For Cifar100, we increased the range of the tested epochs to be $\in [1, 100]$.
-To evaluate the efficacy of different bit-depths on the L4 hardware, we used the Feature Squeezing defence~\cite{feature_squeezing} provided by IBM's adversarial robustness toolbox~\cite{art2018}.
-Model parameters were chosen using the \texttt{optuna} optimization framework, configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.
+So, we sampled learning rates $\in [10^{-6}, 1]$, batch sizes $\in [1, 10^5]$, and epochs $\in [1, 50]$ for MNIST and CIFAR10 on the P100 and V100.
+For CIFAR100, we increased the range of the tested epochs to be $\in [1, 100]$.
+To evaluate the efficacy of different bit-depths on the L4 hardware, we used the Feature Squeezing defence~\cite{feature_squeezing} provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{Pytorch} compatible arrays.
+Model parameters were chosen using the \texttt{Optuna} optimisation framework, the configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.
 
-% \subsection{Attacks}
-% Since the goal in this paper is to evaluate how hardware and deployment cost affect adversarial robustness, we focused on evasion attacks since they induce failures by adding noise to the data.
-Prior research ~\cite{meyers} has shown that the Fast Gradient method (see: Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
+\subsection{Attacks}
+Since we are examining the effect of model parameters at run-run, we focused on evasion attacks since they induce failures by adding noise to the data at the inference stage.
+Prior research~\cite{meyers} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
 To evaluate the effect of adversarial noise on our samples, we varied $\varepsilon \in [0, 1]$, using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
 
-% \subsection{GPU Configurations}
-% We tested several hardware configurations, which have various hourly costs, peak power demands, and theoretical memory bandwidths.
-We tested three Nvidia cards-- the V100, the P100, and L4.
-The V100 was chosen as a baseline, since it's routinely cited in the literature~\cite{svedin2021benchmarking,xu2018deep}.
-The P100 architecture comes from the same line of server-grade training GPUs, but from an older generation.
-The L4, however, is advertised as a machine built for inference--not training, relying on a smaller number of bits per tensor core.
+\subsection{GPU Configurations}
+We tested several hardware configurations, which have various hourly costs, peak power demands, and theoretical memory bandwidths.
+The V100 was chosen as a baseline, since it is  routinely used in the literature ~\cite{svedin2021benchmarking,xu2018deep}.
+The P100 architecture comes from the same line of server-grade GPUs, but from an older generation.
+The L4, however, is advertised as a machine built for inference --- not training --- relying on a smaller number of bits per tensor core.
 Consequently, the number of operations per second is dependent on the bit depth of the data and the model weights, with the peak numbers outlined in Tab.~\ref{tab:hardware} referring to 8-bit inputs.
-% \begin{table}[h]
-% \begin{tabular}{lllll}
-% \hline
-%                         & V100   & P100   & L4    &  \\ \hline
-% Cost (USD/hour)         & 2.55   & 1.60   & .81   &  \\
-% Power (Watts)           & 250    & 250    & 72    &  \\
-% Memory Bandwidth (GB/s) & 900    & 732    & 300   &  \\ \hline
-% \end{tabular}
 
-% \caption{Hardware specifications for tested GPUs. All specifications were retrieved from the Nvidia website at the following links: 
-% \href{https://images.nvidia.com/content/technologies/volta/pdf/volta-v100-datasheet-update-us-1165301-r5.pdf}{V100 Datasheet},
-% \href{https://images.nvidia.com/content/tesla/pdf/nvidia-tesla-p100-PCIe-datasheet.pdf}{P100 Datasheet}, and
-% \href{https://nvdam.widen.net/s/rvq98gbwsw/l4-datasheet-2595652}{L4 Datasheet}.
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lllll}
+    \toprule
+                            & V100   & P100   & L4    &  \\
+    \midrule
+    Cost (USD/hour)         & 2.55   & 1.60   & 0.81   &  \\
+    Power (Watts)           & 250    & 250    & 72    &  \\
+    Memory Bandwidth (GB/s) & 900    & 732    & 300   &  \\
+    \bottomrule
+    \end{tabular}
+    \caption{Hardware specifications for tested GPUs. All specifications were retrieved from the Nvidia website at the following links: 
+    \href{https://images.nvidia.com/content/technologies/volta/pdf/volta-v100-datasheet-update-us-1165301-r5.pdf}{V100 Datasheet},
+    \href{https://images.nvidia.com/content/tesla/pdf/nvidia-tesla-p100-PCIe-datasheet.pdf}{P100 Datasheet}, and
+    \href{https://nvdam.widen.net/s/rvq98gbwsw/l4-datasheet-2595652}{L4 Datasheet}.
 Prices were retrieved from Google Cloud Platform for the \texttt{europe-west4} region on 3 December 2023 at \href{https://cloud.google.com/pricing/list}{this link.}
-% }
-% \label{tab:hardware}
-% \end{table}
+    }
+    \label{tab:hardware}
+\end{table}
 
-% \subsection{Survival Analysis}
-% In addition to the optimization criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the distribution, $S(t)$.
-We attempted adding dummy variables for hardware (\textit{e.g.}~peak power and peak bandwidth) as well as the datasets (\textit{e.g~}resolution, bit depth, and number of color channels), but each of these were strongly co-linear with training time and hindered modelling of the distribution.
-As such, they were not included.
-To find the distribution of the measured data and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}.
-We also compare the chosen distributions (see: Section~\ref{afr}).
-These results can be found Section~\ref{results}.
+\subsection{Survival Analysis}
+In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the function, $S_{\theta}(t)$.
+To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}.
+We also compared the chosen modelling functions (see Sec.~\ref{afr}).
+These results can be found in Sec.~\ref{results}.
 
-% \subsubsection{Hardware}
-% This value, measured in United States Dollars per hour, will indicate the operating cost of a given model.
-To calculate this, we used the price per hour from each of cloud service pricing page~\footnote{ Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} } ~\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimized}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$) and the inference time ($T_{i}$).
+\subsubsection{Hardware}
+The rental cost of the hardware, measured in United States Dollars per hour, will indicate the operating cost of a given model.
+To calculate this, we used the price per hour from each of cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.}}\footnote{Google Cloud prices for L4 obtained  \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} and calculated the cost of training ($C_{t}$) and the ($C_{i}$) from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
 
-% \subsection{Survival Time}
+\section{Results and Discussion}
+\label{results}
 
-% Correspondingly, we can talk about the expected survival time under optimistic, $S_{ben.}$ as well as under adverse (accelerated failure rate distribution), $S_{adv.}$.
-If we assume that the distribution of failures is uniform with respect to latency \footnote{\cm{While this is not necessarily the case, neural networks generally assume independent and identically distributed data~\cite{ma2022state}, but we admit that tracking the per-sample failure rate would be a good way to detect under-sampled regions or otherwise likely-to-fail samples.
-Furthermore, since the modelling distributions include shape and scale parameters for each covariate as well as the model as a whole, whether or not we divide by the number of samples is irrelevant since these shape and scale parameters will absorb this value anyway.
-We include this normalization so that we can compare the benign and adversarial prediction times which are calculated across 10 thousand and 100 samples respectively.
-That is, we merely scaled the y-axis on Figs~\ref{fig:time}~and~\ref{fig:cost} without changing the behaviour of $S(t)$ for the sake of comparison.}}
-% $$
-% S_{ben.} := S(t_i; x, y, \theta) \mathrm{~s.t.~} \varepsilon = 0
-% $$
-% and
-% $$
-% S_{adv.} :=  S(t_i; x, y, \theta) \mathrm{~s.t.~} 0 < \varepsilon \leq \varepsilon_{max}
-% $$
+In this section, we display and discuss the results for all of the experiments across all datasets and hardware.
+First, we discuss the measured data in Secs.~\ref{res:acc}-\ref{res:cost} before discussing the fitted AFR model in Sec.~\ref{res:afr}.
 
-% \section{Results}
-% \label{results}
-% Below, we examine the effect of hardware and dataset on the distribution of the benign/adversarial accuracy (Fig.~\ref{fig:acc}), training/inference/attack time (Fig.~\ref{fig:time}), and both monetary (Fig.~\ref{fig:cost}) and power (Fig.~\ref{fig:power}) costs for training/inference/attacks.
-We also compare all three survival time distributions outlined in Sec.~\ref{afr} using the criteria outlined in the same section.
-Using the best-fit distribution (again, see:~\ref{afr}), we plotted the effect of several covariates on the survival time of the model (Fig.~\ref{fig:partial_effect_train_time}).
+\subsection{Accuracy}
+\label{res:acc}
+Fig.~\ref{fig:acc} shows the adversarial (right) and benign (left) accuracies for all datasets and hardware.
+It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware.
+Benign accuracy decreases with resolution (CIFAR10 vs MNIST) or with the number of classes (CIFAR10 vs CIFAR100).
+For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (e.g.
+the accuracy we would expect on random noise), demonstrating the efficacy of the attack outlined in Sec.~\ref{optimisation}.
 
-% \subsection{Accuracy}
-% Fig.~\ref{fig:acc} reveals little to no improvement in accuracy or adversarial accuracy, regardless of hardware though we see that the Cifar10 has worse benign performance and Cifar100 has significantly adversarial performance.
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=.5\textwidth]{plots/combined/acc.pdf}
-%     \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
-%     \label{fig:acc}
-% \end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.5\textwidth,clip]{plots/combined/acc.pdf}
+    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
+    \label{fig:acc}
+\end{figure}
 
-% \subsection{Time}
-% Fig.~\ref{fig:time} reveals the training time proportional to the GPU bandwidth numbers in Tab.~\ref{tab:hardware}.
-Slower hardware is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
+\begin{figure*}[h]
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
+        \caption{Training (left), Prediction (center), and Attack (right) Times}
+        \label{fig:time}
+    \end{subfigure}
+    \begin{subfigure}[b]{.8\textwidth}
+        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
+        \caption{Training (left), Prediction (center), and Attack (right) Power Consumption}
+        \label{fig:power}
+    \end{subfigure}
+    \begin{subfigure}[b]{.8\textwidth}
+        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
+        \caption{Training (left), Prediction (center), and Attack (right) Monetary Cost}
+        \label{fig:cost}
+    \end{subfigure}
+    \caption{The all cost metrics for all hardware and datasets. For these plots, the y-axes have been scaled by the the number of samples for the sake of comparison.}
+\end{figure*}
+
+\subsection{Time, Power, Cost}
+\label{res:cost}
+Fig.~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models.
+Slower hardware (see Memory Bandwidth in Tab.~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
 This should be no surprise since the less-capable hardware is meant to be used exclusively for inference.
-Additionally, we see that the attack time is colinear with both the training and prediction times across hardware and datasets-- an expected result since this will be driven by the number of samples and the inference time (see: Eq.~\ref{attack_time}).
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=.56\textwidth]{plots/combined/time.pdf}
-%     \caption{Training, Prediction, and Attack times across datasets and hardware.}
-%     \label{fig:time}
-% \end{figure}
+Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).
+We can also see that training takes slightly more than than attack generation, when we normalize by the number of samples.
 
-% \subsection{Power}
-% The power consumption (Fig.~\ref{fig:power})  tracks monetary cost  (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it's unsurprising that cloud billing is colinear with this metric.
+The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Fig.~\ref{fig:power}.
+It tracks monetary cost (Fig.~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is colinear with this metric.
 Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Fig.~\ref{fig:power}).
 
-% \subsection{Cost}
-% \cm{TODO}
+The monetary cost for each dataset and each piece of hardware is shown in Fig.~\ref{fig:cost}.
+For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
+In the best case scenario, they are comparable, but attacks consistently succeed with 100s of samples while model training requires orders of magnitude more.
+%  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=.5\textwidth]{plots/combined/power.pdf}
-%     \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
-%     \label{fig:power}
-% \end{figure}
+\subsection{AFR Models}
+\label{res:afr}
+Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}.
+For building the AFR model, we used 75\% of the available data and withheld 25\% for verification.
+The concordance is both strong (>.5) and similar for all three AFR models and both the train and test sets.
+We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFR models.
+Fig.~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFR models.
+For further analysis, we chose the Weibull AFR due to its superior fir in  Fig.~\ref{fig:qq}.
+\input{plots/combined/aft_comparison}
 
-% \subsection{Partial Effects of Covariates}
-% Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time.
-However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that increase the attack distance by an order of magnitude reduces the survival time marginally.
-Furthermore, Table~\ref{tab:Combined} shows that the log-logistic and log-normal distributions have similar predictive power, but we used the log-logistic model to render the plots due to its marginally improved AIC.
+Fig.~\ref{fig:aft} shows the log-scale coefficients for the AFR model.
+It shows that epochs, batch size, and training time have no effect on the survival time.
+Additionally, it reveals this for the random state variable, which is expected.
+However, we can clearly see that inference time  is as strong an indicator as the attack noise distance, revealing that model speed is at least as important as the attack itself.
+Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance)\cite{carlini_towards_2017}.
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=.5\textwidth]{plots/combined/cost.pdf}
-%     \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
-%     \label{fig:cost}
-% \end{figure}
+Using the $S_{\theta}(t)$ described in Sec.~\ref{afr}, we can model the partial effect of various hardware devices, which is depicted in Fig.~\ref{fig:partial}.
+It clearly shows that hardware choice has no bearing on robustness, despite the disparity in cost outlined in Table~\ref{tab:hardware}.
 
-% \input{plots/combined/aft_comparison}
-% %
+\begin{figure*}[h!]
+    \centering
+    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \caption{ }
+    \end{subfigure}
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{The red line depicts the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
+    \label{fig:qq}
+\end{figure*}
+\begin{figure}[h!]
+    \centering
+    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft.pdf}
+        \caption{Coefficients of the Covariates for the Weibull AFR model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
+        \label{fig:aft}
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_device_num_partial_effect.pdf}
+        \caption{Partial Effect  of device on $S_{\theta}(t)$ }
+        \label{fig:partial}
+    \end{subfigure}
+    \caption{Weibull AFR Model.}
+\end{figure}
 
-% \begin{figure}[ht]
-%   \centering
-%   % include first image
-%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
-%   \caption{This depicts the partial effect of the training time on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
-%   \label{fig:partial_effect_train_time}
-% \end{figure}
+\section{Considerations}
+\label{considerations}
+We have taken much care to conduct these measurements as carefully as possible.
+Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial.
+Given the strong results and uniformity across AFR functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around data storage, file systems, and various access mechanisms.
+Furthermore, we set the attack batch size and the training batch size to be the same for every trial for each dataset and piece of hardware.
+If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.
+Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth. 
+In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
+We restricted our search to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.
 
-% \begin{figure}
-%   \centering
-%   % include second image
-%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_accuracy_partial_effect.pdf} 
-%   \caption{This depicts the partial effect of the accuracy on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
-%   \label{fig:partial_effect_accuracy}
-% \end{figure}
+\section{Conclusions}
+\label{conclusion}
+In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing us the model performance as a function of tested model parameters.
+We then formalize a technique to model the survival time as a function of various model parameters.
+Using this technique, we showed that despite reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.
+Furthermore, we demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields substantially similar results when compared to more expensive and power hungry hardware.
 
-% \begin{figure}
-%   \centering
-%   % include second image
-%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_adv_failure_rate_partial_effect.pdf} 
-%   \caption{This depicts the partial effect of the adversarial failure rate on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
-%   \label{fig:partial_effect_adv_failure_rate}
-% \end{figure}
+% no keywords
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
-% \begin{figure}
-%   \centering
-%   % include second image
-%   \includegraphics[width=.8\linewidth]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}  
-%   \caption{This depicts the partial effct of the attack distance on the survival time across all datasets and models according to the distribution $S(t)$ as outlined in Section~\ref{survival_time}.}
-%   \label{fig:partial_effect_attack_eps}
-% \end{figure}
-
-% \section{Considerations}
-%  We have taken much care to conduct these measurements as carefully as possible.
-Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples, but independent and identically distributed data is already a pre-condition for neural networks \cite{ma2022state}.
-Given the strong ( $>.5$) concordance results and uniformity across distributions in Table~\ref{tab:Combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
-Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning.
-\cm{While this obscures the effect of GPU parallelization, the result doesn't change since all metrics are measured on a particular piece of hardware for both the attacker and defender.
-If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.} In general, distributed/federated models are out of scope, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
-Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth.
-However, we would like to note that the `inference-optimized' Nvidia 4-series GPUs are perfectly capable and affordable training machines.
-We restricted our search to only a single evasion attack (see: Eq.~\ref{eq:fgm}) in the interest of time (and therefore deployment cost), though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks.
-.
-%  % As an additional note, we forgot to store the Prometheus database on the PVC and the data only existed in an ephemeral Docker container, and we recommend against this design flaw in future deployments.
-Instead the Prometheus database should be mounted to the PVC or linked to an external database via the provided web interface.
-%  % In general, we chose to use a PVC rather than externally linked databases to minimize the differences between a single-machine implementation and the cloud deployment and allow our results to be generally reproducible on a developer's local machine, though this comes with the downside of having to interact with critical experiment data manually.
-Proper permissions management on the attached volume store can prevent any critical errors during downstream analysis, though the addition of some kind of searchable log store like \texttt{elasticsearch}\cite{gormley2015elasticsearch} in combination with artifact storage\cite{daher2018cloud} for the datasets, models, and attacks would be a welcome and obvious improvement.
-
-% \section{Conclusion}
-% In this work, we introduced survival analysis to machine learning, developed a method for quickly and efficiently test model parameter choices and to evaluate them in the presence of adversarial noise, allowing us the model the Pareto front as a function of tested model parameters.
-Using this technique, we showed that despite reduced run-times with newer and/or larger hardware, that adversarial robustness is not significantly effected and that the specific choice of attack parameters is far more important than model training time.
-Furthermore, we demonstrate the un-advertised training capability of the Nvidia L4 GPU which can get substantially similar results when compared to more expensive and power hungry hardware.
-However, the marginal run-time is significant, even if it's cost-effective.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{bibliography}
-% \end{document}
+\clearpage
+\bibliographystyle{IEEEtran}
+\bibliography{bibliography}
+\end{document}

### 2024-08-16 main.tex
Updates from Overleaf

@@
 In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}.
-Whether in the context of automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}.
+Whether in the context of automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{IEC61508}.
 An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable.
@@
 
-We propose a methodology for model training and verification using accelerated failure-time (AFT) models, drawn from the field of \textit{survival analysis}.
-Additionally, since one goal is cost-efficiency, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
+We propose a methodology for model training and verification using accelerated failure-time (AFT) models, drawn from the field of \textit{survival analysis}, with a focus on cost-efficient evaluation methods.
 AFT models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}.
-In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components.
+In medical science, these models are used to make claims like ``smokers are twice as likely to die from lung cancer'' or used to set the operating limits of manufactured components.
 This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
@@
     \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
-    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
-    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
-    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
-    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
-    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
-    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
-    \State \textbf{Infer:}  $ \hat{y}_a = K(x_a, \theta) $.
-    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
+    \State  $T_t[i] \gets$ Training Time.
+    \State  $ \hat{y_i} = K(x_i, \theta) $.
+    \State  $ T_i[i] \gets $  Inference Time.
+    \State  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
+    \State find $x_a$ with Eq.~\ref{eq:fgm}.
+    \State  $T_a[i] \gets$ attack generation time.
+    \State  $ \hat{y}_a = K(x_a, \theta) $.
+    \State  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
     \EndWhile
-    \State \textbf{Fit AFT Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
-    \State \textbf{Return:} $S_{\theta}$
+    \State $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ \\
+    % used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
+    \Return $S_{\theta}$
 \end{algorithmic}
@@
 
-Accuracy measures the vulnerability or susceptibility of the model to noise-induced failures.
-A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures.
-Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data.
+Accuracy measures the vulnerability or susceptibility of the model to failures.
+A larger accurate indicates a higher rate of true classifications, signifying a weaker model in terms of \textit{robustness} against (noise-induced) failures.
+Throughout, we use the terminology \textit{benign} accuracy to refer to the performance on the test set using unperturbed data and \textit{adversarial} to refer to the performance in the presence of additive noise that is intended to confuse the model.
+The subscripts \textit{ben} and \textit{adv} are used respectively.
 The accuracy, $\lambda$, is defined as
@@
 \end{equation}
-which is generally assumed to indicate the rate of failures in real-world data sampled from the same distribution as the test data~\cite{tan2021critical}.
-However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}.
+which is generally assumed to indicate the rate of successes in real-world data sampled from the same distribution as the training data~\cite{tan2021critical}.
+However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020.
 In addition, it ignores the run-time cost of a given architectural decision, caring only about accuracy on benchmark data~\cite{desislavov2021compute,bailly2022effects}.
 Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
-We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test data set $\lambda_{adv}$ to denote the accuracy on adversarial samples.
 
@@
 The failure rate refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs~\cite{meyers}.
-To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, such that the failure rate is
+To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, so that the failure rate is the average time until a failure in a time interval around time, $t$, such that:
 \[
@@
 where $p(\textrm{False~Classification} \mid \theta)$ is the probability of a false classification given a particular set of hyper-parameters, $\theta$, $\Delta t$ is a time interval, and $t$ is a point in time.
-Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$.
-By re-parameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure time model.
+Note that  $1 - \lambda$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$.
+By modelling accuracy as a function of time, one can then compare the probability of failure to the cost, which is also measured in time, allowing one to make deployment decisions based on the risk analysis standards outlined in IEC61508~\cite{IEC61508}.
+This then allows us to make claims like ``increasing training time by X\% will yield survival time gains of Y\%''~\cite{meyers_aft}.
 
@@
 
-Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time.
+AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time.
 For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely.
@@
 For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval.
-This should be measured in both the benign and adversarial contexts.
 The full algorithm can be seen in Algorithm~\ref{fig:alg}.
@@
 Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and 0.5 reflects random chance.
-By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}.
-Other measures include the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}.
+By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by IEC61508~\cite{IEC61508}.
+We also noted the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}.
 These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}.
-Then, one should plot all the expected and observed values for all three functions according to the method described by Austin \textit{et al.}~\cite{ici} (see Figure~\ref{fig:qq}) to visually inspect each model for goodness-of-fit.
-\cm{Additionally, we split the data into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and measured the concordance, ICI, and E50 for each set.}
-
-\subsubsection{\cm{The Advantages of AFT models}}
-\cm{
-}
+Then, the fitted AFT models were plotted using that compares the fitted AFT model to a cubic spline fit to the data~\textit{et al.}~\cite{ici}  to visually inspect each model for goodness-of-fit (see Figure~\ref{fig:qq}).
+\cm{Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.}
 
@@
 \begin{equation} \label{assumption}
-    S_{adv} \approx  \phi S_{ben}(\phi t),
+    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right)
 \end{equation}
-where $\phi$ is some acceleration factor described by the joint effect of the covariates.
-This assumption means we can evaluate the benign accuracy using a small number of adversarial samples~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
+where $\phi$ is some acceleration factor described by the joint effect of the covariates and $S_0$ is the baseline hazard function (where the effect of the covariates are 0).
+This assumption means we can evaluate the generalization performance using a small number of adversarial samples~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
 However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.
@@
 
-ML models are typically trained across a wide variety of hyper-parameters where each model is determined by minimizing an optimisation program (minimizing a loss function) associated with the machine learning problem.
+ML models are typically trained by examining the effect of the entire hyper-parameter space on the resulting accuracy.
 However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
@@
 Therefore, a proper search would keep this dual-objective in mind.
-To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) while converging over tens or hundreds of trials~\cite{ozaki2020multiobjective}.
-
-\subsection{Advantages of this Methodology}
-\label{advantages}
-
-Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in machine learning applications.
-This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}.
-It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}.
-Furthermore, by isolating changes and testing them as quickly as possible, it is  easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars, drones, or industrial equipment) to effectively test.
-To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard~\cite{iso26262}.
-This risk analysis is outlined in the subsection below.
+To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimization algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
 
@@
 
-In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by ISO26262~\cite{iso26262} which allows us to quantify the marginal risk.
+In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by IEC61508~\cite{IEC61508} which allows us to quantify the marginal risk.
 To quantify this marginal risk, one must measure the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack.
-The final subsection outlines why these metrics are important and their usage in this methodology.
 
@@
 \end{equation}
-We restricted this to a single iteration such that $i =1$ as described in FGM~\cite{fgm}.
+In the interest of time, our chosen attack, FGM, uses only a single iteration $i =1$~\cite{fgm}.
 
@@
 Furthermore, we approach the cost of deployment at two scales.
-Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using \textit{e.g.}, the Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost.
-However, at a certain scale, (\textit{e.g.}, to deploy a self-driving car) it is  more appropriate to talk about cost in terms of power.
+Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model using \textit{e.g.}, the Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost.
+However, at a certain scale or with certain applications, it is  more appropriate to talk about cost in terms of power (\textit{e.g.}, to deploy a self-driving car with a useful operating range).
 Finally, we define best-case and worst-case success metrics that provide an efficient way to minimize the latency, cost of deployment, and
@@
     C_t = C_h \cdot T_t,
-    \label{eq:cost_training}
 $$
@@
     C_i = C_h \cdot T_i,
-    \label{eq:cost_inference}
 $$
@@
     C_a = C_h \cdot T_a.
-    \label{eq:cost_attack}
 $$
@@
 In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
-For our purposes, by assuming the best-case scenario for both attacker and defender, we can model the Pareto front --- the best-case asymptotic behavior --- of either party~\cite{zitzler2008quality}.
-As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
+Using AFTs, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}.
+By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
+As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
 If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
@@
 Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0, a cluster consisting of six worker nodes was created.
-Three worker nodes were responsible for running the monitoring platforms such as Prometheus 2.47.2 and Grafana 10.2.0.
+Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0.
 These nodes were of the ``e2-medium" instance type provided by GCP.
-In total, three GPU models were used--the Nvidia P100, V100, and L4.
+In total, three GPU architectures were used--the Nvidia P100, V100, and L4.
 For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.
@@
 
-For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds~\cite{legriel2010approximating}.
+For each hardware configuration and dataset, the TPE algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials.
+This was chosen to be significantly larger than the 200 used successfully by Watanabe~\textit{et.
+al.}~\cite{tpe_params} while still allowing for reasonable run times.
+In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}.
+Examining the effect of this and other TPE parameters on the total run-time and performance of this methodology was outside the scope of this work.
 We used three optimisation criteria: benign accuracy, training time, and adversarial accuracy, seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
-We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples.
+We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples for each of the MNIST, CIFAR10, and CIFAR100 datasets.
 Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy.
 Figure~\ref{fig:experiments} illustrates this methodology.
-For each dataset, we tested this on ten random splits of the data.
-For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack.
+For each dataset, we tested this on ten random splits of the data to create 10 unique test/train pairs.
+For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack set.
 Using these values, we fit an AFT model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
-Additionally, we fit the function as described in Algorithm~\ref{fig:alg}.
+Additionally, we approximate the AFT model using the methodology described in Algorithm~\ref{fig:alg}.
 
@@
 Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware.
-As discussed in Section~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict.
+As discussed in Section~\ref{learning_rate}, the relationship between hardware specifications, hyper-parameters, and performance is highly complex and hard to predict.
 So, we sampled learning rates $\in [10^{-6}, 1]$, batch sizes $\in [1, 10^5]$, and epochs $\in [1, 50]$ for MNIST and CIFAR10 on the P100 and V100.
 For CIFAR100, the range of the tested epochs was increased to be $\in [1, 100]$.
-The Feature Squeezing defence~\cite{feature_squeezing} was used to evaluate the efficacy of different bit-depths on the L4 hardware, as provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{Pytorch} compatible arrays.
-Model parameters were chosen using the \texttt{Optuna} optimisation framework, the configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.
+The Feature Squeezing defence~\cite{feature_squeezing} was used to evaluate the efficacy of different bit-depths on the L4 hardware, as provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{pytorch} compatible arrays.
+Model parameters were chosen using the \texttt{optuna} optimisation framework, the configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.
 
@@
 
-Since we are examining the effect of model parameters at run-run, we focused on evasion attacks since they induce failures by adding noise to the data at the inference stage.
-Prior research~\cite{meyers} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
-To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in [0, 1]$.
+To examine the effect of model parameters at run-time, evasion attacks, which attack the model at the prediction stage, were examined.
+Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
+To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1]$.
 This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
@@
 Consequently, the number of operations per second depends on the bit depth of the data and model weights, with peak numbers outlined in Table~\ref{tab:hardware} for 8-bit inputs.
-
+The rental cost of the hardware, measured in United States Dollars per hour, indicates the operating cost of a given model.
+To calculate this, the price per hour from each cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} Google Cloud prices for L4 obtained \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} were used and the cost of training ($C_{t}$) and the cost of inference ($C_{i}$) calculated from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
 \begin{table}[h]
@@
 
-In addition to the optimisation criteria of benign/adversarial accuracy and training time, prediction times, attack times, power consumption, batch size, and number of epochs were also collected to be used as covariates of the function, $S_{\theta}(t)$.
+In addition to the optimisation criteria of benign/adversarial accuracy and training time, prediction times, attack times, power consumption, batch size, and number of epochs were also collected to be used as covariates in the AFT model, $S_{\theta}(t)$.
 To fit the AFT model and to plot the effect of the covariates, the \texttt{lifelines} Python package was used~\cite{lifelines}.
-The chosen modelling functions (see Section~\ref{aft}) were also compared.
-The results can be found in Section~\ref{results}.
-
-\subsubsection{Hardware}
-
-The rental cost of the hardware, measured in United States Dollars per hour, indicates the operating cost of a given model.
-To calculate this, the price per hour from each cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.}}\footnote{Google Cloud prices for L4 obtained \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} were used and the cost of training ($C_{t}$) and the ($C_{i}$) calculated from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
+The Weibull, Log Logistic, and Log Normal AFT models (see Section~\ref{aft}) were also compared.
 
@@
 This section presents and discusses the results for all of the experiments across all datasets and hardware.
-First, the measured data in Secs.~\ref{res:acc}-\ref{res:cost} are discussed, and then the fitted AFT model in Section~\ref{res:aft}.
+First, the accuracy, training time, inference, and monetary cost are discussed in Secs.~\ref{res:acc}-\ref{res:cost}, followed by the fitted AFT model in Section~\ref{res:aft}.
 
@@
 It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware.
-The benign accuracy decreases with resolution (CIFAR10 vs MNIST) or with the number of classes (CIFAR10 vs CIFAR100).
+The benign accuracy decreases with difficulty (CIFAR10 vs MNIST) or with the number of classes (CIFAR10 vs CIFAR100).
 For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (\textit{i.e.}, the accuracy we would expect with random data), demonstrating the efficacy of the attack outlined in Section~\ref{optimisation}.
@@
     \end{subfigure}
-    \caption{The all cost metrics for all hardware and datasets. For these plots, the y-axes have been scaled by the the number of samples for the sake of comparison.}
+    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets.
+For these plots, the y-axes have been scaled by the the number of samples for the sake of comparison.}
 \end{figure*}
@@
 Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).
-We can also see that training takes slightly more than than attack generation, when we normalize by the number of samples.
+We can also see that average training time per sample is takes slightly more than than attack generation time per sample (see:~\ref{fig:time} left and right plots).
 
 The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Figure~\ref{fig:power}.
-It tracks monetary cost (Figure~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is correlated with this metric.
-Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Figure~\ref{fig:power}).
+It tracks monetary cost (Figure~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is correlated with the power requirement.
+Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Figure~\ref{fig:power}) for prediction, while differences between hardware and datasets are insignificant for the training and attack metrics.
 
@@
 For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
-In the best case scenario, they are comparable, but attacks consistently succeed with 100s of samples while model training requires orders of magnitude more.
+In the best case scenario, they are comparable, but attacks consistently succeed with only 100 samples (Figure~\ref{fig:acc}) while model training requires orders of magnitude more.
 %  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
@@
 Table~\ref{tab:combined} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
-A total 75\% of the available data were used to build the AFT models and 25\% were withheld for verification.
+A total 75\% of the available data were used to build the AFT models and 25\% were withheld for evaluation.
 The concordance is both strong ($>0.5$) and similar for all three AFT models and both the train and test sets.
@@
 Figure~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFT models.
-For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}.
+For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}, and average test error of 1\% (ICI) and 0 error for the median sample (E50).
+We also see that these metrics are  functionally identical across all AFT models as well as between the test and train set of each model.
 
@@
 It shows that epochs, batch size, and training time have no effect on the survival time.
-Additionally, it reveals this for the random state variable, which is expected.
-However, we can clearly see that inference time  is as strong an indicator as the attack noise distance, revealing that model speed is at least as important as the attack itself.
-Furthermore, we see that benign accuracy is negatively correlated with accuracy, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to test-set accuracy (which is the normal indicator of generalization performance)~\cite{carlini_towards_2017}.
+Additionally, the covariate value of 0 for random state indicates that random permutations of the training and test data have no effect on the survival time, which is expected.
+However, we can clearly see that inference time  is as strong an indicator as the attack noise distance, revealing that model speed is nearly as important as the the noise value of the attack ($\varepsilon$).
+Furthermore, we see that benign accuracy is negatively correlated with the survival time, confirming previous assertions that robustness ($S_{\theta}(t)$) is inversely related to benign accuracy (which is the standard indicator of generalization performance)~\cite{carlini_towards_2017}.
 
 Using the $S_{\theta}(t)$ described in Section~\ref{aft}, we can model the effect of various hardware devices, which is depicted in Figure~\ref{fig:dummies}.
-It clearly shows that hardware choice has no bearing on robustness, despite the disparity in cost outlined in Table~\ref{tab:hardware}.
+It clearly shows that hardware choice has a relatively small effect (+/- 20\%) on robustness, despite the much larger disparity in cost outlined in Table~\ref{tab:hardware}.
 
@@
 \end{figure*}
-\begin{figure}[h!]
+\begin{figure*}[h!]
     \centering
     \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}[b]{\linewidth}
+    \begin{subfigure}{.5\linewidth}
         \centering
-        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft.pdf}
+        \includegraphics[width=\linewidth]{plots/combined/weibull_aft.pdf}
         \caption{Coefficients of the Covariates for the Weibull AFT model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
+    \begin{subfigure}[b]{.45\linewidth}
         \centering
-        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft_dummies.pdf}
-        \caption{Partial Effect of device and dataset on $S_{\theta}(t)$.}
+        \includegraphics[width=\linewidth]{plots/combined/weibull_aft_dummies.pdf}
+        \caption{AFT coefficients for devices and datasets on $S_{\theta}(t)$.}
         \label{fig:dummies}
@@
     \caption{Weibull AFT Model.}
-\end{figure}
+\end{figure*}
+
+\subsection{Advantages of this Methodology}
+\label{advantages}
+\cm{Moved from the AFT section to here at Tommy's suggestion.}
+\cm{The primary advantage of this methodology over the traditional test/train split measurements is that the precision of the latter is determined by the number of samples; whereas, the precision of the survival time estimate is driven by the resolution of our timing measurements.
+For test-set accuracy,  meeting the weakest safety-critical IEC standard (1 failure in a million) would require many millions of samples to confidently conclude that a model is safe.
+However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see: Table~\ref{tab:combined}).}
+Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in machine learning applications.
+This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}.
+It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}.
+Furthermore, by isolating changes and testing them as quickly as possible, it is easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars, drones, or industrial equipment) to effectively test.
+To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard~\cite{IEC61508}, allowing the model builder to make a quantitative assessment about the efficacy of a model change without testing the effect on real users.
+Additionally, since AFT models have strong predictive power for untested hyper-parameter combinations, this method has a potential to reduce the search space by quickly eliminating candidates that are unlikely to increase the survival time.
 
@@
 
-We have taken much care to conduct these measurements as carefully as possible.
+We have taken much care to conduct all timing measurements as carefully as possible.
 Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial.
-Given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, this assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
-Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around data storage, file systems, and various access mechanisms.
-Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware.
-If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy.
-Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth. 
+While it is very possible (if not altogether guaranteed) that some classes or samples are easier to attack than others, we assume that this averages out over the 100 samples given to each attack.
+Further work examining, for example, the effect of imbalanced datasets on the the distribution of survival times across classes is outside the scope of this work, though the methodology would remain identical.
+Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
+However, given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
+Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (e.g.
+MNIST, CIFAR10, CIFAR100).
+Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.
+If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy compared to the benign measurements.
+Furthermore, while FGM is fast, it is not guaranteed to find failures as quickly as possible, meaning that the survival time estimate is likely to be overestimated.
 In general, distributed/federated models were out of scope for this work, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
-The search was restricted to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.
+The hyper-parameter search was restricted to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.
 
@@
 
-In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing the model performance as a function of tested model parameters.
-We then formalize a technique to model the survival time as a function of various model parameters.
-Using this technique, we showed that despite reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.
-Furthermore, we demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields substantially similar results when compared to more expensive and power hungry hardware.
+In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing one to the model performance as a function of tested model parameters.
+Using this technique, it is clear that reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.
+Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.
 

### 2024-08-20 plots/cifar/aft_comparison.tex
+plots

@@
 \centering
-\caption{Comparison of AFR Models on the CIFAR dataset.}
+\caption{Comparison of AFT Models on the CIFAR dataset.}
 \label{tab:cifar}
@@
 \midrule
-Weibull & -4.87e+03 & -4.87e+03 & 0.8 & 0.79 & 0.01 & 0 & 0 & 0 \\
-Cox & -- & -- & 0.8 & 0.79 & 0.03 & 0.02 & 0 & 0 \\
-Log Logistic & -5.07e+03 & -5.07e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -5.27e+03 & -5.27e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
+Weibull & -5.22e+03 & -5.22e+03 & 0.85 & 0.85 & 0 & 0 & 0 & 0 \\
+Cox & -- & -- & 0.85 & 0.85 & 0.02 & 0.02 & 0 & 0 \\
+Log Logistic & -5.51e+03 & -5.51e+03 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -5.65e+03 & -5.65e+03 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-08-20 plots/cifar100/aft_comparison.tex
+plots

@@
 \centering
-\caption{Comparison of AFR Models on the CIFAR100 dataset.}
+\caption{Comparison of AFT Models on the CIFAR100 dataset.}
 \label{tab:cifar100}
@@
 \midrule
-Weibull & -4.19e+03 & -4.19e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
-Cox & -- & -- & 0.77 & 0.76 & 0.01 & 0.01 & 0 & 0 \\
-Log Logistic & -4.49e+03 & -4.49e+03 & 0.77 & 0.75 & 0.02 & 0.01 & 0 & 0 \\
-Log Normal & -4.65e+03 & -4.65e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
+Weibull & -4.4e+03 & -4.4e+03 & 0.81 & 0.8 & 0 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.81 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
+Log Logistic & -4.73e+03 & -4.73e+03 & 0.82 & 0.81 & 0.01 & 0.02 & 0 & 0 \\
+Log Normal & -4.89e+03 & -4.89e+03 & 0.82 & 0.81 & 0 & 0.02 & 0 & 0 \\
 \bottomrule

### 2024-08-20 plots/mnist/aft_comparison.tex
+plots

@@
 \centering
-\caption{Comparison of AFR Models on the MNIST dataset.}
+\caption{Comparison of AFT Models on the MNIST dataset.}
 \label{tab:mnist}
@@
 \midrule
-Weibull & -5.83e+03 & -5.83e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
-Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
-Log Logistic & -6.1e+03 & -6.1e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
-Log Normal & -6.25e+03 & -6.25e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
+Weibull & -6.51e+03 & -6.51e+03 & 0.9 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
+Cox & -- & -- & 0.9 & 0.9 & 0.04 & 0.04 & 0 & 0 \\
+Log Logistic & -6.48e+03 & -6.48e+03 & 0.91 & 0.9 & 0.03 & 0.04 & 0 & 0 \\
+Log Normal & -6.63e+03 & -6.63e+03 & 0.91 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
 \bottomrule

### 2024-08-20 main.tex

@@
 \begin{document}
-\title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}
+\title{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}
 
@@
 \subsection{Contributions}
-To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see Algorithm~\ref{fig:alg} and Figure~\ref{fig:experiments}) and software framework (see Figure~\ref{fig:architecture}) for the training (see Section~\ref{aft}) and evaluation (see Section~\ref{cost}) of machine learning models that:
+To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see  Figure~\ref{fig:experiments}) and software framework (see Figure~\ref{fig:architecture}) for the training (see Section~\ref{aft}) and evaluation (see Section~\ref{cost}) of machine learning models that:
 \begin{itemize}
@@
 In general, a dataset is split into \textit{training} and \textit{test} sets.
-The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
+The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
 To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
@@
 
-\subsection{Benign and Adversarial Survival Time}
+\subsection{Survival Time}
 \label{accelerated}
@@
 $$
-    S_{adv} := S(t_i; x, y, \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
+    S_{\theta} := S(t_i; x, y, \varepsilon \mid \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
 $$
+\cm{where $\varepsilon$ -- or noise distance -- is treated as a covariate}.
 This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
@@
 
-\subsection{Why Cost Matters}
-
-In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
-In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
-Using AFTs, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}.
-By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
-As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
-If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
-
 \section{Experiments}
@@
 For each hardware configuration and dataset, the TPE algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials.
-This was chosen to be significantly larger than the 200 used successfully by Watanabe~\textit{et.
-al.}~\cite{tpe_params} while still allowing for reasonable run times.
+This was chosen to be substantially larger than the 200 used successfully by Watanabe~\textit{et al.}~\cite{tpe_params} while still allowing for reasonable run times.
 In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}.
@@
     \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}{.5\linewidth}
+    % \begin{subfigure}{.5\linewidth}
         \centering
@@
         \label{fig:aft}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{plots/combined/weibull_aft_dummies.pdf}
-        \caption{AFT coefficients for devices and datasets on $S_{\theta}(t)$.}
-        \label{fig:dummies}
-    \end{subfigure}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{.45\linewidth}
+    %     \centering
+    %     \includegraphics[width=\linewidth]{plots/combined/weibull_aft_dummies.pdf}
+    %     \caption{AFT coefficients for devices and datasets on $S_{\theta}(t)$.}
+    %     \label{fig:dummies}
+    % \end{subfigure}
     \caption{Weibull AFT Model.}

### 2024-08-20 main.tex

@@
     \centering
-    \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
-    \caption{Cloud Architecture Diagram}
+    \includegraphics[width=.6\textwidth]{plots/architecture.pdf}
+    \caption{For our experiments we used 5 concurrent nodes.
+The left column depicts each node used for monitoring the experiments running on the others-- one for each tested GPU.
+The power, performance, and timing metrics, were then stored on  persistent volume claim (PVC) is a request for storage by a user.
+Object storage is...
+    1000 trials were run for each dataset and hardware device.}
     \label{fig:architecture}

### 2024-08-20 combined_plots.py
add plot dvc

@@ -1,0 +1,267 @@
+import pandas as pd
+from pathlib import Path
+import seaborn as sns
+import matplotlib.pyplot as plt
+from deckard.layers.plots import set_matplotlib_vars
+
+set_matplotlib_vars()
+
+
+sns.set_theme(style="whitegrid", font_scale=1.2, font="times new roman")
+
+normal_dir = "data"
+datasets = ["mnist", "cifar", "cifar100"]
+extra_data_dir = "bit_depth"
+
+#
+big_df = pd.DataFrame()
+for data in datasets:
+    df = pd.read_csv(
+        Path(normal_dir) / data / "power.csv",
+        index_col=0,
+        low_memory=False,
+    )
+    df["dataset"] = data
+    big_df = pd.concat([big_df, df], axis=0)
+    if Path(normal_dir, extra_data_dir, data, "power.csv").exists():
+        extra_df = pd.read_csv(
+            Path(normal_dir, extra_data_dir, data, "power.csv"),
+            index_col=0,
+            low_memory=False,
+        )
+        extra_df["dataset"] = data
+        big_df = pd.concat([big_df, extra_df], axis=0)
+
+
+# Device Metadata
+memory_bandwith = {
+    "nvidia-tesla-p100": 732,
+    "nvidia-tesla-v100": 900,
+    "nvidia-l4": 250,
+}
+dataset_resolution = {
+    "mnist": 28,
+    "cifar": 32,
+    "cifar100": 32,
+}
+dataset_channels = {
+    "mnist": 1,
+    "cifar": 3,
+    "cifar100": 3,
+}
+dataset_classes = {
+    "mnist": 10,
+    "cifar": 10,
+    "cifar100": 100,
+}
+cost = {
+    "nvidia-tesla-p100": 1.60,
+    "nvidia-tesla-v100": 2.55,
+    "nvidia-l4": 0.81,
+}
+epochs = "model.trainer.nb_epoch"
+batch_size = "model.trainer.batch_size"
+bit_depth = "model.art.preprocessor.bit_depth"
+resolution = "n_pixels"
+
+# Add Metadata
+for device in big_df.device_id.unique():
+    big_df.loc[big_df.device_id == device, "peak_memory_bandwidth"] = float(
+        memory_bandwith[device],
+    )
+    big_df.loc[big_df.device_id == device, "cost"] = float(cost[device])
[…]

### 2024-08-20 main.tex

--- 2024-08-20 main.tex
@@
 
-\begin{algorithm}[h!]
-    \caption{Survival Analysis for ML}
-    \label{fig:alg}
-\begin{algorithmic}
-    \Require Samples $x$ of size $N$, model parameters $\theta$, loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and the number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, \textit{e.g.}, $N_t$ is size of the training set.
-    \State Initialize classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
-    \State $i = 0$
-    \While{ $i < n$}
-    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
-    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
-    \State  $T_t[i] \gets$ Training Time.
-    \State  $ \hat{y_i} = K(x_i, \theta) $.
-    \State  $ T_i[i] \gets $  Inference Time.
-    \State  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
-    \State find $x_a$ with Eq.~\ref{eq:fgm}.
-    \State  $T_a[i] \gets$ attack generation time.
-    \State  $ \hat{y}_a = K(x_a, \theta) $.
-    \State  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
-    \EndWhile
-    \State $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ \\
-    % used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
-    \Return $S_{\theta}$
-\end{algorithmic}
-\end{algorithm}
+% \begin{algorithm}[h!]
+%     \caption{Survival Analysis for ML}
+%     \label{fig:alg}
+% \begin{algorithmic}
+%     \Require Samples $x$ of size $N$, model parameters $\theta$, loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and the number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, \textit{e.g.}, $N_t$ is size of the training set.
+%     \State Initialize classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
+%     \State $i = 0$
+%     \While{ $i < n$}
+%     \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
+%     \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
+%     \State  $T_t[i] \gets$ Training Time.
+%     \State  $ \hat{y_i} = K(x_i, \theta) $.
+%     \State  $ T_i[i] \gets $  Inference Time.
+%     \State  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
+%     \State find $x_a$ with Eq.~\ref{eq:fgm}.
+%     \State  $T_a[i] \gets$ attack generation time.
+%     \State  $ \hat{y}_a = K(x_a, \theta) $.
+%     \State  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
+%     \EndWhile
+%     \State $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ \\
+%     % used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
+%     \Return $S_{\theta}$
+% \end{algorithmic}
+% \end{algorithm}
 
@@
     \centering
-    \includegraphics[width=.35\textwidth]{plots/experiment.pdf}
-    \caption{Experimental Pipeline Diagram}
+    \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
+    \caption{For each dataset and hardware combination, a random state parameter was chosen at random to decide the test and train sets.
+Next, model parameters and attack parameters are chosen at random.
+After 128 random trials, the TPE algorithm attempts to maximize benign and adversarial accuracy while minimizing training time.}
     \label{fig:experiments}
@@
 However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$.
-The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival}.
-For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval.
-The full algorithm can be seen in Algorithm~\ref{fig:alg}.
+The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival,meyers_aft}.
+For each trial, one can measure the attack generation time to define the time interval and the accuracy to estimate the number of failures and successes in that time interval.
 
@@
 Therefore, a proper search would keep this dual-objective in mind.
-To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimization algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
+To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
 
@@
 In order to estimate the number of failures in a given time period, we measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.
-Under the AFT framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period as outlined in Algorithm~\ref{fig:alg}.
+Under the AFT framework above, we can use the adversarial accuracy as a measure of the survival time across a specified time period as outlined in Figure~\ref{fig:experiments}.
 
@@
     \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
-    \caption{Cloud Architecture Diagram}
+    \caption{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility.
+The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.
+The other node pools each had one node with a specific GPU.
+The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.
+All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC).
+A PVC is a request for storage by user in Kubernetes which is then connected to the object storage.}
     \label{fig:architecture}
@@
 
-Using the $S_{\theta}(t)$ described in Section~\ref{aft}, we can model the effect of various hardware devices, which is depicted in Figure~\ref{fig:dummies}.
+Using the $S_{\theta}(t)$ described in Section~\ref{aft}, we can model the effect of various hardware devices, which is depicted in Figure~\ref{fig:aft}.
 It clearly shows that hardware choice has a relatively small effect (+/- 20\%) on robustness, despite the much larger disparity in cost outlined in Table~\ref{tab:hardware}.
@@
     \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
-The dotted line indicates a perfect model.}}
+The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
     \label{fig:qq}
@@
         \centering
-        \includegraphics[width=\linewidth]{plots/combined/weibull_aft.pdf}
+        \includegraphics[width=.5\textwidth]{plots/combined/weibull_aft.pdf}
         \caption{Coefficients of the Covariates for the Weibull AFT model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
@@
     %     \centering
-    %     \includegraphics[width=\linewidth]{plots/combined/weibull_aft_dummies.pdf}
-    %     \caption{AFT coefficients for devices and datasets on $S_{\theta}(t)$.}
-    %     \label{fig:dummies}
+    %     \includegraphics[width=\linewidth]{plots/combined/weibull_device_num_partial_effect.pdf}
+    %     \caption{\cm{The partial effect GPU on survival time.
+After accounting for GPU bandwidth (see Table~\ref{tab:hardware}) and the covariate effects of the hardware and and inference time, we se ethat Graphic}}
+    %     \label{fig:partial_effect}
     % \end{subfigure}
-    \caption{Weibull AFT Model.}
+    % \caption{Weibull AFT Model.}
 \end{figure*}
+
+\subsection{Why Cost Matters}
+
+In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. 
+In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
+Using AFT models, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}. 
+By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
+As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. 
+If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
 

### 2024-08-22 glossary.tex

\newacronym{aft}{AFT}{Accelerated Failure Time}
\newacronym{cpu}{CPU}{central processing unit}
\newacronym{e50}{E50}{error at 50th percentile}
\newacronym{fgm}{FGM}{Fast Gradient Method}
\newacronym{aic}{AIC}{Akaike Informaiton Criterion}
\newacronym{gpu}{GPU}{graphics processing unit}
\newacronym{ici}{ICI}{integrated calibration index}
\newacronym{bic}{BIC}{Bayesian Information Criteria}
\newglossaryentry{kepler}
{
name=KEPLER,
description={Kubernetes Efficient Power Level Exporter}
}
\newacronym{ml}{ML}{machine learning}

% GB
% VRAM
% MNIST
% CIFAR
% CIFAR100
% GCP

### 2024-08-22 main.tex

@@
 \usepackage{algpseudocode}
+\usepackage[type=\acronymtype]{glossaries}
 
@@
 \newcommand{\mr}[1]{\textit{[{\color{brown}Mohammed: #1}]}}
+
+\input{glossary}
+\makeglossaries
 \begin{document}
+
 \title{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}
 
+\maketitle
+
 \author{}
+
 % author names and affiliations
@@
 
-\maketitle
-
 \begin{abstract}
@@
 
-Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
+Recently, \acrfull{ml} using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
 Statistical learning theory~\cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters. 
@@
 It is also clear that reaching safety-critical standards using test-set accuracy would require an infeasibly large test set~\cite{meyers}. 
-Therefore, we propose using accelerated failure time models to simulate edge-cases and verify models using a small number of samples.
+Therefore, we propose using \acrfull{aft} models to simulate edge-cases and verify models using a small number of samples.
 
@@
 ML pipelines play a crucial role in the development and deployment of robust and accurate models.
-However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
+However, managing complex pipelines across diverse \acrfull{cpu} and \acrfull{gpu}  architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
 One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native" software stack.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
-    \caption{For each dataset and hardware combination, a random state parameter was chosen at random to decide the test and train sets.
-Next, model parameters and attack parameters are chosen at random.
-After 128 random trials, the TPE algorithm attempts to maximize benign and adversarial accuracy while minimizing training time.}
-    \label{fig:experiments}
-\end{figure}
-
 \subsection{Accuracy}
@@
 which is generally assumed to indicate the rate of successes in real-world data sampled from the same distribution as the training data~\cite{tan2021critical}.
-However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020.
+However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}.
 In addition, it ignores the run-time cost of a given architectural decision, caring only about accuracy on benchmark data~\cite{desislavov2021compute,bailly2022effects}.
@@
 This then allows us to make claims like ``increasing training time by X\% will yield survival time gains of Y\%''~\cite{meyers_aft}.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{plots/experiment.pdf}
+    \caption{For each dataset and hardware combination, a random state parameter was chosen at random to decide the test and train sets.
+Next, model parameters and attack parameters are chosen at random.
+After 128 random trials, the TPE algorithm attempts to maximize benign and adversarial accuracy while minimizing training time by tuning the model parameters.
+The random seed for the data split and the attack parameters are sampled independently from this optimization, which is why they are colored differently.
+The model tuning (blue-box) is discussed in Section~\ref{optimisation}.
+After the trials are completed, several AFT models are fit (see: Section~\ref{survival_time}) and compared (see: Section~\ref{best-fit}) using the process depicted in the purple box.
+Finally we conduct the cost analysis outlined in Section~\ref{cost} (green box).}
+    \label{fig:experiments}
+\end{figure*}
+
+\subsection{Optimisation}
+\label{optimisation}
+
+ML models are typically trained by examining the effect of the entire hyper-parameter space on the resulting accuracy.
+However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
+making it infeasible to exhaustively evaluate the entire hyper-parameter search space.
+Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017} --- with several researchers noting an inverse relationship between model accuracy and model robustness~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}.
+Therefore, a proper search would keep this dual-objective in mind.
+To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
+In addition, we seek to minimize the training time in order to maximize the number of hyper-parameters that can be examined on a fixed budget.
+Further discussion of the cost analysis can be found in Section~\ref{cost}.
 
@@
 
-\subsubsection{Choosing the best AFT Model}
+\subsubsection{Survival Time}
+\label{accelerated}
+~\cm{
+By using adversarial samples (see: Equation~\ref{eq:adv_success}, failures can be induced.
+The likelihood of that failure is dependent on the amount of adversarial noise, $\varepsilon$~\cite{meyers_aft}.
+That is, we can say the probability of success at time, $t$ is inversely proportional to  noise distance, $\varepsilon$, and  directly proportional to some baseline survival function, $S_0$, such that the parameterised survival time $S_{\theta}(t)$ is:
+$$
+S_{\theta}(t) \propto  S_0 \left( \frac{t}{\varepsilon} \right)
+$$
+This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
+\begin{equation} \label{assumption}
+    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right),
+\end{equation}
+where $\phi$ is some acceleration factor described by the joint effect of the covariates:
+$$
+phi_{\theta}(x) = \exp( \beta_0 \varepsilon + \beta_1 x_1 + \cdots + \beta_n x_n),
+$$ 
+and where $\varpsilon, x$ are covariates and $\beta_0 \cdots \beta_n$ describe the fitted parameters.
+}
+This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.
+However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.
 
-To choose a best-fit from the possible AFT functions, one should prepare the collected metrics and scores and then compare them using \textit{e.g.}, Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), or Concordance, as per the best-practices for this methodology~\cite{aft_models,kleinbaum1996survival}.
-For AIC and BIC, that means choosing the smallest value.
+\subsection{Choosing the best AFT Model}
+\label{best-fit}
+To choose a best-fit from the possible AFT functions, one should prepare the collected metrics and scores and then compare them using \textit{e.g.}, Akaike Information Criterion (\acrshort{aic}), Bayesian Information Criteria (\acrshort{bic}), or Concordance, as per the best-practices for this methodology~\cite{aft_models,kleinbaum1996survival}.
+For \acrshort{aic} and \acrshort{bic}, that means choosing the smallest value.
 Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and 0.5 reflects random chance.
 By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by IEC61508~\cite{IEC61508}.
-We also noted the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}.
+We also noted the integrated calibration index (\acrshort{ici}) as well as the error at the 50th percentile \acrshort{e50}~\cite{ici}. 
 These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}. 
@@
 \cm{Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.}
-
-\subsection{Survival Time}
-\label{accelerated}
-
-Using accelerated failure time models under adverse ones (accelerated failure time), $S_{adv}$. The survival time for is
-$$
-    S_{\theta} := S(t_i; x, y, \varepsilon \mid \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
-$$
-\cm{where $\varepsilon$ -- or noise distance -- is treated as a covariate}.
-This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
-\begin{equation} \label{assumption}
-    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right)
-\end{equation}
-where $\phi$ is some acceleration factor described by the joint effect of the covariates and $S_0$ is the baseline hazard function (where the effect of the covariates are 0).
-This assumption means we can evaluate the generalization performance using a small number of adversarial samples~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
-However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.
-
-\subsection{Optimisation}
-\label{optimisation}
-
-ML models are typically trained by examining the effect of the entire hyper-parameter space on the resulting accuracy.
-However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
-making it infeasible to exhaustively evaluate the entire hyper-parameter search space.
-Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017} --- with several researchers noting an inverse relationship between model accuracy and model robustness~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}.
-Therefore, a proper search would keep this dual-objective in mind.
-To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
 
@@
 
+\subsection{Why Cost Matters}
+
+In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
+In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
+Using AFT, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}.
+By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
+As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
+If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
+
 \section{Experiments}
@@
 
-To assess the energy consumption of the experiments deployed on a Google Kubernetes Engine, the Kubernetes Efficient Power Level Exporter (KEPLER) was employed as measurement tool~\cite{amaral2023kepler}.
+To assess the energy consumption of the experiments, \Gls{kepler} deployed on a was used to measure the power consumption of each experiment~\cite{amaral2023kepler}.
 This approach enables gathering energy consumption data on granular levels as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components.
-In essence, KEPLER uses extended Berkeley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics.
-The eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space.
-The eBPF programs are invoked by the kernel when certain events occur.
+In essence, KEPLER uses extended Berkeley Packet Filter to probe energy-related system stats and exports them as Prometheus metrics.
+This filter can be described as a lightweight and sandboxed virtual machine (VM) in kernel space.
+The filter programs are invoked by the kernel when certain events occur.
 Examples of such events include system calls or network activity.
@@
 Approximately 10\% of this was used for development and 90\% was used for the evaluations.
+\cm{Over the course of the evaluations, 6\% of the budget went to the storage, 6\% to the monitoring, and the remaining 88\% went the GPUs. TODO: Calculate total cost/gpu for 1000 trials.}.
 
@@
     \centering
-    \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
+    \includegraphics[width=.9\textwidth]{plots/architecture.pdf}
     \caption{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility.
@@
 For each hardware configuration and dataset, the TPE algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials.
-This was chosen to be substantially larger than the 200 used successfully by Watanabe~\textit{et al.}~\cite{tpe_params} while still allowing for reasonable run times.
-In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}.
+This was chosen to be substantially larger than the 200 used successfully by Watanabe \textit{et al.}~\cite{tpe_params} while still allowing for reasonable run times~\cite{legriel2010approximating}.
+% In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}.
 Examining the effect of this and other TPE parameters on the total run-time and performance of this methodology was outside the scope of this work.
@@
 Using these values, we fit an AFT model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device.
-Additionally, we approximate the AFT model using the methodology described in Algorithm~\ref{fig:alg}.
+Additionally, we approximate the \acrshort{aft} model using the methodology depicted in Figure~\ref{fig:experiments}.
 
@@
     \includegraphics[width=0.5\textwidth,clip]{plots/combined/acc.pdf}
-    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware.}
+    \caption{\cm{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot.
+Each color is a different device and the datasets are displayed along the x-axis.
+Outliers are denoted with a white dot.}}
     \label{fig:acc}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
-        \caption{Training (left), Prediction (center), and Attack (right) Times.}
+        \caption{}
         \label{fig:time}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
-        \caption{Training (left), Prediction (center), and Attack (right) Power Consumption.}
+        \caption{}
         \label{fig:power}
@@
         \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
-        \caption{Training (left), Prediction (center), and Attack (right) Monetary Cost.}
+        \caption{}
         \label{fig:cost}
     \end{subfigure}
-    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets.
-For these plots, the y-axes have been scaled by the the number of samples for the sake of comparison.}
+    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets \cm{ for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
+Each color is a different device and the datasets are displayed along the first axis.
+Outliers are denoted with a white dot.}
+    For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
 \end{figure*}
@@
 
-\input{plots/combined/aft_comparison}  % Table II
+\begin{table*}
+\centering
+\caption{Comparison of AFT Models on the combined dataset.
+\cm{\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller one being preferred.
+Concordance is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model.
+\acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model.
+These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}}
+\label{tab:combined}
+\begin{tabular}{lrrrrrrrr}
+\toprule
+ & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
+\midrule
+Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
+Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 The concordance is both strong ($>0.5$) and similar for all three AFT models and both the train and test sets.
-We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFT models.
+We observed no more than 1\% mean absolute error in the probabilities \acrshort{ici} and no error in the median probability \acrshort{e50} across all three AFT models.
 Figure~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFT models.
-For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}, and average test error of 1\% (ICI) and 0 error for the median sample (E50).
+For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}, and average test error of 1\% \acrshort{ici} and 0 error for the median sample \acrshort{e50}.
 We also see that these metrics are  functionally identical across all AFT models as well as between the test and train set of each model.
@@
 \end{figure*}
-\begin{figure*}[h!]
+\begin{figure}[h!]
     \centering
@@
     % \caption{Weibull AFT Model.}
-\end{figure*}
+\end{figure}
 
@@
 Furthermore, by isolating changes and testing them as quickly as possible, it is easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars, drones, or industrial equipment) to effectively test.
-To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard~\cite{IEC61508}, allowing the model builder to make a quantitative assessment about the efficacy of a model change without testing the effect on real users.
+To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the IEC 61508 standard~\cite{IEC61508}, allowing the model builder to make a quantitative assessment about the efficacy of a model change without testing the effect on real users.
 Additionally, since AFT models have strong predictive power for untested hyper-parameter combinations, this method has a potential to reduce the search space by quickly eliminating candidates that are unlikely to increase the survival time.
@@
 \IEEEpeerreviewmaketitle
-
+\clearpage
+\printglossary[type=\acronymtype]
 \clearpage

### 2024-08-22 plots/cifar/aft_comparison.tex
++plots

@@
 \midrule
-Weibull & -5.22e+03 & -5.22e+03 & 0.85 & 0.85 & 0 & 0 & 0 & 0 \\
-Cox & -- & -- & 0.85 & 0.85 & 0.02 & 0.02 & 0 & 0 \\
-Log Logistic & -5.51e+03 & -5.51e+03 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -5.65e+03 & -5.65e+03 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
+Weibull & -5.18e+03 & -5.18e+03 & 0.85 & 0.86 & 0 & 0 & 0 & 0 \\
+Cox & -- & -- & 0.85 & 0.86 & 0.02 & 0.02 & 0 & 0 \\
+Log Logistic & -5.42e+03 & -5.42e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -5.57e+03 & -5.57e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-08-22 plots/cifar100/aft_comparison.tex
++plots

@@
 \midrule
-Weibull & -4.4e+03 & -4.4e+03 & 0.81 & 0.8 & 0 & 0.01 & 0 & 0 \\
-Cox & -- & -- & 0.81 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
-Log Logistic & -4.73e+03 & -4.73e+03 & 0.82 & 0.81 & 0.01 & 0.02 & 0 & 0 \\
-Log Normal & -4.89e+03 & -4.89e+03 & 0.82 & 0.81 & 0 & 0.02 & 0 & 0 \\
+Weibull & -4.39e+03 & -4.39e+03 & 0.81 & 0.8 & 0 & 0 & 0 & 0 \\
+Cox & -- & -- & 0.81 & 0.79 & 0.01 & 0.01 & 0 & 0 \\
+Log Logistic & -4.72e+03 & -4.72e+03 & 0.82 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -4.88e+03 & -4.88e+03 & 0.82 & 0.8 & 0 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-08-22 plots/mnist/aft_comparison.tex
++plots

@@
 \midrule
-Weibull & -6.51e+03 & -6.51e+03 & 0.9 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
-Cox & -- & -- & 0.9 & 0.9 & 0.04 & 0.04 & 0 & 0 \\
-Log Logistic & -6.48e+03 & -6.48e+03 & 0.91 & 0.9 & 0.03 & 0.04 & 0 & 0 \\
-Log Normal & -6.63e+03 & -6.63e+03 & 0.91 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Weibull & -6.47e+03 & -6.47e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Log Logistic & -6.48e+03 & -6.48e+03 & 0.91 & 0.91 & 0.04 & 0.04 & 0 & 0 \\
+Log Normal & -6.62e+03 & -6.62e+03 & 0.9 & 0.91 & 0.03 & 0.03 & 0 & 0 \\
 \bottomrule

### 2024-08-22 plots/combined/aft_comparison.tex
TLs Edits
Updates from Overleaf

@@
 \centering
-\caption{Comparison of AFR Models on the combined dataset.}
+\caption{Comparison of AFT Models on the combined dataset. Concordance is a measure between 0 a 1, with reflecting perfect concordance. }
 \label{tab:combined}
-\begin{tabular}{lrrrrrrrr}
+\begin{tabular}{lllrrrrrr}
 \toprule
@@
 Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
 Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\

### 2024-08-22 old_main.tex

--- 2024-08-22 main.tex
@@
     \centering
-    \begin{subfigure}[b]{.8\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{.8\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{.8\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
@@
     \end{subfigure}
-    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets \cm{ for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
+    \caption{This depicts the training, inference, and attack times (a), power (b), and cost (c), for all hardware and datasets \cm{ for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
 Each color is a different device and the datasets are displayed along the first axis.
@@
 \end{table*}
-
+\begin{figure*}[h!]
+    \centering
+    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \caption{ }
+    \end{subfigure}
+    \begin{subfigure}[b]{.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
+The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
+    \label{fig:qq}
+\end{figure*}
 \subsection{AFT Models}
@@
     \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}[b]{.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
-        \caption{}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{plots/combined/weibull_aft.pdf}
     \end{subfigure}
-    \begin{subfigure}[b]{.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
-        \caption{ }
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{plots/combined/log_normal_aft.pdf}
     \end{subfigure}
-    \begin{subfigure}[b]{.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
-        \caption{}
+    \begin{subfigure}{.3\textwidth}
+        \includegraphics[width=\textwidth]{plots/combined/log_logistic_aft.pdf}
     \end{subfigure}
-    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
-The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
-    \label{fig:qq}
-\end{figure*}
-\begin{figure}[h!]
-    \centering
-    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    % \begin{subfigure}{.5\linewidth}
-        \centering
-        \includegraphics[width=.5\textwidth]{plots/combined/weibull_aft.pdf}
     \caption{Coefficients of the Covariates for the Weibull AFT model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
     \label{fig:aft}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{.45\linewidth}
-    %     \centering
-    %     \includegraphics[width=\linewidth]{plots/combined/weibull_device_num_partial_effect.pdf}
-    %     \caption{\cm{The partial effect GPU on survival time.
-After accounting for GPU bandwidth (see Table~\ref{tab:hardware}) and the covariate effects of the hardware and and inference time, we se ethat Graphic}}
-    %     \label{fig:partial_effect}
-    % \end{subfigure}
-    % \caption{Weibull AFT Model.}
-\end{figure}
+\end{figure*}
 

### 2024-08-23 main.tex

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[sn-mathphys-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style 
 \usepackage{cite}
@@
 \usepackage{subcaption}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage[type=\acronymtype]{glossaries}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\minimise}{\textrm{minimise}}
-\DeclareMathOperator*{\maximise}{\textrm{maximise}}
-\newcommand{\Ie}{\textit{I.e.}\xspace}
-\newcommand{\ie}{\textit{i.e.}\xspace}
-\newcommand{\Eg}{\textit{E.g.}\xspace}
-\newcommand{\eg}{\textit{e.g.}\xspace}
-\newcommand{\probP}{\text{I\kern-0.15em P}}
-\newcommand{\tl}[1]{\textit{[{\color{red}#1}]}}
+\usepackage{glossaries}
 \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
-\newcommand{\erik}[1]{\textit{[{\color{brown}Erik: #1}]}}
-\newcommand{\mr}[1]{\textit{[{\color{brown}Mohammed: #1}]}}
-
 \input{glossary}
 \makeglossaries
+%Version 3 October 2023
+% See section 11 of the User Manual for version history
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
+
+%%=======================================================%%
+%% to print line numbers in the margin use lineno option %%
+%%=======================================================%%
+
+%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%======================================================%%
+%% to compile with pdflatex/xelatex use pdflatex option %%
+%%======================================================%%
+
+%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%Note: the following reference styles support Namedate and Numbered referencing.
+By default the style follows the most common style.
+To switch between the options you can add or remove Numbered in the optional parenthesis.
+%%The option is available for: sn-basic.bst, sn-vancouver.bst, sn-chicago.bst%
+
+%%\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
+%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+%%\documentclass[sn-mathphys-ay]{sn-jnl}% Math and Physical Sciences Author Year Reference Style
+%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
+%%\documentclass[sn-vancouver,Numbered]{sn-jnl}% Vancouver Reference Style
+%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style 
+%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
+
+%%%% Standard Packages
+%%<additional latex packages if required can be included here>
+
+\usepackage{graphicx}%
+\usepackage{multirow}%
+\usepackage{amsthm}%
+\usepackage{mathrsfs}%
+\usepackage[title]{appendix}%
+\usepackage{xcolor}%
+\usepackage{textcomp}%
+\usepackage{manyfoot}%
+\usepackage{booktabs}%
+%%%%
+
+%%%%%=============================================================================%%%%
+%%%%  Remarks: This template is provided to aid authors with the preparation
+%%%%  of original research articles intended for submission to journals published 
+%%%%  by Springer Nature. The guidance has been prepared in partnership with 
+%%%%  production teams to conform to Springer Nature technical requirements. 
+%%%%  Editorial and presentation requirements differ among journal portfolios and 
+%%%%  research disciplines. You may find sections in this template are irrelevant 
+%%%%  to your work and are empowered to omit any such section if allowed by the 
+%%%%  journal you intend to submit to. The submission guidelines and policies 
+%%%%  of the journal take precedence. A detailed User Manual is available in the 
+%%%%  template package for technical guidance.
+%%%%%=============================================================================%%%%
+
+%% as per the requirement new theorem styles can be included as shown below
+\newtheorem{theorem}{Theorem}%  meant for continuous numbers
+%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+
+\raggedbottom
+%%\unnumbered% uncomment this for unnumbered level heads
+
 \begin{document}
 
-\title{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}
+\title[Article Title]{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}
 
-\maketitle
+%%=============================================================%%
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% \author*[1,2]{\fnm{Joergen W.} \spfx{van der} \sur{Ploeg} 
+%%  \sfx{IV}}\email{iauthor@gmail.com}
+%%=============================================================%%
 
-\author{}
+\author*[1,2]{\fnm{First} \sur{Author}}\email{iauthor@gmail.com}
+
+\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
+\equalcont{These authors contributed equally to this work.}
+
+\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
+\equalcont{These authors contributed equally to this work.}
+
+\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}
+
+\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}
+
+\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}
 
@@
 
-\begin{IEEEkeywords}
-artificial intelligence, machine learning, adversarial AI, optimisation, compliance
-\end{IEEEkeywords}
+\keywords{artificial intelligence, machine learning, adversarial AI, optimisation, compliance}
 
@@
 Therefore, we propose using \acrfull{aft} models to simulate edge-cases and verify models using a small number of samples.
-
-\cm{
 Modern neural networks are massive --- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}. 
@@
 At these scales, we have no statistical guarantees about the performance of these models and test-set validation would require many, many billions of samples for each and every model change.
-}
-% One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}.
-Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}.
-One version of this open-source large language model (LLM) was able to outperform the commercially available GPT-3.5 model~\cite{liu2023goat} with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU), suggesting that consumer-level hardware can be used to effectively train large models in a reasonable time.
-Furthermore, popular models like Generative Pre-trained Transformer (GPT)~\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions or billions of parameters, requiring infeasibly large training datasets to verify a model\cite{vcdimension}.
-Media reports place the cost of training a GPT3 somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system.
-While the benefits of a more portable model are plentiful, there is not yet a method for formalizing the relationship between cost and model performance.
-
 Furthermore, even if we ignore the immense cost of training modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for assessing model generalization~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk.
@@
 Therefore, a new evaluation methodology is required.
-
-% As such, the methodology proposed in this paper, centered around survival analysis, tests a model against ``worst-case" (\textit{e.g.}, adversarial) inputs to verify the efficacy of one modelling deployment decision over another.
 We propose to use survival analysis as a methodological framework to model the failure conditions of a machine learning model.
@@
 where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
-\[
+\begin{equation}    
 	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt,
-\]
+    \label{eq:expectation}
+\end{equation}
+
 where $t^*$ is the latest time observed in the survival data.
@@
 That is, we can say the probability of success at time, $t$ is inversely proportional to  noise distance, $\varepsilon$, and  directly proportional to some baseline survival function, $S_0$, such that the parameterised survival time $S_{\theta}(t)$ is:
+}
 $$
-S_{\theta}(t) \propto  S_0 \left( \frac{t}{\varepsilon} \right)
+S_{\theta}(t) \propto  S_0  \frac{1}{\varepsilon} \left( t\right)
 $$
-This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
+\cm{
+This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}}
 \begin{equation} \label{assumption}
@@
 $$
-phi_{\theta}(x) = \exp( \beta_0 \varepsilon + \beta_1 x_1 + \cdots + \beta_n x_n),
+\phi_{\theta}(x) = \exp( \beta_0 \varepsilon + \beta_1 x_1 + \cdots + \beta_n x_n),
 $$
+\cm{
 and where $\varpsilon, x$ are covariates and $\beta_0 \cdots \beta_n$ describe the fitted parameters.
@@
 $$
-which will be driven by the memory bandwidth (measured in bits/second) of a given CPU or GPU and the size~\cite{vgg} and complexity~\cite{resnet} of a given neural network architecture.
+which will be driven by the memory bandwidth (measured in bits/second) of a given \acrshort{cpu} or \acrshort{gpu} and the size~\cite{vgg} and complexity~\cite{resnet} of a given neural network architecture.
 
 \subsection{Attack Generation Time}
-
+\cm{
 A successful attack is one that induces failure in a model.
-That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output.
-We approximate this for each attack/defence configuration by the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
-\begin{equation}
-    \label{attack_time}
-    T_a := t_a \cdot n \cdot i.
-\end{equation}
-In the interest of time, our chosen attack, FGM, uses only a single iteration $i =1$~\cite{fgm}.
+That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a failure.
+That is, the expected attack time \textit{is} the expected survival time.
+We can then define $t_a$ by using the survival model estimation from Equation~\ref{eq:expectation}, such that.
+}
+$$
+t_{a} = \mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt \approx  \frac{T_a}{n}.
+$$
 
@@
 In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
-Using AFT, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}.
+Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}. 
 By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
@@
 If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
+Previous research has provided a useful \textit{training rate and survival heuristic} (\acrshort{trash} score)~\cite{meyers_aft} that quantifies the ratio of training time to attack time.
+\begin{equation}
+    \textrm{TRASH~Score} = \frac{t_{t}}{t_{a}} 
+    \label{eq:trash}
+\end{equation}
 
@@
 \subsection{Cloud Platform and Hardware}
-To conduct the experiments and have access to different types of hardware, we utilized GCP.
+To conduct the experiments and have access to different types of hardware, we utilized \acrshort{gcp}.
 Six virtual machines running container optimised operating system provided by GCP constituted the test-bed.
@@
     \includegraphics[width=.9\textwidth]{plots/architecture.pdf}
-    \caption{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility.
+    \caption{\cm{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility.
 The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.
@@
 All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC).
-A PVC is a request for storage by user in Kubernetes which is then connected to the object storage.}
+A PVC is a request for storage by user in Kubernetes which is then connected to the object storage.
+The blue experiment, blue-green object storage, green analysis component, and purple AFT component correspond to the same colors in Figure~\ref{fig:experiments}.}}
     \label{fig:architecture}
@@
     \href{https://nvdam.widen.net/s/rvq98gbwsw/l4-datasheet-2595652}{L4 Datasheet}.
-Prices were retrieved from Google Cloud Platform for the \texttt{europe-west4} region on 3 December 2023 at \href{https://cloud.google.com/pricing/list}{this link}.
+Prices were retrieved from \href{https://cloud.google.com/pricing/list}{Google Cloud Platform} for the \texttt{europe-west4} region on 3 December 2023.
     }
@@
     \centering
-    \includegraphics[width=0.5\textwidth,clip]{plots/combined/acc.pdf}
+    \includegraphics[width=\textwidth,clip]{plots/combined/acc.pdf}
     \caption{\cm{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot.
@@
     \end{subfigure}
-    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets \cm{ for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
+    \caption{This depicts the training, inference, and attack times (a), power (b), and cost (c), for all hardware and datasets \cm{for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
 Each color is a different device and the datasets are displayed along the first axis.
-Outliers are denoted with a white dot.}
-    For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
+Outliers are denoted with a white dot.} For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
 \end{figure*}
@@
 Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).
-We can also see that average training time per sample is takes slightly more than than attack generation time per sample (see:~\ref{fig:time} left and right plots).
+We can also see that average training time per sample is takes slightly more than than attack generation time per sample (see: Figure~\ref{fig:time} left and right plots).
 
@@
 
-\begin{table*}
+\begin{table}
 \centering
-\caption{Comparison of AFT Models on the combined dataset.
-\cm{\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller one being preferred.
-Concordance is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model.
+\caption{Comparison of AFT Models across all hardware and datasets.
+\cm{\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred.
+Concordance (Conc) is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model.
 \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model.
@@
 \toprule
- & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
+ & AIC & BIC & Conc & Test Conc & ICI & Test ICI & E50 & Test E50 \\
 \midrule
-Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
-Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
+Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0.00 & 0.01 & 0.00 & 0.00 \\
+Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0.00 & 0.00 \\
+Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0.00 & 0.00 & 0.00 \\
 \bottomrule
 \end{tabular}
-\end{table*}
+\end{table}
+\begin{figure*}[h!]
+    \centering
+    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \caption{ }
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_qq.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
+The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
+    \label{fig:qq}
+\end{figure*}
 
+\begin{figure*}[h!]
+    \centering
+    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_trash_score.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_trash_score.pdf}
+        \caption{ }
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_trash_score.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{\cm{TODO}}
+    \label{fig:trash}
+\end{figure*}
 \subsection{AFT Models}
@@
     \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}[b]{.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
-        \caption{}
+    \begin{subfigure}{\textwidth}
+        \includegraphics[width=.8\textwidth]{plots/combined/weibull_aft.pdf}
     \end{subfigure}
-    \begin{subfigure}[b]{.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
-        \caption{ }
+    \begin{subfigure}{\textwidth}
+        \includegraphics[width=.8\textwidth]{plots/combined/log_normal_aft.pdf}
     \end{subfigure}
-    \begin{subfigure}[b]{.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
-        \caption{}
+    \begin{subfigure}{\textwidth}
+        \includegraphics[width=.8\textwidth]{plots/combined/log_logistic_aft.pdf}
     \end{subfigure}
-    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
-The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
-    \label{fig:qq}
+    \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
+    \label{fig:aft}
 \end{figure*}
-\begin{figure}[h!]
-    \centering
-    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    % \begin{subfigure}{.5\linewidth}
-        \centering
-        \includegraphics[width=.5\textwidth]{plots/combined/weibull_aft.pdf}
-        \caption{Coefficients of the Covariates for the Weibull AFT model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
-        \label{fig:aft}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{.45\linewidth}
-    %     \centering
-    %     \includegraphics[width=\linewidth]{plots/combined/weibull_device_num_partial_effect.pdf}
-    %     \caption{\cm{The partial effect GPU on survival time.
-After accounting for GPU bandwidth (see Table~\ref{tab:hardware}) and the covariate effects of the hardware and and inference time, we se ethat Graphic}}
-    %     \label{fig:partial_effect}
-    % \end{subfigure}
-    % \caption{Weibull AFT Model.}
-\end{figure}
 
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 \clearpage
-\printglossary[type=\acronymtype]
+\printglossary
 \clearpage

### 2024-08-23 plots/cifar/aft_comparison.tex
++plots

@@
 \midrule
-Weibull & -5.18e+03 & -5.18e+03 & 0.85 & 0.86 & 0 & 0 & 0 & 0 \\
+Weibull & -5.18e+03 & -5.19e+03 & 0.85 & 0.86 & 0 & 0 & 0 & 0 \\
 Cox & -- & -- & 0.85 & 0.86 & 0.02 & 0.02 & 0 & 0 \\
-Log Logistic & -5.42e+03 & -5.42e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -5.57e+03 & -5.57e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
+Log Logistic & -5.42e+03 & -5.43e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -5.57e+03 & -5.58e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-08-23 plots/cifar100/aft_comparison.tex
++plots

@@
 \midrule
-Weibull & -4.39e+03 & -4.39e+03 & 0.81 & 0.8 & 0 & 0 & 0 & 0 \\
+Weibull & -4.39e+03 & -4.4e+03 & 0.81 & 0.8 & 0 & 0 & 0 & 0 \\
 Cox & -- & -- & 0.81 & 0.79 & 0.01 & 0.01 & 0 & 0 \\
-Log Logistic & -4.72e+03 & -4.72e+03 & 0.82 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
+Log Logistic & -4.72e+03 & -4.73e+03 & 0.82 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
 Log Normal & -4.88e+03 & -4.88e+03 & 0.82 & 0.8 & 0 & 0.01 & 0 & 0 \\

### 2024-08-23 plots/mnist/aft_comparison.tex
++plots

--- 2024-08-20 plots/mnist/aft_comparison.tex
@@
 \midrule
-Weibull & -6.51e+03 & -6.51e+03 & 0.9 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
-Cox & -- & -- & 0.9 & 0.9 & 0.04 & 0.04 & 0 & 0 \\
-Log Logistic & -6.48e+03 & -6.48e+03 & 0.91 & 0.9 & 0.03 & 0.04 & 0 & 0 \\
-Log Normal & -6.63e+03 & -6.63e+03 & 0.91 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Weibull & -6.47e+03 & -6.48e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Log Logistic & -6.48e+03 & -6.49e+03 & 0.91 & 0.91 & 0.04 & 0.04 & 0 & 0 \\
+Log Normal & -6.62e+03 & -6.63e+03 & 0.9 & 0.91 & 0.03 & 0.03 & 0 & 0 \\
 \bottomrule

### 2024-08-23 main.tex
Updates from Overleaf

@@
 \documentclass[sn-mathphys-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style 
-\usepackage{cite}
+% \usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{multirow}%
-\usepackage{amsthm}%
 \usepackage{mathrsfs}%
@@
 Furthermore, even if we ignore the immense cost of training modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for assessing model generalization~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk.
-Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern since inducing a failure at run-time has consistently shown to be trivial~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.
+Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern since inducing a failure at run-time has consistently shown to be trivial~\cite{adversarialpatch,carlini_towards_2017,croce_reliable_2020,hopskipjump,chakraborty2018adversarial,art2018}.
 Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive for these large models.
@@
 Instead of having a test set large enough to cover all of the failure cases, we generate adversarial samples crafted specifically to make the model fail and then use survival analysis to predict these failures in general.
-
 In this work, we used accelerated failure-time methods to predict model performance as a function of various model parameters.
@@
 The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
+~\cm{Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will }
+
 To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
@@
 Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.
+~\cm{To optimize for training time as well as robustness, the TPE optimization was used (see:~Section~\ref{optimisation}).
+However, it is first necessary to define robustness.}
 
@@
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
-These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
+These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch, pixelattack,hopskipjump}.
 
@@
 The model tuning (blue-box) is discussed in Section~\ref{optimisation}.
-After the trials are completed, several AFT models are fit (see: Section~\ref{survival_time}) and compared (see: Section~\ref{best-fit}) using the process depicted in the purple box.
+After the trials are completed, several AFT models are fit (see Section~\ref{survival_time}) and compared (see Section~\ref{best-fit}) using the process depicted in the purple box.
 Finally we conduct the cost analysis outlined in Section~\ref{cost} (green box).}
@@
 \label{accelerated}
-~\cm{
-By using adversarial samples (see: Equation~\ref{eq:adv_success}, failures can be induced.
+\cm{
+By using adversarial samples (see Equation~\ref{eq:adv_success}, failures can be induced.
 The likelihood of that failure is dependent on the amount of adversarial noise, $\varepsilon$~\cite{meyers_aft}.
@@
 \end{equation}
-where $\phi$ is some acceleration factor described by the joint effect of the covariates:
+where $\phi$ is some acceleration factor described by the joint effect of the covariates,
 $$
-\phi_{\theta}(x) = \exp( \beta_0 \varepsilon + \beta_1 x_1 + \cdots + \beta_n x_n),
+    \phi_{\theta}(x) = \exp( \theta_0 \varepsilon + \theta_1 x_1 + \cdots + \theta_n x_n),
 $$
 \cm{
-and where $\varpsilon, x$ are covariates and $\beta_0 \cdots \beta_n$ describe the fitted parameters.
+and where $\varepsilon, x$ are covariates and $\theta_0, \ldots, \theta_n$ describe the fitted parameters.
 }
@@
 }
-$$
-t_{a} = \mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt \approx  \frac{T_a}{n}.
-$$
+\begin{equation}    
+t_{a} = \mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt 
+\label{eq:attack_time}
+\end{equation}
 
@@
 If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
-Previous research has provided a useful \textit{training rate and survival heuristic} (\acrshort{trash} score)~\cite{meyers_aft} that quantifies the ratio of training time to attack time.
+~\cm{Previous research has provided a useful \textit{training rate and survival heuristic} (\acrshort{trash} score)~\cite{meyers_aft} that quantifies the ratio of training time to attack time.}
 \begin{equation}
-    \textrm{TRASH~Score} = \frac{t_{t}}{t_{a}} 
-    \label{eq:trash}
+    \textrm{TRASH~Score} = \frac{t_{\mathrm{train}}}{\mathbb{E}_{\theta}[T \,|\, 0 < \varepsilon \leq \varepsilon^*]}.
+	\label{eq:cost}
 \end{equation}
@@
 Approximately 10\% of this was used for development and 90\% was used for the evaluations.
-\cm{Over the course of the evaluations, 6\% of the budget went to the storage, 6\% to the monitoring, and the remaining 88\% went the GPUs. TODO: Calculate total cost/gpu for 1000 trials.}.
+\cm{Over the course of the evaluations, 6\% of the budget went to the storage, 6\% to the monitoring, and the remaining 88\% went the GPUs.}
 
@@
 
-For each hardware configuration and dataset, the TPE algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials.
+For each hardware configuration and dataset, the \acrshort{tpe} algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials.
 This was chosen to be substantially larger than the 200 used successfully by Watanabe \textit{et al.}~\cite{tpe_params} while still allowing for reasonable run times~\cite{legriel2010approximating}.
@@
 To calculate this, the price per hour from each cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} Google Cloud prices for L4 obtained \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} were used and the cost of training ($C_{t}$) and the cost of inference ($C_{i}$) calculated from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
-\begin{table}[h]
+\begin{table*}[h]
     \centering
@@
     \label{tab:hardware}
-\end{table}
+\end{table*}
 
@@
 This section presents and discusses the results for all of the experiments across all datasets and hardware.
-First, the accuracy, training time, inference, and monetary cost are discussed in Secs.~\ref{res:acc}-\ref{res:cost}, followed by the fitted AFT model in Section~\ref{res:aft}.
+First, the accuracy, training time, inference, and monetary cost are discussed in Sections~\ref{res:acc}--\ref{res:cost}, followed by the fitted AFT model in Section~\ref{res:aft}.
 
@@
 This should be no surprise since the less-capable hardware is meant to be used exclusively for inference.
-Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).
-We can also see that average training time per sample is takes slightly more than than attack generation time per sample (see: Figure~\ref{fig:time} left and right plots).
+Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Equation~\ref{eq:attack_time}).
+We can also see that average training time per sample is takes slightly more than than attack generation time per sample (see Figure~\ref{fig:time} left and right plots).
 
@@
 \midrule
-Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0.00 & 0.01 & 0.00 & 0.00 \\
-Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0.00 & 0.00 \\
-Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0.00 & 0.00 & 0.00 \\
+Weibull      & $-2.11\cdot10^4$ & $-2.11\cdot10^4$ & 0.84 & 0.83 & 0.00 & 0.01 & 0.00 & 0.00 \\
+Log Logistic & $-2.18\cdot10^4$ & $-2.18\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.01 & 0.00 & 0.00 \\
+Log Normal   & $-2.25\cdot10^4$ & $-2.25\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.00 & 0.00 & 0.00 \\
 \bottomrule
@@
 Using the $S_{\theta}(t)$ described in Section~\ref{aft}, we can model the effect of various hardware devices, which is depicted in Figure~\ref{fig:aft}.
-It clearly shows that hardware choice has a relatively small effect (+/- 20\%) on robustness, despite the much larger disparity in cost outlined in Table~\ref{tab:hardware}.
+It clearly shows that hardware choice has a relatively small effect ($\pm 20\%$) on robustness, despite the much larger disparity in cost outlined in Table~\ref{tab:hardware}.
 
@@
 \label{advantages}
-\cm{Moved from the AFT section to here at Tommy's suggestion.}
 \cm{The primary advantage of this methodology over the traditional test/train split measurements is that the precision of the latter is determined by the number of samples; whereas, the precision of the survival time estimate is driven by the resolution of our timing measurements.
 For test-set accuracy,  meeting the weakest safety-critical IEC standard (1 failure in a million) would require many millions of samples to confidently conclude that a model is safe.
-However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see: Table~\ref{tab:combined}).}
+However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:combined}).}
 Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in machine learning applications.
@@
 \clearpage
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
+\bibliography{sn-bibliography}
 

### 2024-08-23 main.tex
Updates from Overleaf

@@
 
-\begin{abstract}
+\abtract{
 Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model at run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
@@
 Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
-\end{abstract}
+}
 
 \keywords{artificial intelligence, machine learning, adversarial AI, optimisation, compliance}
+
+%%\pacs[JEL Classification]{D8, H51}
+
+%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
+
+\maketitle
 
@@
 \subsection{ML Pipelines}
+\label{ml_pipelines}
 ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters.
@@
 The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
-~\cm{Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will }
-
-To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
+\cm{Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.} To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
 Likewise, Nvidia offers hardware that is marketed as either for training (\textit{e.g.}, v100 and p100) or only for inference (\textit{e.g.}, l4).
@@
 Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.
-~\cm{To optimize for training time as well as robustness, the TPE optimization was used (see:~Section~\ref{optimisation}).
+~\cm{To optimize for training time as well as robustness (both $\lambda_{ben}$ and $\lambda_{adv}$), the \acrshort{tpe} optimization was used (see:~Section~\ref{optimisation}).
 However, it is first necessary to define robustness.}
@@
 \begin{equation}
-    \hat{y} \neq \hat{y_a} = K(x + \varepsilon; \theta).
+    \hat{y} \neq \hat{y_a} = K(x + \varepsilon; \theta ) ,
 \label{eq:adv_success}
 \end{equation}
+where $\varepsilon$ is a noise distance bounded by $0 < \varepsilon \leq \varepsilon^*$
 Additionally, one can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accuracy} which is Eq.~\ref{eq:acc} calculated on the perturbed samples.
@@
 These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch, pixelattack,hopskipjump}.
-
-% \cm{I cut itemized list more discussion about learning rate tuning?}
-% \begin{itemize}
-%     \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying certain inputs or otherwise change the behavior of a modelt~\cite{ carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
-%     \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset to influence the model's behaviour at run-time~\cite{biggio_poisoning_2013, saha2020hidden}.
-%     \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
-%     \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
-% \end{itemize}
-
 One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}.
@@
 Therefore, a proper search would keep this dual-objective in mind.
-To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
+\cm{
+In addition, we attempt to minimize the training time for each piece of hardware since optimal batch size and, therefore, learning rate will be determined by the \acrshort{vram}, the size bit depth of the data as well as the size and bit depth of the model.
+To maximise adversarial and benign accuracy simultaneously while minimizing training time, we propose the use of the \acrfull{tpe} because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials typical of other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
 In addition, we seek to minimize the training time in order to maximize the number of hyper-parameters that can be examined on a fixed budget.
 Further discussion of the cost analysis can be found in Section~\ref{cost}.
+}
 
@@
 \cm{
-By using adversarial samples (see Equation~\ref{eq:adv_success}, failures can be induced.
-The likelihood of that failure is dependent on the amount of adversarial noise, $\varepsilon$~\cite{meyers_aft}.
-That is, we can say the probability of success at time, $t$ is inversely proportional to  noise distance, $\varepsilon$, and  directly proportional to some baseline survival function, $S_0$, such that the parameterised survival time $S_{\theta}(t)$ is:
+By using adversarial samples (see Equation~\ref{eq:adv_success}), failures can be induced.
+The likelihood of that failure is dependent on the amount of adversarial noise, $\varepsilon$, since adversarial noise is known to \textit{induce} failures.
+That is, the rate of adversarial success (Equation~\ref{eq:adv_success}), will increase as $\varepsilon$ increases.
+In terms of AFT models, this can be expressed as the expected lifetime of an adversarial sample when treating $\varepsilon$ as a covariate.
+In the language of accelerated failure time models, this can be expressed in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
 }
-$$
-    S_{\theta}(t) \propto  S_0  \frac{1}{\varepsilon} \left( t\right)
-$$
-\cm{
-This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}}
 \begin{equation} \label{assumption}
@@
 \end{equation}
-where $\phi$ is some acceleration factor described by the joint effect of the covariates,
+\cm{
+where $\phi$ is some acceleration factor described by the joint effect of the covariates, such that
+}
 $$
-    \phi_{\theta}(x) = \exp( \theta_0 \varepsilon + \theta_1 x_1 + \cdots + \theta_n x_n),
+    \phi_{\theta}(x) = \exp{ \left( \theta_0 x_0 + \theta_1 x_1 + \cdots + \theta_n x_n \right) },
 $$
 \cm{
-and where $\varepsilon, x$ are covariates and $\theta_0, \ldots, \theta_n$ describe the fitted parameters.
+and where $x_0 \cdots x_n$ are covariates and $\theta_0, \ldots, \theta_n$ describe the fitted parameters when $\varepsilon$ is used as one of the covariates.
+That is, when the adversarial noise increases, it will shorten the expected survival time of a sample proportionally.
 }
-This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.
-However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.
+This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.\
+\cm{
+However, in order to find the the correct distribution, one must measure the goodness-of-fit and conduct a survival probability calibration.
+}
 
@@
 \subsection{Attack Generation Time}
+A successful attack is one that induces failure in a model.
+That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output.
+Assuming a uniform distribution, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
+\begin{equation}
+    T_a := t_a \cdot n \cdot i.
+\end{equation}
+In the interest of time, our chosen attack, FGM, uses only a single iteration $i =1$~\cite{fgm}. 
 \cm{
-A successful attack is one that induces failure in a model.
-That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a failure.
-That is, the expected attack time \textit{is} the expected survival time.
-We can then define $t_a$ by using the survival model estimation from Equation~\ref{eq:expectation}, such that.
+In reality, the attack time will not be drawn from a uniform distribution and prior research~\cite{meyers_aft} has shown that by treating model and attack parameters as  this can be more accurately approximated with $t_{a}'$
 }
 \begin{equation}
-t_{a} = \mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt 
-\label{eq:attack_time}
+	t_{a}' \approx \mathbb{E}_{S_\theta}[T] =  \int_{0}^{t^*} S_{\theta}(t) dt.
 \end{equation}
@@
 
+\subsection{TRASH Score}
+\cm{
+With an estimate of the expected survival time in hand,  quantify the cost-normalized failure rate, or the ratio of training time to attack time.
+Assuming that the cost scales linearly -- as discussed above-- the model builder's cost is proportional to the training time ($C_t \propto t_{t}$), and the attacker's cost is proportional to the attack time, which is approximately the expected survival time ($C_{a} \propto t_{a} \approx \mathbb{E}_{S\theta}[T]$).
+Using the definition of $\varepsilon$ from Equation~\ref{eq:adv_success}, we can express the cost of failure in adversarial terms as follows:
+}
+\begin{equation}
+	\textrm{TRASH~Score}=\frac{t_t}{\mathbb{E}_{\theta}[T \,|\, 0 < \varepsilon \leq \varepsilon^*]} = \frac{t_t}{t_a'}.
+	\label{eq:cost}
+\end{equation}
+
 \subsubsection{Power}
@@
 
-\subsection{Why Cost Matters}
-
-In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
-In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
-Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}. 
-By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
-As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
-If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
-~\cm{Previous research has provided a useful \textit{training rate and survival heuristic} (\acrshort{trash} score)~\cite{meyers_aft} that quantifies the ratio of training time to attack time.}
-\begin{equation}
-    \textrm{TRASH~Score} = \frac{t_{\mathrm{train}}}{\mathbb{E}_{\theta}[T \,|\, 0 < \varepsilon \leq \varepsilon^*]}.
-	\label{eq:cost}
-\end{equation}
-
 \section{Experiments}
@@
 This section outlines specific implementation details for the evaluation of the survival analysis methodology outlined in Section~\ref{aft} and the cost analysis methodology outlined in Sec~\ref{cost}.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.9\textwidth]{plots/architecture.pdf}
+    \caption{\cm{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility.
+The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.
+The other node pools each had one node with a specific GPU.
+The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.
+All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC).
+A PVC is a request for storage by user in Kubernetes which is then connected to the object storage.
+The blue experiment, blue-green object storage, green analysis component, and purple AFT component correspond to the same colors in Figure~\ref{fig:experiments}.}}
+    \label{fig:architecture}
+\end{figure*}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.9\textwidth]{plots/architecture.pdf}
-    \caption{\cm{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility.
-The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.
-The other node pools each had one node with a specific GPU.
-The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.
-All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC).
-A PVC is a request for storage by user in Kubernetes which is then connected to the object storage.
-The blue experiment, blue-green object storage, green analysis component, and purple AFT component correspond to the same colors in Figure~\ref{fig:experiments}.}}
-    \label{fig:architecture}
-\end{figure*}
-
 \subsection{AFT Models}
@@
 This was chosen to be substantially larger than the 200 used successfully by Watanabe \textit{et al.}~\cite{tpe_params} while still allowing for reasonable run times~\cite{legriel2010approximating}.
-% In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}.
-Examining the effect of this and other TPE parameters on the total run-time and performance of this methodology was outside the scope of this work.
 We used three optimisation criteria: benign accuracy, training time, and adversarial accuracy, seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost).
@@
 In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
-Using AFT models, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}. 
+Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}. 
 By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
 As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
-If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.
+If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
+\cm{TODO.
+Discuss the TRASH SCORE plots.}
 

### 2024-08-23 main.tex

@@
     T_a := t_a \cdot n \cdot i.
+    \label{eq:attack_time}
 \end{equation}
@@
 	t_{a}' \approx \mathbb{E}_{S_\theta}[T] =  \int_{0}^{t^*} S_{\theta}(t) dt.
+ \label{eq:aft_time}
 \end{equation}
@@
 With an estimate of the expected survival time in hand,  quantify the cost-normalized failure rate, or the ratio of training time to attack time.
-Assuming that the cost scales linearly -- as discussed above-- the model builder's cost is proportional to the training time ($C_t \propto t_{t}$), and the attacker's cost is proportional to the attack time, which is approximately the expected survival time ($C_{a} \propto t_{a} \approx \mathbb{E}_{S\theta}[T]$).
-Using the definition of $\varepsilon$ from Equation~\ref{eq:adv_success}, we can express the cost of failure in adversarial terms as follows:
+Assuming that the cost scales linearly -- as discussed above-- the model builder's cost is proportional to the training time ($C_t \propto t_{t}$), and the attacker's cost is proportional to the attack time, which is approximately the expected survival time ($C_{a} \propto t_{a}' \approx \mathbb{E}_{S\theta}[T]$).
+Using the definition of $\varepsilon$ from Equation~\ref{eq:adv_success} and definition of $t_a'$ from Equation~\ref{eq:aft_time}, we can express the cost of failure in adversarial terms as follows:
 }
@@
 
+\subsection{Time, Power, Cost}
+\label{res:cost}
+
+Figure~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models.
+Slower hardware (see Memory Bandwidth in Table~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
+This should be no surprise since the less-capable hardware is meant to be used exclusively for inference.
+Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Equation~\ref{eq:attack_time}).
+We can also see that average training time per sample is takes slightly more than than attack generation time per sample (see Figure~\ref{fig:time} left and right plots).
+
+The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Figure~\ref{fig:power}.
+It tracks monetary cost (Figure~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is correlated with the power requirement.
+Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Figure~\ref{fig:power}) for prediction, while differences between hardware and datasets are insignificant for the training and attack metrics.
+
+The monetary cost for each dataset and each piece of hardware is shown in Figure~\ref{fig:cost}.
+For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
+In the best case scenario, they are comparable, but attacks consistently succeed with only 100 samples (Figure~\ref{fig:acc}) while model training requires orders of magnitude more.
+%  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
 \begin{figure}[h!]
@@
 \end{figure*}
-
-\subsection{Time, Power, Cost}
-\label{res:cost}
-
-Figure~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models.
-Slower hardware (see Memory Bandwidth in Table~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference.
-This should be no surprise since the less-capable hardware is meant to be used exclusively for inference.
-Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Equation~\ref{eq:attack_time}).
-We can also see that average training time per sample is takes slightly more than than attack generation time per sample (see Figure~\ref{fig:time} left and right plots).
-
-The power consumption during training, inference, and attack generation for all hardware and datasets is illustrated in Figure~\ref{fig:power}.
-It tracks monetary cost (Figure~\ref{fig:cost}) closely, probably because that's the predominant cost for the datacenter itself~\cite{dayarathna2015data}, so it is unsurprising that cloud billing is correlated with the power requirement.
-Furthermore, we see that the largest dataset (CIFAR100) and smallest GPU (L4) require the least amount of power (Figure~\ref{fig:power}) for prediction, while differences between hardware and datasets are insignificant for the training and attack metrics.
-
-The monetary cost for each dataset and each piece of hardware is shown in Figure~\ref{fig:cost}.
-For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample.
-In the best case scenario, they are comparable, but attacks consistently succeed with only 100 samples (Figure~\ref{fig:acc}) while model training requires orders of magnitude more.
-%  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
 
@@
     \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_trash_score.pdf}
-        \caption{}
+    \begin{subfigure}{\textwidth}
+        \includegraphics[width=.8\textwidth]{plots/combined/weibull_aft.pdf}
     \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_trash_score.pdf}
-        \caption{ }
+    \begin{subfigure}{\textwidth}
+        \includegraphics[width=.8\textwidth]{plots/combined/log_normal_aft.pdf}
     \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_trash_score.pdf}
-        \caption{}
+    \begin{subfigure}{\textwidth}
+        \includegraphics[width=.8\textwidth]{plots/combined/log_logistic_aft.pdf}
     \end{subfigure}
-    \caption{\cm{TODO}}
-    \label{fig:trash}
+    \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models.
+Here, "Random State" is used as a control variable that should be (and is) close to 0.
+\cm{A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
+The symbols $T_i$ and $T_t$ refer training and inference time for all samples, while $\lambda$ refers to the benign accuracy (accuracy on the un-altered samples).}}
+    \label{fig:aft}
 \end{figure*}
@@
     \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}{\textwidth}
-        \includegraphics[width=.8\textwidth]{plots/combined/weibull_aft.pdf}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_trash_score.pdf}
+        \caption{}
     \end{subfigure}
-    \begin{subfigure}{\textwidth}
-        \includegraphics[width=.8\textwidth]{plots/combined/log_normal_aft.pdf}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_trash_score.pdf}
+        \caption{ }
     \end{subfigure}
-    \begin{subfigure}{\textwidth}
-        \includegraphics[width=.8\textwidth]{plots/combined/log_logistic_aft.pdf}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_trash_score.pdf}
+        \caption{}
     \end{subfigure}
-    \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
-    \label{fig:aft}
+    \caption{\cm{TODO}}
+    \label{fig:trash}
 \end{figure*}

### 2024-08-23 main.tex
Updates from Overleaf

@@
 By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by IEC61508~\cite{IEC61508}.
-We also noted the integrated calibration index (\acrshort{ici}) as well as the error at the 50th percentile \acrshort{e50}~\cite{ici}. 
+\cm{
+While the aforementioned metrics measure goodness-of-fit, one should conduct a \textit{survival probability calibration}, where one fits the AFT model to the data and compares it to a cubic-spline that is meant to capture the un-modelled relationship between failures and time~\cite{ici}.
+These plots can be used to visually inspect the goodness-of-fit of various models, as in Figure~\ref{fig:qq}.
+}
+The integrated calibration index (\acrshort{ici}) as well as the error at the 50th percentile \acrshort{e50}~\cite{ici} can then be calculated. 
 These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}. 
-Then, the fitted AFT models were plotted using that compares the fitted AFT model to a cubic spline fit to the data~\textit{et al.}~\cite{ici}  to visually inspect each model for goodness-of-fit (see Figure~\ref{fig:qq}).
 \cm{Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_qq.pdf}
+        \includegraphics[width=.67\linewidth,clip]{plots/combined/weibull_qq.pdf}
         \caption{}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \includegraphics[width=.67\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
         \caption{ }
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_qq.pdf}
+        \includegraphics[width=.67\linewidth,clip]{plots/combined/log_normal_qq.pdf}
         \caption{}
@@
     \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
-The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
+The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $.}}
     \label{fig:qq}
@@
 \cm{A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
-The symbols $T_i$ and $T_t$ refer training and inference time for all samples, while $\lambda$ refers to the benign accuracy (accuracy on the un-altered samples).}}
+The symbols $T_i$ and $T_t$ refer training and inference time for all samples, while \textit{Ben.
+Accuracy} refers to the benign accuracy (accuracy on the un-altered samples), and $\varepsilon$ is the noise distance.}}
     \label{fig:aft}
@@
 Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.
+\cm{TODO add}
 

### 2024-08-26 main.tex
Updates from Overleaf

@@
 
-%%\pacs[JEL Classification]{D8, H51}
-
-%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
-
 \maketitle
@@
 Recently, \acrfull{ml} using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
-Statistical learning theory~\cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters. 
+Statistical learning theory~\cite{vcdimension,shalev2014understanding} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters.
 To overcome this, neural networks need large amounts of data~\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
@@
 Modern neural networks are massive --- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}. 
-For image systems, VGG19~\cite{vgg} is now considered small with \textit{only} 138 million parameters. 
-ResNet152 has a similar number of parameters at 116 million~\cite{resnet}. 
-However, modern advancements in transformer architectures have lead to an explosion in model size with the recent Mamba model boasting a massive 8 \textit{billion} tunable parameters~\cite{mamba}.
+For image systems, AlexNet~\cite{alom2018history} is now considered small with \textit{only} 60 million parameters. 
+ResNet152 has even more parameters at 116 million~\cite{resnet}. 
+However, modern architectures have lead to an explosion in model size with the recent Mamba model boasting a massive 8 \textit{billion} tunable parameters~\cite{mamba}.
 At these scales, we have no statistical guarantees about the performance of these models and test-set validation would require many, many billions of samples for each and every model change.
@@
 In addition, we attempt to minimize the training time for each piece of hardware since optimal batch size and, therefore, learning rate will be determined by the \acrshort{vram}, the size bit depth of the data as well as the size and bit depth of the model.
-To maximise adversarial and benign accuracy simultaneously while minimizing training time, we propose the use of the \acrfull{tpe} because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials typical of other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
+To maximise adversarial and benign accuracy simultaneously while minimizing training time, we propose the use of the \acrfull{tpe} because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials typical of other multi-objective optimisation algorithms like CMAES or NSGA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.
 In addition, we seek to minimize the training time in order to maximize the number of hyper-parameters that can be examined on a fixed budget.
@@
 $$
-    S_{\theta}(t) = p(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
+    S_{\theta}(t) = p(T>t  \mid \theta) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
 $$
@@
 \begin{equation}    
-	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt,
+	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(u) \,du,
     \label{eq:expectation}
@@
 $$
-    \phi_{\theta}(x) = \exp{ \left( \theta_0 x_0 + \theta_1 x_1 + \cdots + \theta_n x_n \right) },
+    \phi_{\theta}(x) = \exp{ \left( \theta_0 x_0 + \theta_1 x_1 + \cdots + \theta_n x_i \right) },
 $$
 \cm{
-and where $x_0 \cdots x_n$ are covariates and $\theta_0, \ldots, \theta_n$ describe the fitted parameters when $\varepsilon$ is used as one of the covariates.
+and where $x_0 \cdots x_n$ are covariates and $\theta_0, \ldots, \theta_n$ describe the fitted parameters  $\varepsilon$ is used as one of the covariates.
 That is, when the adversarial noise increases, it will shorten the expected survival time of a sample proportionally.
 }
-This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.\
+This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.
 \cm{
@@
     \end{subfigure}
-    \caption{\cm{TODO}}
+    \caption{The training rate and survival heuristic that depicts the per-sample ratio of training time to attack time.
+If this value is greater than one (the red line), then the model can be discarded as ineffective.}
     \label{fig:trash}

### 2024-08-26 main.tex

@@
     \centering
-    \includegraphics[width=\textwidth,clip]{plots/combined/acc.pdf}
+    \includegraphics[width=\textwidth]{plots/combined/acc.pdf}
     \caption{\cm{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot.
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
+        \includegraphics[width=\linewidth]{plots/combined/time.pdf}
         \caption{}
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
+        \includegraphics[width=\linewidth]{plots/combined/power.pdf}
         \caption{}
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
+        \includegraphics[width=\linewidth]{plots/combined/cost.pdf}
         \caption{}
@@
 Outliers are denoted with a white dot.} For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
+    \label{fig:costs}
 \end{figure*}
@@
         \centering
-        \includegraphics[width=.67\linewidth,clip]{plots/combined/weibull_qq.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.67\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
+        \includegraphics[width=.57\linewidth]{plots/combined/weibull_qq.pdf}
         \caption{ }
@@
         \centering
-        \includegraphics[width=.67\linewidth,clip]{plots/combined/log_normal_qq.pdf}
-        \caption{}
+        \includegraphics[width=.57\linewidth]{plots/combined/log_logistic_qq.pdf}
+        \caption{ }
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \includegraphics[width=.57\linewidth]{plots/combined/log_normal_qq.pdf}
+        \caption{ }
     \end{subfigure}
     \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
-The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $.}}
+The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $.
+A model that fits this cubic spline exactly would be a diagonal line at $y=x$.
+The process of comparing the fitted AFT model to a default cubic spline is called \textit{survival probability calibration} and is discussed in more detail in Section~\ref{best-fit}.}}
     \label{fig:qq}
@@
     \begin{subfigure}{\textwidth}
-        \includegraphics[width=.8\textwidth]{plots/combined/weibull_aft.pdf}
+        \centering
+        \includegraphics[width=.57\textwidth]{plots/combined/weibull_aft.pdf}
     \end{subfigure}
     \begin{subfigure}{\textwidth}
-        \includegraphics[width=.8\textwidth]{plots/combined/log_normal_aft.pdf}
+        \centering
+        \includegraphics[width=.57\textwidth]{plots/combined/log_normal_aft.pdf}
     \end{subfigure}
     \begin{subfigure}{\textwidth}
-        \includegraphics[width=.8\textwidth]{plots/combined/log_logistic_aft.pdf}
+        \centering
+        \includegraphics[width=.57\textwidth]{plots/combined/log_logistic_aft.pdf}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_trash_score.pdf}
+        \includegraphics[width=.7\linewidth]{plots/combined/weibull_trash_score.pdf}
         \caption{}
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_trash_score.pdf}
+        \includegraphics[width=.7\linewidth]{plots/combined/log_logistic_trash_score.pdf}
         \caption{ }
@@
         \centering
-        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_trash_score.pdf}
+        \includegraphics[width=.7\linewidth]{plots/combined/log_normal_trash_score.pdf}
         \caption{}
     \end{subfigure}
-    \caption{The training rate and survival heuristic that depicts the per-sample ratio of training time to attack time.
-If this value is greater than one (the red line), then the model can be discarded as ineffective.}
+    \caption{\cm{The \textit{training rate and survival heuristic} score (TRASH score) that depicts the per-sample ratio of training time to attack time. 
+    If this value is greater than one (the red line), then the model can be discarded as ineffective.
+The x-axis shows each dataset, the y-axis shows the \acrshort{trash} score and each GPU model is given its own color.
+Outlier scores are depicted with a white dot.}}
     \label{fig:trash}
@@
 
-In this work, we introduced survival analysis to machine learning, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing one to the model performance as a function of tested model parameters.
+In this work, \cm{we applied survival analysis to cloud-native machine learning}, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing one to the model performance as a function of tested model parameters.
 Using this technique, it is clear that reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.
+
+~\cm{
+The experiments conducted confirm that this methodology is both sound and cost-effective.
+While 88\% of the cloud budget went to GPU rentals, the data show how cutting that cost by 75\% and using less power-intensive hardware designed for 8-bit image processing would be \textit{more} effective than using the 32-bit datacenter GPUs (V100 and P100) for typical image classification tasks.
+Using \acrshort{kepler} proved to be a cost-effective as real-time monitoring only used a fraction of the budget (6\%).
+Figure~\ref{fig:acc} confirms the efficacy of the ~\acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing a infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
+Additionally, Table~\ref{tab:combined} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants. 
+By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}, it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
+This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft}. 
+}
+
+\cm{
+Regardless of which AFT model is chosen, the model suggests that the P100 decreases the survival time compared to the V100 and the L4 increases the survival time (both compared to the V100, which has no significant effect).
+Furthermore, the coefficients again confirm an inverse relationship between test-set (benign) accuracy and the adversarial robustness (\textit{i.e.} survival time). 
+Finally, even when we account for the reduced GPU bandwidth (see: Table~\ref{tab:hardware}) and increased training time (see: Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see: Figure~\ref{fig:trash}), despite it being advertised as ``inference only" by the manufacturer.
+}
 Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.
-\cm{TODO add}
 

### 2024-08-28 main.tex
remove footnotes, added links to source code and data

@@
 
-\author*[1,2]{\fnm{First} \sur{Author}}\email{iauthor@gmail.com}
+\author*[1]{\fnm{Charles} \sur{Meyers}}\email{cmeyers@cs.umu.se}
 
-\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
-\equalcont{These authors contributed equally to this work.}
+\author[1]{\fnm{Mohammad} \sur{Reza Saleh Sedghpour}}\email{msaleh@cs.umu.se}
 
-\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
-\equalcont{These authors contributed equally to this work.}
+\author[1]{\fnm{Erik} \sur{Elmroth}}\email{tommy@cs.umu.se}
 
-\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}
+\author[1,2]{\fnm{Erik} \sur{Elmroth}}\email{elmroth@cs.umu.se}
 
-\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}
+\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa University}, \orgaddress{\street{Universitetorget 4}, \city{Ume\aa}, \postcode{901 87}, \country{Sweden}}}
 
-\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}
+\affil[2]{\orgname{Elastisys AB},  \country{Sweden}}
 
@@
 % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-% \textit{Umeå University}\\
-% Umeå, Sweden \\
+% \textit{Ume\aa University}\\
+% Ume\aa, Sweden \\
 % cmeyers@cs.umu.se}
@@
 % \IEEEauthorblockA{\textit{Elastisys} \\
-% % \textit{Umeå University}\\
+% % \textit{Ume\aa University}\\
 % % Lund, Sweden \\
@@
 % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-% \textit{Umeå University}\\
-% Umeå, Sweden \\
+% \textit{Ume\aa University}\\
+% Ume\aa, Sweden \\
 % tommy@cs.umu.se}
@@
 % \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
-% \textit{Umeå University}\\
-% Umeå, Sweden \\
+% \textit{Ume\aa University}\\
+% Ume\aa, Sweden \\
 % elmroth@cs.umu.se}
@@
 
-\abtract{
+\abstract{
 Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model at run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
@@
 Therefore, a new evaluation methodology is required.
-We propose to use survival analysis as a methodological framework to model the failure conditions of a machine learning model.
+We propose to use survival analysis as a methodological framework to model the failure conditions of a machine learning (ML) model.
 Instead of having a test set large enough to cover all of the failure cases, we generate adversarial samples crafted specifically to make the model fail and then use survival analysis to predict these failures in general.
@@
 \subsection{Contributions}
-To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see  Figure~\ref{fig:experiments}) and software framework (see Figure~\ref{fig:architecture}) for the training (see Section~\ref{aft}) and evaluation (see Section~\ref{cost}) of machine learning models that:
+To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see  Figure~\ref{fig:experiments}) and software framework (see Figure~\ref{fig:architecture}) for the training (see Section~\ref{aft}) and evaluation (see Section~\ref{cost}) of ML models that:
 \begin{itemize}
@@
 The loss function, the measure of discrepancy between the true label and the predicted label, is denoted by $L(y, \hat{y})$.
-Because of the complexity of modern machine learning models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset (a mini-batch) of the training samples instead of all training samples.
+Because of the complexity of modern \acrshort{ml} models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset (a mini-batch) of the training samples instead of all training samples.
 % selects the next $N$ samples from the training set before adjusting the model parameters, $\theta$, in the direction that decreases the loss.
@@
 \begin{equation}
-    \hat{y} \neq \hat{y_a} = K(x + \varepsilon; \theta ) ,
+    \hat{y} \neq \hat{y}_a = K(x + \varepsilon; \theta ) ,
 \label{eq:adv_success}
@@
 The next section outlines the methodology for modelling the effect of model hyper-parameters during routine training procedures.
-We precisely outline the methodology for using survival analysis during the training of machine learning methods.
+We precisely outline the methodology for using survival analysis during the training of \acrshort{ml} methods.
 % First, we present the proposed procedure in Algorithm~\ref{fig:alg} and a visual diagram of it in Figure~\ref{fig:experiments}.
@@
 For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease.
-For machine learning, this means inducing failures during training to measure generalization performance.
+For \acrshort{ml}, this means inducing failures during training to measure generalization performance.
 
@@
 \end{equation}
-
 where $t^*$ is the latest time observed in the survival data.
@@
 \cm{
-where $\phi$ is some acceleration factor described by the joint effect of the covariates, such that
+where $\phi_\theta$ is the acceleration factor, described by the joint effect of the covariates, such that
 }
 $$
-    \phi_{\theta}(x) = \exp{ \left( \theta_0 x_0 + \theta_1 x_1 + \cdots + \theta_n x_i \right) },
+    \phi_{\theta}(x) = \exp{ \left( \theta_{0} x_{0} + \theta_{1} x_{1} + \cdots + \theta_{n} x_{n} \right) },
 $$
 \cm{
-and where $x_0 \cdots x_n$ are covariates and $\theta_0, \ldots, \theta_n$ describe the fitted parameters  $\varepsilon$ is used as one of the covariates.
-That is, when the adversarial noise increases, it will shorten the expected survival time of a sample proportionally.
+and where $x=(x_0, \ldots, x_n)$ is a vector of covariates and $\theta=(\theta_0, \ldots, \theta_n)$ describe the fitted parameters, and  $\varepsilon$ is used as one of the covariates.
+That is, when the adversarial noise level changes, it will alter the expected survival time of a sample proportionally.
 }
@@
 In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by IEC61508~\cite{IEC61508} which allows us to quantify the marginal risk.
-To quantify this marginal risk, one must measure the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack.
+To quantify this marginal risk, one must measure the benign and adversarial accuracies (see Equations~\ref{eq:adv_success}~and~\ref{eq:acc}), the model training time, $t_{t}$, the model inference time or latency, $t_{i}$, the attack generation time, $t_{a}$, the cost per hour for a particular hardware, $C$, as well as the power consumption, $P$, of each tested model and attack.
 
@@
 $$
-    T_t := t_t \cdot n  \cdot m,
+    T_t := t_t \cdot n.
 $$
-where $m$ is the number of epochs.
 
@@
 \begin{equation}
-    T_a := t_a \cdot n \cdot i.
+    T_a := t_a \cdot n.
     \label{eq:attack_time}
 \end{equation}
-In the interest of time, our chosen attack, FGM, uses only a single iteration $i =1$~\cite{fgm}. 
+
 \cm{
-In reality, the attack time will not be drawn from a uniform distribution and prior research~\cite{meyers_aft} has shown that by treating model and attack parameters as  this can be more accurately approximated with $t_{a}'$
+In reality, the attack time will not be drawn from a uniform distribution and prior research~\cite{meyers_aft} has shown that by treating model and attack parameters as covariates, one can model the survival time accurately by using and AFT model, such that:
 }
@@
 Furthermore, we approach the cost of deployment at two scales.
-Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model using \textit{e.g.}, the Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost.
+Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model using \textit{e.g.}, the Google Cloud Platform (GCP) compute costs as a measure of total cost.
 However, at a certain scale or with certain applications, it is  more appropriate to talk about cost in terms of power (\textit{e.g.}, to deploy a self-driving car with a useful operating range).
-Finally, we define best-case and worst-case success metrics that provide an efficient way to minimize the latency, cost of deployment, and
+Finally, we define metrics that provide an efficient way to minimize the latency, cost of deployment, and
 maximize the generalized performance of a model. We define the training cost as
@@
 $$
-    C_a = C_h \cdot T_a.
+    C_a = C_h \cdot T_a,
 $$
@@
 \begin{equation}
-	\textrm{TRASH~Score}=\frac{t_t}{\mathbb{E}_{\theta}[T \,|\, 0 < \varepsilon \leq \varepsilon^*]} = \frac{t_t}{t_a'}.
+	\textrm{TRASH}=\frac{t_t}{\mathbb{E}_{\theta}[T]} = \frac{t_t}{t_a'}.
 	\label{eq:cost}
@@
 The rental cost of the hardware, measured in United States Dollars per hour, indicates the operating cost of a given model.
-To calculate this, the price per hour from each cloud service pricing page\footnote{Google Cloud prices for P100 and V100 obtained \href{https://cloud.google.com/compute/gpus-pricing}{here.} Google Cloud prices for L4 obtained \href{https://cloud.google.com/compute/vm-instance-pricing\#accelerator-optimised}{here.}} were used and the cost of training ($C_{t}$) and the cost of inference ($C_{i}$) calculated from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
+To calculate this, the price per hour from each cloud service pricing page~\cite{pricing_1,pricing_2} were used and the cost of training ($C_{t}$) and the cost of inference ($C_{i}$) calculated from the cost of hardware ($C_{h}$), the training time ($T_{t}$), and the inference time ($T_{i}$).
 \begin{table*}[h]
@@
     \end{subfigure}
-    \caption{\cm{The \textit{training rate and survival heuristic} score (TRASH score) that depicts the per-sample ratio of training time to attack time. 
+    \caption{\cm{The \textit{training rate and survival heuristic} score (TRASH score) that depicts the per-sample ratio of training time to attack time for each of the tested AFT models. 
     If this value is greater than one (the red line), then the model can be discarded as ineffective.
@@
 By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
-As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
+As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
 If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
-\cm{TODO.
-Discuss the TRASH SCORE plots.}
+\cm{Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time.
+It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.}
 
@@
 However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:combined}).}
-Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in machine learning applications.
+Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in \acrshort{ml} applications.
 This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}.
@@
 If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy compared to the benign measurements.
-Furthermore, while FGM is fast, it is not guaranteed to find failures as quickly as possible, meaning that the survival time estimate is likely to be overestimated.
+Furthermore, while \acrshort{fgm} is fast, it is not guaranteed to find failures as quickly as possible, meaning that the survival time estimate is likely to be overestimated.
 In general, distributed/federated models were out of scope for this work, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
@@
 
-In this work, \cm{we applied survival analysis to cloud-native machine learning}, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing one to the model performance as a function of tested model parameters.
+In this work, \cm{we applied survival analysis to cloud-native \acrshort{ml}}, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing one to the model performance as a function of tested model parameters.
 Using this technique, it is clear that reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.
@@
 The experiments conducted confirm that this methodology is both sound and cost-effective.
-While 88\% of the cloud budget went to GPU rentals, the data show how cutting that cost by 75\% and using less power-intensive hardware designed for 8-bit image processing would be \textit{more} effective than using the 32-bit datacenter GPUs (V100 and P100) for typical image classification tasks.
+While 88\% of the cloud budget went to GPU rentals, the data show how cutting that cost by 75\% and using less power-intensive hardware designed for 8-bit image processing would be \textit{more} effective than using the 32-bit datacenter \acrshort{gpu}s (V100 and P100) for typical image classification tasks.
 Using \acrshort{kepler} proved to be a cost-effective as real-time monitoring only used a fraction of the budget (6\%).
@@
 By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}, it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
-This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft}. 
+This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.
 }
@@
 \clearpage
+\section{Availability of Data and Materials}
+The source code for conducting the experiments is available \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{in the \texttt{deckard} repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
+Requirements and dependencies are listed within the repository, which is distributed under the GNU Public License version 3.
+The compiled data and the Python source code for this document are available \href{https://github.com/simplymathematics/kepler-ml}{here}.
+The source code has been tested on Windows and various Linux distributions and should work on MacOS, but has not been tested there.
 \printglossary

### 2024-09-02 ccgrid.tex
linting

--- 2024-08-15 old (ccgrid).tex
@@
     \EndWhile
-    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
+    \State \textbf{Fit AFT Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
     \State \textbf{Return:} $S_{\theta}$
@@
 
-\subsection{AFR Models}
+\subsection{AFT Models}
 \label{survival_time}
@@
 
-\subsection{AFR Models}
+\subsection{AFT Models}
 
@@
 
-\subsection{AFR Models}
+\subsection{AFT Models}
 \label{res:afr}
@@
     \end{subfigure}
-    \caption{Weibull AFR Model.}
+    \caption{Weibull AFT Model.}
 \end{figure}

### 2024-09-02 arxiv.py

@@ -1,0 +1,177 @@
+import argparse
+from pathlib import Path
+import os
+import shutil
+import tempfile
+import logging
+
+logger = logging.getLogger(__name__)
+
+
+
+def create_tmp_directory(tmp_directory):
+    logger.info('Creating temporary directory: ' + tmp_directory)
+    os.makedirs(tmp_directory, exist_ok=True)
+
+
+def copy_files_to_tmp_directory(tmp_directory):
+    logger.info('Copying files to temporary directory: ' + tmp_directory)
+    for filename in Path('.').glob('*'):
+        if Path(filename).is_dir():
+            logger.debug(f"Copying {filename} to tmp directory.")
+            shutil.copytree(filename, str(Path(tmp_directory, filename).resolve()))
+        else:
+            logger.debug(f"Copying {filename} to tmp directory.")
+            shutil.copy(filename, str(Path(tmp_directory, filename).resolve()))
+
+
+def remove_unused_files(directory, logfile, enc, filetype=".eps"):
+    logger.info('Removing unused files in directory: ' + directory + ' with extension: ' + filetype)
+    for filename in Path(directory).glob(f'*{filetype}'):
+        filename = str(filename)
+        logfile = str(logfile)
+        if filename in open(logfile, encoding=enc).read():
+            pass
+        else:
+            if os.path.isfile(os.path.join(directory, filename)):
+                logger.info(filename + ' not in use - deleting.')
+                os.remove(os.path.join(directory, filename))
+            else:
+                pass
+
+
+def remove_git_directories():
+    logger.info('Removing git directories')
+    git_directories = ['.git', '.github', '.gitignore', '.gitattributes', ".dvc"]
+    for filename in git_directories:
+        if os.path.isfile(filename):
+            logger.info(f'{filename} not in use - deleting.')
+            os.remove(filename)
+        elif os.path.isdir(filename):
+            logger.info(f'{filename} is a directory.')
+            shutil.rmtree(filename)
+        else:
+            pass
+
+
+def delete_files_with_extension(extension):
+    logger.info('Deleting files with extension: ' + extension)
+    for filename in Path('.').glob(f'*.{extension}'):
+        logger.info(f'{filename} not in use - deleting.')
+        os.remove(filename)
+
+
+def delete_image_directories(directories):
+    logger.info('Deleting image directories')
+    for directory in directories:
+        if Path(directory).exists():
+            logger.info('Removing ' + directory + ' directory.')
[…]

### 2024-09-02 main.tex
linting

--- 2024-08-26 main.tex
@@
 %% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition \textit{etc.}
 
@@
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
-These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch, pixelattack,hopskipjump}.
+These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013,saha2020hidden}, inference~\cite{chakraborty_adversarial_2018,orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump}.
 One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}.
@@
 
-AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time.
+AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival,aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time).
 For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely.
@@
 
-The AFT models were evaluated using the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
+The AFT models were evaluated using the MNIST~\cite{mnist}, CIFAR10~\cite{cifar}, and CIFAR100~\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
 Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets.
@@
 Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
-To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1]$.
+To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1\]$.
 This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
@@
 These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}}
-\label{tab:combined}
+\label{tab:aft_results}
 \begin{tabular}{lrrrrrrrr}
@@
 
-Table~\ref{tab:combined} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
+Table~\ref{tab:aft_results} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
 A total 75\% of the available data were used to build the AFT models and 25\% were withheld for evaluation.
@@
 For test-set accuracy,  meeting the weakest safety-critical IEC standard (1 failure in a million) would require many millions of samples to confidently conclude that a model is safe.
-However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:combined}).}
+However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:aft_results}).}
 Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in machine learning applications.
@@
 Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
-However, given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+However, given the strong results and uniformity across AFT functions in Table~\ref{tab:aft_results}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
-Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (e.g.
-MNIST, CIFAR10, CIFAR100).
+Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (\textit{e.g.} MNIST, CIFAR10, CIFAR100).
 Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.

### 2024-09-02 main.tex
linting

@@
     \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
-    \item \cm{Demonstrates that, even when we control for the slower clock speed of "inference only hardware" compared to hardware marketed for training, that models trained using the "inference only" devices are more robust for image classification tasks than models built on hardware designed for training.}
+    \item \cm{Demonstrates that, even when we control for the slower clock speed of ``inference only hardware'' compared to hardware marketed for training, that models trained using the ``inference only'' devices are more robust for image classification tasks than models built on hardware designed for training.}
 \end{itemize}
@@
 However, managing complex pipelines across diverse \acrfull{cpu} and \acrfull{gpu}  architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
-One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native" software stack.
+One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native'' software stack.
 In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
@@
 Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures using a service mesh.
-For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}.
+For ML applications, these services are often divided into ``training'' and ``inference'' configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}.
 In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see Figure~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see Figure~\ref{fig:architecture}) across a variety of different hardware architectures (see Table~\ref{tab:hardware}).
@@
 GPUs with larger amounts of VRAM are able to hold more data in memory at a time, increasing the effective mini-batch size, and reducing the number of model-tuning steps per epoch.
-A ``good" learning rate will allow a model to converge quickly~\cite{smith2019super,granziol2022learning} and the ideal mini-batch size will be determined by the memory bandwidth of the GPU and the size of the model and the size and dimensionality of the data.
+A ``good'' learning rate will allow a model to converge quickly~\cite{smith2019super,granziol2022learning} and the ideal mini-batch size will be determined by the memory bandwidth of the GPU and the size of the model and the size and dimensionality of the data.
 However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}.
@@
 Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}).
-We then discuss the importance of the ``acceleration assumption" (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).
+We then discuss the importance of the ``acceleration assumption'' (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).
 
@@
 The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
-$$
+\[
     S_{\theta}(t) = p(T>t  \mid \theta) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
-$$
+\]
 where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
@@
 }
-$$
+\[
     \phi_{\theta}(x) = \exp{ \left( \theta_0 x_0 + \theta_1 x_1 + \cdots + \theta_n x_i \right) },
-$$
+\]
 \cm{
@@
 The training time, $T_t$, is the time it takes to evaluate $n$ samples when $t_t$ is the training time per sample. It is defined as
-$$
+\[
     T_t := t_t \cdot n  \cdot m,
-$$
+\]
 where $m$ is the number of epochs.
@@
 Latency is the time it takes to respond to a query. We assume that latency per sample is
-$$
+\[
     T_i := t_i \cdot n,
-$$
+\]
 which will be driven by the memory bandwidth (measured in bits/second) of a given \acrshort{cpu} or \acrshort{gpu} and the size~\cite{vgg} and complexity~\cite{resnet} of a given neural network architecture.
@@
 maximize the generalized performance of a model. We define the training cost as
-$$
+\[
     C_t = C_h \cdot T_t,
-$$
+\]
 the cost of model inference time as,
-$$
+\[
     C_i = C_h \cdot T_i,
-$$
+\]
 and the cost of an attack as,
-$$
+\[
     C_a = C_h \cdot T_a.
-$$
+\]
 where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.
@@
 The power consumption for a particular piece of hardware, $P_h$, measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
-$$
+\[
     P_t = P_h \cdot T_t,
     \label{eq:power_training}
-$$
+\]
 the power consumption during model inference is
-$$
+\[
     P_i = P_h \cdot T_i,
     \label{eq:power_inference}
-$$
+\]
 and the power consumption during attack generation is
-$$
+\[
     P_a = P_h \cdot T_a,
     \label{eq:power_attack}
-$$
+\]
 where $P_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.
@@
 Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0.
-These nodes were of the ``e2-medium" instance type provided by GCP.
+These nodes were of the ``e2-medium'' instance type provided by GCP.
 In total, three GPU architectures were used--the Nvidia P100, V100, and L4.
@@
     \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models.
-Here, "Random State" is used as a control variable that should be (and is) close to 0.
+Here, ``Random State'' is used as a control variable that should be (and is) close to 0.
 \cm{A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
@@
 As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
-If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
+If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken'' in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
 \cm{TODO.

### 2024-09-02 main.tex

--- 2024-08-28 main.tex
@@
 }
-$$
-    \phi_{\theta}(x) = \exp{ \left( \theta_{0} x_{0} + \theta_{1} x_{1} + \cdots + \theta_{n} x_{n} \right) },
-$$
+\[
+    \phi_{\theta}(x) = \exp{ \left( \theta_0 x_0 + \theta_1 x_1 + \cdots + \theta_n x_i \right) },
+\]
 \cm{
@@
 The training time, $T_t$, is the time it takes to evaluate $n$ samples when $t_t$ is the training time per sample. It is defined as
-$$
-    T_t := t_t \cdot n.
-$$
+\[
+    T_t := t_t \cdot n  \cdot m,
+\]
+where $m$ is the number of epochs.
 
@@
 maximize the generalized performance of a model. We define the training cost as
-$$
+\[
     C_t = C_h \cdot T_t,
-$$
+\]
 the cost of model inference time as,
-$$
+\[
     C_i = C_h \cdot T_i,
-$$
+\]
 and the cost of an attack as,
-$$
-    C_a = C_h \cdot T_a,
-$$
+\[
+    C_a = C_h \cdot T_a.
+\]
 where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.

### 2024-09-02 main.tex
linting

@@
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
-Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (e.g.
-MNIST, CIFAR10, CIFAR100).
+Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (\textit{e.g.} MNIST, CIFAR10, CIFAR100).
 Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.

### 2024-09-02 main.tex
linting

@@
 In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
-In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
+In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken'').
 Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}.
@@
 As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
-If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
+If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken'' in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
 \cm{Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time.
@@
 Furthermore, the coefficients again confirm an inverse relationship between test-set (benign) accuracy and the adversarial robustness (\textit{i.e.} survival time).
-Finally, even when we account for the reduced GPU bandwidth (see: Table~\ref{tab:hardware}) and increased training time (see: Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see: Figure~\ref{fig:trash}), despite it being advertised as ``inference only" by the manufacturer.
+Finally, even when we account for the reduced GPU bandwidth (see: Table~\ref{tab:hardware}) and increased training time (see: Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see: Figure~\ref{fig:trash}), despite it being advertised as ``inference only'' by the manufacturer.
 }

### 2024-09-02 main.tex
linting

@@
 Section~\ref{aft} outlines the training and evaluation methodology presented in this paper.
-Section ~\ref{cost} discusses the resulting cost analysis framework, arising from the methodology in the previous section.
+Section~\ref{cost} discusses the resulting cost analysis framework, arising from the methodology in the previous section.
 Section~\ref{experiments} outlines the software components and specific experiments that were conducted, while Section~\ref{results} contains the results and discussions of those experiments.
@@
 The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
-\cm{Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.} To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
+\cm{Since different hardware devices have differing amounts of~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.}
+To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
 Likewise, Nvidia offers hardware that is marketed as either for training (\textit{e.g.}, v100 and p100) or only for inference (\textit{e.g.}, l4).
@@
 However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}.
-Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.
-~\cm{To optimize for training time as well as robustness (both $\lambda_{ben}$ and $\lambda_{adv}$), the \acrshort{tpe} optimization was used (see:~Section~\ref{optimisation}).
+Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.~\cm{To optimize for training time as well as robustness (both $\lambda_{ben}$ and $\lambda_{adv}$), the \acrshort{tpe} optimization was used (see:~Section~\ref{optimisation}).
 However, it is first necessary to define robustness.}
@@
 Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
-To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1\]$.
+To evaluate the effect of adversarial noise on the samples, the noise levels were varied $0 < \varepsilon  \leq 0$.
 This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
@@
 For test-set accuracy,  meeting the weakest safety-critical IEC standard (1 failure in a million) would require many millions of samples to confidently conclude that a model is safe.
-However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:combined}).}
+However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:aft_results}).}
 Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in \acrshort{ml} applications.
@@
 Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
-However, given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+However, given the strong results and uniformity across AFT functions in Table~\ref{tab:aft_results}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
@@
 
-~\cm{
-The experiments conducted confirm that this methodology is both sound and cost-effective.
+\cm{The experiments conducted confirm that this methodology is both sound and cost-effective.
 While 88\% of the cloud budget went to GPU rentals, the data show how cutting that cost by 75\% and using less power-intensive hardware designed for 8-bit image processing would be \textit{more} effective than using the 32-bit datacenter \acrshort{gpu}s (V100 and P100) for typical image classification tasks.
 Using \acrshort{kepler} proved to be a cost-effective as real-time monitoring only used a fraction of the budget (6\%).
-Figure~\ref{fig:acc} confirms the efficacy of the ~\acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing a infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
-Additionally, Table~\ref{tab:combined} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants.
+Figure~\ref{fig:acc} confirms the efficacy of the~\acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing a infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
+Additionally, Table~\ref{tab:aft_results} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants.
 By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}, it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
-This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.
-}
+This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.}
 

### 2024-09-02 main.tex
linting

@@
 A small learning rate will more accurately approximate the class boundaries~\cite{cao2019generalization}, but will converge slower, all other things being equal.
-Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the mini-batch size, number of epochs, dimensionality of the input data, \textit{etc.}~\cite{granziol2022learning}.
+Of course ``small'' is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the mini-batch size, number of epochs, dimensionality of the input data, \textit{etc.}~\cite{granziol2022learning}.
 GPUs with larger amounts of VRAM are able to hold more data in memory at a time, increasing the effective mini-batch size, and reducing the number of model-tuning steps per epoch.
@@
 The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.
-The other node pools each had one node with a specific GPU.
+    The other node pools each had one node with a specific GPU\@.  
     The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.  

### 2024-09-02 main.tex
linting

@@
 \subsection{Cloud Platform and Hardware}
-To conduct the experiments and have access to different types of hardware, we utilized \acrshort{gcp}.
+To conduct the experiments and have access to different types of hardware, we utilized \acrshort{gcp}\@.
 Six virtual machines running container optimised operating system provided by GCP constituted the test-bed.
@@
 Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0.
-These nodes were of the ``e2-medium'' instance type provided by GCP.
-In total, three GPU architectures were used--the Nvidia P100, V100, and L4.
+These nodes were of the ``e2-medium'' instance type provided by GCP\@.
+In total, three GPU architectures were used--the Nvidia P100, V100, and L4\@.
 For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.
@@
     \cm{A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
-The symbols $T_i$ and $T_t$ refer training and inference time for all samples, while \textit{Ben.
-Accuracy} refers to the benign accuracy (accuracy on the un-altered samples), and $\varepsilon$ is the noise distance.}}
+    The symbols $T_i$ and $T_t$ refer training and inference time for all samples, while \textit{Ben.~Accuracy} refers to the benign accuracy (accuracy on the un-altered samples), and $\varepsilon$ is the noise distance.}}
     \label{fig:aft}
@@
 Additionally, Table~\ref{tab:aft_results} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants.
-By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}, it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
+By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}), it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
 This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.}

### 2024-09-02 generate_plots/combined_plots.py
update plot generator

@@ -1,0 +1,294 @@
+import pandas as pd
+from pathlib import Path
+import seaborn as sns
+import matplotlib.pyplot as plt
+from matplotlib import ticker
+from deckard.layers.plots import set_matplotlib_vars
+
+set_matplotlib_vars()
+
+
+sns.set_theme(style="whitegrid", font_scale=2, font="times new roman")
+
+normal_dir = "data"
+datasets = ["mnist", "cifar", "cifar100"]
+extra_data_dir = "bit_depth"
+
+#
+big_df = pd.DataFrame()
+for data in datasets:
+    df = pd.read_csv(
+        Path(normal_dir) / data / "power.csv",
+        index_col=0,
+        low_memory=False,
+    )
+    df["dataset"] = data
+    big_df = pd.concat([big_df, df], axis=0)
+    if Path(normal_dir, extra_data_dir, data, "power.csv").exists():
+        extra_df = pd.read_csv(
+            Path(normal_dir, extra_data_dir, data, "power.csv"),
+            index_col=0,
+            low_memory=False,
+        )
+        extra_df["dataset"] = data
+        big_df = pd.concat([big_df, extra_df], axis=0)
+
+
+# Device Metadata
+memory_bandwith = {
+    "nvidia-tesla-p100": 732,
+    "nvidia-tesla-v100": 900,
+    "nvidia-l4": 250,
+}
+dataset_resolution = {
+    "mnist": 28,
+    "cifar": 32,
+    "cifar100": 32,
+}
+dataset_channels = {
+    "mnist": 1,
+    "cifar": 3,
+    "cifar100": 3,
+}
+dataset_classes = {
+    "mnist": 10,
+    "cifar": 10,
+    "cifar100": 100,
+}
+cost = {
+    "nvidia-tesla-p100": 1.60,
+    "nvidia-tesla-v100": 2.55,
+    "nvidia-l4": 0.81,
+}
+epochs = "model.trainer.nb_epoch"
+batch_size = "model.trainer.batch_size"
+bit_depth = "model.art.preprocessor.bit_depth"
+resolution = "n_pixels"
+
+# Add Metadata
+for device in big_df.device_id.unique():
+    big_df.loc[big_df.device_id == device, "peak_memory_bandwidth"] = float(
+        memory_bandwith[device],
+    )
+    big_df.loc[big_df.device_id == device, "cost"] = float(cost[device])
+big_df["train_cost"] = big_df["train_time"] * big_df["cost"]
[…]

### 2024-09-11 cover_letter.tex
Updates from Overleaf

\documentclass{letter}

\signature{Charles Meyers, \\ Mohammed Reza, \\ Tommy L\"{o}fstedt, \\ and  Erik Elmroth \\ }
\address{Department of \\ Computing Science,\\ Ume\aa University,\\ Sweden}

\begin{document}
\begin{letter}{}
\opening{To whom it may concern}

I am writing you on behalf of the authors of \em{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}, which is the attached manuscript.  In this work, we developed a cloud-native methodology for quickly and precisely modelling the effect of model covariates using accelerated failure time models and a multi-objective search to minimize training cost while maximizing model accuracy. Not only do we provide a detailed outline and related source code, but we show the surprising result that smaller, more power-efficient GPUs create models that are more robust and more cost effective than models built on hardware that is advertised as being more capable. 
\closing{Sincerely,}
\end{letter}
\end{document}

### 2024-09-11 main.tex
Updates from Overleaf

--- 2024-09-02 main.tex
@@
 %% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition \textit{etc.}
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
 
@@
 
-\author[1]{\fnm{Erik} \sur{Elmroth}}\email{tommy@cs.umu.se}
+\author[1]{\fnm{Tommy} \sur{L\"{o}fstedt}}\email{tommy@cs.umu.se}
 
@@
 
-\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa University}, \orgaddress{\street{Universitetorget 4}, \city{Ume\aa}, \postcode{901 87}, \country{Sweden}}}
+\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa ~University},
+\city{Ume\aa}, \postcode{901 87}, \country{Sweden}}
 
@@
     \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
-    \item \cm{Demonstrates that, even when we control for the slower clock speed of ``inference only hardware'' compared to hardware marketed for training, that models trained using the ``inference only'' devices are more robust for image classification tasks than models built on hardware designed for training.}
+    \item Demonstrates that, even when we separately measure the effect of the slower clock speed of "inference only hardware" compared to hardware tailored for training, that models trained using the "inference only" devices are more robust for image classification tasks than models built on hardware designed for training.
 \end{itemize}
@@
 Section~\ref{aft} outlines the training and evaluation methodology presented in this paper.
-Section~\ref{cost} discusses the resulting cost analysis framework, arising from the methodology in the previous section.
+Section ~\ref{cost} discusses the resulting cost analysis framework, arising from the methodology in the previous section.
 Section~\ref{experiments} outlines the software components and specific experiments that were conducted, while Section~\ref{results} contains the results and discussions of those experiments.
@@
 However, managing complex pipelines across diverse \acrfull{cpu} and \acrfull{gpu}  architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
-One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native'' software stack.
+One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native" software stack.
 In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline.
@@
 Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures using a service mesh.
-For ML applications, these services are often divided into ``training'' and ``inference'' configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}.
+For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}.
 In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see Figure~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see Figure~\ref{fig:architecture}) across a variety of different hardware architectures (see Table~\ref{tab:hardware}).
@@
 The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
-\cm{Since different hardware devices have differing amounts of~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.}
+Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.
 To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.
@@
 GPUs with larger amounts of VRAM are able to hold more data in memory at a time, increasing the effective mini-batch size, and reducing the number of model-tuning steps per epoch.
-A ``good'' learning rate will allow a model to converge quickly~\cite{smith2019super,granziol2022learning} and the ideal mini-batch size will be determined by the memory bandwidth of the GPU and the size of the model and the size and dimensionality of the data.
+A ``good" learning rate will allow a model to converge quickly~\cite{smith2019super,granziol2022learning} and the ideal mini-batch size will be determined by the memory bandwidth of the GPU and the size of the model and the size and dimensionality of the data.
 However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}.
-Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.~\cm{To optimize for training time as well as robustness (both $\lambda_{ben}$ and $\lambda_{adv}$), the \acrshort{tpe} optimization was used (see:~Section~\ref{optimisation}).
-However, it is first necessary to define robustness.}
+Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.
+To optimize for training time as well as robustness (both $\lambda_{ben}$ and $\lambda_{adv}$), the \acrshort{tpe} optimization was used (see:~Section~\ref{optimisation}).
+However, before progressing any further, it is first necessary to define robustness.
 
@@
 The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
-These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013,saha2020hidden}, inference~\cite{chakraborty_adversarial_2018,orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump}.
+These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch, pixelattack,hopskipjump}.
 One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}.
@@
 Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}).
-We then discuss the importance of the ``acceleration assumption'' (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).
+We then discuss the importance of the ``acceleration assumption" (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).
 
-% \begin{algorithm}[h!]
+% \begin{algorithm}[tph!]
 %     \caption{Survival Analysis for ML}
@@
 Therefore, a proper search would keep this dual-objective in mind.
-\cm{
 In addition, we attempt to minimize the training time for each piece of hardware since optimal batch size and, therefore, learning rate will be determined by the \acrshort{vram}, the size bit depth of the data as well as the size and bit depth of the model.
@@
 Further discussion of the cost analysis can be found in Section~\ref{cost}.
-}
 
@@
 
-AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival,aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time).
+AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time.
 For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely.
@@
 The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
-\[
+$$
     S_{\theta}(t) = p(T>t  \mid \theta) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
-\]
+$$
 where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
@@
 \label{accelerated}
-\cm{
 By using adversarial samples (see Equation~\ref{eq:adv_success}), failures can be induced.
@@
 In the language of accelerated failure time models, this can be expressed in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
-}
 \begin{equation} \label{assumption}
@@
 \end{equation}
-\cm{
 where $\phi_\theta$ is the acceleration factor, described by the joint effect of the covariates, such that
-}
-\[
-    \phi_{\theta}(x) = \exp{ \left( \theta_0 x_0 + \theta_1 x_1 + \cdots + \theta_n x_i \right) },
-\]
-\cm{
+$$
+    \phi_{\theta}(x) = \exp{ \left( \theta_{0} x_{0} + \theta_{1} x_{1} + \cdots + \theta_{n} x_{n} \right) },
+$$
 and where $x=(x_0, \ldots, x_n)$ is a vector of covariates and $\theta=(\theta_0, \ldots, \theta_n)$ describe the fitted parameters, and  $\varepsilon$ is used as one of the covariates.
-That is, when the adversarial noise level changes, it will alter the expected survival time of a sample proportionally.
-}
+That is, when the adversarial noise level changes, it will also alter the expected survival time of a sample.
 This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.
-\cm{
-However, in order to find the the correct distribution, one must measure the goodness-of-fit and conduct a survival probability calibration.
-}
+However, in order to find the best AFT model, one must compare the tested models using the techniques outlined below.
 
@@
 By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by IEC61508~\cite{IEC61508}.
-\cm{
 While the aforementioned metrics measure goodness-of-fit, one should conduct a \textit{survival probability calibration}, where one fits the AFT model to the data and compares it to a cubic-spline that is meant to capture the un-modelled relationship between failures and time~\cite{ici}.
-These plots can be used to visually inspect the goodness-of-fit of various models, as in Figure~\ref{fig:qq}.
-}
+These plots can be used to visually inspect the goodness-of-fit of various models, as in Figure~\ref{fig:qq}, and this method is called \textit{survival probability calibration} (used in Figure~\ref{fig:experiments}).
 The integrated calibration index (\acrshort{ici}) as well as the error at the 50th percentile \acrshort{e50}~\cite{ici} can then be calculated. 
 These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}. 
-\cm{Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.}
+Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.
 
@@
 The training time, $T_t$, is the time it takes to evaluate $n$ samples when $t_t$ is the training time per sample. It is defined as
-\[
-    T_t := t_t \cdot n  \cdot m,
-\]
-where $m$ is the number of epochs.
+$$
+    T_t := t_t \cdot n.
+$$
 
@@
 Latency is the time it takes to respond to a query. We assume that latency per sample is
-\[
+$$
     T_i := t_i \cdot n,
-\]
+$$
 which will be driven by the memory bandwidth (measured in bits/second) of a given \acrshort{cpu} or \acrshort{gpu} and the size~\cite{vgg} and complexity~\cite{resnet} of a given neural network architecture.
@@
 
-\cm{
 In reality, the attack time will not be drawn from a uniform distribution and prior research~\cite{meyers_aft} has shown that by treating model and attack parameters as covariates, one can model the survival time accurately by using and AFT model, such that:
-}
 \begin{equation}
@@
 maximize the generalized performance of a model. We define the training cost as
-\[
+$$
     C_t = C_h \cdot T_t,
-\]
+$$
 the cost of model inference time as,
-\[
+$$
     C_i = C_h \cdot T_i,
-\]
+$$
 and the cost of an attack as,
-\[
-    C_a = C_h \cdot T_a.
-\]
+$$
+    C_a = C_h \cdot T_a,
+$$
 where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.
@@
 \subsection{TRASH Score}
-\cm{
 With an estimate of the expected survival time in hand,  quantify the cost-normalized failure rate, or the ratio of training time to attack time.
-Assuming that the cost scales linearly -- as discussed above-- the model builder's cost is proportional to the training time ($C_t \propto t_{t}$), and the attacker's cost is proportional to the attack time, which is approximately the expected survival time ($C_{a} \propto t_{a}' \approx \mathbb{E}_{S\theta}[T]$).
+Assuming that the cost scales linearly -- as discussed above -- the model builder's cost is proportional to the training time ($C_t \propto t_{t}$), and the attacker's cost is proportional to the attack time, which is approximately the expected survival time ($C_{a} \propto t_{a}' \approx \mathbb{E}_{S\theta}[T]$).
 Using the definition of $\varepsilon$ from Equation~\ref{eq:adv_success} and definition of $t_a'$ from Equation~\ref{eq:aft_time}, we can express the cost of failure in adversarial terms as follows:
-}
 \begin{equation}
@@
 The power consumption for a particular piece of hardware, $P_h$, measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
-\[
+$$
     P_t = P_h \cdot T_t,
     \label{eq:power_training}
-\]
+$$
 the power consumption during model inference is
-\[
+$$
     P_i = P_h \cdot T_i,
     \label{eq:power_inference}
-\]
+$$
 and the power consumption during attack generation is
-\[
+$$
     P_a = P_h \cdot T_a,
     \label{eq:power_attack}
-\]
+$$
 where $P_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.
@@
     \includegraphics[width=.9\textwidth]{plots/architecture.pdf}
-    \caption{\cm{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility.
+    \caption{
+    For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility. 
     The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana. 
-The other node pools each had one node with a specific GPU.
-The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.
+    The other node pools each had one node with a specific GPU.  The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage. 
     All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC). 
     A PVC is a request for storage by user in Kubernetes which is then connected to the object storage. 
-The blue experiment, blue-green object storage, green analysis component, and purple AFT component correspond to the same colors in Figure~\ref{fig:experiments}.}}
+    The blue experiment, blue-green object storage, green analysis component, and purple AFT component correspond to the same colors in Figure~\ref{fig:experiments}.}
     \label{fig:architecture}
@@
 Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0.
-These nodes were of the ``e2-medium'' instance type provided by GCP.
+These nodes were of the ``e2-medium" instance type provided by GCP.
 In total, three GPU architectures were used--the Nvidia P100, V100, and L4.
@@
 Approximately 10\% of this was used for development and 90\% was used for the evaluations.
-\cm{Over the course of the evaluations, 6\% of the budget went to the storage, 6\% to the monitoring, and the remaining 88\% went the GPUs.}
+Over the course of the evaluations, 6\% of the budget went to the storage, 6\% to the monitoring, and the remaining 88\% went the GPUs.
 
@@
 
-The AFT models were evaluated using the MNIST~\cite{mnist}, CIFAR10~\cite{cifar}, and CIFAR100~\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
+The AFT models were evaluated using the MNIST~\cite{mnist}, CIFAR10\cite{cifar}, and CIFAR100\cite{cifar} datasets, chosen primarily for their standardized use in adversarial analysis~\cite{madry2017towards,croce_reliable_2020,carlini_towards_2017,deepfool} and decades of experimental results.
 Before training, we centered and scaled the data so that the attack distance would be analogous for all tested datasets.
@@
 Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
-To evaluate the effect of adversarial noise on the samples, the noise levels were varied $0 < \varepsilon  \leq 0$.
+To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1]$.
 This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.
@@
 %  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
-\begin{figure}[h!]
+\begin{figure}[tph!]
     \centering
     \includegraphics[width=\textwidth]{plots/combined/acc.pdf}
-    \caption{\cm{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot.
+    \caption{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot.
 Each color is a different device and the datasets are displayed along the x-axis.
-Outliers are denoted with a white dot.}}
+Outliers are denoted with a white dot.}
     \label{fig:acc}
@@
     \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\linewidth]{plots/combined/time.pdf}
-        \caption{}
+    \includegraphics[width=\textwidth]{plots/combined/time.pdf}
+    \caption{This depicts the training, inference, and attack times for all hardware and datasets for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
+The time per sample was assumed to be uniform across the batch of samples for each training, inference, or attack measurement.
+    Each color is a different device and the datasets are displayed along the first axis.
+Outliers are denoted with a white dot.
+For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
     \label{fig:time}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\linewidth]{plots/combined/power.pdf}
-        \caption{}
+\end{figure*}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{plots/combined/power.pdf}
+    \caption{This depicts the training, inference, and attack times for all hardware and datasets for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
+The power per sample was assumed to be uniform across the batch of samples for each training, inference, or attack measurement.
+    Each color is a different device and the datasets are displayed along the first axis.
+Outliers are denoted with a white dot.
+For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
     \label{fig:power}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\linewidth]{plots/combined/cost.pdf}
-        \caption{}
+\end{figure*}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{plots/combined/cost.pdf}
+    \caption{This depicts the training, inference, and attack times for all hardware and datasets for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
+The cost per sample was assumed to be uniform across the batch of samples for each training, inference, or attack measurement.
+    Each color is a different device and the datasets are displayed along the first axis.
+Outliers are denoted with a white dot.
+For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
     \label{fig:cost}
-    \end{subfigure}
-    \caption{This depicts the training, inference, and attack times (a), power (b), and cost (c), for all hardware and datasets \cm{for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot.
-Each color is a different device and the datasets are displayed along the first axis.
-Outliers are denoted with a white dot.} For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
-    \label{fig:costs}
 \end{figure*}
@@
 \caption{Comparison of AFT Models across all hardware and datasets.
-\cm{\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred.
+\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred.
 Concordance (Conc) is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model.
 \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model.
-These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}}
-\label{tab:aft_results}
+These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}
+\label{tab:combined}
 \begin{tabular}{lrrrrrrrr}
@@
 \end{table}
-\begin{figure*}[h!]
+\begin{figure*}[tph!]
     \centering
-    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.57\linewidth]{plots/combined/weibull_qq.pdf}
-        \caption{ }
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.57\linewidth]{plots/combined/log_logistic_qq.pdf}
-        \caption{ }
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.57\linewidth]{plots/combined/log_normal_qq.pdf}
-        \caption{ }
-    \end{subfigure}
-    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
+        \includegraphics[width=.49\linewidth]{plots/combined/weibull_qq.pdf}
+        \includegraphics[width=.49\linewidth]{plots/combined/log_logistic_qq.pdf}
+        \includegraphics[width=.49\linewidth]{plots/combined/log_normal_qq.pdf}
+    \caption{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red).
 The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $.
 A model that fits this cubic spline exactly would be a diagonal line at $y=x$.
-The process of comparing the fitted AFT model to a default cubic spline is called \textit{survival probability calibration} and is discussed in more detail in Section~\ref{best-fit}.}}
+The process of comparing the fitted AFT model to a default cubic spline is called \textit{survival probability calibration} and is discussed in more detail in Section~\ref{best-fit}.}
     \label{fig:qq}
@@
 
-\begin{figure*}[h!]
+\begin{figure*}[tph!]
     \centering
-    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}{\textwidth}
-        \centering
-        \includegraphics[width=.57\textwidth]{plots/combined/weibull_aft.pdf}
-    \end{subfigure}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \includegraphics[width=.57\textwidth]{plots/combined/log_normal_aft.pdf}
-    \end{subfigure}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \includegraphics[width=.57\textwidth]{plots/combined/log_logistic_aft.pdf}
-    \end{subfigure}
+        \includegraphics[width=.49\textwidth]{plots/combined/weibull_aft.pdf}
+        \includegraphics[width=.49\textwidth]{plots/combined/log_normal_aft.pdf}
+        \includegraphics[width=.49\textwidth]{plots/combined/log_logistic_aft.pdf}
     \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models.
-Here, ``Random State'' is used as a control variable that should be (and is) close to 0.
-\cm{A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
+Here, "Random State" is used as a control variable that should be (and is) close to 0.
+A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
 The symbols $T_i$ and $T_t$ refer training and inference time for all samples, while \textit{Ben.
-Accuracy} refers to the benign accuracy (accuracy on the un-altered samples), and $\varepsilon$ is the noise distance.}}
+Accuracy} refers to the benign accuracy (accuracy on the un-altered samples), and $\varepsilon$ is the noise distance.}
     \label{fig:aft}
@@
 
-Table~\ref{tab:aft_results} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
+Table~\ref{tab:combined} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
 A total 75\% of the available data were used to build the AFT models and 25\% were withheld for evaluation.
@@
 
-Figure~\ref{fig:aft} shows the log-scale coefficients for the AFT model.
-It shows that epochs, batch size, and training time have no effect on the survival time.
+Figure~\ref{fig:aft} shows the log-scale coefficients for the AFT model. It shows that epochs, batch size, and training time have no effect on the survival time. 
 Additionally, the covariate value of 0 for random state indicates that random permutations of the training and test data have no effect on the survival time, which is expected. 
@@
 
-\begin{figure*}[h!]
+\begin{figure*}[tph!]
     \centering
-    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.7\linewidth]{plots/combined/weibull_trash_score.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.7\linewidth]{plots/combined/log_logistic_trash_score.pdf}
-        \caption{ }
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-        \centering
-        \includegraphics[width=.7\linewidth]{plots/combined/log_normal_trash_score.pdf}
-        \caption{}
-    \end{subfigure}
-    \caption{\cm{The \textit{training rate and survival heuristic} score (TRASH score) that depicts the per-sample ratio of training time to attack time for each of the tested AFT models.
+        \includegraphics[width=.49\linewidth]{plots/combined/weibull_trash_score.pdf}
+        \includegraphics[width=.49\linewidth]{plots/combined/log_logistic_trash_score.pdf}
+        \includegraphics[width=.49\linewidth]{plots/combined/log_normal_trash_score.pdf}
+    \caption{The \textit{training rate and survival heuristic} score (TRASH score) that depicts the per-sample ratio of training time to attack time for each of the tested AFT models. 
     If this value is greater than one (the red line), then the model can be discarded as ineffective.
 The x-axis shows each dataset, the y-axis shows the \acrshort{trash} score and each GPU model is given its own color.
-Outlier scores are depicted with a white dot.}}
+Outlier scores are depicted with a white dot.}
     \label{fig:trash}
@@
 In security analysis, it is  routine to think in optimistic terms for both the attacker and defender.
-In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken'').
+In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
 Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}. 
@@
 As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. 
-If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken'' in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
-\cm{Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time.
-It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.}
+If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
+Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time. 
+It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.
 
@@
 \label{advantages}
-\cm{The primary advantage of this methodology over the traditional test/train split measurements is that the precision of the latter is determined by the number of samples; whereas, the precision of the survival time estimate is driven by the resolution of our timing measurements.
-For test-set accuracy,  meeting the weakest safety-critical IEC standard (1 failure in a million) would require many millions of samples to confidently conclude that a model is safe.
-However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:aft_results}).}
+The primary advantage of this methodology over the traditional test/train split measurements is that the precision of the latter is determined by the number of samples; whereas, the precision of the survival time estimate is driven by the resolution of our timing measurements.
+For test-set accuracy,  meeting the weakest safety-critical IEC standard (one failure in a million) would require many millions of samples to confidently conclude that a model is safe.
+However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:combined}).
 Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in \acrshort{ml} applications.
@@
 Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
-However, given the strong results and uniformity across AFT functions in Table~\ref{tab:aft_results}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+However, given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
-Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (\textit{e.g.} MNIST, CIFAR10, CIFAR100).
+Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (e.g.
+MNIST, CIFAR10, CIFAR100).
 Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.
@@
 
-In this work, \cm{we applied survival analysis to cloud-native \acrshort{ml}}, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing one to the model performance as a function of tested model parameters.
+In this work, we applied survival analysis to cloud-native \acrshort{ml}, developed a method to quickly and efficiently test model parameter choices and evaluated them in the presence of adversarial noise, allowing one to the model performance as a function of tested model parameters.
 Using this technique, it is clear that reduced run-times with newer and/or larger hardware, that adversarial robustness is not substantially effected and that the specific choice of attack parameters is far more important than model training time.
 
-\cm{The experiments conducted confirm that this methodology is both sound and cost-effective.
+The experiments conducted confirm that this methodology is both sound and cost-effective.
 While 88\% of the cloud budget went to GPU rentals, the data show how cutting that cost by 75\% and using less power-intensive hardware designed for 8-bit image processing would be \textit{more} effective than using the 32-bit datacenter \acrshort{gpu}s (V100 and P100) for typical image classification tasks.
 Using \acrshort{kepler} proved to be a cost-effective as real-time monitoring only used a fraction of the budget (6\%).
-Figure~\ref{fig:acc} confirms the efficacy of the~\acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing a infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
-Additionally, Table~\ref{tab:aft_results} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants.
-By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}, it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
-This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.}
+Figure~\ref{fig:acc} confirms the efficacy of the \acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing an infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
+Additionally, Table~\ref{tab:combined} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants. 
+By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figures~\ref{fig:time}-~\ref{fig:cost}), it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
+This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.
 
-\cm{
 Regardless of which AFT model is chosen, the model suggests that the P100 decreases the survival time compared to the V100 and the L4 increases the survival time (both compared to the V100, which has no significant effect).
-Furthermore, the coefficients again confirm an inverse relationship between test-set (benign) accuracy and the adversarial robustness (\textit{i.e.} survival time).
-Finally, even when we account for the reduced GPU bandwidth (see: Table~\ref{tab:hardware}) and increased training time (see: Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see: Figure~\ref{fig:trash}), despite it being advertised as ``inference only'' by the manufacturer.
-}
+Furthermore, the coefficients again confirm an inverse relationship between test set (benign) accuracy and the adversarial robustness (\textit{i.e.}, survival time). 
+Finally, even when we account for the reduced GPU bandwidth (see Table~\ref{tab:hardware}) and increased training time (see Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see Figure~\ref{fig:trash}), despite it being advertised as ``inference only" by the manufacturer.
 Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.
@@
 \section{Availability of Data and Materials}
-The source code for conducting the experiments is available \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{in the \texttt{deckard} repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
+The source code for conducting the experiments is available in the \texttt{deckard} \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{ repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
 Requirements and dependencies are listed within the repository, which is distributed under the GNU Public License version 3.

### 2024-09-11 plots/cifar/aft_comparison.tex

@@
 \midrule
-Weibull & -5.18e+03 & -5.19e+03 & 0.85 & 0.86 & 0 & 0 & 0 & 0 \\
-Cox & -- & -- & 0.85 & 0.86 & 0.02 & 0.02 & 0 & 0 \\
-Log Logistic & -5.42e+03 & -5.43e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -5.57e+03 & -5.58e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
+Weibull & -8.7e+03 & -8.7e+03 & 0.83 & 0.84 & 0 & 0 & 0 & 0 \\
+Cox & -- & -- & 0.83 & 0.84 & 0.02 & 0.02 & 0 & 0 \\
+Log Logistic & -9.18e+03 & -9.18e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -9.43e+03 & -9.43e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-09-11 plots/combined/aft_comparison.tex
++plots
linting

--- 2024-05-20 plots/combined/aft_comparison.tex
@@
 \centering
-\caption{Comparison of AFR Models on the combined dataset.}
+\caption{Comparison of AFT Models on the combined dataset.}
 \label{tab:combined}
-\begin{tabular}{lrrrrrrrr}
+\begin{tabular}{lllrrrrrr}
 \toprule
@@
 \midrule
-Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
-Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
+Weibull & -1.87e+04 & -1.87e+04 & 0.85 & 0.84 & 0 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.85 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
+Log Logistic & -1.9e+04 & -1.9e+04 & 0.85 & 0.84 & 0.02 & 0.01 & 0 & 0 \\
+Log Normal & -1.98e+04 & -1.98e+04 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-09-11 plots/mnist/aft_comparison.tex

--- 2024-08-20 plots/mnist/aft_comparison.tex
@@
 \midrule
-Weibull & -6.51e+03 & -6.51e+03 & 0.9 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
-Cox & -- & -- & 0.9 & 0.9 & 0.04 & 0.04 & 0 & 0 \\
-Log Logistic & -6.48e+03 & -6.48e+03 & 0.91 & 0.9 & 0.03 & 0.04 & 0 & 0 \\
-Log Normal & -6.63e+03 & -6.63e+03 & 0.91 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Weibull & -1.05e+04 & -1.05e+04 & 0.89 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
+Cox & -- & -- & 0.89 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Log Logistic & -1.07e+04 & -1.07e+04 & 0.89 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
+Log Normal & -1.09e+04 & -1.09e+04 & 0.89 & 0.9 & 0.02 & 0.02 & 0 & 0 \\
 \bottomrule

### 2024-09-11 main.tex

@@
 Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0.
-These nodes were of the ``e2-medium" instance type provided by GCP.
-In total, three GPU architectures were used--the Nvidia P100, V100, and L4.
+These nodes were of the ``e2-medium'' instance type provided by GCP\@.
+In total, three GPU architectures were used--the Nvidia P100, V100, and L4\@.
 For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.
@@
 Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
-To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1]$.
+To evaluate the effect of adversarial noise on the samples, the noise levels were varied $0 < \varepsilon  \leq 0$.
 This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.

### 2024-09-11 plots/cifar100/aft_comparison.tex

@@
 \midrule
-Weibull & -4.39e+03 & -4.4e+03 & 0.81 & 0.8 & 0 & 0 & 0 & 0 \\
-Cox & -- & -- & 0.81 & 0.79 & 0.01 & 0.01 & 0 & 0 \\
-Log Logistic & -4.72e+03 & -4.73e+03 & 0.82 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -4.88e+03 & -4.88e+03 & 0.82 & 0.8 & 0 & 0.01 & 0 & 0 \\
+Weibull & -3.65e+03 & -3.65e+03 & 0.79 & 0.79 & 0.01 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.78 & 0.78 & 0.03 & 0.04 & 0.02 & 0.02 \\
+Log Logistic & -3.95e+03 & -3.95e+03 & 0.8 & 0.8 & 0.03 & 0.02 & 0.01 & 0.01 \\
+Log Normal & -4.29e+03 & -4.29e+03 & 0.79 & 0.8 & 0.02 & 0.02 & 0.01 & 0.01 \\
 \bottomrule

### 2024-09-11 cover_letter.tex
Updates from Overleaf

@@
 
-\signature{Charles Meyers, \\ Mohammed Reza, \\ Tommy L\"{o}fstedt, \\ and  Erik Elmroth \\ }
-\address{Department of \\ Computing Science,\\ Ume\aa University,\\ Sweden}
+\signature{Charles Meyers}
+\address{Department of \\ Computing Science,\\ Ume\aa{}~University,\\ Sweden}
 
@@
 \begin{letter}{}
-\opening{To whom it may concern}
+\opening{Dear Editors,}
 
-I am writing you on behalf of the authors of \em{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}, which is the attached manuscript.
+I am writing you on behalf of the authors of \textit{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}, which is the attached manuscript.
 In this work, we developed a cloud-native methodology for quickly and precisely modelling the effect of model covariates using accelerated failure time models and a multi-objective search to minimize training cost while maximizing model accuracy.
 Not only do we provide a detailed outline and related source code, but we show the surprising result that smaller, more power-efficient GPUs create models that are more robust and more cost effective than models built on hardware that is advertised as being more capable.
-\closing{Sincerely,}
+
+% You can add something about why we submit to this journal (showing that we are in scope and that we think highly of the journal) and that we look forward to a swift processing of the manuscript.)
+
+\closing{On behalf of the authors, sincerely,}
 \end{letter}

### 2024-09-11 main.tex
Updates from Overleaf

--- 2024-09-11 main.tex
@@
 
-\author[1]{\fnm{Mohammad} \sur{Reza Saleh Sedghpour}}\email{msaleh@cs.umu.se}
+\author[2]{\fnm{Mohammad} \sur{Reza Saleh Sedghpour}}\email{mohammad.saleh@elastisys.com}
 
@@
 
-\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa ~University},
-\city{Ume\aa}, \postcode{901 87}, \country{Sweden}}
+\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa{} University},
+\city{Ume\aa{}}, \postcode{901 87}, \country{Sweden}}
 
@@
 \begin{itemize}
-    \item Optimises for benign and adversarial accuracy simultaneously,
+    \item Optimises for benign and adversarial accuracy simultaneously.
     % \item Extends survival analysis to the realm of neural networks, 
-    \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyperparameters, and
+    \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyperparameters.
     \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
@@
 
+\subsection{Availability of Data and Materials}
+The source code for conducting the experiments is available in the \texttt{deckard} \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{ repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
+Requirements and dependencies are listed within the repository, which is distributed under the GNU Public License version 3.
+The compiled data and the Python source code for this document are available \href{https://github.com/simplymathematics/kepler-ml}{here}.
+The source code has been tested on Windows and various Linux distributions and should work on MacOS, but has not been tested there.
+
 \section{Results and Discussion}
@@
 
-% no keywords
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\clearpage
-\section{Availability of Data and Materials}
-The source code for conducting the experiments is available in the \texttt{deckard} \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{ repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
-Requirements and dependencies are listed within the repository, which is distributed under the GNU Public License version 3.
-The compiled data and the Python source code for this document are available \href{https://github.com/simplymathematics/kepler-ml}{here}.
-The source code has been tested on Windows and various Linux distributions and should work on MacOS, but has not been tested there.
+% \clearpage
+
 \printglossary
-\clearpage
+% \clearpage
 \bibliography{sn-bibliography}

### 2024-09-11 main.tex
hyperparameter --> hyper-parmater

--- 2024-09-11 main.tex
@@
     % \item Extends survival analysis to the realm of neural networks,
-    \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyperparameters, and
+    \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyper-parameters, and
     \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
@@
 \label{ml_pipelines}
-ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters. 
+ML pipelines are often long-running and complex software tool-chains with many tunable hyper-parameters. 
 Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}. 

### 2024-09-11 main.tex
changed the name of aft table

@@
 These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}
-\label{tab:combined}
+\label{tab:aft_summary}
 \begin{tabular}{lrrrrrrrr}
@@
 For test-set accuracy,  meeting the weakest safety-critical IEC standard (one failure in a million) would require many millions of samples to confidently conclude that a model is safe.
-However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:combined}).
+However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:aft_summary}).
 Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in \acrshort{ml} applications.
@@
 Figure~\ref{fig:acc} confirms the efficacy of the \acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing an infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
-Additionally, Table~\ref{tab:combined} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants. 
+Additionally, Table~\ref{tab:aft_summary} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants.
 By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figures~\ref{fig:time}-~\ref{fig:cost}), it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).

### 2024-09-11 main.tex
fix quotes

@@
 
-\author[1]{\fnm{Tommy} \sur{L\"{o}fstedt}}\email{tommy@cs.umu.se}
+\author[1]{\fnm{Tommy} \sur{L\''{o}fstedt}}\email{tommy@cs.umu.se}
 
@@
     \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
-    \item Demonstrates that, even when we separately measure the effect of the slower clock speed of "inference only hardware" compared to hardware tailored for training, that models trained using the "inference only" devices are more robust for image classification tasks than models built on hardware designed for training.
+    \item Demonstrates that, even when we separately measure the effect of the slower clock speed of ``inference only hardware'' compared to hardware tailored for training, that models trained using the ``inference only'' devices are more robust for image classification tasks than models built on hardware designed for training.
 \end{itemize}
@@
     \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models.
-Here, "Random State" is used as a control variable that should be (and is) close to 0.
+Here, ``Random Stat'' is used as a control variable that should be (and is) close to 0.
 A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
@@
 As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
-If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
+If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken'' in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
 Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time.
@@
 Furthermore, the coefficients again confirm an inverse relationship between test set (benign) accuracy and the adversarial robustness (\textit{i.e.}, survival time).
-Finally, even when we account for the reduced GPU bandwidth (see Table~\ref{tab:hardware}) and increased training time (see Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see Figure~\ref{fig:trash}), despite it being advertised as ``inference only" by the manufacturer.
+Finally, even when we account for the reduced GPU bandwidth (see Table~\ref{tab:hardware}) and increased training time (see Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see Figure~\ref{fig:trash}), despite it being advertised as ``inference only'' by the manufacturer.
 Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.

### 2024-09-11 main.tex
fix sentences that end with acroynm

@@
 \caption{Comparison of AFT Models across all hardware and datasets.
-\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred.
+\acrshort{aic}~and~\acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred.
 Concordance (Conc) is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model.
@@
 Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time.
-It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.
+It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR\@.
 

### 2024-09-11 main.tex
remove double space

@@
 The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
-Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.
+Since different hardware devices have differing amounts of \acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.
 To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.

### 2024-09-11 main.tex
change 50136 to \[\]$

@@
 where $\phi_\theta$ is the acceleration factor, described by the joint effect of the covariates, such that
-$$
+\[
     \phi_{\theta}(x) = \exp{ \left( \theta_{0} x_{0} + \theta_{1} x_{1} + \cdots + \theta_{n} x_{n} \right) },
-$$
+\]
 and where $x=(x_0, \ldots, x_n)$ is a vector of covariates and $\theta=(\theta_0, \ldots, \theta_n)$ describe the fitted parameters, and  $\varepsilon$ is used as one of the covariates.

### 2024-09-11 main.tex
fix spacing after periods
add line breaks
fix quotes

@@
     The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.
-    The other node pools each had one node with a specific GPU.  The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.
+    The other node pools each had one node with a specific GPU\@.
+    The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.
     All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC).

### 2024-09-11 main.tex
fix quotes

@@
 
-\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa ~University},
+\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa{}~University},
 \city{Ume\aa}, \postcode{901 87}, \country{Sweden}}
@@
 \centering
-\caption{Comparison of AFT Models across all hardware and datasets.
+\caption{
+    Comparison of AFT Models across all hardware and datasets. 
     \acrshort{aic}~and~\acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred. 

### 2024-09-11 arxiv.py
linting

@@ -94,16 +94,14 @@ def flatten_directories(directories):
             logger.info(directory + ' does not exist.')
             logger.info('Current working directory: ' + os.getcwd())
             logger.info('Contents of current working directory: ' + str(os.listdir()))
-            input('Press enter to continue.')
-            exit()
         else:
             logger.info('Flattening ' + directory + ' directory.')
-        for filename in os.listdir(directory):
-            if os.path.isfile(os.path.join(directory, filename)):
-                new_name = str(Path(Path(directory).parent, Path(directory).name + '_' + filename).resolve())
-                shutil.copy(os.path.join(directory, filename), new_name)
-            else:
-                logger.info(filename + ' is a directory.')
+            for filename in os.listdir(directory):
+                if os.path.isfile(os.path.join(directory, filename)):
+                    new_name = str(Path(Path(directory).parent, Path(directory).name + '_' + filename).resolve())
+                    shutil.copy(os.path.join(directory, filename), new_name)
+                else:
+                    logger.info(filename + ' is a directory.')
 
 
 def replace_contents(directories, tex_files):

### 2024-09-11 main.tex
trailing ws
submission to journal of cloud computing

@@
 %%%%
-
+\renewcommand{\glossarysection}[2][]{}
 %%%%%=============================================================================%%%%
@@
 \subsection{Motivation}
-% \begin{itemize}
-%     % \item \textit{BIG} Data is the trend
-%     % \item Costs are astronomical
-%     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
-%     \item Other work relies on unreliable test/train split methodology
-%     \item Which means that cars, medical equipment is tested in the wild
-% \end{itemize}
-
 Recently, \acrfull{ml} using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
@@
     \item Optimises for benign and adversarial accuracy simultaneously,
-    % \item Extends survival analysis to the realm of neural networks,
     \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyper-parameters, and
@@
 
-% Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying ML models under varying computational and adversarial constraints.
 \subsection{Cloud Architectures}
@@
 Because of the complexity of modern \acrshort{ml} models, researchers rely on numerical optimisation, and one popular choice of optimisation algorithm is \textit{stochastic gradient descent}, which updates the model parameters by taking a step in the negative gradient direction, where the gradient is computed using a subset (a mini-batch) of the training samples instead of all training samples.
-% selects the next $N$ samples from the training set before adjusting the model parameters, $\theta$, in the direction that decreases the loss.
-% This is in the direction of the negative gradient of the loss, $-\nabla L(y, K(x, \theta))$.
 This procedure is repeated for some number of \textit{epochs} (iterations through the entire training set). Every iteration takes a step,
@@
 We precisely outline the methodology for using survival analysis during the training of \acrshort{ml} methods.
-% First, we present the proposed procedure in Algorithm~\ref{fig:alg} and a visual diagram of it in Figure~\ref{fig:experiments}.
-Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}).
-We then discuss the importance of the ``acceleration assumption'' (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).
-
-% \begin{algorithm}[tph!]
-%     \caption{Survival Analysis for ML}
-%     \label{fig:alg}
-% \begin{algorithmic}
-%     \Require Samples $x$ of size $N$, model parameters $\theta$, loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and the number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, \textit{e.g.}, $N_t$ is size of the training set.
-%     \State Initialize classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
-%     \State $i = 0$
-%     \While{ $i < n$}
-%     \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
-%     \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
-%     \State  $T_t[i] \gets$ Training Time.
-%     \State  $ \hat{y_i} = K(x_i, \theta) $.
-%     \State  $ T_i[i] \gets $  Inference Time.
-%     \State  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
-%     \State find $x_a$ with Eq.~\ref{eq:fgm}.
-%     \State  $T_a[i] \gets$ attack generation time.
-%     \State  $ \hat{y}_a = K(x_a, \theta) $.
-%     \State  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
-%     \EndWhile
-%     \State $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ \\
-%     % used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
-%     \Return $S_{\theta}$
-% \end{algorithmic}
-% \end{algorithm}
 
@@
 
-Table~\ref{tab:aft_results} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
+Table~\ref{tab:aft_summary} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}.
 A total 75\% of the available data were used to build the AFT models and 25\% were withheld for evaluation.
@@
 Figure~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFT models.
-For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}, and average test error of 1\% \acrshort{ici} and 0 error for the median sample \acrshort{e50}.
+All three models have strong predictive power (see Table:~\ref{tab:aft_summary}), with an average test error of around 1\% \acrshort{ici} and a similar error for the median sample \acrshort{e50}.
 We also see that these metrics are  functionally identical across all AFT models as well as between the test and train set of each model.
@@
 Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
-However, given the strong results and uniformity across AFT functions in Table~\ref{tab:aft_results}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
+However, given the strong results and uniformity across AFT functions in Table~\ref{tab:aft_summary}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
 Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
@@
 Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.
+% Prepared according to:
+% https://journalofcloudcomputing.springeropen.com/submission-guidelines/preparing-your-manuscript/research-article
+\subsection{List of Abbreviations}
+\printglossary[title={}]
 
-% no keywords
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\clearpage
-\section{Availability of Data and Materials}
-The source code for conducting the experiments is available in the \texttt{deckard} \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{ repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
+% \section{Declarations}
+
+% \subsection{Availability of Data and Materials}
+% The source code for conducting the experiments is available in the \texttt{deckard} git repository located at \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{https://github.com/simplymathematics/deckard/tree/main/examples/power}.
+% The pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
 Requirements and dependencies are listed within the repository, which is distributed under the GNU Public License version 3.
@@
 The source code has been tested on Windows and various Linux distributions and should work on MacOS, but has not been tested there.
-\printglossary
-\clearpage
+
+% \subsection{Competing Interests}
+% The authors have no conflict of interest regarding the content of this work.
+
+% \subsection{Funding}
+% Financial support has been provided in part by the Knut and Alice Wallenberg Foundation grant number 2019.0352 and by the eSSENCE Programme under the Swedish Government's Strategic Research Initiative.
+
+% \subsection{Author's Contributions}
+% CM wrote most of the manuscript, except the portions focused on cloud architectures, which were authored by MRSS.
+The math sections were clarified and edited by TL.
+CM prepared all figures.
+Source code was mostly written by CM, except the cloud architecture components, which were written by MRSS.
+EE provided guidance on narrative, pedagogy, and clarity.
+All authors reviewed the manuscript.
+% \subsection{Acknowledgements}
+
 \bibliography{sn-bibliography}
-
 \end{document}

### 2024-09-11 cover_letter.tex
letter update

@@
 Not only do we provide a detailed outline and related source code, but we show the surprising result that smaller, more power-efficient GPUs create models that are more robust and more cost effective than models built on hardware that is advertised as being more capable.
-
-% You can add something about why we submit to this journal (showing that we are in scope and that we think highly of the journal) and that we look forward to a swift processing of the manuscript.)
+We targeted your venue not only because of its open-access policies, but because we feel that the problems of deploying and verifying neural networks can be abstracted away from the expertise required for their operation.
+That is to say, this technique and this text were developed and written for cloud-focused system administrators and computer scientists, not machine learning specialists and mathematicians.
+Finally, we think that the surprising result is worth communicating to this audience in particular since our results show how to significantly reduce infrastructure costs and power requirements for image classification systems without sacrificing quality.
 

### 2024-09-11 plots/cifar/aft_comparison.tex
update plots

@@
 \midrule
-Weibull & -8.7e+03 & -8.7e+03 & 0.83 & 0.84 & 0 & 0 & 0 & 0 \\
-Cox & -- & -- & 0.83 & 0.84 & 0.02 & 0.02 & 0 & 0 \\
-Log Logistic & -9.18e+03 & -9.18e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -9.43e+03 & -9.43e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
+Weibull & -5.18e+03 & -5.19e+03 & 0.85 & 0.86 & 0 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.85 & 0.86 & 0.02 & 0.02 & 0 & 0 \\
+Log Logistic & -5.42e+03 & -5.43e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
+Log Normal & -5.57e+03 & -5.58e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
 \bottomrule

### 2024-09-11 plots/cifar100/aft_comparison.tex
update plots

--- 2024-08-23 plots/cifar100/aft_comparison.tex
@@
 \midrule
-Weibull & -4.39e+03 & -4.4e+03 & 0.81 & 0.8 & 0 & 0 & 0 & 0 \\
-Cox & -- & -- & 0.81 & 0.79 & 0.01 & 0.01 & 0 & 0 \\
-Log Logistic & -4.72e+03 & -4.73e+03 & 0.82 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
-Log Normal & -4.88e+03 & -4.88e+03 & 0.82 & 0.8 & 0 & 0.01 & 0 & 0 \\
+Weibull & -1.79e+03 & -1.8e+03 & 0.81 & 0.81 & 0.01 & 0.01 & 0 & 0 \\
+Cox & -- & -- & 0.8 & 0.81 & 0.03 & 0.02 & 0.02 & 0.01 \\
+Log Logistic & -1.92e+03 & -1.93e+03 & 0.82 & 0.82 & 0.02 & 0.01 & 0.01 & 0 \\
+Log Normal & -2.11e+03 & -2.12e+03 & 0.82 & 0.81 & 0.01 & 0.01 & 0.01 & 0 \\
 \bottomrule

### 2024-09-11 plots/mnist/aft_comparison.tex
update plots

--- 2024-08-23 plots/mnist/aft_comparison.tex
@@
 \midrule
-Weibull & -6.47e+03 & -6.48e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
+Weibull & -6.46e+03 & -6.47e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
 Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
-Log Logistic & -6.48e+03 & -6.49e+03 & 0.91 & 0.91 & 0.04 & 0.04 & 0 & 0 \\
-Log Normal & -6.62e+03 & -6.63e+03 & 0.9 & 0.91 & 0.03 & 0.03 & 0 & 0 \\
+Log Logistic & -6.47e+03 & -6.48e+03 & 0.91 & 0.91 & 0.04 & 0.04 & 0 & 0 \\
+Log Normal & -6.61e+03 & -6.62e+03 & 0.9 & 0.91 & 0.03 & 0.03 & 0 & 0 \\
 \bottomrule

### 2024-09-11 arxiv.py
update pipeline

@@ -60,27 +60,38 @@ def delete_files_with_extension(extension):
         logger.info(f'{filename} not in use - deleting.')
         os.remove(filename)
 
+def delete_these_directories(directories):
+    logger.info(f'Deleting these directories: {directories}')
+    for dir in directories:
+        shutil.rmtree(dir)
+
+def delete_these_files(files = []):
+    logger.info(f'Deleting these files:{files}')
+    if files is None:
+        files = []
+    for file in files:
+        os.remove(file)
 
 def delete_image_directories(directories):
     logger.info('Deleting image directories')
     for directory in directories:
         if Path(directory).exists():
-            logger.info('Removing ' + directory + ' directory.')
+            logger.info(f'Removing {directory} directory.')
             shutil.rmtree(directory)
 
 
 def zip_tmp_directory(title, tmp_directory):
-    logger.info('Zipping temporary directory: ' + tmp_directory)
+    logger.info(f'Zipping temporary directory: {tmp_directory}')
     shutil.make_archive(f"{title}", 'zip', tmp_directory)
 
 
 def delete_tmp_directory_final(tmp_directory):
-    logger.info('Deleting temporary directory: ' + tmp_directory)
+    logger.info(f'Deleting temporary directory: {tmp_directory}')
     shutil.rmtree(tmp_directory)
 
 
 def delete_tmp_directory(tmp_directory):
-    logger.info('Deleting temporary directory: ' + tmp_directory)
+    logger.info(f"Deleting temporary directory: {tmp_directory}")
     if Path(tmp_directory).exists():
         shutil.rmtree(tmp_directory)
     else:
@@ -91,30 +102,33 @@ def flatten_directories(directories):
     logger.info('Flattening directories')
     for directory in directories:
         if not Path(directory).exists():
-            logger.info(directory + ' does not exist.')
-            logger.info('Current working directory: ' + os.getcwd())
-            logger.info('Contents of current working directory: ' + str(os.listdir()))
+            logger.error(directory + ' does not exist.')
+            exit()
         else:
             logger.info('Flattening ' + directory + ' directory.')
-            for filename in os.listdir(directory):
-                if os.path.isfile(os.path.join(directory, filename)):
-                    new_name = str(Path(Path(directory).parent, Path(directory).name + '_' + filename).resolve())
-                    shutil.copy(os.path.join(directory, filename), new_name)
-                else:
[…]

### 2024-09-11 combined_plots.py

@@ -1,267 +1,0 @@
-import pandas as pd
-from pathlib import Path
-import seaborn as sns
-import matplotlib.pyplot as plt
-from deckard.layers.plots import set_matplotlib_vars
-
-set_matplotlib_vars()
-
-
-sns.set_theme(style="whitegrid", font_scale=1.2, font="times new roman")
-
-normal_dir = "data"
-datasets = ["mnist", "cifar", "cifar100"]
-extra_data_dir = "bit_depth"
-
-#
-big_df = pd.DataFrame()
-for data in datasets:
-    df = pd.read_csv(
-        Path(normal_dir) / data / "power.csv",
-        index_col=0,
-        low_memory=False,
-    )
-    df["dataset"] = data
-    big_df = pd.concat([big_df, df], axis=0)
-    if Path(normal_dir, extra_data_dir, data, "power.csv").exists():
-        extra_df = pd.read_csv(
-            Path(normal_dir, extra_data_dir, data, "power.csv"),
-            index_col=0,
-            low_memory=False,
-        )
-        extra_df["dataset"] = data
-        big_df = pd.concat([big_df, extra_df], axis=0)
-
-
-# Device Metadata
-memory_bandwith = {
-    "nvidia-tesla-p100": 732,
-    "nvidia-tesla-v100": 900,
-    "nvidia-l4": 250,
-}
-dataset_resolution = {
-    "mnist": 28,
-    "cifar": 32,
-    "cifar100": 32,
-}
-dataset_channels = {
-    "mnist": 1,
-    "cifar": 3,
-    "cifar100": 3,
-}
-dataset_classes = {
-    "mnist": 10,
-    "cifar": 10,
-    "cifar100": 100,
-}
-cost = {
-    "nvidia-tesla-p100": 1.60,
-    "nvidia-tesla-v100": 2.55,
-    "nvidia-l4": 0.81,
-}
-epochs = "model.trainer.nb_epoch"
-batch_size = "model.trainer.batch_size"
-bit_depth = "model.art.preprocessor.bit_depth"
-resolution = "n_pixels"
-
-# Add Metadata
-for device in big_df.device_id.unique():
-    big_df.loc[big_df.device_id == device, "peak_memory_bandwidth"] = float(
-        memory_bandwith[device],
-    )
-    big_df.loc[big_df.device_id == device, "cost"] = float(cost[device])
[…]

### 2024-09-11 main.tex
added elastisys to mohammad

@@
 
-\author[1]{\fnm{Mohammad} \sur{Reza Saleh Sedghpour}}\email{msaleh@cs.umu.se}
+\author[2,1]{\fnm{Mohammad} \sur{Reza Saleh Sedghpour}}\email{msaleh@cs.umu.se}
 
@@
 Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model at run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
-Additionally, testing model changes likely means deploying the models to \textit{e.g.}, a car, a medical imaging device, or a drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
+Additionally, testing model changes likely means deploying the models to (\textit{e.g.} a car or a medical imaging device), or a drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
 In this work, we used survival analysis as a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.

### 2025-05-17 main.tex
removed commented stuff
Updates from Overleaf

@@
 \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
-\input{glossary}
+\newacronym{aft}{AFT}{Accelerated Failure Time}
+\newacronym{cpu}{CPU}{central processing unit}
+\newacronym{e50}{E50}{error at 50th percentile}
+\newacronym{fgm}{FGM}{Fast Gradient Method}
+\newacronym{aic}{AIC}{Akaike Information Criterion}
+\newacronym{gcp}{GCP}{Google Cloud Platform}
+\newacronym{gpu}{GPU}{graphics processing unit}
+\newacronym{ici}{ICI}{integrated calibration index}
+\newacronym{bic}{BIC}{Bayesian Information Criteria}
+\newacronym{trash}{TRASH}{training rate and survival heuristic}
+\newglossaryentry{kepler}
+{
+name=KEPLER,
+description={Kubernetes Efficient Power Level Exporter}
+}
+\newacronym{ml}{ML}{machine learning}
+\newacronym{tpe}{TPE}{Tree-structured Parzen Estimator}
+\newacronym{vram}{VRAM}{video random access memory}
+
 \makeglossaries
+
 %Version 3 October 2023
@@
 \begin{document}
-
+\pagenumbering{gobble}
 \title[Article Title]{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}
@@
 
-\author[1]{\fnm{Tommy} \sur{L\''{o}fstedt}}\email{tommy@cs.umu.se}
+\author[1,2]{\fnm{Erik} \sur{Elmroth}}\email{elmroth@cs.umu.se}
 
-\author[1,2]{\fnm{Erik} \sur{Elmroth}}\email{elmroth@cs.umu.se}
+% \pagestyle{empty}
+\author[1]{\fnm{Tommy} \sur{L\"{o}fstedt}}\email{tommy@cs.umu.se}
 
@@
     \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models.
-Here, ``Random Stat'' is used as a control variable that should be (and is) close to 0.
+Here, ``Random State'' is used as a control variable that should be (and is) close to 0.
 A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time.
@@
 % https://journalofcloudcomputing.springeropen.com/submission-guidelines/preparing-your-manuscript/research-article
+\pagebreak
 \subsection{List of Abbreviations}
@@
 
-% \section{Declarations}
+\section{Declarations}
 
+\subsection{Ethics Approval and Consent to Participate}
+Not Applicable
+
+\subsection{Consent for Publication}
+All authors consent for this manuscript to be published under the terms specified by the \textit{Journal of Cloud Computing}.
+
+\subsection{Funding}
+Financial support has been provided in part by the Knut and Alice Wallenberg Foundation grant number 2019.0352 and by the eSSENCE Programme under the Swedish Government's Strategic Research Initiative.
+
+\subsection{Acknowledgements}
+Not Applicable
+% \subsection{Competing Interests}
+% The authors have no conflict of interest regarding the content of this work.
 % \subsection{Availability of Data and Materials}
-% The source code for conducting the experiments is available in the \texttt{deckard} git repository located at \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{https://github.com/simplymathematics/deckard/tree/main/examples/power}.
+% The source code for conducting the experiments is available in the \texttt{deckard} git repository located \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{here}.
 % The pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments.
@@
 The source code has been tested on Windows and various Linux distributions and should work on MacOS, but has not been tested there.
-
-% \subsection{Competing Interests}
-% The authors have no conflict of interest regarding the content of this work.
-
-% \subsection{Funding}
-% Financial support has been provided in part by the Knut and Alice Wallenberg Foundation grant number 2019.0352 and by the eSSENCE Programme under the Swedish Government's Strategic Research Initiative.
-
 % \subsection{Author's Contributions}
@@
 All authors reviewed the manuscript.
-% \subsection{Acknowledgements}
 
